### 2016-03-07 doc/paper.tex
Paper beginnings!

%% bare_conf.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference]{IEEEtran}

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{The Protracted and Generally Unpleasant Death\\ of Justin A. Middleton\\ \large A Methodological Obituary}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Justin A. Middleton (posthumous)}
\IEEEauthorblockA{North Carolina State University\\
Raleigh, North Carolina\\
(Please address all flowers and review notes to cemetery lot 126, grave 2)}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Finding information on how people use built-in Excel functions individually is easy; how they're used together is not. With no analysis of functions in conjunction, a dearth on information about how end users construct more sophisticated programs within spreadsheets restricts current research. I've developed a visualization tool, informed by existing spreadsheet corpora, which offers insight into the patterns of how formulas comprise several functions in practice. Even in its initial state, the tool illustrates how some people think that have 27 arguments in a single SUM function is, for whatever reason, a good idea.
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart
The world of business owes a considerable debt to spreadsheets, the table-based interface which enables organization and manipulation of massive amounts of data. Their allure is in their versatility: while the end user does not need sophisticated programming skills to fill out a spreadsheet, the expert user has at their disposal numerous built-in operations, or functions, to expedite their work. As such, it should be of little surprise when Scaffidi and colleagues estimated that by 2012, over 50 million workers could be using them, including the 25 million who would be writing programs out of the functions included (citation and such).\par

Considering this ubiquity, it's crucial to get spreadsheets right. Something, something. \par

Fortunately, the vanguards of spreadsheet research have assembled, organized, and released a number of spreadsheet corpora to inform work on how people actually use these tools in different contexts. Collections like EUSES[yada], FUSE[yada], and the Enron corpus[yada] have already enabled fruitful work across the field: [WORK PENDING MORE RESEARCH]. A number of these studies focus on discovering which built-in functions are the most common (enabling something). \par

This paper presents a tool, informed by such variegated sources, that visualizes not how people employ individual Excel functions but how they combine to make more sophisticated shreadsheet formulas.

\section{Related Work}
Spreadsheets, being a core component of business that they are, have prompted the development of many tools to evaluate them and their many qualities. [RESEARCH ON NON-VISUAL ANALYSIS TOOLS] \par
Furthermore, this tool comes from a line of spreadsheet visualization tools before it, each with a different focus. For example, Breviz, developed by Hermans and colleagues, uses visualization to illustrate workbook dataflow to address the need for a clearly communicable representation of spreadsheets as they move from person to person. \par
Other studies focus on API and built-in function use outside the domain of spreadsheets. [BUT FIRST I HAVE TO FIND THEM]

\section{Approach}
In visualizing the spreadsheet data, I aimed to accomplish the following goals:
\begin{itemize}
	\item The data should come from a varied enough sources to avoid having too narrow or specialized a scope.
	\item The tool should accommodate dataset sizes from the single spreadsheet to corpora of thousands.
	\item The tool should visualize as much data as possible in order to capture (and clearly indicate) both the most typical and the most anomalous cases...
	\item ...while being interactive enough to let the user choose which cases they see, as to not sacrifice readability.
	\item The tool should facilitate quantitative understanding by showing which functions and which combinations are used most frequently...
	\item ...and it should facilitate qualitative understanding by incorporating actual examples into the visualization from the datasets it studies, and it should help the user find these examples in their original context.
	\item The tool, by the same method as above, should thus guide a user from the abstract patterns of function usage into the specific and applied techniques of functions in their natural habitat.
\end{itemize} \par
Likewise, there were a few goals that I was specifically not trying to accomplish with this:
\begin{itemize}
	\item The tool should not be, by itself, responsible for generating functions from the data it collects. It is purely analytical.
	%TODO: I do have an idea which could actually do the below, but, eh, it would take
	%TODO: a fair amount of time to implement.
	\item The tool will not visualize isolated Excel functions, linking the specific instance to the abstract pattern. It works only the other way.
	\item Likewise, the tool will make no effort to explain what any given set of functions in combination actually does; the function of any given example is up to the user to infer.
\end{itemize}

\section{Case Study}
The patient exhibits strong cadaverous tendencies.

\section{Conclusion}
This paper is the end-all, be-all. There is no future work simply because the concept of future work cannot exist with reference to this paper. The work is done. I perfected it. Go home, kiss your love, kick back, call it a day. This is not just a good thing, but the best thing. Your job here is done, and I'm the one who did it.

% conference papers do not normally have an appendix

% use section* for acknowledgment
\section*{Acknowledgment}
This material is based upon work supported in whole or in part with funding from the Laboratory for Analytic Sciences (LAS). Any opinions, findings, conclusions, or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the LAS and/or any agency or entity of the United States Government.

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

### 2016-03-07 src/scripts/trees/IFTree.java

@@ -1,0 +1,72 @@
+package scripts.trees;
+
+import java.io.BufferedWriter;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.sql.Connection;
+import java.sql.PreparedStatement;
+import java.sql.ResultSet;
+import java.sql.SQLException;
+
+import com.google.gson.Gson;
+import com.google.gson.GsonBuilder;
+
+import core.FormulaToken;
+import core.FunctionStatsNode;
+import core.Parser;
+import utils.DBUtils;
+
+public class IFTree {
+  public static void main(String[] args) throws SQLException, IOException {
+    int limit = 100000, offset = 0, currentlyAt;
+    Connection con = DBUtils.connectToDatabase();
+    PreparedStatement ps = con.prepareStatement("SELECT * FROM formulas WHERE formula like 'IF%' and ID > ? LIMIT " + limit + ";");
+    
+    FunctionStatsNode sum = null;
+    do {
+      currentlyAt = 0;
+      ps.setInt(1, offset);
+      ResultSet rs = ps.executeQuery();
+      
+      while (rs.next()) {
+        ++currentlyAt;
+        int id = rs.getInt(1);
+        String formula = rs.getString(2);
+        int sheet = rs.getInt(5);
+        
+        FormulaToken tree = null;
+        try {
+          tree = Parser.parseFormula(formula, sheet, Parser.BLANK);
+        } catch (Exception e) {
+          continue;
+        }
+        
+        if (!tree.toSimpleString().equals("IF()"))
+          continue;
+        
+        if (sum == null)
+          sum = new FunctionStatsNode(id, tree);
+        else
+          sum.addChildrenOf(tree);
+        
+        System.out.println(currentlyAt + " : " + formula);        
+      }
+      
+      rs.previous();
+      offset = rs.getInt(1);
+      System.out.println("At " + offset + "...");
+    } while (limit == currentlyAt);
+    
+    sum.sortArgumentsByFrequency();
+    
+    GsonBuilder builder = new GsonBuilder();
+    builder.setPrettyPrinting().serializeNulls().excludeFieldsWithoutExposeAnnotation();
+    Gson gson = builder.create();
+    
+    BufferedWriter write = new BufferedWriter(new FileWriter("./src/viz/iftree.json"));
+    write.write(gson.toJson(sum));
+    System.out.println(gson.toJson(sum));
+    write.close();
+
+  }
+}

### 2016-03-07 src/viz/treeMaker.js

@@ -26,7 +26,13 @@ var scale; //To be determined when when tree chosen.
 var tree = d3.layout.tree()
   //.size([height, width])
   .nodeSize([square_side, square_side])
-  .sort(function(a, b) { return b.frequency - a.frequency; });
+  .sort(function(a, b) {
+    var order = b.frequency - a.frequency;
+    if (order == 0)
+      if (a.function) order = a.function.localeCompare(b.function);
+      else order = a.position - b.position;
+    return order;
+  });
 
 var zoomer = d3.behavior.zoom()
   .scaleExtent([.5, 8])
@@ -44,6 +50,11 @@ var svg = d3.select("body")
   .on("dblclick.zoom", null)
   .attr("transform", "translate(" + view_start_x + "," + view_start_y + ")")
   .append("g");
+
+var div = d3.select("body")
+  .append("svg")
+  .attr("class", "tooltip")
+  .style("display", "none");
 
 var lines = d3.svg.line()
   .x(function(d) { return d.ly; })
@@ -136,7 +147,9 @@ function enterNode(node, src) {
 function enterCircle(circles, src) {
   circles.append("circle")
     .attr("r", 1e-6)
-    .style("fill", function(d) { return d._children ? "#4C7B61" : "white"; });
+    .style("fill", function(d) { return d._children ? "#4C7B61" : "white"; })
+    .on("mouseover", mouseover)
+    .on("mouseleave", mouseleave);
 
   circles.append("text")
     .attr("dx", function(d) { return d.children || d._children ? -15 : 10; })
@@ -144,6 +157,18 @@ function enterCircle(circles, src) {
     .attr("text-anchor", function(d) {
       return d.children || d._children ? "end" : "start";
     }).text(function(d) { return d.function; })
+}
+
+function mouseover(d) {
+  console.log("show! " + d.x0 + " " + d.y0)//d3.event.pageX + " " + d3.event.pageY);
+  div.text("Test!")
+    .style("left", d.x + "px")
+    .style("top", d.y + "px")
+    .style("display", "inline");
+}
+
+function mouseleave(d) {
+  div.style("display", "none");
 }
 
 function enterRect(rects, src) {

### 2016-03-08 src/core/FunctionArgumentNode.java
Start of day, 8Mar16

@@ -31,9 +31,9 @@ public class FunctionArgumentNode {
     this.position = pos;
   }
   
-  public void add(FormulaToken child) {
+  public void add(int ex, FormulaToken child) {
     increment();
-    possibleArguments_unsorted.put(child.toSimpleString(), new FunctionStatsNode(child));
+    possibleArguments_unsorted.put(child.toSimpleString(), new FunctionStatsNode(ex, child));
   }
 
   public boolean contains(FormulaToken child) {

### 2016-03-08 src/core/FunctionStatsNode.java

@@ -19,8 +19,10 @@ public class FunctionStatsNode implements Comparable<FunctionStatsNode> {
   private FunctionArgumentNode[] children = null;
   
   @Expose
-  private FunctionExample example = null;
+  private int example;
   
+  private int shortestExampleLen;
+    
   /**
    * Represents a certain type of function or primitive type that can appear in a formula. Stores
    * the number of times that this function has been observed here, and it records every type of argument
@@ -35,7 +37,10 @@ public class FunctionStatsNode implements Comparable<FunctionStatsNode> {
    * 
    * @param token The type of formula token that this node wraps.
    */
-  public FunctionStatsNode(FormulaToken token) {
+  public FunctionStatsNode(int ex, FormulaToken token) {
+    this.example = ex;
+    this.shortestExampleLen = token.toString().length();  //TODO: What if reconstructed length different from original?
+    
     function = token.toSimpleString();
     
     increment();    //Construction entails one use.
@@ -43,7 +48,7 @@ public class FunctionStatsNode implements Comparable<FunctionStatsNode> {
     for (int i = 0; i < children.length; ++i) {
       FormulaToken child = children[i];
       FunctionArgumentNode arg = new FunctionArgumentNode(i);
-      arg.add(child);//map.put(child.toSimpleString(), new FunctionStatsNode(child));
+      arg.add(ex, child);//map.put(child.toSimpleString(), new FunctionStatsNode(child));
       arguments_unsorted.put(i, arg);
     }
   }
@@ -51,17 +56,24 @@ public class FunctionStatsNode implements Comparable<FunctionStatsNode> {
   /**
    * Record the occurrence of whatever type of formula element the parameter `token` is, and then
    * recursively record the occurrences of all of `tokens` children further down in the tree.
+   * @param id 
    * @param token   The type of formula token to record, which should be of the same type as this stats node.
    * 
    * Example: If we have the formula IF(A1<A2, SUM(B1:B10), 0), then we want to say we have observed
    * 1 more instance of a formula which has IF() as its uppermost function, and then record that it has
    * the tokens `<`, SUM(), and 0 (<NUM>) one level below that, and so on.
    */
-  public void addChildrenOf(FormulaToken token) {
+  public void addChildrenOf(int id, FormulaToken token) {    
     if (!this.equals(token))
       throw new UnsupportedOperationException("Trying to pass a FormulaToken which does not "
[…]

### 2016-03-08 src/scripts/trees/AllTrees.java

@@ -36,6 +36,7 @@ public class AllTrees {
       
       while (rs.next()) {
         ++currentlyAt;
+        int id = rs.getInt(1);
         String formula = rs.getString(2);
         int sheet = rs.getInt(5);
         
@@ -48,9 +49,9 @@ public class AllTrees {
         
         String toplevel = tree.toSimpleString();
         if (!trees.containsKey(toplevel))
-          trees.put(toplevel, new FunctionStatsNode(tree));
+          trees.put(toplevel, new FunctionStatsNode(id ,tree));
         else
-          trees.get(toplevel).addChildrenOf(tree);
+          trees.get(toplevel).addChildrenOf(id, tree);
         
         //System.out.println(currentlyAt + " : " + formula);        
       }

### 2016-03-08 src/scripts/trees/IFTree.java

@@ -47,7 +47,7 @@ public class IFTree {
         if (sum == null)
           sum = new FunctionStatsNode(id, tree);
         else
-          sum.addChildrenOf(tree);
+          sum.addChildrenOf(id, tree);
         
         System.out.println(currentlyAt + " : " + formula);        
       }

### 2016-03-08 src/scripts/trees/SUMTree.java

@@ -30,6 +30,7 @@ public class SUMTree {
       
       while (rs.next()) {
         ++currentlyAt;
+        int id = rs.getInt(1);
         String formula = rs.getString(2);
         int sheet = rs.getInt(5);
         
@@ -44,9 +45,9 @@ public class SUMTree {
           continue;
         
         if (sum == null)
-          sum = new FunctionStatsNode(tree);
+          sum = new FunctionStatsNode(id, tree);
         else
-          sum.addChildrenOf(tree);
+          sum.addChildrenOf(id, tree);
         
         System.out.println(currentlyAt + " : " + formula);        
       }
@@ -62,7 +63,7 @@ public class SUMTree {
     builder.setPrettyPrinting().serializeNulls().excludeFieldsWithoutExposeAnnotation();
     Gson gson = builder.create();
     
-    BufferedWriter write = new BufferedWriter(new FileWriter("./src/scripts/viz/sumtree.json"));
+    BufferedWriter write = new BufferedWriter(new FileWriter("./src/viz/sumtree.json"));
     write.write(gson.toJson(sum));
     System.out.println(gson.toJson(sum));
     write.close();

### 2016-03-08 src/viz/treeMaker.js

@@ -23,6 +23,9 @@ var margin = {
 
 var scale; //To be determined when when tree chosen.
 
+/**
+ * Create the tree and define it's general behavior.
+ */
 var tree = d3.layout.tree()
   //.size([height, width])
   .nodeSize([square_side, square_side])
@@ -34,6 +37,9 @@ var tree = d3.layout.tree()
     return order;
   });
 
+/**
+ * Define the zooming behavior for the svg element below this.
+ */
 var zoomer = d3.behavior.zoom()
   .scaleExtent([.5, 8])
   .on("zoom", function() {
@@ -41,6 +47,9 @@ var zoomer = d3.behavior.zoom()
       + d3.event.scale + ")")
   })
 
+/**
+ * Create the svg box in which you will see everything.
+ */
 var svg = d3.select("body")
   .append("svg")
   .attr("width", width + margin.left + margin.right)
@@ -51,20 +60,17 @@ var svg = d3.select("body")
   .attr("transform", "translate(" + view_start_x + "," + view_start_y + ")")
   .append("g");
 
-var div = d3.select("body")
-  .append("svg")
-  .attr("class", "tooltip")
-  .style("display", "none");
-
+/**
+ * Create a line generator, into which you must pass two x,y coordinates.
+ */
 var lines = d3.svg.line()
   .x(function(d) { return d.ly; })
   .y(function(d) { return d.lx; })
   .interpolate("linear");
 
-d3.text('examples.php?id=1', function(error, data) {
-  console.log(data);
-})
-
+/**
+ * Initialize the tree with only one level down expanded.
+ */
 var src ="iftree.json"; //If python server started in tree folder
 var root;
 d3.json(src, function(error, json) {
@@ -97,13 +103,15 @@ d3.json(src, function(error, json) {
 d3.select(self.frameElement)
   .style("height", height + "px");
 
+/**
+ * Update the tree after a clicking event.
+ */
 var i = 0;
-
 function update(src) {
   var nodes = tree.nodes(root),
     links = tree.links(nodes);
 
-  nodes.forEach(function(d) { d.y = d.depth * 100; })
+  nodes.forEach(function(d) { d.y = d.depth * 150; })
 
   var node = svg.selectAll("g")
     .data(nodes, function(d) { return d.id || (d.id = ++i); });
@@ -125,6 +133,9 @@ function update(src) {
   });
 }
 
+/**
+ * Creates both circular function nodes and rectangular function argument nodes.
[…]

### 2016-03-08 src/core/FormulaToken.java
Fixed shortest examples.

@@ -13,6 +13,7 @@ import org.apache.poi.ss.formula.ptg.StringPtg;
 public class FormulaToken {
   protected String tokenStr;
   protected Ptg token;
+  private int origLen = Integer.MAX_VALUE;
   
   //TODO: Don't like this blank string possibility, but OperationToken needs a blank super...
   public FormulaToken() {
@@ -84,6 +85,24 @@ public class FormulaToken {
    */
   public FormulaToken[] getChildren() {
     return new FormulaToken[0];
+  }
+  
+  /**
+   * This is to store the length of the original formula turned into tokens. Since the length
+   * can differ between how the parser can reconstruct it and what it was originally, I want
+   * to store the number with this extra step rather than trying to recalculate.
+   * 
+   * Mainly so I can pick out the shortest example from the database to display.
+   * @param origLen   The length in characters of the original formula.
+   */
+  public void setOrigLen(int origLen) {
+    this.origLen = origLen;
+    for (FormulaToken child : getChildren())
+      child.setOrigLen(origLen);
+  }
+  
+  public int getOrigLen() {
+    return origLen;
   }
   
   public String toString() {

### 2016-03-08 src/core/FunctionStatsNode.java

@@ -39,7 +39,7 @@ public class FunctionStatsNode implements Comparable<FunctionStatsNode> {
    */
   public FunctionStatsNode(int ex, FormulaToken token) {
     this.example = ex;
-    this.shortestExampleLen = token.toString().length();  //TODO: What if reconstructed length different from original?
+    this.shortestExampleLen = token.getOrigLen();  //TODO: What if reconstructed length different from original?
     
     function = token.toSimpleString();
     
@@ -69,7 +69,7 @@ public class FunctionStatsNode implements Comparable<FunctionStatsNode> {
           + "refer to the same type of token as the FunctionStatsNode: " + token.toSimpleString() 
           + " vs. " + this.function);
     
-    int otherExampleLen = token.toString().length();
+    int otherExampleLen = token.getOrigLen();
     if (shortestExampleLen > otherExampleLen) {
       example = id;
       shortestExampleLen = otherExampleLen;

### 2016-03-08 src/core/Parser.java

@@ -63,7 +63,9 @@ public class Parser {
     }
     
     FormulaRenderingWorkbook render = (FormulaRenderingWorkbook) parse;
-    return parseFormula(tokens, render);
+    FormulaToken tree = parseFormula(tokens, render);
+    tree.setOrigLen(formula.length());
+    return tree;
   }
   
   /**

### 2016-03-08 src/scripts/trees/IFTree.java

@@ -49,7 +49,7 @@ public class IFTree {
         else
           sum.addChildrenOf(id, tree);
         
-        System.out.println(currentlyAt + " : " + formula);        
+        //System.out.println(currentlyAt + " : " + formula);        
       }
       
       rs.previous();

### 2016-03-08 src/tests/SingleTests.java

@@ -263,6 +263,15 @@ public class SingleTests {
     singleSuccessTest(filename, sheetNum, row, col);
   }
   
+  /**
+   * IF(AND(I676,I722>0),IF(I676-I719<=0,0,IF(I676<I722,I676,I722)),0)
+   */
+  @Test
+  public void test_20_graphmistake1() {
+    String formula = "IF(AND(I676,I722>0),IF(I676-I719<=0,0,IF(I676<I722,I676,I722)),0)";
+    singleSuccessTest(formula);
+  }
+  
   private void singleSuccessTest(String filename, int sheetNum, int row, int col) {
     XSSFWorkbook wb = POIUtils.getWorkbook(filename);
     String formula = getFormulaAt(wb, sheetNum, row, col);
@@ -277,6 +286,11 @@ public class SingleTests {
     XSSFWorkbook wb = POIUtils.getWorkbook(filename);
     XSSFEvaluationWorkbook parse = XSSFEvaluationWorkbook.create(wb);
     String result = Parser.parseFormula(formula, sheetNum, parse).toString();
+    TestUtils.compare(formula, result);
+  }
+  
+  private void singleSuccessTest(String formula) {
+    String result = Parser.parseFormula(formula).toString();
     TestUtils.compare(formula, result);
   }
   

### 2016-03-08 src/viz/treeMaker.js

@@ -167,11 +167,10 @@ function enterCircle(circles, src) {
     .on("mouseleave", mouseleave);
 
   circles.append("text")
-    .attr("dx", function(d) { return d.children || d._children ? -15 : 10; })
+    .attr("dx", -15 )
     .attr("dy", 3)
-    .attr("text-anchor", function(d) {
-      return d.children || d._children ? "end" : "start";
-    }).text(function(d) { return d.function; })
+    .attr("text-anchor", "end")
+    .text(function(d) { return d.function; })
 }
 
 /**
@@ -190,7 +189,8 @@ var tip = d3.select("body")
 var tip_x = 5,
     tip_y = -50;
 function mouseover(d) {
-  var i = "<i>", ii = "</i>",
+  var b = "<b>", bb = "</b>",
+      i = "<i>", ii = "</i>",
       br = "<br/>",
       func = d.function + br,
       freq = d.frequency + br,
@@ -202,14 +202,16 @@ function mouseover(d) {
   d3.json("examples.php?id=" + id, function(error, data) {
     if (error) throw error;
 
-    ex = i + data["formula"] + ii + br;
+    form = data["formula"].replace(/</g, "&lt;").replace(/>/g, "&gt;");
+    ex = b + i + form + ii + bb + br;
     tip.html(func + freq + full + ex)
 
+    console.log(ex);
     //TODO: Changing widths of the tooltip?
     /*var width = $('.tooltip').width();
     console.log(width);
     if (width > 200) {
-      tip.style("width", width + "px");
+      tip.style("width", null);
     }*/
   })
 
@@ -231,7 +233,8 @@ function mousemove(d) {
  * Dismisses the tooltip once the mouse leaves the node.
  */
 function mouseleave(d) {
-  tip.style("display", "none");
+  tip.style("display", "none")
+     .style("width", null);
 }
 
 /**
@@ -248,7 +251,7 @@ function enterRect(rects, src) {
     .style("fill", function(d) { return d._children ? "#627884" : "white"; });
 
   rects.append("text")
-    .text(function(d) { return d.position; })
+    .text(function(d) { return d.position + 1; })
     .attr("dx", function(d) { return d.position > 9 ? -7 : -3; })
     .attr("dy", 5);
 }

### 2016-03-11 src/viz/treeMaker.js
Start of 11March16

@@ -67,11 +67,12 @@ var svg = d3.select("body")
   .append("svg")
   .attr("width", width + margin.left + margin.right)
   .attr("height", height + margin.top + margin.bottom)
-  .append("g")
   .call(zoomer)
   .on("dblclick.zoom", null)
-  .attr("transform", "translate(" + view_start_x + "," + view_start_y + ")")
-  .append("g");
+  .append("g")
+  .attr("transform", "translate(" + view_start_x + "," + view_start_y + ")");
+
+zoomer.translate([view_start_x, view_start_y]);
 
 //gist.github.com/pnavarrc/20950640812489f13246
 var gradient = svg.append("defs")

### 2016-03-11 src/viz/treeMaker.js
Large branches handle. Resolves #10

@@ -19,8 +19,8 @@ var margin = {
   square_side = 20,
   square_side_half = square_side / 2,
 
-  view_start_x = margin.left,
-  view_start_y = height / 2 + margin.top,
+  view_start_x = width / 2,
+  view_start_y = height / 2,
 
   circle_col =    "#4C7B61",
   circle_hover =  "#1D5134",
@@ -129,6 +129,7 @@ d3.json(src, function(error, json) {
   }
 
   root.children.forEach(collapse);
+  center(root);
   update(root);
 })
 
@@ -188,7 +189,8 @@ function enterNode(node, src) {
       }),
       rects = nodeEnter.filter(function(d) { return d.depth % 2 != 0; })
 
-  circles.on("click", click);
+  circles.filter(function(d) { return d.children || d._children; }) //Only click those that have any children.
+    .on("click", click);
   rects.on("click", click)
     .on("mouseover", rect_mouseover)
     .on("mouseleave", rect_mouseout);
@@ -459,6 +461,7 @@ function click(d) {
     d._children = null;
   }
 
+  center(d);
   update(d);
 }
 
@@ -474,5 +477,17 @@ function expandclick(d) {
     par.children.splice(par.children.length, 0, d);
   }
 
+  center(par);
   update(par);
+}
+
+//http://bl.ocks.org/robschmuecker/7880033
+function center(d) {
+  var scale = zoomer.scale(),
+      x = -d.y0 * scale + (width/2),
+      y = -d.x0 * scale + (height/2);
+  d3.select("g").transition().duration(duration)
+    .attr("transform", "translate(" + x + "," + y + ")scale(" + scale + ")");
+  zoomer.scale(scale);
+  zoomer.translate([x, y]);
 }

### 2016-03-12 doc/paper.tex
Linear repeating gradients! Resolves #14

@@
 \begin{document}
-\title{The Protracted and Generally Unpleasant Death\\ of Justin A. Middleton\\ \large A Methodological Obituary}
+\title{A Tool for Visualizing Patterns of Spreadsheet Function Combinations \\ \large The Protracted and Generally Unpleasant Death of Justin A. Middleton\\ A Methodological Obituary}
 
@@
 \begin{abstract}
-Finding information on how people use built-in Excel functions individually is easy; how they're used together is not.
-With no analysis of functions in conjunction, a dearth on information about how end users construct more sophisticated programs within spreadsheets restricts current research.
-I've developed a visualization tool, informed by existing spreadsheet corpora, which offers insight into the patterns of how formulas comprise several functions in practice.
-Even in its initial state, the tool illustrates how some people think that have 27 arguments in a single SUM function is, for whatever reason, a good idea.
+Spreadsheet environments often come equipped with a plethora of functions to manipulate and calculate data, but it can be difficult to understand how end-users employ these functions in practice.
+Without this knowledge, both researchers and practitioners lack information about how end users construct sophisticated programs from these basic elements.
+We developed a tool that visualizes patterns of how functions are combined into formulae within Excel spreadsheets.
+Using the Enron spreadsheet dataset as an example, this paper shows how the tool can display both common and anomalous formulas and their respective contexts in an actual workbook.
 \end{abstract}

### 2016-03-12 src/viz/treeMaker.js

@@ -77,11 +77,13 @@ zoomer.translate([view_start_x, view_start_y]);
 //gist.github.com/pnavarrc/20950640812489f13246
 var gradient = svg.append("defs")
   .append("linearGradient")
-  .attr("id", "gradient");
-  /*.attr("x1", "0")
-  .attr("y1", "1")
-  .attr("x2", "1")
-  .attr("y2", "1");*/
+  .attr("id", "gradient")
+  .attr("gradientUnits", "userSpaceOnUse")
+  .attr("spreadMethod", "repeat")
+  .attr("x1", "0px")
+  .attr("y1", "0px")
+  .attr("x2", "150px")
+  .attr("y2", "0px");
 
 gradient.append("stop")
   .attr("offset", "0")
@@ -89,7 +91,7 @@ gradient.append("stop")
   .attr("stop-opacity", "1");
 
 gradient.append("stop")
-  .attr("offset", "1")
+  .attr("offset", ".9")
   .attr("stop-color", "black")
   .attr("stop-opacity", "0");
 
@@ -164,6 +166,8 @@ function update(src) {
     d.x0 = d.x;
     d.y0 = d.y;
   });
+
+  center(src);
 }
 
 /**
@@ -237,7 +241,11 @@ var tip = d3.select("body")
   .append("svg.rect")
   .attr("class", "tooltip")
   .attr("color", "gray")
-  .style("display", "none");
+  .style("display", "none")
+  .on("mouseover", function() { tip.hover = true; })
+  .on("mouseleave", function() { tip.hover = false; });
+
+console.log(tip);
 
 /**
  * Makes the tooltip visible over current mouse position over node. Sets text.
@@ -250,9 +258,8 @@ function mouseover(d) {
       br = "<br/>",
       func = b + d.function + bb + br,
       freq = d.frequency.toLocaleString() + br,
-      full = i + "unavailable" + ii + br,
-      ex = i + "unavailable" + ii,
-
+      ex = i + "unavailable" + ii + br,
+      loc = i + "unavailable" + ii,
       id = d.example;
 
   d3.json("examples.php?id=" + id, function(error, data) {
@@ -260,7 +267,11 @@ function mouseover(d) {
 
     form = data["formula"].replace(/</g, "&lt;").replace(/>/g, "&gt;");
     ex = i + form + ii + br;
-    tip.html(func + freq + full + ex)
+    loc = data["file"] + br + data["sheet"] + " " + data["row"]
[…]

### 2016-03-12 src/core/FormulaToken.java
Test adjustments

@@ -11,6 +11,7 @@ import org.apache.poi.ss.formula.ptg.RefPtgBase;
 import org.apache.poi.ss.formula.ptg.StringPtg;
 
 public class FormulaToken {
+  protected static boolean replace = true;
   protected String tokenStr;
   protected Ptg token;
   private int origLen = Integer.MAX_VALUE;
@@ -22,6 +23,16 @@ public class FormulaToken {
   }
   
   /**
+   * Names in a spreadsheet require the spreadsheet context in order to parse correctly.
+   * @param token   The Name token.
+   * @param render  The contain spreadsheet.
+   */
+  public FormulaToken(NamePtg token, FormulaRenderingWorkbook render) {
+    this.token = token;
+    this.tokenStr = token.toFormulaString(render).trim();
+  }
+  
+  /**
    * Creates a class that refers to a discrete token within an Excel formula.
    * ex:  SUM(A:A)+IF(B1<B2, B1, B2) -> SUM(), A:A, +, IF(), B1, <, B2, B1, B2 
    * @param tok   The discrete token in the formula, expected to not be an operation
@@ -29,9 +40,11 @@ public class FormulaToken {
    */
   public FormulaToken(Ptg tok) {
     this.token = tok;
-    //this.tokenStr = token.toFormulaString().trim();
-
-    this.tokenStr = getTypeString(tok);
+    this.tokenStr = replace ? getTypeString(tok) : token.toFormulaString().trim();
+  }
+  
+  public static void dontReplace() {
+    replace = false;
   }
 
   /**
@@ -59,16 +72,6 @@ public class FormulaToken {
       type = "~OTHER~";
     
     return type;
-  }
-  
-  /**
-   * Names in a spreadsheet require the spreadsheet context in order to parse correctly.
-   * @param token   The Name token.
-   * @param render  The contain spreadsheet.
-   */
-  public FormulaToken(NamePtg token, FormulaRenderingWorkbook render) {
-    this.token = token;
-    this.tokenStr = token.toFormulaString(render).trim();
   }
   
   /**

### 2016-03-12 src/tests/AllTests.java

@@ -4,11 +4,13 @@ import java.io.File;
 import java.util.ArrayList;
 import java.util.Collection;
 
+import org.junit.Before;
 import org.junit.Test;
 import org.junit.runner.RunWith;
 import org.junit.runners.Parameterized;
 import org.junit.runners.Parameterized.Parameters;
 
+import core.FormulaToken;
 import utils.TestUtils;
 
 //http://stackoverflow.com/questions/358802/junit-test-with-dynamic-number-of-tests
@@ -24,7 +26,7 @@ public class AllTests {
   public static Collection<Object[]> getFiles() {
     Collection<Object[]> files = new ArrayList<Object[]>();
     
-    String enronDir = System.getenv("ENRON_DIR");
+    String enronDir = "./sheets/ENRON/";
     for (File file : new File(enronDir).listFiles()) {
       if (!file.isFile()) continue;
       
@@ -35,6 +37,11 @@ public class AllTests {
     }
     
     return files;
+  }
+  
+  @Before
+  public void setUp() {
+    FormulaToken.dontReplace();
   }
   
   @Test

### 2016-03-12 src/tests/BlankTests.java

@@ -8,11 +8,13 @@ import java.sql.SQLException;
 import java.util.ArrayList;
 import java.util.Collection;
 
+import org.junit.Before;
 import org.junit.Test;
 import org.junit.runner.RunWith;
 import org.junit.runners.Parameterized;
 import org.junit.runners.Parameterized.Parameters;
 
+import core.FormulaToken;
 import core.Parser;
 import utils.DBUtils;
 import utils.TestUtils;
@@ -42,6 +44,11 @@ public class BlankTests {
     }
     
     return files;
+  }
+  
+  @Before
+  public void setUp() {
+    FormulaToken.dontReplace();
   }
   
   @Test

### 2016-03-12 src/tests/SheetTests.java

@@ -1,14 +1,20 @@
 package tests;
 
+import org.junit.Before;
 import org.junit.Test;
 
+import core.FormulaToken;
 import utils.TestUtils;
 
 public class SheetTests {
+  @Before
+  public void setUp() {
+    FormulaToken.dontReplace();
+  }
 
   @Test
   public void test_01_albertmeyers01() {
-    String filename = "./sheets/albert_meyers__1__1-25act.xlsx";    
+    String filename = "./sheets/ENRON/albert_meyers__1__1-25act.xlsx";    
     TestUtils.parseFullFile(filename);    
   }
   
@@ -17,7 +23,7 @@ public class SheetTests {
    */
   @Test
   public void test_02_andyzipper01() {
-    String filename = "./sheets/andy_zipper__112__mODEL 3 7 01 Base.xlsx";    
+    String filename = "./sheets/ENRON/andy_zipper__112__mODEL 3 7 01 Base.xlsx";    
     TestUtils.parseFullFile(filename);    
   }
   
@@ -27,7 +33,7 @@ public class SheetTests {
    */
   @Test
   public void test_03_barrytycholiz01() {
-    String filename = "./sheets/barry_tycholiz__880__EPNG Results.xlsx";
+    String filename = "./sheets/ENRON/barry_tycholiz__880__EPNG Results.xlsx";
     TestUtils.parseFullFile(filename);
   }
   
@@ -37,7 +43,7 @@ public class SheetTests {
    */
   @Test
   public void test_04_benjaminrogers01() {
-    String filename = "./sheets/benjamin_rogers__1013__Pro Forma2.xlsx";
+    String filename = "./sheets/ENRON/benjamin_rogers__1013__Pro Forma2.xlsx";
     TestUtils.parseFullFile(filename);
   }
   
@@ -46,7 +52,7 @@ public class SheetTests {
    */
   @Test
   public void test_05_benjaminrogers02() {
-    String filename = "./sheets/benjamin_rogers__1239__Simple Cycle Florida model.xlsx";
+    String filename = "./sheets/ENRON/benjamin_rogers__1239__Simple Cycle Florida model.xlsx";
     TestUtils.parseFullFile(filename);
   }
   
@@ -55,7 +61,7 @@ public class SheetTests {
    */
   @Test 
   public void test_06_benjaminrogers03() {
-    String filename = "./sheets/benjamin_rogers__909__PJMupdate1.xlsx";
[…]

### 2016-03-12 src/tests/SingleTests.java

@@ -5,17 +5,24 @@ import static org.junit.Assert.fail;
 import org.apache.poi.ss.formula.FormulaParseException;
 import org.apache.poi.xssf.usermodel.XSSFEvaluationWorkbook;
 import org.apache.poi.xssf.usermodel.XSSFWorkbook;
+import org.junit.Before;
 import org.junit.Test;
 
+import core.FormulaToken;
 import core.Parser;
 import utils.POIUtils;
 import utils.TestUtils;
 
 public class SingleTests {
+  @Before
+  public void setUp() {
+    FormulaToken.dontReplace();
+  }
+  
 
   @Test
   public void test_01() {
-    String filename = "./sheets/albert_meyers__1__1-25act.xlsx",
+    String filename = "./sheets/ENRON/albert_meyers__1__1-25act.xlsx",
            formula = "SUM(IF((DelPoint= \"4C\")*(DType = \"pre\")*(OFFSET(DelPoint,0,B3+2)<0),OFFSET(DelPoint,0,B3+2),0))";
     int    sheetNum = 0;
     
@@ -24,7 +31,7 @@ public class SingleTests {
   
   @Test
   public void test_02_sum() {
-    String filename = "./core/utils/sum.xlsx",
+    String filename = "./src/utils/sum.xlsx",
            formula = "IF(A1>A2, SUM(A3:A4), SUM(A5, A6))";
     int    sheetNum = 0;
     
@@ -34,7 +41,7 @@ public class SingleTests {
   //TODO: MissingArgPtg present, which included space in my parser's result.
   @Test
   public void test_03_blanksum() {
-    String filename = "./sheets/albert_meyers__1__1-25act.xlsx",
+    String filename = "./sheets/ENRON/albert_meyers__1__1-25act.xlsx",
            formula = "IF(-SUM(B18:B20,B35:B37)>134,\"err\",-SUM(B18:B20,))";
     int    sheetNum = 0;
 
@@ -47,7 +54,7 @@ public class SingleTests {
    */
   @Test
   public void test_04_referror() {
-    String filename = "./sheets/albert_meyers__1__1-25act.xlsx",
+    String filename = "./sheets/ENRON/albert_meyers__1__1-25act.xlsx",
            formula = "IF(SUM(Deals!#REF!)=0,0,SUM(Deals!#REF!*Deals!#REF!)/SUM(Deals!#REF!))";
     int    sheetNum = 0;
 
@@ -60,7 +67,7 @@ public class SingleTests {
    */
   @Test
[…]

### 2016-03-13 src/core/FormulaToken.java
Work on #4.

@@ -1,5 +1,7 @@
 package core;
 
+import org.apache.poi.ss.formula.EvaluationName;
+import org.apache.poi.ss.formula.FormulaParsingWorkbook;
 import org.apache.poi.ss.formula.FormulaRenderingWorkbook;
 import org.apache.poi.ss.formula.ptg.AreaPtgBase;
 import org.apache.poi.ss.formula.ptg.BoolPtg;
@@ -26,10 +28,17 @@ public class FormulaToken {
    * Names in a spreadsheet require the spreadsheet context in order to parse correctly.
    * @param token   The Name token.
    * @param render  The contain spreadsheet.
+   * @param sheet 
    */
-  public FormulaToken(NamePtg token, FormulaRenderingWorkbook render) {
+  public FormulaToken(NamePtg token, FormulaRenderingWorkbook render, int sheet) {
     this.token = token;
     this.tokenStr = token.toFormulaString(render).trim();
+    
+    //TODO: Make unique name class?
+    EvaluationName eval = ((FormulaParsingWorkbook) render).getName(tokenStr, sheet);
+    Ptg[] toks = eval.getNameDefinition();
+    FormulaToken expanded = Parser.parseFormula(toks, render, sheet);
+    this.tokenStr = expanded.toString();
   }
   
   /**

### 2016-03-13 src/core/Parser.java

@@ -63,7 +63,7 @@ public class Parser {
     }
     
     FormulaRenderingWorkbook render = (FormulaRenderingWorkbook) parse;
-    FormulaToken tree = parseFormula(tokens, render);
+    FormulaToken tree = parseFormula(tokens, render, sheet);
     tree.setOrigLen(formula.length());
     return tree;
   }
@@ -73,7 +73,7 @@ public class Parser {
    * @param tokens  The Ptg tokens from POI.
    * @param render  The rendering workbook which contained the formula.
    */
-  public static FormulaToken parseFormula(Ptg[] tokens, FormulaRenderingWorkbook render) {
+  public static FormulaToken parseFormula(Ptg[] tokens, FormulaRenderingWorkbook render, int sheet) {
     Stack<FormulaToken> formula = new Stack<FormulaToken>();
     
     for (Ptg ptg : tokens) {
@@ -85,7 +85,7 @@ public class Parser {
       } else if (ptg instanceof OperationPtg) {        
         form = operationParse(ptg, formula);       
       } else if (ptg instanceof OperandPtg) {           
-        form = operandParse(ptg, render);        
+        form = operandParse(ptg, render, sheet);        
       } else if (ptg instanceof ParenthesisPtg) {
         form = parseParen(formula);
       } else if (ptg instanceof AttrPtg) {
@@ -143,15 +143,16 @@ public class Parser {
    * Wrap operands in FormulaTokens. If the operand is a name, pass in the rendering workbook too.
    * @param ptg     The operand token.
    * @param render  The rendering workbook in which the formula was found.
+   * @param sheet 
    * @return        The new formula token.
    */
-  private static FormulaToken operandParse(Ptg ptg, FormulaRenderingWorkbook render) {
+  private static FormulaToken operandParse(Ptg ptg, FormulaRenderingWorkbook render, int sheet) {
     FormulaToken form;
     
     //Name tokens need renderer, others don't.
     if (ptg instanceof NamePtg) {
       NamePtg name = (NamePtg) ptg;
-      form = new FormulaToken(name, render);
+      form = new FormulaToken(name, render, sheet);
     } else {
       OperandPtg operand = (OperandPtg) ptg;
       form = new FormulaToken(operand);

### 2016-03-13 src/utils/TestUtils.java

@@ -156,13 +156,14 @@ public class TestUtils {
                          doublePlus                  = Pattern.compile("\\+\\+")                 .matcher("");
 
   //TODO: THESE THINGS ARE A MESS: TOO MANY REGEXES YIELDS TOO MANY UNCERTAINTIES
+  //      AND THREATEN TO RUIN THE PURPOSE OF TESTING IN THE FIRST PLACE
   /**
    * @param str String to format.
    * @return    String with all above steps applied to it.
    */
   public static String format(String str) {
-    String formatted = dollar                     .reset(str)      .replaceAll("");
-           formatted = whiteSpace                 .reset(formatted).replaceAll("");
+    String //formatted = dollar                     .reset(str)      .replaceAll("");
+           formatted = whiteSpace                 .reset(str).replaceAll("");
            formatted = quotesBeforeErrors         .reset(formatted).replaceAll("#");
            formatted = wordsOrBracketsBeforeErrors.reset(formatted).replaceAll("$1");
            formatted = allColumns1                .reset(formatted).replaceAll("$1:$2");

### 2016-03-13 src/core/OperationToken.java
R1C1 work.

@@ -34,7 +34,6 @@ public class OperationToken extends FormulaToken {
     this.op = extractOp(tok, len);
         
     addChildren(len, args);
-    this.toString();
   }
   
   /**

### 2016-03-13 src/core/Parser.java

@@ -7,6 +7,7 @@ import org.apache.poi.ss.formula.FormulaParser;
 import org.apache.poi.ss.formula.FormulaParsingWorkbook;
 import org.apache.poi.ss.formula.FormulaRenderingWorkbook;
 import org.apache.poi.ss.formula.FormulaType;
+import org.apache.poi.ss.formula.ptg.AreaPtg;
 import org.apache.poi.ss.formula.ptg.AttrPtg;
 import org.apache.poi.ss.formula.ptg.MemAreaPtg;
 import org.apache.poi.ss.formula.ptg.MemFuncPtg;
@@ -30,14 +31,14 @@ public class Parser {
    */
   public static FormulaToken parseFormula(String formula) 
       throws FormulaParseException, UnsupportedOperationException {
-    return parseFormula(formula, 0, BLANK);
+    return parseFormula(formula, BLANK, 0);
   }
   
   /**
    * Break down a formula into individual tokens and wrap them up in nested FormulaTokens.
    * @param formula                         Formula to parse.
-   * @param sheet                           Sheet number of the formula.
    * @param parse                           The workbook in which the formula was found.
+   * @param sheet                           Sheet number of the formula.
    * @return                                A FormulaToken which represents the top-level function
    *                                          of the formula and contains all interior FormulaTokens.
    * @throws FormulaParseException          If Apache POI can't properly parse the formula.
@@ -45,7 +46,7 @@ public class Parser {
    * @throws UnsupportedOperationException  If the formula is blank or has quotes after exclamation
    *                                          ( !' ), which I saw in a few and it couldn't parse.
    */
-  public static FormulaToken parseFormula(String formula, int sheet, FormulaParsingWorkbook parse) 
+  public static FormulaToken parseFormula(String formula, FormulaParsingWorkbook parse, int sheet) 
       throws FormulaParseException, UnsupportedOperationException {
     Ptg[] tokens = null;
     
@@ -152,7 +153,8 @@ public class Parser {
     //Name tokens need renderer, others don't.
     if (ptg instanceof NamePtg) {
       NamePtg name = (NamePtg) ptg;
-      form = new FormulaToken(name, render, sheet);
+      Ptg[] nameTokens = POIUtils.resolveName(name, render, sheet);
+      form = parseFormula(nameTokens, render, sheet);
     } else {
       OperandPtg operand = (OperandPtg) ptg;
       form = new FormulaToken(operand);

### 2016-03-13 src/scripts/filesAndDB/FindBetterFormulas.java

@@ -12,13 +12,16 @@ import org.apache.poi.ss.usermodel.Workbook;
 import org.apache.poi.xssf.usermodel.XSSFEvaluationWorkbook;
 import org.apache.poi.xssf.usermodel.XSSFWorkbook;
 
+import core.FormulaToken;
 import core.Parser;
+import utils.POIUtils;
 
-public class FindFormulas {
-  private static final String SSDIRECTORY = System.getenv("ENRON_DIR");
+public class FindBetterFormulas {
+  private static final String SSDIRECTORY = "./sheets/ENRON/";
 
   public static void main(String[] args) throws Exception {
     File dir = new File(SSDIRECTORY);
+    FormulaToken.dontReplace();
     
     if (!dir.isDirectory()) {
       System.err.println("SSDirectory is not a directory!");
@@ -59,11 +62,24 @@ public class FindFormulas {
       for (Row row : sheet) {
         for (Cell cell : row) {
           
-        	if (cell.getCellType() == Cell.CELL_TYPE_FORMULA) {
-        		String formula = cell.getCellFormula();        		
-        		System.out.println(">>> " + formula);
-        		Parser.parseFormula(formula, parse, i);
-        	}          
+        	if (cell.getCellType() == Cell.CELL_TYPE_FORMULA) {        
+        	  FormulaToken tok = null;
+        	  
+        		try {
+              String formula = cell.getCellFormula();   
+              
+              System.out.println(formula);
+              
+              System.out.println(POIUtils.toR1C1String(formula, cell.getRowIndex(), cell.getColumnIndex()));
+           
+              System.out.println(">>> " + formula);
+              System.out.println();
+        		  tok = Parser.parseFormula(formula, parse, i);
+        		} catch (Exception | Error e) {
+        		  System.out.println(e + " (" + cell.getRowIndex() + "," + cell.getColumnIndex() + ")");
+        		  continue;
+        		}
+         	}          
         }
       }
       

### 2016-03-13 src/scripts/trees/AllTrees.java

@@ -42,7 +42,7 @@ public class AllTrees {
         
         FormulaToken tree = null;
         try {
-          tree = Parser.parseFormula(formula, sheet, Parser.BLANK);
+          tree = Parser.parseFormula(formula, Parser.BLANK, sheet);
         } catch (Exception e) {
           continue;
         }

### 2016-03-13 src/scripts/trees/IFTree.java

@@ -39,7 +39,7 @@ public class IFTree {
         
         FormulaToken tree = null;
         try {
-          tree = Parser.parseFormula(formula, sheet, Parser.BLANK);
+          tree = Parser.parseFormula(formula, Parser.BLANK, sheet);
         } catch (Exception e) {
           continue;
         }

### 2016-03-13 src/scripts/trees/SUMTree.java

@@ -39,7 +39,7 @@ public class SUMTree {
         
         FormulaToken tree = null;
         try {
-          tree = Parser.parseFormula(formula, sheet, Parser.BLANK);
+          tree = Parser.parseFormula(formula, Parser.BLANK, sheet);
         } catch (Exception e) {
           continue;
         }

### 2016-03-13 src/scripts/trees/ViewTrees.java

@@ -26,7 +26,7 @@ public class ViewTrees {
       
       XSSFWorkbook wb = POIUtils.getWorkbook(filepath);
       FormulaParsingWorkbook parse = POIUtils.getParser(wb);
-      FormulaToken tree = Parser.parseFormula("SUM(A:A)+1+2+3", sheet, parse);
+      FormulaToken tree = Parser.parseFormula("SUM(A:A)+1+2+3", parse, sheet);
       
       System.out.println(tree);
       System.out.println(tree.toTreeString());

### 2016-03-13 src/tests/BlankTests.java

@@ -54,7 +54,7 @@ public class BlankTests {
   @Test
   public void test() {
     try {
-      String result = Parser.parseFormula(formula, 0, Parser.BLANK).toString();
+      String result = Parser.parseFormula(formula, Parser.BLANK, 0).toString();
       TestUtils.compare(formula, result);
     } catch (Exception | Error e) {
       fail(e.getMessage());

### 2016-03-13 src/tests/SingleTests.java

@@ -75,7 +75,7 @@ public class SingleTests {
     XSSFEvaluationWorkbook parse = XSSFEvaluationWorkbook.create(wb);
     
     try {
-      Parser.parseFormula(formula, sheetNum, parse);
+      Parser.parseFormula(formula, parse, sheetNum);
       fail("No FormulaParseException thrown");
     } catch (FormulaParseException e) {
       assert(true);
@@ -103,7 +103,7 @@ public class SingleTests {
     XSSFEvaluationWorkbook parse = XSSFEvaluationWorkbook.create(wb);
     
     try {
-      Parser.parseFormula(formula, sheetNum, parse);
+      Parser.parseFormula(formula, parse, sheetNum);
       fail("No UnsupportedOperationException caught.");
     } catch (UnsupportedOperationException e) {
       //Success!
@@ -123,7 +123,7 @@ public class SingleTests {
     XSSFEvaluationWorkbook parse = XSSFEvaluationWorkbook.create(wb);
     
     try {
-      Parser.parseFormula(formula, sheetNum, parse);
+      Parser.parseFormula(formula, parse, sheetNum);
       fail("No UnsupportedOperationException caught.");
     } catch (UnsupportedOperationException e) {
       //Success!
@@ -285,14 +285,14 @@ public class SingleTests {
     
     /*Used to call function below, but that would create two workbooks.*/
     XSSFEvaluationWorkbook parse = XSSFEvaluationWorkbook.create(wb);
-    String result = Parser.parseFormula(formula, sheetNum, parse).toString();
+    String result = Parser.parseFormula(formula, parse, sheetNum).toString();
     TestUtils.compare(formula, result);
   }
   
   private void singleSuccessTest(String filename, String formula, int sheetNum) {
     XSSFWorkbook wb = POIUtils.getWorkbook(filename);
     XSSFEvaluationWorkbook parse = XSSFEvaluationWorkbook.create(wb);
-    String result = Parser.parseFormula(formula, sheetNum, parse).toString();
+    String result = Parser.parseFormula(formula, parse, sheetNum).toString();
     TestUtils.compare(formula, result);
   }
   

### 2016-03-13 src/utils/POIUtils.java

@@ -4,14 +4,23 @@ import static org.junit.Assert.fail;
 
 import java.io.File;
 import java.io.IOException;
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
 
 import org.apache.poi.openxml4j.exceptions.InvalidFormatException;
 import org.apache.poi.openxml4j.opc.OPCPackage;
 import org.apache.poi.openxml4j.opc.PackageAccess;
+import org.apache.poi.ss.formula.EvaluationName;
 import org.apache.poi.ss.formula.FormulaParsingWorkbook;
 import org.apache.poi.ss.formula.FormulaRenderingWorkbook;
+import org.apache.poi.ss.formula.ptg.NamePtg;
+import org.apache.poi.ss.formula.ptg.Ptg;
+import org.apache.poi.ss.util.CellReference;
 import org.apache.poi.xssf.usermodel.XSSFEvaluationWorkbook;
 import org.apache.poi.xssf.usermodel.XSSFWorkbook;
+
+import core.FormulaToken;
+import core.Parser;
 
 public class POIUtils {  
   /**
@@ -62,5 +71,56 @@ public class POIUtils {
    */
   public static FormulaRenderingWorkbook getRender(XSSFWorkbook wb) {
     return XSSFEvaluationWorkbook.create(wb);
+  }
+  
+  /**
+   * Replaces a name with what it actually stands for in the workbook.
+   * Returns String so the parser is forced to parse it again, because the presence of names
+   *  can alter how the tokens are parsed. For example, ranges might be broken up into
+   *  two reference tokens and a colon token, rather than a single range token.
+   * @param token   The name to resolve.
+   * @param render  The workbook it came from.
+   * @param sheet   The sheet the name was in.
+   * @return
+   */
+  public static Ptg[] resolveName(NamePtg token, FormulaRenderingWorkbook render, int sheet) {
+    String nameStr = token.toFormulaString(render).trim();
+    EvaluationName eval = ((FormulaParsingWorkbook) render).getName(nameStr, sheet);
+    return eval.getNameDefinition();
+  }
+  
+  public static String toR1C1String(String formula, int row, int col) {
+    //TODO: This might match things in strings...but for my purposes, I don't think that
+    //      would change my results?
+    StringBuffer newFormula = new StringBuffer();
+    
+    Matcher match = Pattern.compile("\\$?[A-Z]+$?\\d+").matcher(formula);
+    while (match.find()) {
[…]

### 2016-03-13 src/utils/TestUtils.java

@@ -61,7 +61,7 @@ public class TestUtils {
           //System.out.println(coord);
           try {
             formula = cell.getCellFormula();
-            String result = Parser.parseFormula(formula, i, parse).toString();
+            String result = Parser.parseFormula(formula, parse, i).toString();
             ++numOfTests;
             compare(coord+":"+formula, coord+":"+result);             
           } catch (FormulaParseException e) {
@@ -146,12 +146,12 @@ public class TestUtils {
   
   private static Matcher dollar                      = Pattern.compile("\\$")                    .matcher(""),
                          whiteSpace                  //= Pattern.compile("\\s+(?=([^']*'[^']*')*[^']*$)").matcher(""),
-                                                     = Pattern.compile("[ \t\r\n$]")             .matcher(""),
+                                                     = Pattern.compile("[ \t\r\n]")             .matcher(""),
                          quotesBeforeErrors          = Pattern.compile("('[^']*')+!?#")          .matcher(""),
                          wordsOrBracketsBeforeErrors = Pattern.compile("[\\w \\[\\]]+!?(#[A-Z])").matcher(""),
-                         allColumns1                 = Pattern.compile("(\\w*)1:(\\w*)65536")    .matcher(""),
-                         allColumns2                 = Pattern.compile("(\\w*)1:(\\w*)1048576")  .matcher(""),
-                         allRows                     = Pattern.compile("A(\\d+)?:XFD(\\d+)?")    .matcher(""),
+                         allColumns1                 = Pattern.compile("\\$?(\\w*)\\$1:\\$?(\\w*)\\$65536")    .matcher(""),
+                         allColumns2                 = Pattern.compile("\\$?(\\w*)\\$1:\\$?(\\w*)\\$1048576")  .matcher(""),
+                         allRows                     = Pattern.compile("\\$A(\\d+)?:\\$XFD(\\d+)?")    .matcher(""),
                          quotesInSheetName           = Pattern.compile("'([^' \\-]*)'!")         .matcher(""),
                          doublePlus                  = Pattern.compile("\\+\\+")                 .matcher("");
 

### 2016-03-14 src/scripts/filesAndDB/StoreBetterFunctionsInDB.java
DB work. Resolves #3

@@ -1,0 +1,160 @@
+package scripts.filesAndDB;
+
+import java.io.File;
+import java.sql.Connection;
+import java.sql.PreparedStatement;
+import java.sql.SQLException;
+
+import org.apache.poi.hssf.util.CellReference;
+import org.apache.poi.openxml4j.opc.OPCPackage;
+import org.apache.poi.openxml4j.opc.PackageAccess;
+import org.apache.poi.ss.formula.FormulaParser;
+import org.apache.poi.ss.formula.FormulaParsingWorkbook;
+import org.apache.poi.ss.formula.FormulaType;
+import org.apache.poi.ss.formula.ptg.*;
+import org.apache.poi.ss.usermodel.Cell;
+import org.apache.poi.ss.usermodel.Row;
+import org.apache.poi.ss.usermodel.Sheet;
+import org.apache.poi.ss.usermodel.Workbook;
+import org.apache.poi.xssf.usermodel.XSSFEvaluationWorkbook;
+import org.apache.poi.xssf.usermodel.XSSFWorkbook;
+
+import utils.DBUtils;
+
+public class StoreBetterFunctionsInDB {
+  private static String insert = "INSERT INTO formulas "
+      + "(formula, src, file, sheet, sheetName, row, col, usedNames) "
+      + "VALUES (?, 'ENRON', ?, ?, ?, ?, ?, 0);";
+  private static PreparedStatement ps = null;
+
+  public static void main(String[] args) throws Throwable {
+    Connection con = DBUtils.connectToDatabase();
+    ps = con.prepareStatement(insert);
+
+    String ENRON = "./sheets/ENRON/";
+    for (File file : new File(ENRON).listFiles()) {
+      if (file.isDirectory()) continue;
+
+      String name = file.toString().replaceAll(".*\\\\", "");
+      //System.out.println(name);
+      XSSFWorkbook wb = null;
+
+      try {
+
+        wb = new XSSFWorkbook(OPCPackage.open(file, PackageAccess.READ));
+        FormulaParsingWorkbook parse = XSSFEvaluationWorkbook.create(wb);
+        iterateOverSheets(name, wb, parse);
+
+      } catch (Exception | Error e) {
+
+        System.out.println(file);
+        System.out.println(e);
+        System.out.println();
+        //throw e;
+
+      } finally {
+        if (wb != null) {
+          wb.close();  //If it throws an IOException here, I'll just give up.
+        }
+      }
+
[…]

### 2016-03-14 src/scripts/filesAndDB/ReduceR1C1.java
Name and R1C1 work. Resolves #4 and #5

@@ -1,0 +1,64 @@
+package scripts.filesAndDB;
+
+import java.sql.Connection;
+import java.sql.PreparedStatement;
+import java.sql.ResultSet;
+import java.sql.SQLException;
+import java.util.HashMap;
+
+import org.apache.poi.ss.util.CellReference;
+
+import utils.DBUtils;
+import utils.POIUtils;
+
+public class ReduceR1C1 { 
+  public static void main(String[] args) throws SQLException {
+    Connection con = DBUtils.connectToDatabase();
+    PreparedStatement insert = con.prepareStatement("INSERT INTO formulas_unique "
+        + "(id, formula, src, file, sheet, sheetName, row, col, usedNames, freq) "
+        + "VALUES (?, ?, 'ENRON', ?, ?, ?, ?, ?, ?, 0);");
+    PreparedStatement update = con.prepareStatement("UPDATE formulas_unique SET freq = ? WHERE id = ?;");
+    PreparedStatement get = con.prepareStatement("SELECT * FROM formulas WHERE file = ? and sheet = ? ORDER BY row, col;");
+    ResultSet files = con.createStatement().executeQuery("SELECT DISTINCT file, sheet FROM formulas;");
+    
+    while (files.next()) {
+      String file = files.getString(1);   get.setString(1, file);
+      int sheet = files.getInt(2);        get.setInt(2, sheet);
+      
+      HashMap<String, Integer> seenFreqs = new HashMap<String, Integer>();
+      HashMap<String, Integer> seenIds = new HashMap<String, Integer>();
+      ResultSet formulas = get.executeQuery();
+      while (formulas.next()) {
+        int id = formulas.getInt(1);
+        String formula = formulas.getString(2);
+        String sheetName = formulas.getString(6);
+        int row = formulas.getInt(7);
+        String c = formulas.getString(8);
+        int col = CellReference.convertColStringToIndex(c);
+        boolean usedNames = formulas.getBoolean(9);
+        
+        String r1c1 = POIUtils.toR1C1String(formula, row, col);
+        //System.out.println(r1c1);
+        if (seenFreqs.containsKey(r1c1)) {
+          seenFreqs.put(r1c1, seenFreqs.get(r1c1) + 1);
+        } else {
+          seenFreqs.put(r1c1, 1);
+          seenIds.put(r1c1, id);
+          
+          insert.setInt(1, id);           insert.setString(2, formula);
[…]

### 2016-03-14 src/scripts/filesAndDB/StoreBetterFunctionsInDB.java

@@ -111,7 +111,7 @@ public class StoreBetterFunctionsInDB {
       }      
     }
 
-    ps.executeBatch();
+    //ps.executeBatch();
   }
 
   static int total = 0, batchsize = 1000, tooLarge = 0, error = 0;
@@ -127,13 +127,13 @@ public class StoreBetterFunctionsInDB {
     }
 
     try {
-      ps.setString(1, formula);
-      ps.setString(2, file);
-      ps.setInt(3, sheet);
-      ps.setString(4, sheetName);
-      ps.setInt(5, rowIndex);
-      ps.setString(6, column);
-      ps.addBatch();
+//      ps.setString(1, formula);
+//      ps.setString(2, file);
+//      ps.setInt(3, sheet);
+//      ps.setString(4, sheetName);
+//      ps.setInt(5, rowIndex);
+//      ps.setString(6, column);
+//      ps.addBatch();
       ++total;
     } catch (Exception e) {
       System.err.println(e.getMessage());
@@ -141,9 +141,9 @@ public class StoreBetterFunctionsInDB {
       System.err.println();
     }
 
-    if (total % batchsize == 0) {
-      ps.executeBatch();
-    }
+//    if (total % batchsize == 0) {
+//      ps.executeBatch();
+//    }
 
   }
 

### 2016-03-15 doc/paper.tex
aaaaaaaaaaaaaaa paper

@@
 % no \IEEEPARstart
-The world of business owes a considerable debt to spreadsheets, the table-based interface which enables organization and manipulation of massive amounts of data.
-Their allure is in their versatility: while the end user does not need sophisticated programming skills to fill out a spreadsheet, the expert user has at their disposal numerous built-in operations, or functions, to expedite their work.
-As such, it should be of little surprise when Scaffidi and colleagues estimated that by 2012, over 50 million workers could be using them, including the 25 million who would be writing programs out of the functions included (citation and such).\par
+Business and research alike owe their debts to spreadsheets, the table-based interface which empowers users to organize and manipulate huge bodies of data [citation for definition].
+Their allure is in their versatility: while the novice end user can work without a deep knowledge of programming, the expert can expedite their work with a variety of built-in operations, or functions.\footnote{https://support.office.com/en-us/article/Excel-functions-alphabetical-b3944572-255d-4efb-bb96-c6d90033e188} As such, it should be of little surprise when Scaffidi and colleagues estimated that by 2012, over 50 million U.S.
+workers could be using them, including the 25 million who would be writing programs out of the functions included (Scaffidi citations).\par
 
-Considering this ubiquity, it's crucial to get spreadsheets right. Something, something. \par
+Considering this ubiquity, it's crucial to get spreadsheets right.
+Our failures in their use can be ruinous, as in 2012 when the influential findings on economic growth were reversed by a selection error [Enron paper], among other horror stories.\footnote{http://www.eusprig.org/horror-stories.htm}
 
@@
 
-This paper presents a tool, informed by such variegated sources, that visualizes not how people employ individual Excel functions but how they combine to make more sophisticated shreadsheet formulas.
+This paper presents a tool, informed by such varied sources, that visualizes not how people employ individual Excel functions but how they combine to make more sophisticated spreadsheet formulas.
 
@@
 \section{Approach}
-In visualizing the spreadsheet data, I aimed to accomplish the following goals:
+\subsection{Goals}
+In visualizing the spreadsheet data, I outlined a few core goals for what the tool should accomplish:
 \begin{itemize}
-	\item The data should come from a varied enough sources to avoid having too narrow or specialized a scope.
-	\item The tool should accommodate dataset sizes from the single spreadsheet to corpora of thousands.
-	\item The tool should visualize as much data as possible in order to capture (and clearly indicate) both the most typical and the most anomalous cases...
-	\item ...while being interactive enough to let the user choose which cases they see, as to not sacrifice readability.
-	\item The tool should facilitate quantitative understanding by showing which functions and which combinations are used most frequently...
-	\item ...and it should facilitate qualitative understanding by incorporating actual examples into the visualization from the datasets it studies, and it should help the user find these examples in their original context.
-	\item The tool, by the same method as above, should thus guide a user from the abstract patterns of function usage into the specific and applied techniques of functions in their natural habitat.
+	\item [1] \textbf{Draw an interactive interface to explore observed function combinations.} The combination space for all Excel functions is massive, let alone the space for observed formulas.
+Working from data with actual referents in practice, the tool must aid the user in navigating this space.
+	\item [2] \textbf{Emphasize the quantitative patterns in formula construction.} The tool, accommodating datasets of a few spreadsheets to millions, should address the questions of how often the end users employed a certain function and where they used it.
+In this way, it must show precise metrics, such as frequency of  use and depth of function nesting, of the dataset it conveys.
+	\item [3] \textbf{Promote a qualitative understanding of the patterns.} Lest these patterns remain abstract, the tool should supplement its observations with concrete instances of relevant formulas from the corpus.
+Ideally, it should even direct users to the exact cell in the spreadsheets where the formula was used, contextualizing the functions.
 \end{itemize} \par
-Likewise, there were a few goals that I was specifically not trying to accomplish with this:
+Likewise, to bound our scope, we outlined a few goals to specifically avoid accomplishing with this:
 \begin{itemize}
-	\item The tool should not be, by itself, responsible for generating functions from the data it collects. It is purely analytical.
+	\item [!1] \textbf{Do not try to directly explain what a function does.} Though the tool tries to foster tries understanding by linking pattern to example, it won't provide a precise description of what a function accomplishes.
+The tool's user must infer this.
+	\item [!2] \textbf{Do not create new formulas.} This is essentially an exploratory tool, not a generative one. It should not produce any information other than new views of the original data. 
 	%TODO: I do have an idea which could actually do the below, but, eh, it would take
 	%TODO: a fair amount of time to implement.
-	\item The tool will not visualize isolated Excel functions, linking the specific instance to the abstract pattern. It works only the other way.
-	\item Likewise, the tool will make no effort to explain what any given set of functions in combination actually does; the function of any given example is up to the user to infer.
+	\item [!3] \textbf{Do not visualize individual formulas.} Though there is room to explore the place of a single function in the group, the tool must design the core visualization around the entire body of data, not the other way around.
 \end{itemize}
 
+\subsection{Design}
+Given the composition of formulas as functions and their arguments (which could be yet more functions), we need a visualization style that conveys this sense of parent-child relationship.
+As such, we decided to represent formulas as trees where the branching factor depends on both the number of arguments in a function and the number of possible functions observed as an argument in a function.
+\par
+Guided by these goals, we faced a number of decision points in our design, which we outline below.
+
+\begin{itemize}
+	\item [1a] \textit{Copied formulas}: Excel allows users to spread a formula over an area, repeating the same task in each cell with minor adjustments.
+Without checking for this, the analysis may not reveal the functions most commonly used together but rather the formulas most often applied to large areas.
+To combat this, we converted formulas from their native A1 format to the relative R1C1, in which copied formulas should be identical, and reduced the records to unique R1C1 formulas per sheet.
+	\item [1b] \textit{Optional arguments}: How should the tool handle functions which accept a variable number of arguments?
+SUM, for example, can have anywhere from 1 to 255, and IF can accept either 2 or 3.
+\footnote{https://support.office.com/en-us/article/Excel-functions-by-category-5f91f4e9-7b42-46d2-9bd1-63f26a86c0eb} Without prior evidence, it's possible that spreadsheet programmers use different techniques for different numbers arguments.
+To account for this, we separate and analyze the different quantities of arguments observed for each function; the tool, however, uses as default all of the options collapsed into a single representation.
+\end{itemize}
+
+\begin{itemize}
+	%TODO: A picture would go well here.
+	\item [2a] \textit{Importance of depth}: When a function appears within another, should it be analyzed only as a nested function or would it also be valid to analyze the nested function on its own?
+If the former, then information about the same function will be scattered across different trees with no way to aggregate them.
+If the latter, then the tool will analyze some functions multiple times to capture every possible level of nesting.
+Both approaches have benefits and drawbacks, and so we included both.
+	\item [2b] \textit{Pattern density}: How should the tool quantitatively order its elements: by a function's raw frequency or by the unity of patterns it leads to?
+For example, if SUM has for its first argument two possibilities, one which itself contains 1000 unique argument possibilities with 1 occurrence each (high frequency, low pattern density) and another seen with 2 argument possibilities of 100 occurrences each (low frequency, high pattern density), which would be more interesting to emphasize?
+The answer depends on the nuances of the questions, but for simplicity, I've shown the former.
+	\item [2c] \textit{Non-functions}: How should the tool represent everything in the formula that isn't a function: numbers, string literals, errors, references, etc?
+Since these don't accept arguments, they will adorn the tree as leaves, and their precise content won't affect the functions around them as long as their types are known.
+As such, in the visualization, all of these nodes are replaced and aggregated under their types.
+\end{itemize}
+
+\begin{itemize}
+	\item [3a] \textit{Suitable examples}: Goal 3 supports the inclusion of examples in the visualization as a way of tying pattern to example, but how should examples be chosen?
+For this, the simpler is the better, and we made the broad working assumption that shorter (by character length) functions are simpler, and thus chose the shortest available.
+	\item [3b] \textit{Spreadsheet connections}: Is it possible to contextualize these examples even better?
+Yes, by leading the user directly back to the originating spreadsheet.
+The tool hyperlinks each example, then, back to the file that contains it, providing sheet, row, and column numbers if it doesn't open directly there.
+\end{itemize}
+
+\subsection{Implementation}
+We can view the final visualization as the product of two discrete processes:
+\begin{itemize}
+	\item \textit{Collection}: Given a set of Excel sheets, the tool, written mostly in Java, uses Apache POI\footnote{https://poi.apache.org/} to identify and iterate over every cell containing a valid formula.
+Afterward, it calls POI's formula parser to break the formula text into an ordered set of individual tokens, which the tool then parses into the tree-like form by which it is recorded.
+When all formulas have been analyzed like this, it produces JSON files for each top-level function in the set.
+	\item \textit{Presentation}: The JSON files, meanwhile, feed into the presentation code, implemented in Javascript with much help from the visualization library D3\footnote{https://d3js.org/}. 
+\end{itemize}
+When the presentation code displays the tree, it shows two types of nodes with different meanings: the circles represent a function that has been observed at that structural place, and hovering over these yields a tooltip with supplementary information and examples; and squares, which represent the argument positions for the function which is their parent.
+For example, if the IF function has been observed with three arguments, 3 squares will extend from it as children.
+Clicking on the square labeled '1' will yield more circles, all of which are functions or values that the tool observed as the first argument in an IF function; clicking on '2' will yield those possibilities in the second position; and so on.
+
+\subsection{Limitations}
+Because the data collection depends on POI's formula parser, it affords no leeway or partial information from a formula; it either processes it perfectly or throws it out.
+As such, the visualization inhibits insight into anything with syntactical errors.
+Note, however, that this does not include standard Excel errors like \#REF!
+and \#DIV/0, which the parser handles well.
+\par
+Unfortunately, the parse also failed to handle any externally defined functions, even if they were syntactically correct in their original context.
+On one hand, we don't consider the loss of these specific functions to be tragic, as they are not part of Excel proper and thus provide no insight into how people use built-in functions.
+However, information about other functions within them are lost.
+\par
+Many functions have an expected order of arguments, but some, like SUM and MATCH, can be reordered in various ways and maintain their value.
+However, the representation that this tool uses reinforces for all functions that the order is important, even in these exceptions.
+\par
+
 \section{Case Study}
-The patient exhibits strong cadaverous tendencies.
+---
 
 \section{Conclusion}
-This paper is the end-all, be-all.
-There is no future work simply because the concept of future work cannot exist with reference to this paper.
-The work is done.
-I perfected it.
-Go home, kiss your love, kick back, call it a day.
-This is not just a good thing, but the best thing.
-Your job here is done, and I'm the one who did it.
+---
 

### 2016-03-15 doc/paper.tex
Task paragraph written; all traces of humor removed.

@@
 \begin{document}
-\title{A Tool for Visualizing Patterns of Spreadsheet Function Combinations \\ \large The Protracted and Generally Unpleasant Death of Justin A. Middleton\\ A Methodological Obituary}
+\title{A Tool for Visualizing Patterns of Spreadsheet Function Combinations}
 
@@
 % affiliations
-\author{\IEEEauthorblockN{Justin A. Middleton (posthumous)}
+\author{\IEEEauthorblockN{Justin A. Middleton}
 \IEEEauthorblockA{North Carolina State University\\
-Raleigh, North Carolina\\
-(Please address all flowers and review notes to cemetery lot 126, grave 2)}}
+Raleigh, North Carolina}}
 
@@
 
-This paper presents a tool, informed by such varied sources, that visualizes not how people employ individual Excel functions but how they combine to make more sophisticated spreadsheet formulas.
+A tool, then, which empowers users of many intentions to explore these datasets would be rife with potential.
+On a simple level, the tool could provide concrete statistics on which functions are used in practice most (or least) often, and what other functions that work in conjunction with them.
+These numbers, then, could inform future work done on intelligently recommending functions to users or generating new formulas from these patterns of function use.
+Spreadsheet APIs, likewise, could be augmented or pruned through the discovery of frequent combinations or anomalous use of functions.
+Furthermore, if the tool maintains the connection between patterns and the actual, it could serve as a boon to educators as well, guiding lesson plans to the most commonly employed functions and offering a bounty of instructive (and real) examples.\par
+This paper presents such a tool, informed by such varied sources, that visualizes not how people employ individual Excel functions but how they combine to make more sophisticated spreadsheet formulas.
 
@@
 \section{Case Study}
----
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Vivamus ultricies volutpat laoreet.
+Suspendisse tempus sapien metus, eget eleifend risus vehicula nec.
+Nulla facilisi.
+Aliquam non sapien ut tellus sagittis varius vel non nisl.
+Ut interdum nibh interdum odio ullamcorper, ac rhoncus leo tincidunt.
+Suspendisse potenti.
+Sed at scelerisque urna.
+Duis vehicula, nulla sed luctus aliquet, ante ante finibus arcu, at condimentum ante velit accumsan ligula.
+Sed suscipit, risus et blandit vestibulum, nibh felis mollis tellus, id pharetra nisi tellus sed augue.
+Cras nunc orci, semper auctor cursus sed, sodales eu risus.
+Etiam nec diam sed mi fringilla luctus sit amet quis neque.
+
+Etiam porttitor lectus a augue volutpat suscipit.
+Pellentesque sodales dictum convallis.
+Cras varius pharetra tempor.
+Sed id finibus libero.
+Nullam aliquet posuere pellentesque.
+Sed rhoncus consequat lectus sed fermentum.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Fusce euismod justo non velit molestie, vitae efficitur dui molestie.
+Ut molestie eros ullamcorper, convallis nibh vel, varius libero.
+Nulla sit amet tincidunt risus, sed porta nisi.
+Phasellus faucibus ut nisl vitae convallis.
+
+Nulla efficitur diam diam, ac aliquam sapien vestibulum nec.
+Aliquam eu tempus sem, placerat dapibus metus.
+Sed augue tortor, hendrerit vitae ex et, vestibulum placerat erat.
+Donec rhoncus scelerisque nunc, sed elementum ipsum pharetra scelerisque.
+In bibendum massa eros, tristique sodales justo placerat at.
+Praesent egestas convallis nunc, in tempor ex tempus at.
+Suspendisse potenti.
+Maecenas mi tortor, aliquet a nibh nec, pretium dignissim nunc.
+Nullam eleifend volutpat facilisis.
+In condimentum ut ante nec ullamcorper.
+Sed finibus cursus justo vel pharetra.
+Praesent elit odio, semper eget dolor eu, tempor tristique eros.
+Praesent dapibus nec velit at aliquet.
+
+Sed a tempor velit.
+Maecenas congue consectetur elementum.
+Vestibulum dolor ante, aliquet et augue sed, congue vestibulum ligula.
+Vivamus viverra ex quis justo varius sodales.
+Nulla finibus risus vitae orci porta, a ornare ex aliquet.
+Sed mi sapien, sollicitudin tempus justo vitae, eleifend auctor sem.
+Aliquam aliquam purus quam.
+
+In rutrum tortor et enim fringilla, in dictum dui vulputate.
+Maecenas ut ligula et ipsum euismod ornare ut vel eros.
+Duis sit amet urna in tortor pretium convallis.
+Morbi vitae sollicitudin nisl.
+Etiam semper urna a ex aliquam malesuada.
+Aenean non bibendum velit, eu auctor metus.
+Integer vestibulum id turpis eget mattis.
+Donec diam nisi, rhoncus bibendum sollicitudin sed, eleifend vel massa.
+Curabitur ut ornare felis.
+Nullam viverra nulla in suscipit facilisis.
+Quisque mollis turpis id massa mattis sagittis.
+Ut vitae arcu a lectus gravida varius.
+Ut porttitor auctor rhoncus.
+
+Nam in est nec diam mattis suscipit.
+Morbi eget quam at arcu pellentesque dignissim quis vitae tellus.
+Sed leo dui, suscipit at feugiat a, tristique sed neque.
+Aenean rutrum dapibus mauris a rutrum.
+Nullam sapien purus, fringilla non varius nec, consectetur vitae massa.
+Fusce elit quam, vulputate vestibulum tempor et, pellentesque eget nisi.
+Vivamus ac congue dolor.
+Aliquam magna nulla, dapibus ac justo vitae, pharetra tristique mauris.
+Vivamus dictum massa a diam vestibulum, quis congue nibh mattis.
+Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
+Pellentesque quis ligula at augue pretium ullamcorper eu nec nunc.
+Nunc porta lorem eget purus fringilla, nec posuere purus sodales.
+Duis vel efficitur diam.
 
 \section{Conclusion}
----
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Fusce tristique lobortis euismod.
+Suspendisse dapibus ultrices bibendum.
+Etiam accumsan augue metus, sit amet accumsan dui tempus eu.
+Donec sed nibh id tellus posuere luctus.
+Ut vel sagittis tellus.
+Phasellus dapibus pharetra nibh a consectetur.
+Phasellus dignissim nibh posuere, auctor mauris eu, vestibulum nulla.
+Aliquam mi nibh, maximus vel interdum non, molestie vitae ante.
+Donec vitae lacinia purus, eget maximus leo.
+Duis volutpat congue ligula non hendrerit.
+
+Donec ac nibh imperdiet, hendrerit mi ac, viverra dolor.
+Vivamus tincidunt vehicula aliquet.
+In mollis egestas justo vel tincidunt.
+Donec in efficitur nisl.
+Donec eu nisl eu sem mattis malesuada et vitae lorem.
+Morbi urna purus, consectetur eget enim eget, interdum tincidunt diam.
+Etiam ultrices, metus nec fermentum porta, eros augue faucibus mauris, vitae ultricies nulla urna eget eros.
+Ut egestas, lorem ac volutpat pretium, est sem iaculis augue, et congue nisl massa vitae ipsum.
+Nulla facilisi.
+Donec metus nibh, laoreet et finibus ut, pretium eu ante.
+Fusce mauris enim, interdum nec consequat ac, interdum vitae ipsum.
+Mauris malesuada vitae arcu eu sagittis.
+Nullam euismod purus arcu, vitae consequat erat efficitur eu.
+Donec egestas felis sed mauris sagittis, at sodales neque lobortis.
+
+Curabitur sed ultricies nisi.
+Sed pharetra non dui nec dapibus.
+Sed tincidunt lacinia mi at elementum.
+Suspendisse egestas risus scelerisque viverra vestibulum.
+In hac habitasse platea dictumst.
+Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
+Donec fermentum libero eget libero iaculis porttitor.
+Curabitur libero nisl, varius ac lorem vel, ornare viverra erat.
+Nunc id magna est.
+Integer interdum tristique nulla, nec mattis nisl hendrerit a.
+Quisque turpis nisl, feugiat in sagittis a, viverra at massa.
 

### 2016-03-16 doc/paper.tex
Paper examples

@@
 \ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
+   \usepackage[pdftex]{graphicx}
   % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
+   \graphicspath{{pic/}}
   % and their extensions so you won't have to specify these with
   % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+   \DeclareGraphicsExtensions{.png}
 \else
@@
 
+\subsection{Description}
+To show how this all came together and demonstrate the interface, we will use an example of a quick task: discovering what kind of conditions people use in IF statements.
+Considering only formulas in which the IF function itself is the top-level function (that is, not nested within another function), we will approach a tree that begins like this:
+
+\includegraphics{start}
+
+The visualization so far comprises two types of node: the circle, which represents a discrete function in the formula and is size according to its relative frequency (the top-level node, by definition, will be the largest); and the numbered squares, which represent the positions of arguments within its parent function.
+From this, we can infer that, of the times it was observed, IF can have at most three arguments passed into it, which corresponds with its specifications in the API.\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2} \par
+Knowing that it is the first argument which contains the conditionals, we click on the square labeled "1" to explore.
+To save space, when more than 10 unique arguments have been observed in any position, the tool displays only the first ten, with an option to display the rest.
+The results are shown below:
+
+\includegraphics[width=.43\textwidth]{IFexpand}
+
+As expected, we see that IF contains as its first argument a number of comparison operators, such as = and <=, and boolean-returning functions, like ISNA and AND, with simple equality being the most common and some use as ABS being the least seen of everything actually used.
+From here, we can further explore the common options among these functions.
+Clicking on the "=" node will yield two arguments, it being a binary operator, and expanding each of them will peer into the range of common values of equality comparison:
+
+\includegraphics[width = .43\textwidth]{IFargslabel}
+
+For both sides of the equal sign, the operator has certain types of arguments which predominate over the others: on the left side is most often a reference to another cell; on the right, a string or number literal, which makes sense for the case of confirming a value in another cell before assigning this one.
+Furthermore, if the concept is difficult to imagine is practice, a tooltip accompanies each function node in the tree, providing a concrete example of a function that uses this structure and where it can be found.
+
 \subsection{Design}
-Given the composition of formulas as functions and their arguments (which could be yet more functions), we need a visualization style that conveys this sense of parent-child relationship.
-As such, we decided to represent formulas as trees where the branching factor depends on both the number of arguments in a function and the number of possible functions observed as an argument in a function.
+Early in the process, we decided that the tree form would be a suitable fit to represent the parent-child or caller-callee relationships inherent in the data, given the composition of formulas as functions and their arguments (which could be yet more functions).
+By adapting this structure to accommodate a broad range of possibilities for nested functions, the branching factor depends on both the number of arguments in a function and the number of possible functions observed as an argument in a function.
 \par
-Guided by these goals, we faced a number of decision points in our design, which we outline below.
+Guided by the goals in section A, we faced a number of decision points, which we describe below, before we arrived at the design shown above.
 
@@
 Because the data collection depends on POI's formula parser, it affords no leeway or partial information from a formula; it either processes it perfectly or throws it out.
-As such, the visualization inhibits insight into anything with syntactical errors.
+As such, the visualization inhibits insight into anything with syntactical errors or third-party functions that can't be evaluated without additional tools.
 Note, however, that this does not include standard Excel errors like \#REF!
 and \#DIV/0, which the parser handles well.
-\par
-Unfortunately, the parse also failed to handle any externally defined functions, even if they were syntactically correct in their original context.
-On one hand, we don't consider the loss of these specific functions to be tragic, as they are not part of Excel proper and thus provide no insight into how people use built-in functions.
-However, information about other functions within them are lost.
 \par
@@
 \par
+A larger and related problem is the loss of argument combination.
+In the example in section B, we saw how the tools conveys which arguments are used most often on each side of an equals sign, but it does not encode how these whether references were actually compared to strings and numbers the most or whether it corresponded more to all the arguments beneath those two
 
@@
 
-Nam in est nec diam mattis suscipit.
-Morbi eget quam at arcu pellentesque dignissim quis vitae tellus.
-Sed leo dui, suscipit at feugiat a, tristique sed neque.
-Aenean rutrum dapibus mauris a rutrum.
-Nullam sapien purus, fringilla non varius nec, consectetur vitae massa.
-Fusce elit quam, vulputate vestibulum tempor et, pellentesque eget nisi.
-Vivamus ac congue dolor.
-Aliquam magna nulla, dapibus ac justo vitae, pharetra tristique mauris.
-Vivamus dictum massa a diam vestibulum, quis congue nibh mattis.
-Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
-Pellentesque quis ligula at augue pretium ullamcorper eu nec nunc.
-Nunc porta lorem eget purus fringilla, nec posuere purus sodales.
-Duis vel efficitur diam.
-
 \section{Conclusion}
@@
 
+-extensible to other spreadsheets?
 % conference papers do not normally have an appendix

### 2016-03-16 doc/paper.tex
Some viz formatting work

@@
 Fortunately, the vanguards of spreadsheet research have assembled, organized, and released a number of spreadsheet corpora to inform work on how people actually use these tools in different contexts.
-Collections like EUSES[yada], FUSE[yada], and the Enron corpus[yada] have already enabled fruitful work across the field: [WORK PENDING MORE RESEARCH].
+Collections like EUSES[cite], FUSE[cite], and the Enron corpus[cite] have already enabled fruitful work across the field: [EXAMPLES FROM RESEARCH].
 A number of these studies focus on discovering which built-in functions are the most common (enabling something).
@@
 \par
-Other studies focus on API and built-in function use outside the domain of spreadsheets. [BUT FIRST I HAVE TO FIND THEM]
+Other studies focus on API and built-in function use outside the domain of spreadsheets. [RESEARCH ON API STUDIES]
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Vivamus ultricies volutpat laoreet.
-Suspendisse tempus sapien metus, eget eleifend risus vehicula nec.
-Nulla facilisi.
-Aliquam non sapien ut tellus sagittis varius vel non nisl.
-Ut interdum nibh interdum odio ullamcorper, ac rhoncus leo tincidunt.
-Suspendisse potenti.
-Sed at scelerisque urna.
-Duis vehicula, nulla sed luctus aliquet, ante ante finibus arcu, at condimentum ante velit accumsan ligula.
-Sed suscipit, risus et blandit vestibulum, nibh felis mollis tellus, id pharetra nisi tellus sed augue.
-Cras nunc orci, semper auctor cursus sed, sodales eu risus.
-Etiam nec diam sed mi fringilla luctus sit amet quis neque.
-
-Etiam porttitor lectus a augue volutpat suscipit.
-Pellentesque sodales dictum convallis.
-Cras varius pharetra tempor.
-Sed id finibus libero.
-Nullam aliquet posuere pellentesque.
-Sed rhoncus consequat lectus sed fermentum.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Fusce euismod justo non velit molestie, vitae efficitur dui molestie.
-Ut molestie eros ullamcorper, convallis nibh vel, varius libero.
-Nulla sit amet tincidunt risus, sed porta nisi.
-Phasellus faucibus ut nisl vitae convallis.
-
-Nulla efficitur diam diam, ac aliquam sapien vestibulum nec.
-Aliquam eu tempus sem, placerat dapibus metus.
-Sed augue tortor, hendrerit vitae ex et, vestibulum placerat erat.
-Donec rhoncus scelerisque nunc, sed elementum ipsum pharetra scelerisque.
-In bibendum massa eros, tristique sodales justo placerat at.
-Praesent egestas convallis nunc, in tempor ex tempus at.
-Suspendisse potenti.
-Maecenas mi tortor, aliquet a nibh nec, pretium dignissim nunc.
-Nullam eleifend volutpat facilisis.
-In condimentum ut ante nec ullamcorper.
-Sed finibus cursus justo vel pharetra.
-Praesent elit odio, semper eget dolor eu, tempor tristique eros.
-Praesent dapibus nec velit at aliquet.
-
-Sed a tempor velit.
-Maecenas congue consectetur elementum.
-Vestibulum dolor ante, aliquet et augue sed, congue vestibulum ligula.
-Vivamus viverra ex quis justo varius sodales.
-Nulla finibus risus vitae orci porta, a ornare ex aliquet.
-Sed mi sapien, sollicitudin tempus justo vitae, eleifend auctor sem.
-Aliquam aliquam purus quam.
-
-In rutrum tortor et enim fringilla, in dictum dui vulputate.
-Maecenas ut ligula et ipsum euismod ornare ut vel eros.
-Duis sit amet urna in tortor pretium convallis.
-Morbi vitae sollicitudin nisl.
-Etiam semper urna a ex aliquam malesuada.
-Aenean non bibendum velit, eu auctor metus.
-Integer vestibulum id turpis eget mattis.
-Donec diam nisi, rhoncus bibendum sollicitudin sed, eleifend vel massa.
-Curabitur ut ornare felis.
-Nullam viverra nulla in suscipit facilisis.
-Quisque mollis turpis id massa mattis sagittis.
-Ut vitae arcu a lectus gravida varius.
-Ut porttitor auctor rhoncus.
+[to be filled in]
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Fusce tristique lobortis euismod.
-Suspendisse dapibus ultrices bibendum.
-Etiam accumsan augue metus, sit amet accumsan dui tempus eu.
-Donec sed nibh id tellus posuere luctus.
-Ut vel sagittis tellus.
-Phasellus dapibus pharetra nibh a consectetur.
-Phasellus dignissim nibh posuere, auctor mauris eu, vestibulum nulla.
-Aliquam mi nibh, maximus vel interdum non, molestie vitae ante.
-Donec vitae lacinia purus, eget maximus leo.
-Duis volutpat congue ligula non hendrerit.
-
-Donec ac nibh imperdiet, hendrerit mi ac, viverra dolor.
-Vivamus tincidunt vehicula aliquet.
-In mollis egestas justo vel tincidunt.
-Donec in efficitur nisl.
-Donec eu nisl eu sem mattis malesuada et vitae lorem.
-Morbi urna purus, consectetur eget enim eget, interdum tincidunt diam.
-Etiam ultrices, metus nec fermentum porta, eros augue faucibus mauris, vitae ultricies nulla urna eget eros.
-Ut egestas, lorem ac volutpat pretium, est sem iaculis augue, et congue nisl massa vitae ipsum.
-Nulla facilisi.
-Donec metus nibh, laoreet et finibus ut, pretium eu ante.
-Fusce mauris enim, interdum nec consequat ac, interdum vitae ipsum.
-Mauris malesuada vitae arcu eu sagittis.
-Nullam euismod purus arcu, vitae consequat erat efficitur eu.
-Donec egestas felis sed mauris sagittis, at sodales neque lobortis.
-
-Curabitur sed ultricies nisi.
-Sed pharetra non dui nec dapibus.
-Sed tincidunt lacinia mi at elementum.
-Suspendisse egestas risus scelerisque viverra vestibulum.
-In hac habitasse platea dictumst.
-Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
-Donec fermentum libero eget libero iaculis porttitor.
-Curabitur libero nisl, varius ac lorem vel, ornare viverra erat.
-Nunc id magna est.
-Integer interdum tristique nulla, nec mattis nisl hendrerit a.
-Quisque turpis nisl, feugiat in sagittis a, viverra at massa.
+[to be filled in]
 

### 2016-03-16 src/core/FunctionStatsNode.java

@@ -20,16 +20,16 @@ public class FunctionStatsNode implements Node, Comparable<FunctionStatsNode> {
   private Map<Integer, QuantityOfArgumentsNode> specific_quantities = null;
   
   private Map<Integer, FunctionArgumentNode> all_quantities = new LinkedHashMap<Integer, FunctionArgumentNode>();
+    
+  @Expose
+  private int example;
   
   @Expose
   private FunctionArgumentNode[] children = null;
   
-  @Expose
-  private int example;
-  
   private int shortestExampleLen = Integer.MAX_VALUE;
   
-  private Matcher nonvariadicFuncs = Pattern.compile("[\\+\\-\\*/\\^]").matcher("");
+  private Matcher nonvariadicFuncs = Pattern.compile("[\\+\\-\\*/\\^&]").matcher("");
     
   /**
    * Represents a certain type of function or primitive type that can appear in a formula. Stores

### 2016-03-16 src/scripts/trees/AllTrees.java

@@ -25,7 +25,7 @@ public class AllTrees {
   public static void main(String[] args) throws SQLException, IOException {
     int limit = 100000, offset = 0, currentlyAt;
     Connection con = DBUtils.connectToDatabase();
-    PreparedStatement ps = con.prepareStatement("SELECT * FROM formulas WHERE ID > ? LIMIT " + limit + ";");
+    PreparedStatement ps = con.prepareStatement("SELECT * FROM formulas_unique WHERE ID > ? LIMIT " + limit + ";");
     
     Map<String, FunctionStatsNode> trees = new HashMap<String, FunctionStatsNode>();
     do {
@@ -41,9 +41,11 @@ public class AllTrees {
         int sheet = rs.getInt(5);
         
         FormulaToken tree = null;
+
         try {
           tree = Parser.parseFormula(formula, Parser.BLANK, sheet);
         } catch (Exception e) {
+          System.err.println("ARRRGH");
           continue;
         }
         
@@ -52,7 +54,7 @@ public class AllTrees {
           trees.put(toplevel, new FunctionStatsNode(tree.toSimpleString()));
         trees.get(toplevel).add(id, tree);
         
-        //System.out.println(currentlyAt + " : " + formula);        
+        System.out.println(currentlyAt + " : " + formula);        
       }
       
       rs.previous();
@@ -74,7 +76,7 @@ public class AllTrees {
     builder.setPrettyPrinting().serializeNulls().excludeFieldsWithoutExposeAnnotation();
     Gson gson = builder.create();
     
-    BufferedWriter write = new BufferedWriter(new FileWriter("./src/scripts/viz/all.json"));
+    BufferedWriter write = new BufferedWriter(new FileWriter("./src/viz/all.json"));
     write.write(gson.toJson(allFuncs));
     //System.out.println(gson.toJson(sum));
     write.close();

### 2016-03-16 src/scripts/trees/IFTree.java

@@ -21,7 +21,7 @@ public class IFTree {
   public static void main(String[] args) throws SQLException, IOException {
     int limit = 100000, offset = 0, currentlyAt;
     Connection con = DBUtils.connectToDatabase();
-    PreparedStatement ps = con.prepareStatement("SELECT * FROM formulas WHERE formula like 'IF%' and ID > ? LIMIT " + limit + ";");
+    PreparedStatement ps = con.prepareStatement("SELECT * FROM formulas_unique WHERE formula like 'IF%' and ID > ? LIMIT " + limit + ";");
     
     Node sum = null;
     do {
@@ -46,8 +46,6 @@ public class IFTree {
         
         if (!tree.toSimpleString().equals("IF()"))
           continue;
-        else if (formula.equals("IF(BQ17,IF(BP17,SQRT(LN(1+((BU17*AZ17)^2*(EXP(CG17^2*BT17)-1)+(BV17*BA17)^2*(EXP(CH17^2*BT17)-1)+(BW17*BB17)^2*(EXP(CI17^2*BT17)-1)+2*BU17*AZ17*BV17*BA17*(EXP(CG17*CH17*BT17)-1)+2*BV17*BA17*BW17*BB17*(EXP(CH17*CI17*BT17)-1)+2*BW17*BB17*BU17*AZ17*(EXP(CI17*CG17*BT17)-1))/(BY17*BP17)^2)/BT17),0),\"\")"))
-          System.out.println();
         
         if (sum == null)
           sum = new FunctionStatsNode(tree.toSimpleString());

### 2016-03-16 src/viz/treeMaker.js

@@ -82,11 +82,11 @@ var gradient = svg.append("defs")
   .attr("spreadMethod", "repeat")
   .attr("x1", "0px")
   .attr("y1", "0px")
-  .attr("x2", "150px")
+  .attr("x2", "250px")
   .attr("y2", "0px");
 
 gradient.append("stop")
-  .attr("offset", "0")
+  .attr("offset", ".4")
   .attr("stop-color", "black")
   .attr("stop-opacity", "1");
 
@@ -94,6 +94,17 @@ gradient.append("stop")
   .attr("offset", ".9")
   .attr("stop-color", "black")
   .attr("stop-opacity", "0");
+
+/*var background = svg.select("defs")
+  .append("pattern")
+  .attr("id", "stripes")
+  .attr("width", "150px")
+  .attr("height", "150px")
+  .attr("patternUnits", "userSpaceOnUse")
+  .append("rect")
+  .attr("width", "100px")
+  .attr("height", "100px")
+  .attr("fill", "black");*/
 
 /**
  * Initialize the tree with only one level down expanded.
@@ -146,7 +157,13 @@ function update(src) {
   var nodes = tree.nodes(root),
     links = tree.links(nodes);
 
-  nodes.forEach(function(d) { d.y = d.depth * 150; })
+  nodes.forEach(function(d) {
+    if (d.depth % 2 == 0) {
+      d.y = d.depth * 125;
+    } else {
+      d.y = (d.depth - 1) * 125 + 100;
+    }
+  })
 
   var node = svg.selectAll("g")
     .data(nodes, function(d) { return d.id || (d.id = ++i); });
@@ -245,8 +262,6 @@ var tip = d3.select("body")
   .on("mouseover", function() { tip.hover = true; })
   .on("mouseleave", function() { tip.hover = false; });
 
-console.log(tip);
-
 /**
  * Makes the tooltip visible over current mouse position over node. Sets text.
  */
@@ -262,13 +277,22 @@ function mouseover(d) {
       loc = i + "unavailable" + ii,
       id = d.example;
 
+  /*var tt = d3.select("#n" + d.id)
+    .append("rect")
+    .attr("class", "tooltip")
+    .attr("color", "gray")
+    .attr("x", d.x)
+    .attr("y", d.y)
+    .style("display", "inline");
+  console.log(tt);*/
+
   d3.json("examples.php?id=" + id, function(error, data) {
     if (error) throw error;
 
[…]

### 2016-03-17 src/viz/treeMaker.js
Start of double click.

@@ -210,8 +210,12 @@ function enterNode(node, src) {
       }),
       rects = nodeEnter.filter(function(d) { return d.depth % 2 != 0; })
 
+  circles.on("mouseover", mouseover)
+    .on("mousemove", mousemove)
+    .on("mouseleave", mouseleave);
   circles.filter(function(d) { return d.children || d._children; }) //Only click those that have any children.
-    .on("click", click);
+    .on("click", click)
+    .on("dblclick", newWindow);
   rects.on("click", click)
     .on("mouseover", rect_mouseover)
     .on("mouseleave", rect_mouseout);
@@ -238,10 +242,7 @@ function enterNode(node, src) {
 function enterCircle(circles) {
   circles.append("circle")
     .attr("r", 1e-6)
-    .style("fill", function(d) { return d._children ? circle_col : empty_col; })
-    .on("mouseover", mouseover)
-    .on("mousemove", mousemove)
-    .on("mouseleave", mouseleave);
+    .style("fill", function(d) { return d._children ? circle_col : empty_col; });
 
   circles.append("text")
     .attr("dx", function(d) { return -scale(d.frequency) - 2; })
@@ -258,9 +259,7 @@ var tip = d3.select("body")
   .append("svg.rect")
   .attr("class", "tooltip")
   .attr("color", "gray")
-  .style("display", "none")
-  .on("mouseover", function() { tip.hover = true; })
-  .on("mouseleave", function() { tip.hover = false; });
+  .style("display", "none");
 
 /**
  * Makes the tooltip visible over current mouse position over node. Sets text.
@@ -271,53 +270,47 @@ function mouseover(d) {
   var b = "<b>", bb = "</b>",
       i = "<i>", ii = "</i>",
       br = "<br/>",
-      func = b + d.function + bb + br,
-      freq = d.frequency.toLocaleString() + br,
-      ex = i + "unavailable" + ii + br,
-      loc = i + "unavailable" + ii,
+      func = "func: " + b + d.function + bb + br,
+      freq = "count: " + d.frequency.toLocaleString() + br,
+      ex = "ex: " + i + "unavailable" + ii + br,
+      //loc = i + "unavailable" + ii,
       id = d.example;
 
-  /*var tt = d3.select("#n" + d.id)
-    .append("rect")
+  var hovered = d3.select("#n" + d.id);
+
+  /*var tt = hovered.append("svg:rect")
     .attr("class", "tooltip")
     .attr("color", "gray")
[…]

### 2016-03-17 src/core/ArgumentNode.java
Work for examples.

@@ -12,22 +12,16 @@ import com.google.gson.annotations.Expose;
  * @author dlf
  *
  */
-public class FunctionArgumentNode implements Node {
+public class ArgumentNode extends Node {
   @Expose
   private int position;
   
-  @Expose
-  private int frequency = 0;  //TODO: The way this freq differs from FunctionStatsNode is very slight
-                                      //      and could probably eventually cause a bug. (FSN increments first
-                                      //      in constructor because it adds all children there. This doesn't add
-                                      //      anything in constructor, only in `add` and `get`
-  
-  private Map<String, FunctionStatsNode> possibleArguments_unsorted = new HashMap<String, FunctionStatsNode>();
+  private Map<String, Node> possibleArguments_unsorted = new HashMap<String, Node>();
   
   @Expose
   private Node[] children = null;  //because it preserves insertion order
   
-  public FunctionArgumentNode(int pos) {
+  public ArgumentNode(int pos) {
     this.position = pos;
   }
   
@@ -35,23 +29,23 @@ public class FunctionArgumentNode implements Node {
     String func = child.toSimpleString();
     increment();
 
-    FunctionStatsNode statsNode;
+    Node statsNode;
     if (possibleArguments_unsorted.containsKey(func)) {
       statsNode = possibleArguments_unsorted.get(func);
     } else {
-      statsNode = new FunctionStatsNode(child.toSimpleString());
+      statsNode = isLeafToken(func) ? new LeafNode(func) : new FunctionNode(func);
       possibleArguments_unsorted.put(child.toSimpleString(), statsNode);
     }
     
     statsNode.add(ex, child);
   }
   
-  public int increment() {
-    return ++frequency;
+  private boolean isLeafToken(String tok) {
+    return tok.startsWith("~") && tok.endsWith("~");
   }
 
-  public ArrayList<FunctionStatsNode> getPossibilities() {
-    return new ArrayList<FunctionStatsNode>(possibleArguments_unsorted.values());
+  public ArrayList<Node> getPossibilities() {
+    return new ArrayList<Node>(possibleArguments_unsorted.values());
   }
   
   public void setChildren() {
@@ -59,9 +53,15 @@ public class FunctionArgumentNode implements Node {
     for (Node node : children)
       node.setChildren();
   }
-
+  
   @Override
-  public int getFrequency() {
-    return frequency;
+  public String toString() {
+    return position + "";
   }
+
+  /*@Override
[…]

### 2016-03-17 src/core/FormulaToken.java

@@ -173,8 +173,8 @@ public class FormulaToken {
     if (o == this)
       return true;
     
-    if (o instanceof FunctionStatsNode) {
-      FunctionStatsNode fsn = (FunctionStatsNode) o;
+    if (o instanceof FunctionNode) {
+      FunctionNode fsn = (FunctionNode) o;
       return this.tokenStr.equals(fsn.getFunction());
     } else if (o instanceof FormulaToken) {
       FormulaToken ft = (FormulaToken) o;

### 2016-03-17 src/core/FunctionNode.java

@@ -1,7 +1,5 @@
 package core;
 
-import java.util.ArrayList;
-import java.util.Collections;
 import java.util.LinkedHashMap;
 import java.util.Map;
 import java.util.regex.Matcher;
@@ -9,27 +7,24 @@ import java.util.regex.Pattern;
 
 import com.google.gson.annotations.Expose;
 
-public class FunctionStatsNode implements Node, Comparable<FunctionStatsNode> {
+public class FunctionNode extends Node {
   @Expose
-  private String function;
-  
-  @Expose
-  private int frequency = 0;    
+  private String function;  
   
   @Expose
   private Map<Integer, QuantityOfArgumentsNode> specific_quantities = null;
   
-  private Map<Integer, FunctionArgumentNode> all_quantities = new LinkedHashMap<Integer, FunctionArgumentNode>();
+  private Map<Integer, ArgumentNode> all_quantities = new LinkedHashMap<Integer, ArgumentNode>();
     
   @Expose
   private int example;
   
   @Expose
-  private FunctionArgumentNode[] children = null;
+  private ArgumentNode[] children = null;
   
   private int shortestExampleLen = Integer.MAX_VALUE;
   
-  private Matcher nonvariadicFuncs = Pattern.compile("[\\+\\-\\*/\\^&]").matcher("");
+  private static Matcher nonvariadicFuncs = Pattern.compile("[\\+\\-\\*/\\^&]").matcher("");
     
   /**
    * Represents a certain type of function or primitive type that can appear in a formula. Stores
@@ -45,9 +40,9 @@ public class FunctionStatsNode implements Node, Comparable<FunctionStatsNode> {
    * 
    * @param token The type of formula token that this node wraps.
    */
-  public FunctionStatsNode(String func) {    
+  public FunctionNode(String func) {    
     this.function = func;
-    if (!nonvariadicFuncs.reset(func).matches() && !func.startsWith("~"))
+    if (!nonvariadicFuncs.reset(func).matches())
       specific_quantities = new LinkedHashMap<Integer, QuantityOfArgumentsNode>();
   }
   
@@ -84,7 +79,7 @@ public class FunctionStatsNode implements Node, Comparable<FunctionStatsNode> {
     
     for (int i = 0; i < children.length; ++i) {
       FormulaToken child = children[i];
-      FunctionArgumentNode argumentPosition = getArgumentAtPosition(i);
+      ArgumentNode argumentPosition = getArgumentAtPosition(i);
       argumentPosition.add(ex, child);
     }
[…]

### 2016-03-17 src/core/LeafNode.java

@@ -1,0 +1,56 @@
+package core;
+
+import java.util.ArrayList;
+
+import com.google.gson.annotations.Expose;
+
+public class LeafNode extends Node {
+  @Expose
+  private String function;
+  
+  @Expose
+  private int example;
+  
+  @Expose
+  private ArrayList<Integer> allExamples = new ArrayList<Integer>();
+  
+  private int shortestExampleLen = Integer.MAX_VALUE;
+
+  public LeafNode(String func) {
+    this.function = func;
+  }
+
+  @Override
+  public void add(int ex, FormulaToken token) {
+    if (!function.equals(token.toString()))
+      throw new UnsupportedOperationException("Trying to pass a FormulaToken which does not "
+          + "refer to the same type of token as the FunctionStatsNode: " + token.toSimpleString() 
+          + " vs. " + this.function);
+    
+    increment();
+    int otherExampleLen = token.getOrigLen();
+    if (shortestExampleLen > otherExampleLen) {
+      example = ex;
+      shortestExampleLen = otherExampleLen;
+    }    
+    
+    allExamples.add(ex);
+  }
+
+  @Override
+  public void setChildren() {
+    // Nothing    
+  }
+
+  @Override
+  public String toString() {
+    return function;
+  }
+
+  /*@Override
+  public void toTreeString(StringBuilder sb, int i) {
+    tabs(sb, i);
+    sb.append(function);
+    sb.append('\n');
+  }*/ 
+}

### 2016-03-17 src/core/Node.java

@@ -1,13 +1,52 @@
 package core;
 
-public interface Node {
-  void add(int ex, FormulaToken token);
+import com.google.gson.annotations.Expose;
 
-  void setChildren();
+public abstract class Node implements Comparable<Node> {
+  @Expose
+  protected int frequency = 0;  
+  
+  public abstract void add(int ex, FormulaToken token);
 
-  int increment();
+  public abstract void setChildren();
 
-  int getFrequency();
+  /**
+   * Record this type of function as being used one more time.
+   * @return    New frequency.
+   */
+  public int increment() {
+    return ++frequency;
+  }
+  
+  public int getFrequency() {
+    return frequency;
+  }
 
-  String toString();
+  public abstract String toString();
+
+  //public abstract void toTreeString(StringBuilder sb, int i);
+
+  /**
+   * Adds the appropriate amount of tabbing to an element this deep in the tree
+   * @param sb    The stringbuilder which is compiling the string for the entire tree.
+   * @param depth How deep we are into the hierarchy right now.
+   */
+  /*protected void tabs(StringBuilder sb, int depth) {
+    sb.append(depth % 2 == 0 
+                ? depth/2 + "."
+                : "..");
+    
+    for (int i = 0; i < depth; ++i) {
+      sb.append("..");
+    }
+  }*/
+  
+  
+  /**
+   * Things with higher frequency should be prioritized higher.
+   */
+  @Override
+  public int compareTo(Node o) {
+    return o.getFrequency() - this.frequency;
+  }
 }

### 2016-03-17 src/core/QuantityOfArgumentsNode.java

@@ -2,15 +2,12 @@ package core;
 
 import com.google.gson.annotations.Expose;
 
-public class QuantityOfArgumentsNode implements Node, Comparable<QuantityOfArgumentsNode> {
+public class QuantityOfArgumentsNode extends Node {
   @Expose
   private int quantity;
   
   @Expose
-  private int frequency;
-  
-  @Expose
-  private FunctionArgumentNode[] children;  //arguments
+  private ArgumentNode[] children;  //arguments
   
   @Expose
   private int example;
@@ -19,9 +16,9 @@ public class QuantityOfArgumentsNode implements Node, Comparable<QuantityOfArgum
   
   public QuantityOfArgumentsNode(int quantity) {
     this.quantity = quantity;
-    children = new FunctionArgumentNode[quantity];
+    children = new ArgumentNode[quantity];
     for (int i = 0; i < quantity; ++i)
-      children[i] = new FunctionArgumentNode(i);
+      children[i] = new ArgumentNode(i);
   }
   
   public void add(int ex, FormulaToken token) {
@@ -39,7 +36,7 @@ public class QuantityOfArgumentsNode implements Node, Comparable<QuantityOfArgum
     
     for (int i = 0; i < tokChildren.length; ++i) {
       FormulaToken child = tokChildren[i];
-      FunctionArgumentNode argumentPosition = children[i];        
+      ArgumentNode argumentPosition = children[i];        
       argumentPosition.add(ex, child);
     }
   }
@@ -48,19 +45,17 @@ public class QuantityOfArgumentsNode implements Node, Comparable<QuantityOfArgum
     return ++frequency;
   }
 
-  @Override
   public void setChildren() {
-    for (FunctionArgumentNode node : children)
+    for (ArgumentNode node : children)
       node.setChildren();
   }
 
-  @Override
   public int getFrequency() {
     return frequency;
   }
 
   @Override
-  public int compareTo(QuantityOfArgumentsNode o) {
-    return o.getFrequency() - this.frequency;
+  public String toString() {
+    return quantity + "";
   }
 }

### 2016-03-17 src/scripts/trees/AllTrees.java

@@ -17,7 +17,7 @@ import com.google.gson.Gson;
 import com.google.gson.GsonBuilder;
 
 import core.FormulaToken;
-import core.FunctionStatsNode;
+import core.FunctionNode;
 import core.Parser;
 import utils.DBUtils;
 
@@ -27,7 +27,7 @@ public class AllTrees {
     Connection con = DBUtils.connectToDatabase();
     PreparedStatement ps = con.prepareStatement("SELECT * FROM formulas_unique WHERE ID > ? LIMIT " + limit + ";");
     
-    Map<String, FunctionStatsNode> trees = new HashMap<String, FunctionStatsNode>();
+    Map<String, FunctionNode> trees = new HashMap<String, FunctionNode>();
     do {
       long start = System.currentTimeMillis();
       currentlyAt = 0;
@@ -51,7 +51,7 @@ public class AllTrees {
         
         String toplevel = tree.toSimpleString();
         if (!trees.containsKey(toplevel))
-          trees.put(toplevel, new FunctionStatsNode(tree.toSimpleString()));
+          trees.put(toplevel, new FunctionNode(tree.toSimpleString()));
         trees.get(toplevel).add(id, tree);
         
         System.out.println(currentlyAt + " : " + formula);        
@@ -63,11 +63,11 @@ public class AllTrees {
       System.out.println("At " + offset + "... (" + (end/1000.) + "sec)");
     } while (limit == currentlyAt);
     
-    ArrayList<FunctionStatsNode> sort = new ArrayList<FunctionStatsNode>(trees.values());
+    ArrayList<FunctionNode> sort = new ArrayList<FunctionNode>(trees.values());
     Collections.sort(sort);
     
-    LinkedHashMap<String, FunctionStatsNode> allFuncs = new LinkedHashMap<String, FunctionStatsNode>();
-    for (FunctionStatsNode node : sort) {
+    LinkedHashMap<String, FunctionNode> allFuncs = new LinkedHashMap<String, FunctionNode>();
+    for (FunctionNode node : sort) {
       allFuncs.put(node.getFunction(), node);
       node.setChildren();
     }

### 2016-03-17 src/scripts/trees/IFTree.java

@@ -12,7 +12,7 @@ import com.google.gson.Gson;
 import com.google.gson.GsonBuilder;
 
 import core.FormulaToken;
-import core.FunctionStatsNode;
+import core.FunctionNode;
 import core.Node;
 import core.Parser;
 import utils.DBUtils;
@@ -48,7 +48,7 @@ public class IFTree {
           continue;
         
         if (sum == null)
-          sum = new FunctionStatsNode(tree.toSimpleString());
+          sum = new FunctionNode(tree.toSimpleString());
         sum.add(id, tree);
         
         System.out.println(currentlyAt + " : " + formula);        

### 2016-03-17 src/scripts/trees/SUMTree.java

@@ -12,7 +12,7 @@ import com.google.gson.Gson;
 import com.google.gson.GsonBuilder;
 
 import core.FormulaToken;
-import core.FunctionStatsNode;
+import core.FunctionNode;
 import core.Node;
 import core.Parser;
 import utils.DBUtils;
@@ -48,7 +48,7 @@ public class SUMTree {
           continue;
         
         if (sum == null)
-          sum = new FunctionStatsNode(tree.toSimpleString());
+          sum = new FunctionNode(tree.toSimpleString());
         sum.add(id, tree);
         
         System.out.println(currentlyAt + " : " + formula);        

### 2016-03-17 doc/paper.tex
Related work work.

@@
 Their allure is in their versatility: while the novice end user can work without a deep knowledge of programming, the expert can expedite their work with a variety of built-in operations, or functions.\footnote{https://support.office.com/en-us/article/Excel-functions-alphabetical-b3944572-255d-4efb-bb96-c6d90033e188} As such, it should be of little surprise when Scaffidi and colleagues estimated that by 2012, over 50 million U.S.
-workers could be using them, including the 25 million who would be writing programs out of the functions included (Scaffidi citations).\par
+workers could be using them, including the 25 million who would be writing programs out of the functions included \cite{scaffidi2005estimating}.\par
 
 Considering this ubiquity, it's crucial to get spreadsheets right.
-Our failures in their use can be ruinous, as in 2012 when the influential findings on economic growth were reversed by a selection error [Enron paper], among other horror stories.\footnote{http://www.eusprig.org/horror-stories.htm}
+Our failures in their use can be ruinous, as in 2012 when the influential findings on economic growth were reversed by a selection error, among other horror stories.\footnote{http://www.eusprig.org/horror-stories.htm}
 
 Fortunately, the vanguards of spreadsheet research have assembled, organized, and released a number of spreadsheet corpora to inform work on how people actually use these tools in different contexts.
-Collections like EUSES[cite], FUSE[cite], and the Enron corpus[cite] have already enabled fruitful work across the field: [EXAMPLES FROM RESEARCH].
-A number of these studies focus on discovering which built-in functions are the most common (enabling something).
+Collections like EUSES \cite{fisher2005euses}, FUSE \cite{barik2015fuse}, and the Enron corpus \cite{hermans2015enron} have already enabled fruitful work across the field, such as detecting code smells in spreadsheets \cite{hermans2012detecting} \cite{cunha2012smellsheet}.
 \par
@@
 \section{Related Work}
-Spreadsheets, being a core component of business that they are, have prompted the development of many tools to evaluate them and their many qualities. [RESEARCH ON NON-VISUAL ANALYSIS TOOLS] \par
-Furthermore, this tool comes from a line of spreadsheet visualization tools before it, each with a different focus.
-For example, Breviz, developed by Hermans and colleagues, uses visualization to illustrate workbook dataflow to address the need for a clearly communicable representation of spreadsheets as they move from person to person.
+This tool comes from a line of spreadsheet visualization tools before it, each with a different focus.
+Some tools, such as Igarashi and colleague's fluid visualizations \cite{igarashi1998fluid}, seek to visualize the hidden formulas within a spreadsheet by imposing the dataflow graphs over the cells.
+Likewise, Clermont \cite{clermont2003scalable} (and Hipfl \cite{hipfl2008using}, who extended his work) explored various ways of visualizing groups of related cells through similar functions, neighbors, or references.
+Others focus on creating visualizations outside of the sheets: Hermans and colleagues address a spreadsheet programmer's information needs through their work on the tools GyroSAT \cite{hermans2011supporting} and Breviz \cite{hermans2011breviz} to make dataflow diagrams of individual spreadsheets.
+These, however, tend to focus on individual spreadsheets and not bodies of them.
 \par
+Nevertheless, other studies and tools focus more on evaluating the content of the cells therein. (Hermans, Smellsheet) \par
 Other studies focus on API and built-in function use outside the domain of spreadsheets. [RESEARCH ON API STUDIES]
@@
 % http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
+\bibliographystyle{IEEEtran}
 % argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
+\bibliography{paper}
 %
@@
 % (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
-
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\end{thebibliography}
+%\begin{thebibliography}{1}
+%
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+%
+%
+%\end{thebibliography}
 

### 2016-03-17 src/core/ArgumentNode.java
Remove unused tree string.

@@ -58,10 +58,4 @@ public class ArgumentNode extends Node {
   public String toString() {
     return position + "";
   }
-
-  /*@Override
-  public void toTreeString(StringBuilder sb, int i) {
-    // TODO Auto-generated method stub
-    
-  }*/
 }

### 2016-03-17 src/core/FunctionNode.java

@@ -155,29 +155,8 @@ public class FunctionNode extends Node {
    */
   @Override
   public String toString() {
-    return function; //toTreeString(new StringBuilder(), 0).toString();
+    return function; 
   }
-  
-  /*private StringBuilder toTreeString(StringBuilder sb, int depth) {
-    tabs(sb, depth);
-    sb.append(function + " (" + frequency + ")");
-    sb.append("\n");
-    
-    for (int i = 0; i < all_quantities.size(); ++i) {
-      ArgumentNode argument = getArgumentAtPosition(i);
-      tabs(sb, depth+1);
-      sb.append("Argument #" + (i+1));
-      sb.append("\n");
-      
-      ArrayList<Node> funcs = argument.getPossibilities();
-      Collections.sort(funcs);
-      for (Node func : funcs) {
-        func.toTreeString(sb, depth+2);
-      }
-    }
-    
-    return sb;
-  }*/
   
   /**
    * When comparing to FunctionStatsNodes, equality must be exact since distinct

### 2016-03-17 src/core/LeafNode.java

@@ -46,11 +46,4 @@ public class LeafNode extends Node {
   public String toString() {
     return function;
   }
-
-  /*@Override
-  public void toTreeString(StringBuilder sb, int i) {
-    tabs(sb, i);
-    sb.append(function);
-    sb.append('\n');
-  }*/ 
 }

### 2016-03-17 src/core/Node.java

@@ -22,25 +22,7 @@ public abstract class Node implements Comparable<Node> {
     return frequency;
   }
 
-  public abstract String toString();
-
-  //public abstract void toTreeString(StringBuilder sb, int i);
-
-  /**
-   * Adds the appropriate amount of tabbing to an element this deep in the tree
-   * @param sb    The stringbuilder which is compiling the string for the entire tree.
-   * @param depth How deep we are into the hierarchy right now.
-   */
-  /*protected void tabs(StringBuilder sb, int depth) {
-    sb.append(depth % 2 == 0 
-                ? depth/2 + "."
-                : "..");
-    
-    for (int i = 0; i < depth; ++i) {
-      sb.append("..");
-    }
-  }*/
-  
+  public abstract String toString();  
   
   /**
    * Things with higher frequency should be prioritized higher.

### 2016-03-17 src/tests/SingleTests.java

@@ -279,6 +279,12 @@ public class SingleTests {
     singleSuccessTest(formula);
   }
   
+  @Test
+  public void test_21_coloninsheetname() {
+    String formula = "SUM('111678 (0013):111706 (0238)'!E62:E62)";
+    singleSuccessTest(formula);
+  }
+  
   private void singleSuccessTest(String filename, int sheetNum, int row, int col) {
     XSSFWorkbook wb = POIUtils.getWorkbook(filename);
     String formula = getFormulaAt(wb, sheetNum, row, col);

### 2016-03-18 src/core/FormulaToken.java
Other R1C1 fixes.

@@ -1,22 +1,37 @@
 package core;
 
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
 import org.apache.poi.ss.formula.EvaluationName;
 import org.apache.poi.ss.formula.FormulaParsingWorkbook;
 import org.apache.poi.ss.formula.FormulaRenderingWorkbook;
+import org.apache.poi.ss.formula.ptg.Area2DPtgBase;
+import org.apache.poi.ss.formula.ptg.Area3DPxg;
 import org.apache.poi.ss.formula.ptg.AreaPtgBase;
 import org.apache.poi.ss.formula.ptg.BoolPtg;
 import org.apache.poi.ss.formula.ptg.IntPtg;
 import org.apache.poi.ss.formula.ptg.NamePtg;
 import org.apache.poi.ss.formula.ptg.NumberPtg;
+import org.apache.poi.ss.formula.ptg.OperandPtg;
 import org.apache.poi.ss.formula.ptg.Ptg;
 import org.apache.poi.ss.formula.ptg.RefPtgBase;
 import org.apache.poi.ss.formula.ptg.StringPtg;
+import org.apache.poi.ss.util.CellReference;
+
+import core.Parser.CellContext;
 
 public class FormulaToken {
-  protected static boolean replace = true;
+  protected static Mode mode = Mode.REPLACE;
   protected String tokenStr;
   protected Ptg token;
   private int origLen = Integer.MAX_VALUE;
+  
+  public enum Mode {
+    NO_CHANGE,
+    REPLACE,
+    R1C1
+  }
   
   //TODO: Don't like this blank string possibility, but OperationToken needs a blank super...
   public FormulaToken() {
@@ -48,12 +63,33 @@ public class FormulaToken {
    *              token and thus have no arguments.
    */
   public FormulaToken(Ptg tok) {
+    this(tok, new CellContext(0,0,0));
+  }
+
+  public FormulaToken(Ptg tok, CellContext cell) {
     this.token = tok;
-    this.tokenStr = replace ? getTypeString(tok) : token.toFormulaString().trim();
+    
+    switch (mode) {
+      case NO_CHANGE:
+        this.tokenStr = tok.toFormulaString().trim();   break;
+      case REPLACE:
+        this.tokenStr = getTypeString(tok);               break;
+      case R1C1:
+        this.tokenStr = toR1C1String(tok.toFormulaString().trim(), cell);
+        break;      
+    }
[…]

### 2016-03-18 src/core/OperationToken.java

@@ -81,7 +81,11 @@ public class OperationToken extends FormulaToken {
   }
   private static final Matcher NULL = Pattern.compile("null,?").matcher("");
 
-
+  public String wrap() {
+    this.tokenStr = "(" + tokenStr + ")";
+    return tokenStr;
+  }
+  
   public FormulaToken[] getChildren() {
     return children;
   }

### 2016-03-18 src/core/Parser.java

@@ -16,6 +16,7 @@ import org.apache.poi.ss.formula.ptg.OperandPtg;
 import org.apache.poi.ss.formula.ptg.OperationPtg;
 import org.apache.poi.ss.formula.ptg.ParenthesisPtg;
 import org.apache.poi.ss.formula.ptg.Ptg;
+import org.apache.poi.ss.usermodel.Cell;
 import org.apache.poi.xssf.usermodel.XSSFEvaluationWorkbook;
 
 import utils.POIUtils;
@@ -31,14 +32,29 @@ public class Parser {
    */
   public static FormulaToken parseFormula(String formula) 
       throws FormulaParseException, UnsupportedOperationException {
-    return parseFormula(formula, BLANK, 0);
+    return parseFormula(formula, BLANK, new CellContext(0, 0, 0));
   }
   
+  public static FormulaToken parseFormula(String formula, FormulaParsingWorkbook parse, int sheet)
+      throws FormulaParseException, UnsupportedOperationException {
+    return parseFormula(formula, parse, new CellContext(sheet, 0, 0));
+  }
+  
+  public static FormulaToken parseFormula(String formula, int row, int col) 
+      throws FormulaParseException, UnsupportedOperationException {
+    return parseFormula(formula, BLANK, new CellContext(0, row, col));
+  }
+  
+  public static FormulaToken parseFormula(Cell cell, FormulaParsingWorkbook parse, int sheet)
+      throws FormulaParseException, UnsupportedOperationException {
+    return parseFormula(cell.getCellFormula(), parse, new CellContext(sheet, cell.getRowIndex(), cell.getColumnIndex()));    
+  }
+
   /**
    * Break down a formula into individual tokens and wrap them up in nested FormulaTokens.
    * @param formula                         Formula to parse.
    * @param parse                           The workbook in which the formula was found.
-   * @param sheet                           Sheet number of the formula.
+   * @param cell TODO
    * @return                                A FormulaToken which represents the top-level function
    *                                          of the formula and contains all interior FormulaTokens.
    * @throws FormulaParseException          If Apache POI can't properly parse the formula.
@@ -46,7 +62,7 @@ public class Parser {
    * @throws UnsupportedOperationException  If the formula is blank or has quotes after exclamation
    *                                          ( !' ), which I saw in a few and it couldn't parse.
    */
[…]

### 2016-03-18 src/scripts/filesAndDB/FindBetterFormulas.java

@@ -21,7 +21,7 @@ public class FindBetterFormulas {
 
   public static void main(String[] args) throws Exception {
     File dir = new File(SSDIRECTORY);
-    FormulaToken.dontReplace();
+    Parser.dontReplace();
     
     if (!dir.isDirectory()) {
       System.err.println("SSDirectory is not a directory!");
@@ -70,7 +70,7 @@ public class FindBetterFormulas {
               
               System.out.println(formula);
               
-              System.out.println(POIUtils.toR1C1String(formula, cell.getRowIndex(), cell.getColumnIndex()));
+              //System.out.println(POIUtils.toR1C1String(formula, cell.getRowIndex(), cell.getColumnIndex()));
            
               System.out.println(">>> " + formula);
               System.out.println();

### 2016-03-18 src/scripts/filesAndDB/ReduceR1C1.java

@@ -8,57 +8,51 @@ import java.util.HashMap;
 
 import org.apache.poi.ss.util.CellReference;
 
+import com.mysql.jdbc.MysqlDataTruncation;
+
+import core.FormulaToken;
+import core.Parser;
 import utils.DBUtils;
 import utils.POIUtils;
 
 public class ReduceR1C1 { 
   public static void main(String[] args) throws SQLException {
     Connection con = DBUtils.connectToDatabase();
-    PreparedStatement insert = con.prepareStatement("INSERT INTO formulas_unique "
-        + "(id, formula, src, file, sheet, sheetName, row, col, usedNames, freq) "
-        + "VALUES (?, ?, 'ENRON', ?, ?, ?, ?, ?, ?, 0);");
-    PreparedStatement update = con.prepareStatement("UPDATE formulas_unique SET freq = ? WHERE id = ?;");
+    PreparedStatement insert = con.prepareStatement("INSERT INTO formulas_r1c1 "
+        + "(id, formula) VALUES (?, ?);");
     PreparedStatement get = con.prepareStatement("SELECT * FROM formulas WHERE file = ? and sheet = ? ORDER BY row, col;");
-    ResultSet files = con.createStatement().executeQuery("SELECT DISTINCT file, sheet FROM formulas;");
+    ResultSet files = con.createStatement().executeQuery("SELECT DISTINCT file, sheet FROM formulas WHERE id > 10363645;");
     
+    Parser.goRelative();
     while (files.next()) {
       String file = files.getString(1);   get.setString(1, file);
       int sheet = files.getInt(2);        get.setInt(2, sheet);
-      
-      HashMap<String, Integer> seenFreqs = new HashMap<String, Integer>();
-      HashMap<String, Integer> seenIds = new HashMap<String, Integer>();
+
       ResultSet formulas = get.executeQuery();
       while (formulas.next()) {
         int id = formulas.getInt(1);
-        String formula = formulas.getString(2);
-        String sheetName = formulas.getString(6);
-        int row = formulas.getInt(7);
-        String c = formulas.getString(8);
-        int col = CellReference.convertColStringToIndex(c);
-        boolean usedNames = formulas.getBoolean(9);
+        if (id <= 10363645) continue;
         
-        String r1c1 = POIUtils.toR1C1String(formula, row, col);
-        //System.out.println(r1c1);
-        if (seenFreqs.containsKey(r1c1)) {
[…]

### 2016-03-18 src/scripts/filesAndDB/ReplaceNames.java

@@ -23,7 +23,7 @@ public class ReplaceNames {
   private static PreparedStatement update;
   
   public static void main(String[] args) throws Throwable {
-    FormulaToken.dontReplace();
+    Parser.dontReplace();
     Connection con = DBUtils.connectToDatabase();
     update = con.prepareStatement("UPDATE formulas SET formula = ?, usedNames = 1 WHERE id = ?;");
     Statement s1 = con.createStatement(), s2 = con.createStatement();

### 2016-03-18 src/scripts/trees/IFTree.java

@@ -68,7 +68,7 @@ public class IFTree {
     
     BufferedWriter write = new BufferedWriter(new FileWriter("./src/viz/iftree.json"));
     write.write(gson.toJson(sum));
-    System.out.println(gson.toJson(sum));
+    //System.out.println(gson.toJson(sum));
     write.close();
 
   }

### 2016-03-18 src/tests/AllTests.java

@@ -11,6 +11,7 @@ import org.junit.runners.Parameterized;
 import org.junit.runners.Parameterized.Parameters;
 
 import core.FormulaToken;
+import core.Parser;
 import utils.TestUtils;
 
 //http://stackoverflow.com/questions/358802/junit-test-with-dynamic-number-of-tests
@@ -41,7 +42,7 @@ public class AllTests {
   
   @Before
   public void setUp() {
-    FormulaToken.dontReplace();
+    Parser.dontReplace();
   }
   
   @Test

### 2016-03-18 src/tests/BlankTests.java

@@ -48,7 +48,7 @@ public class BlankTests {
   
   @Before
   public void setUp() {
-    FormulaToken.dontReplace();
+    Parser.dontReplace();
   }
   
   @Test

### 2016-03-18 src/tests/SheetTests.java

@@ -4,12 +4,13 @@ import org.junit.Before;
 import org.junit.Test;
 
 import core.FormulaToken;
+import core.Parser;
 import utils.TestUtils;
 
 public class SheetTests {
   @Before
   public void setUp() {
-    FormulaToken.dontReplace();
+    Parser.dontReplace();
   }
 
   @Test

### 2016-03-18 src/tests/SingleTests.java

@@ -1,6 +1,6 @@
 package tests;
 
-import static org.junit.Assert.fail;
+import static org.junit.Assert.*;
 
 import org.apache.poi.ss.formula.FormulaParseException;
 import org.apache.poi.xssf.usermodel.XSSFEvaluationWorkbook;
@@ -16,7 +16,7 @@ import utils.TestUtils;
 public class SingleTests {
   @Before
   public void setUp() {
-    FormulaToken.dontReplace();
+    Parser.dontReplace();
   }
   
 
@@ -283,6 +283,54 @@ public class SingleTests {
   public void test_21_coloninsheetname() {
     String formula = "SUM('111678 (0013):111706 (0238)'!E62:E62)";
     singleSuccessTest(formula);
+  }
+  
+  @Test
+  public void test_23_r1c1_1() {
+    Parser.goRelative();
+    assertEquals("R[25]C[2]", Parser.parseFormula("B25").toString());
+  }
+  
+  @Test
+  public void test_24_r1c1_2() {
+    Parser.goRelative();
+    assertEquals("A1xC5xE9!R[25]C[2]", Parser.parseFormula("A1xC5xE9!B25").toString());
+  }
+  
+  @Test
+  public void test_25_r1c1_3() {
+    Parser.goRelative();
+    assertEquals("A1xC5xE9!R[25]C[2]", Parser.parseFormula("'A1xC5xE9'!B25").toString());
+  }
+  
+  @Test
+  public void test_26_r1c1_4() {
+    Parser.goRelative();
+    assertEquals("R[25]C[2]:R[26]C[2]", Parser.parseFormula("B25:B26").toString());
+  }
+  
+  @Test
+  public void test_27_r1c1_5() {
+    Parser.goRelative();
+    assertEquals("A1xC5xE9!R[25]C[2]:Sheet!R[26]C[2]", Parser.parseFormula("A1xC5xE9!B25:Sheet!B26").toString());
+  }
+  
+  @Test
+  public void test_28_r1c1_6() {
+    Parser.goRelative();
+    assertEquals("Sheet!R[25]C[2]:A1xC5xE9!R[26]C[2]", Parser.parseFormula("'Sheet'!B25:'A1xC5xE9'!B26").toString());
+  }
+  
+  @Test
+  public void test_29_r1c1_7() {
+    Parser.goRelative();
[…]

### 2016-03-18 src/utils/POIUtils.java

@@ -88,39 +88,4 @@ public class POIUtils {
     EvaluationName eval = ((FormulaParsingWorkbook) render).getName(nameStr, sheet);
     return eval.getNameDefinition();
   }
-  
-  public static String toR1C1String(String formula, int row, int col) {
-    //TODO: This might match things in strings...but for my purposes, I don't think that
-    //      would change my results?
-    StringBuffer newFormula = new StringBuffer();
-    
-    Matcher match = Pattern.compile("\\$?[A-Z]+\\$?\\d+").matcher(formula);
-    while (match.find()) {
-      String orig = match.group();
-      String[] parts = orig.replaceAll("([A-Z])(\\$?\\d)", "$1 $2").split(" ");
-      
-      //if (!parts[0].startsWith("$")) {
-      String refCol = parts[0];
-      boolean absCol = refCol.startsWith("$");
-      if (absCol) 
-        refCol = refCol.replace("$", "");
-      int refColNum = CellReference.convertColStringToIndex(refCol);
-      refCol = absCol ? "C" + refColNum : "C[" + (refColNum - col) + "]";
-      
-      String refRow = parts[1];
-      boolean absRow = refRow.startsWith("$");
-      if (absRow) 
-        refRow = refRow.replace("$", "");
-      int refRowNum = Integer.parseInt(refRow);
-      refRow = absRow ? "R" + refRowNum : "R[" + (refRowNum - row) + "]";
-      
-      
-      String newRef = refRow + refCol;
-      //System.out.println(match.group() + " -> " + newRef + " (" + col + "," + row + ")");
-      match.appendReplacement(newFormula, newRef);      
-    }      
-    
-    match.appendTail(newFormula);
-    return newFormula.toString();
-  }
 }

### 2016-03-18 src/core/FormulaToken.java
Use existing class and not my own.

@@ -19,8 +19,6 @@ import org.apache.poi.ss.formula.ptg.RefPtgBase;
 import org.apache.poi.ss.formula.ptg.StringPtg;
 import org.apache.poi.ss.util.CellReference;
 
-import core.Parser.CellContext;
-
 public class FormulaToken {
   protected static Mode mode = Mode.REPLACE;
   protected String tokenStr;
@@ -63,10 +61,10 @@ public class FormulaToken {
    *              token and thus have no arguments.
    */
   public FormulaToken(Ptg tok) {
-    this(tok, new CellContext(0,0,0));
+    this(tok, new CellReference(0,0));
   }
 
-  public FormulaToken(Ptg tok, CellContext cell) {
+  public FormulaToken(Ptg tok, CellReference cellReference) {
     this.token = tok;
     
     switch (mode) {
@@ -75,7 +73,7 @@ public class FormulaToken {
       case REPLACE:
         this.tokenStr = getTypeString(tok);               break;
       case R1C1:
-        this.tokenStr = toR1C1String(tok.toFormulaString().trim(), cell);
+        this.tokenStr = toR1C1String(tok.toFormulaString().trim(), cellReference);
         break;      
     }
   }
@@ -125,8 +123,8 @@ public class FormulaToken {
   private static String refPattern = "(?!\\d)\\$?[A-Z]+\\$?\\d+(?![a-zA-Z!])",
                         followedByEvenNumOfQuotes = "(?=([^']*'[^']*')*[^']*$)";
   private static Matcher match = Pattern.compile(refPattern+followedByEvenNumOfQuotes).matcher("");
-  public static String toR1C1String(String formula, CellContext cell) {
-    int row = cell.getRow() + 1, col = cell.getCol() + 1; //When using POI, cell A1 is 0,0. We need to offset by one.
+  public static String toR1C1String(String formula, CellReference cell) {
+    int row = cell.getRow(), col = cell.getCol();
     StringBuffer newFormula = new StringBuffer();
     
     match.reset(formula);

### 2016-03-18 src/core/FunctionNode.java

@@ -11,7 +11,7 @@ public class FunctionNode extends Node {
   @Expose
   private String function;  
   
-  @Expose
+  //@Expose
   private Map<Integer, QuantityOfArgumentsNode> specific_quantities = null;
   
   private Map<Integer, ArgumentNode> all_quantities = new LinkedHashMap<Integer, ArgumentNode>();

### 2016-03-18 src/core/Parser.java

@@ -17,6 +17,7 @@ import org.apache.poi.ss.formula.ptg.OperationPtg;
 import org.apache.poi.ss.formula.ptg.ParenthesisPtg;
 import org.apache.poi.ss.formula.ptg.Ptg;
 import org.apache.poi.ss.usermodel.Cell;
+import org.apache.poi.ss.util.CellReference;
 import org.apache.poi.xssf.usermodel.XSSFEvaluationWorkbook;
 
 import utils.POIUtils;
@@ -32,22 +33,22 @@ public class Parser {
    */
   public static FormulaToken parseFormula(String formula) 
       throws FormulaParseException, UnsupportedOperationException {
-    return parseFormula(formula, BLANK, new CellContext(0, 0, 0));
+    return parseFormula(formula, BLANK, 0, new CellReference(0, 0));
   }
   
   public static FormulaToken parseFormula(String formula, FormulaParsingWorkbook parse, int sheet)
       throws FormulaParseException, UnsupportedOperationException {
-    return parseFormula(formula, parse, new CellContext(sheet, 0, 0));
+    return parseFormula(formula, parse, sheet, new CellReference(0, 0));
   }
   
   public static FormulaToken parseFormula(String formula, int row, int col) 
       throws FormulaParseException, UnsupportedOperationException {
-    return parseFormula(formula, BLANK, new CellContext(0, row, col));
+    return parseFormula(formula, BLANK, 0, new CellReference(row, col));
   }
   
   public static FormulaToken parseFormula(Cell cell, FormulaParsingWorkbook parse, int sheet)
       throws FormulaParseException, UnsupportedOperationException {
-    return parseFormula(cell.getCellFormula(), parse, new CellContext(sheet, cell.getRowIndex(), cell.getColumnIndex()));    
+    return parseFormula(cell.getCellFormula(), parse, sheet, new CellReference(cell));    
   }
 
   /**
@@ -62,7 +63,7 @@ public class Parser {
    * @throws UnsupportedOperationException  If the formula is blank or has quotes after exclamation
    *                                          ( !' ), which I saw in a few and it couldn't parse.
    */
-  public static FormulaToken parseFormula(String formula, FormulaParsingWorkbook parse, CellContext cell) 
+  public static FormulaToken parseFormula(String formula, FormulaParsingWorkbook parse, int sheet, CellReference cell) 
       throws FormulaParseException, UnsupportedOperationException {
     Ptg[] tokens = null;
[…]

### 2016-03-18 src/scripts/trees/AllTrees.java

@@ -25,7 +25,7 @@ public class AllTrees {
   public static void main(String[] args) throws SQLException, IOException {
     int limit = 100000, offset = 0, currentlyAt;
     Connection con = DBUtils.connectToDatabase();
-    PreparedStatement ps = con.prepareStatement("SELECT * FROM formulas_unique WHERE ID > ? LIMIT " + limit + ";");
+    PreparedStatement ps = con.prepareStatement("SELECT * FROM old_formulas_unique WHERE ID > ? LIMIT " + limit + ";");
     
     Map<String, FunctionNode> trees = new HashMap<String, FunctionNode>();
     do {
@@ -54,7 +54,9 @@ public class AllTrees {
           trees.put(toplevel, new FunctionNode(tree.toSimpleString()));
         trees.get(toplevel).add(id, tree);
         
-        System.out.println(currentlyAt + " : " + formula);        
+        //if (toplevel.equals("()"))
+        //    System.out.println();
+        //System.out.println(currentlyAt + " : " + formula);        
       }
       
       rs.previous();
@@ -76,10 +78,27 @@ public class AllTrees {
     builder.setPrettyPrinting().serializeNulls().excludeFieldsWithoutExposeAnnotation();
     Gson gson = builder.create();
     
-    BufferedWriter write = new BufferedWriter(new FileWriter("./src/viz/all.json"));
-    write.write(gson.toJson(allFuncs));
-    //System.out.println(gson.toJson(sum));
-    write.close();
-
+    ArrayList<String> list = new ArrayList<String>();
+    for (String func : allFuncs.keySet()) {
+      String fileFunc;
+      if (func.equals("/")) fileFunc="DIV";
+      else if (func.equals("*")) fileFunc="MUL";
+      else if (func.equals(" ")) fileFunc="SPACE";
+      else if (func.equals("()")) fileFunc="PAREN";
+      else if (func.equals("=")) fileFunc="EQUALS";
+      else if (func.equals("&")) fileFunc="AMP";
+      else fileFunc = func;
+      //else func = func.replace("()", "");
+      BufferedWriter write = new BufferedWriter(new FileWriter("./src/viz/json/j" + fileFunc + ".json"));
+      write.write(gson.toJson(allFuncs.get(func)));
+      write.close();
+      
+      list.add(fileFunc);
+    }
+    
+    Collections.sort(list);
[…]

### 2016-04-11 src/core/FormulaToken.java
R1C1 work from 10 April 2016 -- uses CellReference instead of regexes.

@@ -73,7 +73,7 @@ public class FormulaToken {
       case REPLACE:
         this.tokenStr = getTypeString(tok);               break;
       case R1C1:
-        this.tokenStr = toR1C1String(tok.toFormulaString().trim(), cellReference);
+        this.tokenStr = toR1C1String(tok, cellReference);
         break;      
     }
   }
@@ -117,44 +117,63 @@ public class FormulaToken {
     return type;
   }
   
-  //(?!\\d)\\$?[A-Z]+\\$?\\d+(?![a-zA-Z]) -> Capture all instance of a set of letters 
-  //  followed by a set of numbers. Can't be immediately preceded by another number or 
-  //  followed by another letter or an exclamation, as might be indicative in sheet names or strings.
-  private static String refPattern = "(?!\\d)\\$?[A-Z]+\\$?\\d+(?![a-zA-Z!])",
-                        followedByEvenNumOfQuotes = "(?=([^']*'[^']*')*[^']*$)";
-  private static Matcher match = Pattern.compile(refPattern+followedByEvenNumOfQuotes).matcher("");
-  public static String toR1C1String(String formula, CellReference cell) {
-    int row = cell.getRow(), col = cell.getCol();
-    StringBuffer newFormula = new StringBuffer();
+  public String toR1C1String(Ptg tok, CellReference cell) {
+    String original = tok.toFormulaString(),
+           relative = "";
     
-    match.reset(formula);
-    while (match.find()) {
-      String orig = match.group();
-      String[] parts = orig.replaceAll("([A-Z])(\\$?\\d)", "$1 $2").split(" ");
+    if (tok instanceof AreaPtgBase) {
+      AreaPtgBase area = (AreaPtgBase) tok;
+      int firstRow = area.getFirstRow(),
+          firstCol = area.getFirstColumn(); //Plus 1 because POI offsets by one.
+      boolean firstRowRel = area.isFirstRowRelative(),
+              firstColRel = area.isFirstColRelative();
+      String firstRef = convertToR1C1(firstRow, firstRowRel, firstCol, firstColRel, cell),
+             originalFirst = (firstColRel?"":"$") + CellReference.convertNumToColString(firstCol)
+                            +(firstRowRel?"":"$") + (firstRow + 1);
       
-      //if (!parts[0].startsWith("$")) {
-      String refCol = parts[0];
-      boolean absCol = refCol.startsWith("$");
-      if (absCol) 
-        refCol = refCol.replace("$", "");
[…]

### 2016-04-11 src/scripts/filesAndDB/r1c1/ReduceR1C1.java

@@ -1,4 +1,4 @@
-package scripts.filesAndDB;
+package scripts.filesAndDB.r1c1;
 
 import java.sql.Connection;
 import java.sql.PreparedStatement;
@@ -21,7 +21,7 @@ public class ReduceR1C1 {
     PreparedStatement insert = con.prepareStatement("INSERT INTO formulas_r1c1 "
         + "(id, formula) VALUES (?, ?);");
     PreparedStatement get = con.prepareStatement("SELECT * FROM formulas WHERE file = ? and sheet = ? ORDER BY row, col;");
-    ResultSet files = con.createStatement().executeQuery("SELECT DISTINCT file, sheet FROM formulas WHERE id > 10363645;");
+    ResultSet files = con.createStatement().executeQuery("SELECT DISTINCT file, sheet FROM formulas;");
     
     Parser.goRelative();
     while (files.next()) {
@@ -30,9 +30,7 @@ public class ReduceR1C1 {
 
       ResultSet formulas = get.executeQuery();
       while (formulas.next()) {
-        int id = formulas.getInt(1);
-        if (id <= 10363645) continue;
-        
+        int id = formulas.getInt(1);        
         String formula = formulas.getString(2);
         int row = formulas.getInt(7), col = CellReference.convertColStringToIndex(formulas.getString(8));
                 
@@ -40,6 +38,7 @@ public class ReduceR1C1 {
         try {          
           newFormula = Parser.parseFormula(formula, row, col).toString();
         } catch (UnsupportedOperationException e) {
+          System.err.println(e.getMessage());
           System.err.println(id + " : " + formula);
           newFormula = "error";
         }

### 2016-04-12 doc/paper.tex
R1C1 - fixing :/! in quotes bug.

@@
 \section{Case Study}
+The obvious question to pose to any visualization is this: Why does it matter that we see this way?
+In other words, it is not enough to prove that something can be visualized; instead we must also demonstrate what we can be gained from any particular visualization.
+As such, we raised a few tasks in the introduction in which we thought the tool could help: identifying places for API improvement, detecting bad smells or common programmer misunderstanding, and guiding spreadsheet education.
+Thus, to demonstrate the tool's applicability, we sought out places in the tree which best exemplify these respective concerns.
 
-[to be filled in]
+\subsection{Bad Smells}
+Fowler's (?) seminal description of code smells underscored
+an important point of code quality: between perfect code and 
+bug-crippled spaghetti,  there is a spectrum of code designs 
+which, by themselves, are not faulty but nevertheless may
+point to problems and vulnerabilities in how code is written.
+Code smells, as we call them, soon commanded attention and earned wide-ranging 
+applicability, eventually making it to the art of spreadsheet design.
+Since then, Hermans and others catalog the odors of spreadsheets, 
+often built off Fowler's (?) original specifications to articulate
+the subtle problems in spreadsheet design. \par 
+Collected, some of the intra-spreadsheet smells fall well within the
+purview of this visualization tool. Some such smells can be found
+in a figure [FIGURE]. \par 
+The smells described above, then, entail a corresponding structure
+visible in the visualization: the deeper a branch runs, or the
+taller the range of arguments, the more it emits the stench of suboptimal
+design. \par 
+To be sure, these rank occurrences must be leveraged with their prevalence
+across the dataset. One person's anomaly, though perhaps still interesting,
+will not be as impactful as a smell of thousands. \par
+Some examples are meaningful not for the space they take up but for how
+they clash with the expectations around a function. For example, Excel
+offers a number of functions that accept any number arguments given to 
+them, up to a resource-defined limit. SUM and CONCATENATE are two such functions:
+adding more arguments simply adds or appends that element in the same way
+as every previous argument. Strange cases were found, then, in the cases where
+these functions were used with only one argument. \par
+Hermans, in her paper on the nuances of VLOOKUP and its common misuses, explore
+the problem of the final, optional argument. A tool there helped, but how might
+a visualization such as this illuminated the same?
+
+\subsection{Education}
+Learning by example has long been a cornerstone of effective teacher techniques:
+by showing the student a concrete example of something, rather than dwelling in
+the realm of abstract description, comprehension increases [I'm sure there's a cite
+out there somewhere.] This is no different in software, where every explanation of
+a tricky programming concept is much untangled by the illustrative stub. Even APIs,
+researchers have found, by the inclusion of an in-practice example of the function
+described. Spreadsheet programming, then, should not be essentially different: 
+examples of spreadsheet functions in use
+
+\section{Limitations}
 

### 2016-04-12 src/core/FormulaToken.java

@@ -1,19 +1,13 @@
 package core;
 
-import java.util.regex.Matcher;
-import java.util.regex.Pattern;
-
 import org.apache.poi.ss.formula.EvaluationName;
 import org.apache.poi.ss.formula.FormulaParsingWorkbook;
 import org.apache.poi.ss.formula.FormulaRenderingWorkbook;
-import org.apache.poi.ss.formula.ptg.Area2DPtgBase;
-import org.apache.poi.ss.formula.ptg.Area3DPxg;
 import org.apache.poi.ss.formula.ptg.AreaPtgBase;
 import org.apache.poi.ss.formula.ptg.BoolPtg;
 import org.apache.poi.ss.formula.ptg.IntPtg;
 import org.apache.poi.ss.formula.ptg.NamePtg;
 import org.apache.poi.ss.formula.ptg.NumberPtg;
-import org.apache.poi.ss.formula.ptg.OperandPtg;
 import org.apache.poi.ss.formula.ptg.Ptg;
 import org.apache.poi.ss.formula.ptg.RefPtgBase;
 import org.apache.poi.ss.formula.ptg.StringPtg;
@@ -117,42 +111,50 @@ public class FormulaToken {
     return type;
   }
   
-  public String toR1C1String(Ptg tok, CellReference cell) {
+  private String toR1C1String(Ptg tok, CellReference cell) {
     String original = tok.toFormulaString(),
            relative = "";
     
     if (tok instanceof AreaPtgBase) {
+      String[] limits = original.split(":");
+      if (limits.length > 2) {
+        try { limits = findHalves(limits, ':'); } 
+        catch (UnsupportedOperationException e) {
+          throw new UnsupportedOperationException(e.getMessage() + ": " + original);
+        }
+      } else if (limits.length == 1) //TODO
+        throw new UnsupportedOperationException("Not a proper area (no colon): " + original);   
+      
+      String first = limits[0], last = limits[1];
+      
       AreaPtgBase area = (AreaPtgBase) tok;
       int firstRow = area.getFirstRow(),
-          firstCol = area.getFirstColumn(); //Plus 1 because POI offsets by one.
+          firstCol = area.getFirstColumn(); 
       boolean firstRowRel = area.isFirstRowRelative(),
               firstColRel = area.isFirstColRelative();
       String firstRef = convertToR1C1(firstRow, firstRowRel, firstCol, firstColRel, cell),
[…]

### 2016-04-12 src/tests/SingleTests.java

@@ -288,49 +288,63 @@ public class SingleTests {
   @Test
   public void test_23_r1c1_1() {
     Parser.goRelative();
-    assertEquals("R[25]C[2]", Parser.parseFormula("B25").toString());
+    assertEquals("R[24]C[1]", Parser.parseFormula("B25").toString());
   }
   
   @Test
   public void test_24_r1c1_2() {
     Parser.goRelative();
-    assertEquals("A1xC5xE9!R[25]C[2]", Parser.parseFormula("A1xC5xE9!B25").toString());
+    assertEquals("A1xC5xE9!R[24]C[1]", Parser.parseFormula("A1xC5xE9!B25").toString());
   }
   
   @Test
   public void test_25_r1c1_3() {
     Parser.goRelative();
-    assertEquals("A1xC5xE9!R[25]C[2]", Parser.parseFormula("'A1xC5xE9'!B25").toString());
+    assertEquals("A1xC5xE9!R[24]C[1]", Parser.parseFormula("'A1xC5xE9'!B25").toString());
   }
   
   @Test
   public void test_26_r1c1_4() {
     Parser.goRelative();
-    assertEquals("R[25]C[2]:R[26]C[2]", Parser.parseFormula("B25:B26").toString());
+    assertEquals("R[24]C[1]:R[25]C[1]", Parser.parseFormula("B25:B26").toString());
   }
   
   @Test
   public void test_27_r1c1_5() {
     Parser.goRelative();
-    assertEquals("A1xC5xE9!R[25]C[2]:Sheet!R[26]C[2]", Parser.parseFormula("A1xC5xE9!B25:Sheet!B26").toString());
+    assertEquals("A1xC5xE9!R[24]C[1]:Sheet!R[25]C[1]", Parser.parseFormula("A1xC5xE9!B25:Sheet!B26").toString());
   }
   
   @Test
   public void test_28_r1c1_6() {
     Parser.goRelative();
-    assertEquals("Sheet!R[25]C[2]:A1xC5xE9!R[26]C[2]", Parser.parseFormula("'Sheet'!B25:'A1xC5xE9'!B26").toString());
[…]

### 2016-04-12 src/viz/treeMaker.js
Relative frequency. Fixes #15.

@@ -140,6 +140,7 @@ function collapse(d) {
 
         d._children = d.children;
         d._children.forEach(collapse);
+        d._children.forEach(function(c) { c.parent = d; });
         d.children = null;
 
         //Sorts arguments by frequency, leaves only the first 10 and hides
@@ -193,6 +194,9 @@ var i = 0;
 var interfunc_gap = 125, //times two, technically; must work with gradient regularity
     func_arg_gap = 75;
 
+/**
+ * Central function; updates what the graph looks like when the nodes change.
+ */
 function update(src) {
     var nodes = tree.nodes(root),
         links = tree.links(nodes);
@@ -271,9 +275,37 @@ function enterNode(node, src) {
         .on("mouseleave", rect_mouseout);
     expand.on("click", expandclick);
 
-    enterCircle(circles);
-    enterRect(rects);
+    //ENTER CIRCLES//////////////////////////////////////////
+    circles.append("circle")
+        .attr("r", 1e-6);
 
+    circles.append("text")
+        .attr("dx", function(d) {
+            return -scale(d.frequency) - 2;
+        })
+        .attr("dy", 3)
+        .attr("text-anchor", "end")
+        .text(function(d) {
+            return d.function;
+        });
+
+    //ENTER RECTANGLES////////////////////////////////////////
+    rects.append("rect")
+        .attr("width", 1e-6)
+        .attr("height", 1e-6)
+        .attr("x", -square_side_half)
+        .attr("y", -square_side_half);
+
+    rects.append("text")
+        .text(function(d) {
+            return d.position + 1;
+        })
+        .attr("dx", function(d) {
+            return d.position + 1 > 9 ? -7 : -3;
+        })
+        .attr("dy", 5);
+
+    //ENTER EXPAND NODES//////////////////////////////////////
     expand.append("polygon")
         .attr("height", "20")
         .attr("width", "20")
@@ -288,24 +320,6 @@ function enterNode(node, src) {
             d3.select("#n" + d.id).select("polygon")
                 .style("fill", expand_col);
         })
-}
-
-/**
- * Creates the new function nodes.
- */
-function enterCircle(circles) {
-    circles.append("circle")
-        .attr("r", 1e-6);
-
-    circles.append("text")
-        .attr("dx", function(d) {
-            return -scale(d.frequency) - 2;
-        })
-        .attr("dy", 3)
[…]

### 2016-04-13 src/viz/treeMaker.js
Draft of depth encoding.

@@ -120,13 +120,17 @@ d3.json(src, function(error, json) {
     root = json;
     root.x0 = 0;
     root.y0 = 0;
+    root.max_depth = 0;
 
     scale = d3.scale.log()
         .domain([1, root.frequency])
         .range([3, 20])
         .nice();
 
-    root.children.forEach(collapse);
+    root.children.forEach(function(c) {
+        var other_depth = collapse(c);
+        root.max_depth = Math.max(other_depth, root.max_depth);
+    });
     initQuantities(root);
     center(root);
     update(root);
@@ -135,17 +139,22 @@ d3.json(src, function(error, json) {
 function collapse(d) {
     if (d.children && d.children.length > 0) {
         //For when they have optional arguments.
-        if (d.position == null) //If it is a function node and not an argument node...
+        if (isFunction(d)) //If it is a function node and not an argument node...
             initQuantities(d);
 
         d._children = d.children;
-        d._children.forEach(collapse);
-        d._children.forEach(function(c) { c.parent = d; });
         d.children = null;
+
+        d.max_depth = 0;
+        d._children.forEach(function(c) {
+            c.parent = d;
+            var new_possible_max = collapse(c) + (isFunction(d) ? 0 : 1);
+            d.max_depth = Math.max(new_possible_max, d.max_depth);
+        });
 
         //Sorts arguments by frequency, leaves only the first 10 and hides
         //the rest.
-        if (d.position != null && d._children.length > 10) {
+        if (!isFunction(d) && d._children.length > 10) {
             d._children.sort(function(a, b) {
                 return b.frequency - a.frequency;
             });
@@ -158,8 +167,15 @@ function collapse(d) {
         }
     } else {
         d.children = null;
-        //d._children = null;
+        d.max_depth = 0;
     }
+
+    return d.max_depth; //Should have been set by parent.
+}
+
+//If the function does not have a position value set, then it is an argument node.
+function isFunction(d) {
+    return d.position == null;
 }
 
 //TODO: This conversion from string to int is kludgy; normalize.
@@ -345,8 +361,10 @@ function mouseover(d) {
         ii = "</i>",
         br = "<br/>",
         func = "func: " + b + d.function+bb + br,
-        freq = "count: " + d.frequency.toLocaleString() + " ("
[…]

### 2016-04-17 doc/paper.tex
Paper work.

@@
 \begin{abstract}
-Spreadsheet environments often come equipped with a plethora of functions to manipulate and calculate data, but it can be difficult to understand how end-users employ these functions in practice.
-Without this knowledge, both researchers and practitioners lack information about how end users construct sophisticated programs from these basic elements.
-We developed a tool that visualizes patterns of how functions are combined into formulae within Excel spreadsheets.
-Using the Enron spreadsheet dataset as an example, this paper shows how the tool can display both common and anomalous formulas and their respective contexts in an actual workbook.
+	Spreadsheet environments often come equipped with an abundance of functions and operations to manipulate data, but it can be difficult to understand how programmers actually use these in practice.
+Furthermore, users can combine several functions into a complex formula, complicating matters for both researchers and practitioners who want to study formulae to improve spreadsheet practices.
+Therefore, we developed a tool that visualizes patterns of function combination in spreadsheets as an interactive tree of possibilities.
+Using spreadsheets from the public spreadsheet corpora, we then apply to the tool to real datasets and demonstrate its ability to capture the most common and most anomalous patterns of function combination and their contexts in actual workbooks.
 \end{abstract}
 
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
 \section{Introduction}
-% no \IEEEPARstart
-Business and research alike owe their debts to spreadsheets, the table-based interface which empowers users to organize and manipulate huge bodies of data [citation for definition].
-Their allure is in their versatility: while the novice end user can work without a deep knowledge of programming, the expert can expedite their work with a variety of built-in operations, or functions.\footnote{https://support.office.com/en-us/article/Excel-functions-alphabetical-b3944572-255d-4efb-bb96-c6d90033e188} As such, it should be of little surprise when Scaffidi and colleagues estimated that by 2012, over 50 million U.S.
-workers could be using them, including the 25 million who would be writing programs out of the functions included \cite{scaffidi2005estimating}.\par
-
-Considering this ubiquity, it's crucial to get spreadsheets right.
-Our failures in their use can be ruinous, as in 2012 when the influential findings on economic growth were reversed by a selection error, among other horror stories.\footnote{http://www.eusprig.org/horror-stories.htm}
-
-Fortunately, the vanguards of spreadsheet research have assembled, organized, and released a number of spreadsheet corpora to inform work on how people actually use these tools in different contexts.
-Collections like EUSES \cite{fisher2005euses}, FUSE \cite{barik2015fuse}, and the Enron corpus \cite{hermans2015enron} have already enabled fruitful work across the field, such as detecting code smells in spreadsheets \cite{hermans2012detecting} \cite{cunha2012smellsheet}.
-\par
-
-A tool, then, which empowers users of many intentions to explore these datasets would be rife with potential.
-On a simple level, the tool could provide concrete statistics on which functions are used in practice most (or least) often, and what other functions that work in conjunction with them.
-These numbers, then, could inform future work done on intelligently recommending functions to users or generating new formulas from these patterns of function use.
-Spreadsheet APIs, likewise, could be augmented or pruned through the discovery of frequent combinations or anomalous use of functions.
-Furthermore, if the tool maintains the connection between patterns and the actual, it could serve as a boon to educators as well, guiding lesson plans to the most commonly employed functions and offering a bounty of instructive (and real) examples.\par
-This paper presents such a tool, informed by such varied sources, that visualizes not how people employ individual Excel functions but how they combine to make more sophisticated spreadsheet formulas.
+Business and research alike a lot to spreadsheets, the tabular interface that offers users a structured way to store
+and manipulate potentially huge bodies of data. Their allure is in their versatility: while the novice can still work 
+without a deep knowledge of programming, they can learn to expedite their work by building programs out of several available functions
+\cite{nardi1990spreadsheet}. As such, it should not be surprising that when Scaffidi and colleagues estimated that 
+over 50 million U.S. workers could be using them by 2012, with 25 million of them writing programs  \cite{scaffidi2005estimating}. \par
+Considering this ubiquity, it's crucial to understand how people are actually using spreadsheets. After all, failures
+in their practice can be ruinous, as demonstrated in EuSpRIG's many horror stories of spreadsheets gone wrong. In 
+2013, for example, they detail the influence of an economics paper on debt and national growth which shaped many 
+political initiates around it, only to discover that the spreadsheets used in the data analysis contained an error that
+reversed the findings. The other stories, likewise, do not augur well if shoddy spreadsheet practices persist
+\footnote{http://www.eusprig.org/horror-stories.htm}. \par 
+Fortunately, many spreadsheet researchers have assembled and released a number of spreadsheet corpora to inform work
+of how people actually use these tools. Collections like EUSES \cite{fisher2005euses}, FUSE \cite{barik2015fuse}, and
+the Enron corpus \cite{hermans2015enron} have already enabled fruitful work across the field. Hermans and colleagues,
+for example, used the EUSES corpus in 2011 to inform and evaluate their work on exploring code smells, or inelegant
+places in code that suggest the need for refactoring, between worksheets \cite{hermans2012detecting}. \par 
+A tool, then, that empowers users of any intention to explore these datasets would be rife with potential. On a simple
+level, the tool could provide concrete statistics on which functions are used in practice most (or least) often for a
+given dataset. Beyond this, though, it could also inform future work on recommending functions through an understanding
+of this patterns, or it could guide API improvement by suggesting functions to add or prune based how people actually
+use them. Furthermore, if the tool maintains the connection between its broad patterns and the actual instances of
+formulae in workbooks, it could serve as a boon to educators not only by showing which functions and combinations are
+most practical to learn but also by offering a bounty of instructive, and real, examples \par 
+This paper contributes a tool, informed by some of the aforementioned spreadsheet corpora, that seeks to accomplish these 
+tasks by offering an interactive interface for exploring how people combine functions. It seeks to balance several needs,
+such as capturing these patterns in a broad enough overview while still be specific enough lead back to the precise 
+places in spreadsheets where these patterns are realized. Along with the tool, then, is also a discussion of the various
+goals which the tool seeks to fulfill and the trade-offs that we negotiated at each point. All of this culminates in an
+evaluation of the tool through a study of possible cases to which the tool might apply.
 
@@
 \par
-Nevertheless, other studies and tools focus more on evaluating the content of the cells therein. (Hermans, Smellsheet) \par
-Other studies focus on API and built-in function use outside the domain of spreadsheets. [RESEARCH ON API STUDIES]
+Nevertheless, other studies and tools focus more on evaluating the content of the cells therein.
+Badame, for example, implements a number of Excel formula refactorings and uses Euses in part to evaluate it \cite{badame2012refactoring}.
+Hermans, leveraging her work with the aforementioned dataflow diagrams, approached the same dataset to assess the prevalence of common inter-worksheet smells, such as feature envy and inappropriate intimacy \cite{hermans2012detecting}.
+Cunha and colleagues, likewise, constructed and refined a catalogue of smells and implemented the SmellSheet Detective tool to detect bad smells in chosen spreadsheets \cite{cunha2012towards}, which Abreu and colleagues later extended to detect faults.
+\cite{abreu2014smelling}.\par
+Implicit in this study is an exploration of how users interact with the Excel API.
+Previous research, such as the first study on the Enron spreadsheet corpus \cite{hermans2015enron}, on how users employ certain functions or commands.
+Researchers have applied such questions to other contexts as well, such as Murphy and colleague's study into how Java developers use Eclipse and what commands they use most often \cite{murphy2006java}.
+Others focus on the documentation of the API itself: Robillard and DeLine, for example conducted a series of surveys and interviews to diagnose common problems with learning APIs, and they found that code examples, one of the focuses of this tool, is one of the most important aids to have in learning a new system \cite{robillard2011field}.
 
-\section{Approach}
-\subsection{Goals}
+\section{Approach/Methodology}
+\subsection{Walkthrough of Tool}
+Before discussing the minutiae of how the tool was developed, it will help first to give a basic example of how the
+tool can be used and how to interpret its symbols. One such example might be to find the answer to this question: \textit{
+	What kinds of functions do people use to define the condition in an IF function?} The final visualization is available
+in figure \ref{fig:fullpic}; however, to understand the interaction, we will start rather from the beginning. \par
+When the user first approaches the tree for a given top-level function -- that is, a function nested within none other -- only a few nodes are visible, as shown in figure \ref{fig:startpic}. \par
+
+\centerline{\includegraphics{start}}
+
+The visualization so far comprises two types of node: the circle, which represents a discrete function in the formula and is size according to its relative frequency (the top-level node, by definition, will be the largest); and the numbered squares, which represent the positions of arguments within its parent function.
+From this, we can infer that, of the times it was observed, IF can have at most three arguments passed into it, which corresponds with its specifications in the API.\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2} \par
+Knowing that it is the first argument which contains the conditionals, we click on the square labeled "1" to explore.
+To save space, when more than 10 unique arguments have been observed in any position, the tool displays only the first ten, with an option to display the rest.
+The results are shown below:
+
+\centerline{\includegraphics[width=.43\textwidth]{IFexpand}}
+
+As expected, we see that IF contains as its first argument a number of comparison operators, such as = and <=, and boolean-returning functions, like ISNA and AND, with simple equality being the most common and some use as ABS being the least seen of everything actually used.
+\par
+From here, we can further explore the common options among these functions.
+Clicking on the "=" node will yield two arguments, it being a binary operator, and expanding each of them will peer into the range of common values of equality comparison, which Figure \ref{fig:fullpic} shows.
+\par
+For both sides of the equal sign, the operator has certain types of arguments which predominate over the others: on the left side is most often a reference to another cell; on the right, a string or number literal, which makes sense for the case of confirming a value in another cell before assigning this one.
+Furthermore, if the concept is difficult to imagine is practice, a tooltip accompanies each function node in the tree, providing a concrete example of a function that uses this structure and where it can be found.
+If this single instance is not enough, then the user also has the option to double-click the individual function node, which will open up a new tab with a table of many more examples from dataset.
+
+\begin{figure*}[t]
+	\includegraphics[width = \textwidth]{IFargslabel}
+	\caption{A picture of the tool.}
+	\centering
+	\label{fig:fullpic}
+\end{figure*}
+
+\subsection{Design Goals}
 In visualizing the spreadsheet data, I outlined a few core goals for what the tool should accomplish:
@@
 	\item [!2] \textbf{Do not create new formulas.} This is essentially an exploratory tool, not a generative one. It should not produce any information other than new views of the original data. 
-	%TODO: I do have an idea which could actually do the below, but, eh, it would take
-	%TODO: a fair amount of time to implement.
 	\item [!3] \textbf{Do not visualize individual formulas.} Though there is room to explore the place of a single function in the group, the tool must design the core visualization around the entire body of data, not the other way around.
@@
 
-\subsection{Description}
-To show how this all came together and demonstrate the interface, we will use an example of a quick task: discovering what kind of conditions people use in IF statements.
-Considering only formulas in which the IF function itself is the top-level function (that is, not nested within another function), we will approach a tree that begins like this:
-
-\includegraphics{start}
-
-The visualization so far comprises two types of node: the circle, which represents a discrete function in the formula and is size according to its relative frequency (the top-level node, by definition, will be the largest); and the numbered squares, which represent the positions of arguments within its parent function.
-From this, we can infer that, of the times it was observed, IF can have at most three arguments passed into it, which corresponds with its specifications in the API.\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2} \par
-Knowing that it is the first argument which contains the conditionals, we click on the square labeled "1" to explore.
-To save space, when more than 10 unique arguments have been observed in any position, the tool displays only the first ten, with an option to display the rest.
-The results are shown below:
-
-\includegraphics[width=.43\textwidth]{IFexpand}
-
-As expected, we see that IF contains as its first argument a number of comparison operators, such as = and <=, and boolean-returning functions, like ISNA and AND, with simple equality being the most common and some use as ABS being the least seen of everything actually used.
-From here, we can further explore the common options among these functions.
-Clicking on the "=" node will yield two arguments, it being a binary operator, and expanding each of them will peer into the range of common values of equality comparison:
-
-\includegraphics[width = .43\textwidth]{IFargslabel}
-
-For both sides of the equal sign, the operator has certain types of arguments which predominate over the others: on the left side is most often a reference to another cell; on the right, a string or number literal, which makes sense for the case of confirming a value in another cell before assigning this one.
-Furthermore, if the concept is difficult to imagine is practice, a tooltip accompanies each function node in the tree, providing a concrete example of a function that uses this structure and where it can be found.
-
-\subsection{Design}
+\subsection{Design Decisions}
 Early in the process, we decided that the tree form would be a suitable fit to represent the parent-child or caller-callee relationships inherent in the data, given the composition of formulas as functions and their arguments (which could be yet more functions).
@@
 \par
-Guided by the goals in section A, we faced a number of decision points, which we describe below, before we arrived at the design shown above.
-
+Guided by the goals in section A, we faced a number of decision points, a sample of which we describe below, before we arrived at the design shown above.
 \begin{itemize}
-	\item [1a] \textit{Copied formulas}: Excel allows users to spread a formula over an area, repeating the same task in each cell with minor adjustments.
+	\item \textit{Copied formulas}: Excel allows users to spread a formula over an area, repeating the same task in each cell with minor adjustments.
 Without checking for this, the analysis may not reveal the functions most commonly used together but rather the formulas most often applied to large areas.
 To combat this, we converted formulas from their native A1 format to the relative R1C1, in which copied formulas should be identical, and reduced the records to unique R1C1 formulas per sheet.
-	\item [1b] \textit{Optional arguments}: How should the tool handle functions which accept a variable number of arguments?
+	\item \textit{Importance of depth}: When a function appears within another, should it be analyzed only as a nested function or would it also be valid to analyze the nested function on its own?  \par
+	For example, in the pictured IF function, we found that people often use another IF statement as the second or third arguments of the top-level IF.
+If we only consider functions exactly where they're found embedded in the formula, then information about the same function -- IF, in this case -- will be scattered across different trees with no way to aggregate them.
+If we record every instance of a function by ignoring their context -- that is, including an IF embedded within a SUM function in the same node as the top-level IF -- then the tool will represent some functions in multiple nodes to capture every possible level of nesting.
+Both approaches have benefits and drawbacks, and so we included both.
+	\item \textit{Pattern density}: How should the tool quantitatively order its elements: by a function's raw frequency or by the unity of patterns it leads to?
+For example, if SUM has for its first argument two possibilities, one which itself contains 1000 unique argument possibilities with 1 occurrence each (high frequency, low pattern density) and another seen with 2 argument possibilities of 100 occurrences each (low frequency, high pattern density), which would be more interesting to emphasize?
+The answer depends on the nuances of the questions, but for simplicity, I've shown the former.
+	\item \textit{Non-functions}: How should the tool represent everything in the formula that isn't a function: numbers, string literals, errors, references, etc?
+Since these don't accept arguments, they will adorn the tree as leaves, and their precise content won't affect the functions around them as long as their types are known.
+As such, in the visualization, all of these nodes are replaced and aggregated under their types and represented as empty white nodes.
+	\item \textit{Optional arguments}: How should the tool handle functions which accept a variable number of arguments?
 SUM, for example, can have anywhere from 1 to 255, and IF can accept either 2 or 3.
-\footnote{https://support.office.com/en-us/article/Excel-functions-by-category-5f91f4e9-7b42-46d2-9bd1-63f26a86c0eb} Without prior evidence, it's possible that spreadsheet programmers use different techniques for different numbers arguments.
+\footnote{https://support.office.com/en-us/article/Excel-functions-by-category-5f91f4e9-7b42-46d2-9bd1-63f26a86c0eb} Without prior evidence, it's possible that, when people use optional arguments, they use different kinds of types and functions for arguments versus the cases when they ignore optional arguments.
 To account for this, we separate and analyze the different quantities of arguments observed for each function; the tool, however, uses as default all of the options collapsed into a single representation.
@@
 
-\begin{itemize}
-	%TODO: A picture would go well here.
-	\item [2a] \textit{Importance of depth}: When a function appears within another, should it be analyzed only as a nested function or would it also be valid to analyze the nested function on its own?
-If the former, then information about the same function will be scattered across different trees with no way to aggregate them.
-If the latter, then the tool will analyze some functions multiple times to capture every possible level of nesting.
-Both approaches have benefits and drawbacks, and so we included both.
-	\item [2b] \textit{Pattern density}: How should the tool quantitatively order its elements: by a function's raw frequency or by the unity of patterns it leads to?
-For example, if SUM has for its first argument two possibilities, one which itself contains 1000 unique argument possibilities with 1 occurrence each (high frequency, low pattern density) and another seen with 2 argument possibilities of 100 occurrences each (low frequency, high pattern density), which would be more interesting to emphasize?
-The answer depends on the nuances of the questions, but for simplicity, I've shown the former.
-	\item [2c] \textit{Non-functions}: How should the tool represent everything in the formula that isn't a function: numbers, string literals, errors, references, etc?
-Since these don't accept arguments, they will adorn the tree as leaves, and their precise content won't affect the functions around them as long as their types are known.
-As such, in the visualization, all of these nodes are replaced and aggregated under their types.
-\end{itemize}
-
-\begin{itemize}
-	\item [3a] \textit{Suitable examples}: Goal 3 supports the inclusion of examples in the visualization as a way of tying pattern to example, but how should examples be chosen?
-For this, the simpler is the better, and we made the broad working assumption that shorter (by character length) functions are simpler, and thus chose the shortest available.
-	\item [3b] \textit{Spreadsheet connections}: Is it possible to contextualize these examples even better?
-Yes, by leading the user directly back to the originating spreadsheet.
-The tool hyperlinks each example, then, back to the file that contains it, providing sheet, row, and column numbers if it doesn't open directly there.
-\end{itemize}
-
-\subsection{Implementation}
+\subsection{Implementation Details}
 We can view the final visualization as the product of two discrete processes:
@@
 	\item \textit{Presentation}: The JSON files, meanwhile, feed into the presentation code, implemented in Javascript with much help from the visualization library D3\footnote{https://d3js.org/}.
+We chose D3 primarily for its accessibility: given the JSON, the visualization can be rather simply embedded into a webpage accessible through a browser.
 \end{itemize}
-When the presentation code displays the tree, it shows two types of nodes with different meanings: the circles represent a function that has been observed at that structural place, and hovering over these yields a tooltip with supplementary information and examples; and squares, which represent the argument positions for the function which is their parent.
-For example, if the IF function has been observed with three arguments, 3 squares will extend from it as children.
-Clicking on the square labeled '1' will yield more circles, all of which are functions or values that the tool observed as the first argument in an IF function; clicking on '2' will yield those possibilities in the second position; and so on.
+A demonstration of the tool can be found at [LINK HERE].
 
-\subsection{Limitations}
-Because the data collection depends on POI's formula parser, it affords no leeway or partial information from a formula; it either processes it perfectly or throws it out.
-As such, the visualization inhibits insight into anything with syntactical errors or third-party functions that can't be evaluated without additional tools.
-Note, however, that this does not include standard Excel errors like \#REF!
-and \#DIV/0, which the parser handles well.
-\par
-Many functions have an expected order of arguments, but some, like SUM and MATCH, can be reordered in various ways and maintain their value.
-However, the representation that this tool uses reinforces for all functions that the order is important, even in these exceptions.
-\par
-A larger and related problem is the loss of argument combination.
-In the example in section B, we saw how the tools conveys which arguments are used most often on each side of an equals sign, but it does not encode how these whether references were actually compared to strings and numbers the most or whether it corresponded more to all the arguments beneath those two
-
+\section{User Study}
+Midway through production, we conducted a brief, four-participant user study in order to gauge how well we were capturing the initial
+design goals. The study was, in general, a flexible and exploratory
+affair: rather than giving the users any specific tasks or pointed
+questions, we asked instead that they choose for themselves which trees to explore and report anything that they deemed interesting. 
+Specifically, given trees rooted in the Enron dataset and at least 20 to thirty minutes, the participants situated themselves within the persona 
+of a consultant asked to evaluate a company's spreadsheet practice, which could be arranged around questions like which functions on which the
+employees most depended, which sheets presented the most anomalous or dangerous designs, and so on.
+Interpretation of "spreadsheet practice" can certainly vary from participant to participant, but since we wanted a range of views and backgrounds despite the persona, we readily accepted
+this interpretive wiggle room. \par
+We clarified, furthermore, that these notes could be directed either at the quality of the data conveyed by the tool or at the tool's conveyance
+itself. Since the tool's philosophy was based in exploration, we
+decided that it would not have been appropriate to restrict what people
+were to look for, letting them find interesting stories of formula 
+construction for themselves. Additionally, either kind of comment -- on data or on tool -- would direct us back to the central evaluation; a user's
+silence, or lack of any interesting findings, would tacitly indicate that
+perhaps the tool does not convey information well enough. \par 
+Still, several limitations cropped up during the study that complicate
+the evaluation. For one thing, though the source of the data was not 
+explicitly stated at the outset of the session, several users studied the file names (unchanged as they were) to deduce its roots in finance, if not
+Enron itself. Because of these notorious connotations, then, some were
+inclined from this moment of discovery to orient their exploration around finance-related functions, potentially limiting their findings or perceived
+users for the tool -- though some also said that, without this essential 
+context, they could not have properly explored a dataset in the first place.
+Comments like these point out the trade-offs of unguided exploration, too: though it might not restrict them to a single purpose, it
+might, at the same time, not afford them any mindset at all with which to 
+interpret the data. Another potential problem is that the data which users
+explored was processed and created before we had fully completed the tool,
+meaning some of the counts and patterns in the trees were inaccurate. 
+However, we decided that this was not a pressing concern, being that we 
+were primarily with whether any interesting reports could be made at all, 
+not with whether these reports were 100\% accurate assessments of reality. \par
+Nevertheless, these user studies were a formative moment in evaluating
+the tool's performance, generating a number of directions or corrections
+in the process.
 \section{Case Study}
@@
 
-\section{Limitations}
+\subsection{Limitations}
+Because the data collection depends on POI's formula parser, it affords no leeway or partial information from a formula; it either processes it perfectly or throws it out.
+As such, the visualization inhibits insight into anything with syntactical errors or third-party functions that can't be evaluated without additional tools.
+Note, however, that this does not include standard Excel errors like \#REF!
+and \#DIV/0, which the parser handles well.
+\par
+Many functions have an expected order of arguments, but some, like SUM and MATCH, can be reordered in various ways and maintain their value.
+However, the representation that this tool uses reinforces for all functions that the order is important, even in these exceptions.
+\par
+A larger and related problem is the loss of argument combination.
+In the example in section B, we saw how the tools conveys which arguments are used most often on each side of an equals sign, but it does not encode how these whether references were actually compared to strings and numbers the most or whether it corresponded more to all the arguments beneath those two
 

### 2016-04-19 doc/paper.tex
More paper work -- user study.
Commit before big paper changes.

@@
 % *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% *** trigger bugs that do not appear when using other class files.       ***
+%                       ***
 % The testflow support page is at:
@@
 %
-\ifCLASSINFOpdf
-   \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-   \graphicspath{{pic/}}
-  % and their extensions so you won't have to specify these with
+\ifCLASSINFOpdf \usepackage[pdftex]{graphicx} \usepackage{wrapfig} % declare the
+% path(s) where your graphic files are
+\graphicspath{{pic/}} % and their extensions so you won't have to specify these
+% with
 % every instance of \includegraphics
-   \DeclareGraphicsExtensions{.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+\DeclareGraphicsExtensions{.png} \else % or other class option (dvipsone,
+% dvipdf, if not using dvips). graphicx
 % will default to the driver specified in the system graphics.cfg if no
@@
 
-\begin{document}
-\title{A Tool for Visualizing Patterns of Spreadsheet Function Combinations}
+\begin{document} \title{A Tool for Visualizing Patterns of Spreadsheet Function
+		Combinations}
 
@@
 	% affiliations
-\author{\IEEEauthorblockN{Justin A. Middleton}
-\IEEEauthorblockA{North Carolina State University\\
-Raleigh, North Carolina}}
+	\author{\IEEEauthorblockN{Justin A. Middleton} \IEEEauthorblockA{North Carolina
+			State University\\ Raleigh, North Carolina}}
 
@@
 	% in the abstract
-\begin{abstract}
-	Spreadsheet environments often come equipped with an abundance of functions and operations to manipulate data, but it can be difficult to understand how programmers actually use these in practice.
-Furthermore, users can combine several functions into a complex formula, complicating matters for both researchers and practitioners who want to study formulae to improve spreadsheet practices.
-Therefore, we developed a tool that visualizes patterns of function combination in spreadsheets as an interactive tree of possibilities.
-Using spreadsheets from the public spreadsheet corpora, we then apply to the tool to real datasets and demonstrate its ability to capture the most common and most anomalous patterns of function combination and their contexts in actual workbooks.
-\end{abstract}
+	\begin{abstract} Spreadsheet environments often come equipped with an abundance
+		of functions and operations to manipulate data, but it can be difficult to
+		understand how programmers actually use these in practice. Furthermore, users
+		can combine several functions into a complex formula, complicating matters for
+		both researchers and practitioners who want to study formulae to improve
+		spreadsheet practices. Therefore, we developed a tool that visualizes patterns
+		of function combination in spreadsheets as an interactive tree of
+		possibilities. Using spreadsheets from the public spreadsheet corpora, we then
+		apply to the tool to real datasets and demonstrate its ability to capture the
+		most common and most anomalous patterns of function combination and their
+		contexts in actual workbooks. \end{abstract}
 
-\section{Introduction}
-Business and research alike a lot to spreadsheets, the tabular interface that offers users a structured way to store
-and manipulate potentially huge bodies of data. Their allure is in their versatility: while the novice can still work 
-without a deep knowledge of programming, they can learn to expedite their work by building programs out of several available functions
-\cite{nardi1990spreadsheet}. As such, it should not be surprising that when Scaffidi and colleagues estimated that 
-over 50 million U.S. workers could be using them by 2012, with 25 million of them writing programs  \cite{scaffidi2005estimating}. \par
-Considering this ubiquity, it's crucial to understand how people are actually using spreadsheets. After all, failures
-in their practice can be ruinous, as demonstrated in EuSpRIG's many horror stories of spreadsheets gone wrong. In 
-2013, for example, they detail the influence of an economics paper on debt and national growth which shaped many 
-political initiates around it, only to discover that the spreadsheets used in the data analysis contained an error that
-reversed the findings. The other stories, likewise, do not augur well if shoddy spreadsheet practices persist
-\footnote{http://www.eusprig.org/horror-stories.htm}. \par 
-Fortunately, many spreadsheet researchers have assembled and released a number of spreadsheet corpora to inform work
-of how people actually use these tools. Collections like EUSES \cite{fisher2005euses}, FUSE \cite{barik2015fuse}, and
-the Enron corpus \cite{hermans2015enron} have already enabled fruitful work across the field. Hermans and colleagues,
-for example, used the EUSES corpus in 2011 to inform and evaluate their work on exploring code smells, or inelegant
-places in code that suggest the need for refactoring, between worksheets \cite{hermans2012detecting}. \par 
-A tool, then, that empowers users of any intention to explore these datasets would be rife with potential. On a simple
-level, the tool could provide concrete statistics on which functions are used in practice most (or least) often for a
-given dataset. Beyond this, though, it could also inform future work on recommending functions through an understanding
-of this patterns, or it could guide API improvement by suggesting functions to add or prune based how people actually
-use them. Furthermore, if the tool maintains the connection between its broad patterns and the actual instances of
-formulae in workbooks, it could serve as a boon to educators not only by showing which functions and combinations are
-most practical to learn but also by offering a bounty of instructive, and real, examples \par 
-This paper contributes a tool, informed by some of the aforementioned spreadsheet corpora, that seeks to accomplish these 
-tasks by offering an interactive interface for exploring how people combine functions. It seeks to balance several needs,
-such as capturing these patterns in a broad enough overview while still be specific enough lead back to the precise 
-places in spreadsheets where these patterns are realized. Along with the tool, then, is also a discussion of the various
-goals which the tool seeks to fulfill and the trade-offs that we negotiated at each point. All of this culminates in an
-evaluation of the tool through a study of possible cases to which the tool might apply.
+	\section{Introduction} Business and research alike a lot to spreadsheets, the
+	tabular interface that offers users a structured way to store and manipulate
+	potentially huge bodies of data. Their allure is in their versatility: while
+	the novice can still work without a deep knowledge of programming, they can
+	learn to expedite their work by building programs out of several available
+	functions \cite{nardi1990spreadsheet}. As such, it should not be surprising
+	that when Scaffidi and colleagues estimated that over 50 million U.S. workers
+	could be using them by 2012, with 25 million of them writing programs 
+	\cite{scaffidi2005estimating}. \par Considering this ubiquity, it's crucial to
+	understand how people are actually using spreadsheets. After all, failures in
+	their practice can be ruinous, as demonstrated in EuSpRIG's many horror stories
+	of spreadsheets gone wrong. In 2013, for example, they detail the influence of
+	an economics paper on debt and national growth which shaped many political
+	initiates around it, only to discover that the spreadsheets used in the data
+	analysis contained an error that reversed the findings. The other stories,
+	likewise, do not augur well if shoddy spreadsheet practices persist
+	\footnote{http://www.eusprig.org/horror-stories.htm}. \par Fortunately, many
+	spreadsheet researchers have assembled and released a number of spreadsheet
+	corpora to inform work of how people actually use these tools. Collections like
+	EUSES \cite{fisher2005euses}, FUSE \cite{barik2015fuse}, and the Enron corpus
+	\cite{hermans2015enron} have already enabled fruitful work across the field.
+	Hermans and colleagues, for example, used the EUSES corpus in 2011 to inform
+	and evaluate their work on exploring code smells, or inelegant places in code
+	that suggest the need for refactoring, between worksheets
+	\cite{hermans2012detecting}. \par A tool, then, that empowers users of any
+	intention to explore these datasets would be rife with potential. On a simple
+	level, the tool could provide concrete statistics on which functions are used
+	in practice most (or least) often for a given dataset. Beyond this, though, it
+	could also inform future work on recommending functions through an
+	understanding of this patterns, or it could guide API improvement by suggesting
+	functions to add or prune based how people actually use them. Furthermore, if
+	the tool maintains the connection between its broad patterns and the actual
+	instances of formulae in workbooks, it could serve as a boon to educators not
+	only by showing which functions and combinations are most practical to learn
+	but also by offering a bounty of instructive, and real, examples \par This
+	paper contributes a tool, informed by some of the aforementioned spreadsheet
+	corpora, that seeks to accomplish these tasks by offering an interactive
+	interface for exploring how people combine functions. It seeks to balance
+	several needs, such as capturing these patterns in a broad enough overview
+	while still be specific enough lead back to the precise places in spreadsheets
+	where these patterns are realized. Along with the tool, then, is also a
+	discussion of the various goals which the tool seeks to fulfill and the
+	trade-offs that we negotiated at each point. All of this culminates in an
+	evaluation of the tool through a study of possible cases to which the tool
+	might apply.
 
-\section{Related Work}
-This tool comes from a line of spreadsheet visualization tools before it, each with a different focus.
-Some tools, such as Igarashi and colleague's fluid visualizations \cite{igarashi1998fluid}, seek to visualize the hidden formulas within a spreadsheet by imposing the dataflow graphs over the cells.
-Likewise, Clermont \cite{clermont2003scalable} (and Hipfl \cite{hipfl2008using}, who extended his work) explored various ways of visualizing groups of related cells through similar functions, neighbors, or references.
-Others focus on creating visualizations outside of the sheets: Hermans and colleagues address a spreadsheet programmer's information needs through their work on the tools GyroSAT \cite{hermans2011supporting} and Breviz \cite{hermans2011breviz} to make dataflow diagrams of individual spreadsheets.
-These, however, tend to focus on individual spreadsheets and not bodies of them.
-\par
-Nevertheless, other studies and tools focus more on evaluating the content of the cells therein.
-Badame, for example, implements a number of Excel formula refactorings and uses Euses in part to evaluate it \cite{badame2012refactoring}.
-Hermans, leveraging her work with the aforementioned dataflow diagrams, approached the same dataset to assess the prevalence of common inter-worksheet smells, such as feature envy and inappropriate intimacy \cite{hermans2012detecting}.
-Cunha and colleagues, likewise, constructed and refined a catalogue of smells and implemented the SmellSheet Detective tool to detect bad smells in chosen spreadsheets \cite{cunha2012towards}, which Abreu and colleagues later extended to detect faults.
-\cite{abreu2014smelling}.\par
-Implicit in this study is an exploration of how users interact with the Excel API.
-Previous research, such as the first study on the Enron spreadsheet corpus \cite{hermans2015enron}, on how users employ certain functions or commands.
-Researchers have applied such questions to other contexts as well, such as Murphy and colleague's study into how Java developers use Eclipse and what commands they use most often \cite{murphy2006java}.
-Others focus on the documentation of the API itself: Robillard and DeLine, for example conducted a series of surveys and interviews to diagnose common problems with learning APIs, and they found that code examples, one of the focuses of this tool, is one of the most important aids to have in learning a new system \cite{robillard2011field}.
+	\section{Related Work} This tool comes from a line of spreadsheet visualization
+	tools before it, each with a different focus. Some tools, such as Igarashi and
+	colleague's fluid visualizations \cite{igarashi1998fluid}, seek to visualize
+	the hidden formulas within a spreadsheet by imposing the dataflow graphs over
+	the cells. Likewise, Clermont \cite{clermont2003scalable} (and Hipfl
+	\cite{hipfl2008using}, who extended his work) explored various ways of
+	visualizing groups of related cells through similar functions, neighbors, or
+	references. Others focus on creating visualizations outside of the sheets:
+	Hermans and colleagues address a spreadsheet programmer's information needs
+	through their work on the tools GyroSAT \cite{hermans2011supporting} and Breviz
+	\cite{hermans2011breviz} to make dataflow diagrams of individual spreadsheets.
+	These, however, tend to focus on individual spreadsheets and not bodies of
+	them. \par Nevertheless, other studies and tools focus more on evaluating the
+	content of the cells therein. Badame, for example, implements a number of Excel
+	formula refactorings and uses Euses in part to evaluate it
+	\cite{badame2012refactoring}. Hermans, leveraging her work with the
+	aforementioned dataflow diagrams, approached the same dataset to assess the
+	prevalence of common inter-worksheet smells, such as feature envy and
+	inappropriate intimacy \cite{hermans2012detecting}. Cunha and colleagues,
+	likewise, constructed and refined a catalogue of smells and implemented the
+	SmellSheet Detective tool to detect bad smells in chosen spreadsheets
+	\cite{cunha2012towards}, which Abreu and colleagues later extended to detect
+	faults. \cite{abreu2014smelling}.\par Implicit in this study is an exploration
+	of how users interact with the Excel API. Previous research, such as the first
+	study on the Enron spreadsheet corpus \cite{hermans2015enron}, on how users
+	employ certain functions or commands. Researchers have applied such questions
+	to other contexts as well, such as Murphy and colleague's study into how Java
+	developers use Eclipse and what commands they use most often
+	\cite{murphy2006java}.  Others focus on the documentation of the API itself:
+	Robillard and DeLine, for example conducted a series of surveys and interviews
+	to diagnose common problems with learning APIs, and they found that code
+	examples, one of the focuses of this tool, is one of the most important aids to
+	have in learning a new system \cite{robillard2011field}.
 
-\section{Approach/Methodology}
-\subsection{Walkthrough of Tool}
-Before discussing the minutiae of how the tool was developed, it will help first to give a basic example of how the
-tool can be used and how to interpret its symbols. One such example might be to find the answer to this question: \textit{
-	What kinds of functions do people use to define the condition in an IF function?} The final visualization is available
-in figure \ref{fig:fullpic}; however, to understand the interaction, we will start rather from the beginning. \par
-When the user first approaches the tree for a given top-level function -- that is, a function nested within none other -- only a few nodes are visible, as shown in figure \ref{fig:startpic}. \par
+	\section{Approach/Methodology} \subsection{Walkthrough of Tool} Before
+	discussing the minutiae of how the tool was developed, it will help first to
+	give a basic example of how the tool can be used and how to interpret its
+	symbols. One such example might be to find the answer to this question:
+	\textit{ What kinds of functions do people use to define the condition in an IF
+		function?} The final visualization is available in figure \ref{fig:fullpic};
+	however, to understand the interaction, we will start rather from the
+	beginning. \par When the user first approaches the tree for a given top-level
+	function -- that is, a function nested within none other -- only a few nodes
+	are visible, as shown in figure \ref{fig:startpic}. \par
 
@@
 
-The visualization so far comprises two types of node: the circle, which represents a discrete function in the formula and is size according to its relative frequency (the top-level node, by definition, will be the largest); and the numbered squares, which represent the positions of arguments within its parent function.
-From this, we can infer that, of the times it was observed, IF can have at most three arguments passed into it, which corresponds with its specifications in the API.\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2} \par
-Knowing that it is the first argument which contains the conditionals, we click on the square labeled "1" to explore.
+	The visualization so far comprises two types of node: the circle, which
+	represents a discrete function in the formula and is size according to its
+	relative frequency (the top-level node, by definition, will be the largest);
+	and the numbered squares, which represent the positions of arguments within its
+	parent function. From this, we can infer that, of the times it was observed, IF
+	can have at most three arguments passed into it, which corresponds with its
+	specifications in the
+	API.\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2} \par Knowing that it is the first argument which contains the conditionals, we click on the square labeled "1" to explore.
 To save space, when more than 10 unique arguments have been observed in any position, the tool displays only the first ten, with an option to display the rest.
@@
 
-As expected, we see that IF contains as its first argument a number of comparison operators, such as = and <=, and boolean-returning functions, like ISNA and AND, with simple equality being the most common and some use as ABS being the least seen of everything actually used.
-\par
-From here, we can further explore the common options among these functions.
-Clicking on the "=" node will yield two arguments, it being a binary operator, and expanding each of them will peer into the range of common values of equality comparison, which Figure \ref{fig:fullpic} shows.
-\par
-For both sides of the equal sign, the operator has certain types of arguments which predominate over the others: on the left side is most often a reference to another cell; on the right, a string or number literal, which makes sense for the case of confirming a value in another cell before assigning this one.
-Furthermore, if the concept is difficult to imagine is practice, a tooltip accompanies each function node in the tree, providing a concrete example of a function that uses this structure and where it can be found.
-If this single instance is not enough, then the user also has the option to double-click the individual function node, which will open up a new tab with a table of many more examples from dataset.
+	As expected, we see that IF contains as its first argument a number of
+	comparison operators, such as = and <=, and boolean-returning functions, like
+	ISNA and AND, with simple equality being the most common and some use as ABS
+	being the least seen of everything actually used. \par From here, we can
+	further explore the common options among these functions. Clicking on the "="
+	node will yield two arguments, it being a binary operator, and expanding each
+	of them will peer into the range of common values of equality comparison, which
+	Figure \ref{fig:fullpic} shows. \par For both sides of the equal sign, the
+	operator has certain types of arguments which predominate over the others: on
+	the left side is most often a reference to another cell; on the right, a string
+	or number literal, which makes sense for the case of confirming a value in
+	another cell before assigning this one. Furthermore, if the concept is
+	difficult to imagine is practice, a tooltip accompanies each function node in
+	the tree, providing a concrete example of a function that uses this structure
+	and where it can be found. If this single instance is not enough, then the user
+	also has the option to double-click the individual function node, which will
+	open up a new tab with a table of many more examples from dataset.
 
-\begin{figure*}[t]
-	\includegraphics[width = \textwidth]{IFargslabel}
-	\caption{A picture of the tool.}
-	\centering
-	\label{fig:fullpic}
-\end{figure*}
+	\begin{figure*}[t] \includegraphics[width = \textwidth]{IFargslabel} \caption{A
+			picture of the tool.} \centering \label{fig:fullpic} \end{figure*}
 
-\subsection{Design Goals}
-In visualizing the spreadsheet data, I outlined a few core goals for what the tool should accomplish:
-\begin{itemize}
-	\item [1] \textbf{Draw an interactive interface to explore observed function combinations.} The combination space for all Excel functions is massive, let alone the space for observed formulas.
-Working from data with actual referents in practice, the tool must aid the user in navigating this space.
-	\item [2] \textbf{Emphasize the quantitative patterns in formula construction.} The tool, accommodating datasets of a few spreadsheets to millions, should address the questions of how often the end users employed a certain function and where they used it.
-In this way, it must show precise metrics, such as frequency of  use and depth of function nesting, of the dataset it conveys.
-	\item [3] \textbf{Promote a qualitative understanding of the patterns.} Lest these patterns remain abstract, the tool should supplement its observations with concrete instances of relevant formulas from the corpus.
-Ideally, it should even direct users to the exact cell in the spreadsheets where the formula was used, contextualizing the functions.
-\end{itemize} \par
-Likewise, to bound our scope, we outlined a few goals to specifically avoid accomplishing with this:
-\begin{itemize}
-	\item [!1] \textbf{Do not try to directly explain what a function does.} Though the tool tries to foster tries understanding by linking pattern to example, it won't provide a precise description of what a function accomplishes.
-The tool's user must infer this.
-	\item [!2] \textbf{Do not create new formulas.} This is essentially an exploratory tool, not a generative one. It should not produce any information other than new views of the original data. 
-	\item [!3] \textbf{Do not visualize individual formulas.} Though there is room to explore the place of a single function in the group, the tool must design the core visualization around the entire body of data, not the other way around.
-\end{itemize}
+	\subsection{Design Goals} In visualizing the spreadsheet data, I outlined a few
+	core goals for what the tool should accomplish: \begin{itemize} \item [1]
+		\textbf{Draw an interactive interface to explore observed function
+			combinations.} The combination space for all Excel functions is massive, let
+		alone the space for observed formulas. Working from data with actual referents
+		in practice, the tool must aid the user in navigating this space. \item [2]
+		\textbf{Emphasize the quantitative patterns in formula construction.} The tool,
+		accommodating datasets of a few spreadsheets to millions, should address the
+		questions of how often the end users employed a certain function and where they
+		used it. In this way, it must show precise metrics, such as frequency of  use
+		and depth of function nesting, of the dataset it conveys. \item [3]
+		\textbf{Promote a qualitative understanding of the patterns.} Lest these
+		patterns remain abstract, the tool should supplement its observations with
+		concrete instances of relevant formulas from the corpus. Ideally, it should
+		even direct users to the exact cell in the spreadsheets where the formula was
+		used, contextualizing the functions. \end{itemize} \par Likewise, to bound our
+	scope, we outlined a few goals to specifically avoid accomplishing with this:
+	\begin{itemize} \item [!1] \textbf{Do not try to directly explain what a
+			function does.} Though the tool tries to foster tries understanding by linking
+		pattern to example, it won't provide a precise description of what a function
+		accomplishes. The tool's user must infer this. \item [!2] \textbf{Do not create
+			new formulas.} This is essentially an exploratory tool, not a generative one.
+		It should not produce any information other than new views of the original
+		data. \item [!3] \textbf{Do not visualize individual formulas.} Though there is
+		room to explore the place of a single function in the group, the tool must
+		design the core visualization around the entire body of data, not the other way
+		around. \end{itemize}
 
-\subsection{Design Decisions}
-Early in the process, we decided that the tree form would be a suitable fit to represent the parent-child or caller-callee relationships inherent in the data, given the composition of formulas as functions and their arguments (which could be yet more functions).
-By adapting this structure to accommodate a broad range of possibilities for nested functions, the branching factor depends on both the number of arguments in a function and the number of possible functions observed as an argument in a function.
-\par
-Guided by the goals in section A, we faced a number of decision points, a sample of which we describe below, before we arrived at the design shown above.
-\begin{itemize}
-	\item \textit{Copied formulas}: Excel allows users to spread a formula over an area, repeating the same task in each cell with minor adjustments.
-Without checking for this, the analysis may not reveal the functions most commonly used together but rather the formulas most often applied to large areas.
-To combat this, we converted formulas from their native A1 format to the relative R1C1, in which copied formulas should be identical, and reduced the records to unique R1C1 formulas per sheet.
-	\item \textit{Importance of depth}: When a function appears within another, should it be analyzed only as a nested function or would it also be valid to analyze the nested function on its own?  \par
-	For example, in the pictured IF function, we found that people often use another IF statement as the second or third arguments of the top-level IF.
-If we only consider functions exactly where they're found embedded in the formula, then information about the same function -- IF, in this case -- will be scattered across different trees with no way to aggregate them.
-If we record every instance of a function by ignoring their context -- that is, including an IF embedded within a SUM function in the same node as the top-level IF -- then the tool will represent some functions in multiple nodes to capture every possible level of nesting.
-Both approaches have benefits and drawbacks, and so we included both.
-	\item \textit{Pattern density}: How should the tool quantitatively order its elements: by a function's raw frequency or by the unity of patterns it leads to?
-For example, if SUM has for its first argument two possibilities, one which itself contains 1000 unique argument possibilities with 1 occurrence each (high frequency, low pattern density) and another seen with 2 argument possibilities of 100 occurrences each (low frequency, high pattern density), which would be more interesting to emphasize?
-The answer depends on the nuances of the questions, but for simplicity, I've shown the former.
-	\item \textit{Non-functions}: How should the tool represent everything in the formula that isn't a function: numbers, string literals, errors, references, etc?
-Since these don't accept arguments, they will adorn the tree as leaves, and their precise content won't affect the functions around them as long as their types are known.
-As such, in the visualization, all of these nodes are replaced and aggregated under their types and represented as empty white nodes.
-	\item \textit{Optional arguments}: How should the tool handle functions which accept a variable number of arguments?
-SUM, for example, can have anywhere from 1 to 255, and IF can accept either 2 or 3.
+	\subsection{Design Decisions} Early in the process, we decided that the tree
+	form would be a suitable fit to represent the parent-child or caller-callee
+	relationships inherent in the data, given the composition of formulas as
+	functions and their arguments (which could be yet more functions). By adapting
+	this structure to accommodate a broad range of possibilities for nested
+	functions, the branching factor depends on both the number of arguments in a
+	function and the number of possible functions observed as an argument in a
+	function. \par Guided by the goals in section A, we faced a number of decision
+	points, a sample of which we describe below, before we arrived at the design
+	shown above. \begin{itemize} \item \textit{Copied formulas}: Excel allows users
+		to spread a formula over an area, repeating the same task in each cell with
+		minor adjustments. Without checking for this, the analysis may not reveal the
+		functions most commonly used together but rather the formulas most often
+		applied to large areas. To combat this, we converted formulas from their native
+		A1 format to the relative R1C1, in which copied formulas should be identical,
+		and reduced the records to unique R1C1 formulas per sheet. \item
+		\textit{Importance of depth}: When a function appears within another, should it
+		be analyzed only as a nested function or would it also be valid to analyze the
+		nested function on its own?  \par For example, in the pictured IF function, we
+		found that people often use another IF statement as the second or third
+		arguments of the top-level IF. If we only consider functions exactly where
+		they're found embedded in the formula, then information about the same function
+		-- IF, in this case -- will be scattered across different trees with no way to
+		aggregate them. If we record every instance of a function by ignoring their
+		context -- that is, including an IF embedded within a SUM function in the same
+		node as the top-level IF -- then the tool will represent some functions in
+		multiple nodes to capture every possible level of nesting. Both approaches have
+		benefits and drawbacks, and so we included both. \item \textit{Pattern
+			density}: How should the tool quantitatively order its elements: by a
+		function's raw frequency or by the unity of patterns it leads to? For example,
+		if SUM has for its first argument two possibilities, one which itself contains
+		1000 unique argument possibilities with 1 occurrence each (high frequency, low
+		pattern density) and another seen with 2 argument possibilities of 100
+		occurrences each (low frequency, high pattern density), which would be more
+		interesting to emphasize? The answer depends on the nuances of the questions,
+		but for simplicity, I've shown the former. \item \textit{Non-functions}: How
+		should the tool represent everything in the formula that isn't a function:
+		numbers, string literals, errors, references, etc? Since these don't accept
+		arguments, they will adorn the tree as leaves, and their precise content won't
+		affect the functions around them as long as their types are known. As such, in
+		the visualization, all of these nodes are replaced and aggregated under their
+		types and represented as empty white nodes. \item \textit{Optional arguments}:
+		How should the tool handle functions which accept a variable number of
+		arguments? SUM, for example, can have anywhere from 1 to 255, and IF can accept
+		either 2 or 3.
 		\footnote{https://support.office.com/en-us/article/Excel-functions-by-category-5f91f4e9-7b42-46d2-9bd1-63f26a86c0eb} Without prior evidence, it's possible that, when people use optional arguments, they use different kinds of types and functions for arguments versus the cases when they ignore optional arguments.
@@
 
-\subsection{Implementation Details}
-We can view the final visualization as the product of two discrete processes:
-\begin{itemize}
-	\item \textit{Collection}: Given a set of Excel sheets, the tool, written mostly in Java, uses Apache POI\footnote{https://poi.apache.org/} to identify and iterate over every cell containing a valid formula.
-Afterward, it calls POI's formula parser to break the formula text into an ordered set of individual tokens, which the tool then parses into the tree-like form by which it is recorded.
-When all formulas have been analyzed like this, it produces JSON files for each top-level function in the set.
-	\item \textit{Presentation}: The JSON files, meanwhile, feed into the presentation code, implemented in Javascript with much help from the visualization library D3\footnote{https://d3js.org/}.
-We chose D3 primarily for its accessibility: given the JSON, the visualization can be rather simply embedded into a webpage accessible through a browser.
-\end{itemize}
-A demonstration of the tool can be found at [LINK HERE].
+	\subsection{Implementation Details} We can view the final visualization as the
+	product of two discrete processes: \begin{itemize} \item \textit{Collection}:
+		Given a set of Excel sheets, the tool, written mostly in Java, uses Apache
+		POI\footnote{https://poi.apache.org/} to identify and iterate over every cell
+		containing a valid formula. Afterward, it calls POI's formula parser to break
+		the formula text into an ordered set of individual tokens, which the tool then
+		parses into the tree-like form by which it is recorded. When all formulas have
+		been analyzed like this, it produces JSON files for each top-level function in
+		the set. \item \textit{Presentation}: The JSON files, meanwhile, feed into the
+		presentation code, implemented in Javascript with much help from the
+		visualization library D3\footnote{https://d3js.org/}. We chose D3 primarily for
+		its accessibility: given the JSON, the visualization can be rather simply
+		embedded into a webpage accessible through a browser. \end{itemize} A
+	demonstration of the tool can be found at [LINK HERE].
 
-\section{User Study}
-Midway through production, we conducted a brief, four-participant user study in order to gauge how well we were capturing the initial
-design goals. The study was, in general, a flexible and exploratory
-affair: rather than giving the users any specific tasks or pointed
-questions, we asked instead that they choose for themselves which trees to explore and report anything that they deemed interesting. 
-Specifically, given trees rooted in the Enron dataset and at least 20 to thirty minutes, the participants situated themselves within the persona 
-of a consultant asked to evaluate a company's spreadsheet practice, which could be arranged around questions like which functions on which the
-employees most depended, which sheets presented the most anomalous or dangerous designs, and so on.
-Interpretation of "spreadsheet practice" can certainly vary from participant to participant, but since we wanted a range of views and backgrounds despite the persona, we readily accepted
-this interpretive wiggle room. \par
-We clarified, furthermore, that these notes could be directed either at the quality of the data conveyed by the tool or at the tool's conveyance
-itself. Since the tool's philosophy was based in exploration, we
-decided that it would not have been appropriate to restrict what people
-were to look for, letting them find interesting stories of formula 
-construction for themselves. Additionally, either kind of comment -- on data or on tool -- would direct us back to the central evaluation; a user's
+	\section{Case Study} The obvious question to pose to any visualization is this:
+	Why does it matter that we see this way? In other words, it is not enough to
+	prove that something can be visualized; instead we must also demonstrate what
+	we can be gained from any particular visualization. As such, we raised a few
+	tasks in the introduction in which we thought the tool could help: identifying
+	places for API improvement, detecting bad smells or common programmer
+	misunderstanding, and guiding spreadsheet education. To demonstrate the tool's
+	applicability, then, we sought out places in the tree which best exemplify
+	these respective concerns.
+
+	\subsection{Bad Smells} Fowler's (?) seminal description of code smells
+	underscored an important point of code quality: between perfect code and
+	bug-crippled spaghetti,  there is a spectrum of code designs which, by
+	themselves, are not faulty but nevertheless suggest problems and
+	vulnerabilities in code design. Code smells, as we call them, soon commanded
+	attention and earned wide-ranging applicability, eventually making it to the
+	art of spreadsheet design. Since then, Hermans and others catalog the odors of
+	spreadsheets, often built off Fowler's (?) original specifications to
+	articulate the subtle problems in spreadsheet design. \par Collected, some of
+	the intra-spreadsheet smells fall well within the purview of this visualization
+	tool. Some such smells can be found in a figure [FIGURE]. \par The smells
+	described above, then, entail a corresponding structure visible in the
+	visualization: the deeper a branch runs, or the taller the range of arguments,
+	the more it emits the stench of suboptimal design. \par To be sure, these rank
+	occurrences must be leveraged with their prevalence across the dataset. One
+	person's anomaly, though perhaps still interesting, will not be as impactful as
+	a smell of thousands. \par Some examples are meaningful not for the space they
+	take up but for how they clash with the expectations around a function. For
+	example, Excel offers a number of functions that accept any number arguments
+	given to them, up to a resource-defined limit. SUM and CONCATENATE are two such
+	functions: adding more arguments simply adds or appends that element in the
+	same way as every previous argument. Strange cases were found, then, in the
+	cases where these functions were used with only one argument. \par Hermans, in
+	her paper on the nuances of VLOOKUP and its common misuses, explore the problem
+	of the final, optional argument. A tool there helped, but how might a
+	visualization such as this illuminated the same?
+
+	\subsection{Education} Learning by example has long been a cornerstone of
+	effective teacher techniques: by showing the student a concrete example of
+	something, rather than dwelling in the realm of abstract description,
+	comprehension increases [I'm sure there's a cite out there somewhere.] This is
+	no different in software, where every explanation of a tricky programming
+	concept is much untangled by the illustrative stub. Even APIs, researchers have
+	found, by the inclusion of an in-practice example of the function described.
+	Spreadsheet programming, then, should not be essentially different: examples of
+	spreadsheet functions in use
+
+	\section{User Study} Midway through production, we conducted a brief,
+	four-participant user study in order to gauge how well we were capturing the
+	initial design goals. The study was, in general, a flexible and exploratory
+	affair: rather than giving the users any specific tasks or pointed questions,
+	we asked instead that they choose for themselves which trees to explore and
+	report anything that they deemed interesting. Specifically, given trees rooted
+	in the Enron dataset and at least 20 to thirty minutes, the participants
+	situated themselves within the persona of a consultant asked to evaluate a
+	company's spreadsheet practice, which could be arranged around questions like
+	which functions on which the employees most depended, which sheets presented
+	the most anomalous or dangerous designs, and so on. Interpretation of
+	"spreadsheet practice" can certainly vary from participant to participant, but
+	since we wanted a range of views and backgrounds despite the persona, we
+	readily accepted this interpretive wiggle room. \par We clarified, furthermore,
+	that these notes could be directed either at the quality of the data conveyed
+	by the tool or at the tool's conveyance itself. Since the tool's philosophy was
+	based in exploration, we decided that it would not have been appropriate to
+	restrict what people were to look for, letting them find interesting stories of
+	formula construction for themselves. Additionally, either kind of comment -- on
+	data or on tool -- would direct us back to the central evaluation; a user's
 	silence, or lack of any interesting findings, would tacitly indicate that
-perhaps the tool does not convey information well enough. \par 
-Still, several limitations cropped up during the study that complicate
-the evaluation. For one thing, though the source of the data was not 
-explicitly stated at the outset of the session, several users studied the file names (unchanged as they were) to deduce its roots in finance, if not
-Enron itself. Because of these notorious connotations, then, some were
-inclined from this moment of discovery to orient their exploration around finance-related functions, potentially limiting their findings or perceived
-users for the tool -- though some also said that, without this essential 
-context, they could not have properly explored a dataset in the first place.
-Comments like these point out the trade-offs of unguided exploration, too: though it might not restrict them to a single purpose, it
+	perhaps the tool does not convey information well enough. \par Still, several
+	limitations cropped up during the study that complicate the evaluation. For one
+	thing, though the source of the data was not explicitly stated at the outset of
+	the session, several users studied the file names (unchanged as they were) to
+	deduce its roots in finance, if not Enron itself. Because of these notorious
+	connotations, then, some were inclined from this moment of discovery to orient
+	their exploration around finance-related functions, potentially limiting their
+	findings or perceived users for the tool -- though some also said that, without
+	this essential context, they could not have properly explored a dataset in the
+	first place. Comments like these point out the trade-offs of unguided
+	exploration, too: though it might not restrict them to a single purpose, it
 	might, at the same time, not afford them any mindset at all with which to
@@
 	explored was processed and created before we had fully completed the tool,
-meaning some of the counts and patterns in the trees were inaccurate. 
-However, we decided that this was not a pressing concern, being that we 
-were primarily with whether any interesting reports could be made at all, 
-not with whether these reports were 100\% accurate assessments of reality. \par
-Nevertheless, these user studies were a formative moment in evaluating
-the tool's performance, generating a number of directions or corrections
-in the process.
-\section{Case Study}
-The obvious question to pose to any visualization is this: Why does it matter that we see this way?
-In other words, it is not enough to prove that something can be visualized; instead we must also demonstrate what we can be gained from any particular visualization.
-As such, we raised a few tasks in the introduction in which we thought the tool could help: identifying places for API improvement, detecting bad smells or common programmer misunderstanding, and guiding spreadsheet education.
-Thus, to demonstrate the tool's applicability, we sought out places in the tree which best exemplify these respective concerns.
+	meaning some of the counts and patterns in the trees were inaccurate. However,
+	we decided that this was not a pressing concern, being that we were primarily
+	with whether any interesting reports could be made at all, not with whether
+	these reports were 100\% accurate assessments of reality. \par Nevertheless,
+	these user studies were a formative moment in evaluating the tool's
+	performance, generating a number of directions or corrections in the process.
+	We present an overview of responses below, with the four participants recorded
+	simply as P1 through P4. \par \subsection{Positive Responses} The inclusion of
+	formula examples, grounded in and linking back to the originating spreadsheets,
+	proved to be an especial draw to the tool. After all, none of the participants
+	professed themselves to be experts with Excel, their self-reported
+	proficiencies ranging from "fairly familiar" (P2) to "not extremely familiar"
+	(P4); even if they were experts, it would likely be unreasonable to expect an
+	evenly distributed familiarity with the 100+ function trees available.
+	Nevertheless, the list of actual formulas accessible through a node's
+	double-click allowed the users a way to find examples of formulas with exactly
+	the configuration they wanted. For example, as P1 explored the VLOOKUP
+	function, even though they knew the official API more verbosely explained its
+	signature, they said they could use the tool to collect more examples than the
+	documentation offers. \par Furthermore, it offers a simple way of finding
+	examples where certain functions were used together. though a standard
+	text-search tool might yield the same results for a function alone,
+	combinations can require more complex text queries, whereas here, the
+	information is already captured in nodes. [This paragraph contrasts it with
+	previous approaches, but lacks compelling evidence -- a lot of "mights"] \par
+	\begin{wrapfigure}{l}{.12\textwidth} \centering \includegraphics{SUM}
+		\label{"fig:sum"} \end{wrapfigure} The discovery of errors and bad design,
+	whether by purpose or accident, produced the more jarring events of the study,
+	and as such, most users commented on the tool's ability to locate these
+	problems in spreadsheet design. This was often supported by the distinctive
+	visual signatures of certain bad practices: multiple arguments produce towers
+	of nodes, deep function nesting stretches the tree horizontally, and so on. As
+	such, the participants remarked on the problems quickly after opening: P3,
+	exploring the example for a 27-argument SUM (with SUM's initial appearance
+	pictured left), diagnosed the situation with either incompetency or just plain
+	weirdness; P2, meanwhile, decided that the spreadsheet's author "was having a
+	bad day" when writing an AVERAGE with 18 distinct arguments. Aside from these
+	implicit cues, there are also nodes which refer to formula errors, prefixed
+	with \#s, which P4 said could be useful if marked well. Furthermore, once these
+	errors are found, the participants could then open the offending spreadsheets,
+	discovering that, even in context, some of these formulas remained
+	incomprehensible, posing problems for mere functioning and maintainability.
+	[Hermanns discussed in one of her paper the transfer scenarios -- would go well
+	here.] The tool, then, aggregates these issues in a single place, accessible to
+	either the unguided user and the ones who know exactly where to find these
+	issues. \par The detection of bad design, however, is certainly not limited to
+	a visualization tool, and some users remarked that a tool which printed a list
+	of errors could suffice just as well for that purpose. However, they also
+	remarked that this visual interface better supports the case when searching for
+	new and unknown brands of bad smell.
 
-\subsection{Bad Smells}
-Fowler's (?) seminal description of code smells underscored
-an important point of code quality: between perfect code and 
-bug-crippled spaghetti,  there is a spectrum of code designs 
-which, by themselves, are not faulty but nevertheless may
-point to problems and vulnerabilities in how code is written.
-Code smells, as we call them, soon commanded attention and earned wide-ranging 
-applicability, eventually making it to the art of spreadsheet design.
-Since then, Hermans and others catalog the odors of spreadsheets, 
-often built off Fowler's (?) original specifications to articulate
-the subtle problems in spreadsheet design. \par 
-Collected, some of the intra-spreadsheet smells fall well within the
-purview of this visualization tool. Some such smells can be found
-in a figure [FIGURE]. \par 
-The smells described above, then, entail a corresponding structure
-visible in the visualization: the deeper a branch runs, or the
-taller the range of arguments, the more it emits the stench of suboptimal
-design. \par 
-To be sure, these rank occurrences must be leveraged with their prevalence
-across the dataset. One person's anomaly, though perhaps still interesting,
-will not be as impactful as a smell of thousands. \par
-Some examples are meaningful not for the space they take up but for how
-they clash with the expectations around a function. For example, Excel
-offers a number of functions that accept any number arguments given to 
-them, up to a resource-defined limit. SUM and CONCATENATE are two such functions:
-adding more arguments simply adds or appends that element in the same way
-as every previous argument. Strange cases were found, then, in the cases where
-these functions were used with only one argument. \par
-Hermans, in her paper on the nuances of VLOOKUP and its common misuses, explore
-the problem of the final, optional argument. A tool there helped, but how might
-a visualization such as this illuminated the same?
+	Because the exploratory design makes no qualitative judgment and visualizes
+	benign designs with the problematic, it therefore allows for flexible
+	interpretation of what is an issue; that is, a user might not realize a certain
+	design is suboptimal until they see it in the tree and, at the point, find
+	every instance of it.
 
-\subsection{Education}
-Learning by example has long been a cornerstone of effective teacher techniques:
-by showing the student a concrete example of something, rather than dwelling in
-the realm of abstract description, comprehension increases [I'm sure there's a cite
-out there somewhere.] This is no different in software, where every explanation of
-a tricky programming concept is much untangled by the illustrative stub. Even APIs,
-researchers have found, by the inclusion of an in-practice example of the function
-described. Spreadsheet programming, then, should not be essentially different: 
-examples of spreadsheet functions in use
+	\subsection{Negative Responses} Some interaction with the tool underlined how a
+	lack of contextual information may limit the tool. For example, the benefits
+	described in the previous sections imply a hidden complication: if the tool
+	educates through example but doesn't explicitly distinguish between good design
+	and bad design, how can we be sure that people won't inadvertently learn bad
+	design from it. Right now, we can't be sure; the tool would have to be
 
-\subsection{Limitations}
-Because the data collection depends on POI's formula parser, it affords no leeway or partial information from a formula; it either processes it perfectly or throws it out.
-As such, the visualization inhibits insight into anything with syntactical errors or third-party functions that can't be evaluated without additional tools.
-Note, however, that this does not include standard Excel errors like \#REF!
-and \#DIV/0, which the parser handles well.
-\par
-Many functions have an expected order of arguments, but some, like SUM and MATCH, can be reordered in various ways and maintain their value.
-However, the representation that this tool uses reinforces for all functions that the order is important, even in these exceptions.
-\par
-A larger and related problem is the loss of argument combination.
-In the example in section B, we saw how the tools conveys which arguments are used most often on each side of an equals sign, but it does not encode how these whether references were actually compared to strings and numbers the most or whether it corresponded more to all the arguments beneath those two
+	supplemented with a distinguishing eye, informed on bad design already, and
+	supplying the tool with this would take it beyond a design-agnostic view. [More
+	on this in the conclusion.] \par Furthermore, just because a user can
+	exhaustively explore every variation of how a function was used doesn't mean
+	they will learn exactly what it does. P1, in their exploration, examined
+	functions that they hadn't used before, such as KURT and PV, and described
+	precisely what types of arguments it accepted and how many. However, even after
+	exploring the spreadsheets, they could not accurately describe what the
+	functions produced without consulting the official documentation. Whether
+	through reticence of the tool or obscurity of the functions themselves, the
+	exploratory environment is not enough for independent education. However,
+	unlike the previous problem, this can be addressed, perhaps, by guiding the
+	user directly to such documentation from within the tool without violating any
+	design concerns. \par A threat to the exploratory philosophy may also mount
+	from the problem of too much data, particularly in the popular functions, like
+	SUM and IF. We had added some precautions before the study: for any position in
+	the tree, for example, only the ten most common functions were displayed
+	without clicking on the expansion arrow \includegraphics[scale=.35]{arrow}.
+	Nevertheless, P3 remarked that they specifically avoided the most popular
+	functions, anticipating a flood of nodes from which they could salvage nothing
+	interesting -- which might not have been a bad prediction, considering that the
+	SUM is built from 910 nodes and IF, at least 18000 [double-check these with
+	refined data]. P2 corroborated this by explaining how they gravitated toward
+	specific examples over the plane of nodes but complicates it further by also
+	deeming the tool at its best when it shows either every possibility of an
+	side-by-side (for comparison) or nothing on that branch at all, a balance that
+	is hard to strike with node-dense trees. \par Throughout the study, it became
+	apparent that some of the concepts, particularly optional arguments, were
+	easily lost in the representation. To illustrate this, consider the following
+	two trees: \par \includegraphics[width = .46\textwidth]{comparison} The
+	difference is, perhaps, too subtle: on the left, the tree contains instances of
+	AND functions with any number of arguments, up to four; on the right, the tree
+	contains only instances with exactly four arguments. In other words, an
+	instance of "=AND(A1, B2, C3, D4)" would be found in both trees, while
+	"=AND(A1, B2)" would be found in only the left. Though the users naturally did
+	not explicitly report misinterpreting the icons, it became clear in their
+	out-loud thoughts that they viewed each box as a fundamentally different set of
+	possibilities in formula construction rather than just a specific parameter.
+	Though we clarified the meanings when these misunderstandings became apparent,
+	these events point to a failure in the tool to properly indicate every function
+	with clarity.   \par
 
-\section{Conclusion}
+	\section{Limitations} Beyond the negative responses in the user study, a few
+	more inherent limitations beset the tool. These largely resulted from
+	trade-offs in which we found no acceptable way to win the best of both worlds,
+	and necessary compromises were made. \par Because the data collection depends
+	on POI's formula parser, it affords no leeway or partial information from a
+	formula; it either processes it perfectly or throws it out. As such, the
+	visualization inhibits insight into anything with syntactical errors or
+	third-party functions that can't be evaluated without additional tools. Note,
+	however, that this does not include standard Excel errors like \#REF! and
+	\#DIV/0, which the parser handles well. This poses more egregious problems,
+	however, when POI does not support the parsing of certain functions, such as
+	EOMONTH (as obscure as it may be), preventing the healthy growth of those
+	trees. \par Many functions have an expected order of arguments, but some, like
+	SUM and MATCH, can be reordered in various ways and maintain their value.
+	However, the representation that this tool uses reinforces for all functions
+	that the order is important, even in these exceptions. Future work could design
+	a new family of tree to accommodate these loose cases, however, by bucketing
+	order-insignificant arguments together; this, of course, would still have to
+	address the profusion of co-presented data. \par A larger and related problem
+	is the loss of argument combination. In the example in section B, we saw how
+	the tools conveys which arguments are used most often on each side of an equals
+	sign, but it does not encode how these whether references were actually
+	compared to strings and numbers the most or whether it corresponded more to all
+	the arguments beneath those two
+
+	\section{Conclusion} Why design agnostic?
 
@@
 
--extensible to other spreadsheets?
-% conference papers do not normally have an appendix
+	-extensible to other spreadsheets? % conference papers do not normally have an
+	% appendix
 
 	% use section* for acknowledgment
-\section*{Acknowledgment}
-This material is based upon work supported in whole or in part with funding from the Laboratory for Analytic Sciences (LAS).
-Any opinions, findings, conclusions, or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the LAS and/or any agency or entity of the United States Government.
+	\section*{Acknowledgment} This material is based upon work supported in whole
+	or in part with funding from the Laboratory for Analytic Sciences (LAS). Any
+	opinions, findings, conclusions, or recommendations expressed in this material
+	are those of the author(s) and do not necessarily reflect the views of the LAS
+	and/or any agency or entity of the United States Government.
 
@@
 	% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{paper}
-%
+	\bibliographystyle{IEEEtran} % argument is your BibTeX string definitions and
+	% bibliography database(s)
+	\bibliography{paper} %
 	% <OR> manually copy in the resultant .bbl file

### 2016-04-20 doc/paper.tex
Paper syncronization.

@@
 
-	\section{Introduction} Business and research alike a lot to spreadsheets, the
+	\section{Introduction} Business and research alike owe a lot to spreadsheets, the
 	tabular interface that offers users a structured way to store and manipulate
@@
 	could be using them by 2012, with 25 million of them writing programs
-	\cite{scaffidi2005estimating}. \par Considering this ubiquity, it's crucial to
-	understand how people are actually using spreadsheets. After all, failures in
-	their practice can be ruinous, as demonstrated in EuSpRIG's many horror stories
-	of spreadsheets gone wrong. In 2013, for example, they detail the influence of
-	an economics paper on debt and national growth which shaped many political
-	initiates around it, only to discover that the spreadsheets used in the data
-	analysis contained an error that reversed the findings. The other stories,
-	likewise, do not augur well if shoddy spreadsheet practices persist
-	\footnote{http://www.eusprig.org/horror-stories.htm}. \par Fortunately, many
-	spreadsheet researchers have assembled and released a number of spreadsheet
-	corpora to inform work of how people actually use these tools. Collections like
-	EUSES \cite{fisher2005euses}, FUSE \cite{barik2015fuse}, and the Enron corpus
-	\cite{hermans2015enron} have already enabled fruitful work across the field.
-	Hermans and colleagues, for example, used the EUSES corpus in 2011 to inform
-	and evaluate their work on exploring code smells, or inelegant places in code
-	that suggest the need for refactoring, between worksheets
-	\cite{hermans2012detecting}. \par A tool, then, that empowers users of any
-	intention to explore these datasets would be rife with potential. On a simple
-	level, the tool could provide concrete statistics on which functions are used
-	in practice most (or least) often for a given dataset. Beyond this, though, it
-	could also inform future work on recommending functions through an
-	understanding of this patterns, or it could guide API improvement by suggesting
-	functions to add or prune based how people actually use them. Furthermore, if
-	the tool maintains the connection between its broad patterns and the actual
-	instances of formulae in workbooks, it could serve as a boon to educators not
-	only by showing which functions and combinations are most practical to learn
-	but also by offering a bounty of instructive, and real, examples \par This
-	paper contributes a tool, informed by some of the aforementioned spreadsheet
-	corpora, that seeks to accomplish these tasks by offering an interactive
-	interface for exploring how people combine functions. It seeks to balance
-	several needs, such as capturing these patterns in a broad enough overview
-	while still be specific enough lead back to the precise places in spreadsheets
-	where these patterns are realized. Along with the tool, then, is also a
-	discussion of the various goals which the tool seeks to fulfill and the
+	\cite{scaffidi2005estimating}. \par
+
+	Considering this ubiquity, it's crucial to understand how people are actually
+	using spreadsheets. After all, failures in their practice can be ruinous, as
+	demonstrated in EuSpRIG's many horror stories of spreadsheets gone wrong. In
+	2013, for example, they detail the influence of an economics paper on debt and
+	national growth which shaped many political initiates around it, only to
+	discover that the spreadsheets used in the data analysis contained an error
+	that reversed the findings. The other stories, likewise, do not augur well if
+	shoddy spreadsheet practices persist
+	\footnote{http://www.eusprig.org/horror-stories.htm}. \par
+
+	Fortunately, many spreadsheet researchers have assembled and released a number
+	of spreadsheet corpora to inform work of how people actually use these tools.
+	Collections like EUSES \cite{fisher2005euses}, FUSE \cite{barik2015fuse}, and
+	the Enron corpus \cite{hermans2015enron} have already enabled fruitful work
+	across the field. Hermans and colleagues, for example, used the EUSES corpus in
+	2011 to inform and evaluate their work on exploring code smells, or inelegant
+	places in code that suggest the need for refactoring, between worksheets
+	\cite{hermans2012detecting}. Furthermore, these corpora have been compared
+	and cross-referenced, such as in Jansen's contrast on Enron and EUSES, to
+	gather insight in how different domains use spreadsheets differently 
+	\cite{jansen2015enron}, or in Aivaloglou and colleague's evaluation of a
+	spreadsheet grammar \cite{aivaloglou2015grammar}.\par
+
+	A tool, then, that empowers users of any intention to explore these datasets
+	would be rife with potential. On a simple level, the tool could provide
+	concrete statistics on which functions are used in practice most (or least)
+	often for a given dataset. Beyond this, though, it could also inform future
+	work on recommending functions through an understanding of this patterns, or it
+	could guide API improvement by suggesting functions to add or prune based how
+	people actually use them. Furthermore, if the tool maintains the connection
+	between its broad patterns and the actual instances of formulae in workbooks,
+	it could serve as a boon to educators not only by showing which functions and
+	combinations are most practical to learn but also by offering a bounty of
+	instructive, and real, examples \par
+
+	This paper contributes a tool, informed by some of the aforementioned
+	spreadsheet corpora, that seeks to accomplish these tasks by offering an
+	interactive interface for exploring how people combine functions. It seeks to
+	balance several needs, such as capturing these patterns in a broad enough
+	overview while still be specific enough lead back to the precise places in
+	spreadsheets where these patterns are realized. Along with the tool, then, is
+	also a discussion of the various goals which the tool seeks to fulfill and the
 	trade-offs that we negotiated at each point. All of this culminates in an
@@
 	These, however, tend to focus on individual spreadsheets and not bodies of
-	them. \par Nevertheless, other studies and tools focus more on evaluating the
-	content of the cells therein. Badame, for example, implements a number of Excel
-	formula refactorings and uses Euses in part to evaluate it
+	them. \par
+
+	Nevertheless, other studies and tools focus more on evaluating the content of
+	the cells therein. Badame, for example, implements a number of Excel formula
+	refactorings and uses Euses in part to evaluate it
 	\cite{badame2012refactoring}. Hermans, leveraging her work with the
@@
 	\cite{cunha2012towards}, which Abreu and colleagues later extended to detect
-	faults. \cite{abreu2014smelling}.\par Implicit in this study is an exploration
-	of how users interact with the Excel API. Previous research, such as the first
-	study on the Enron spreadsheet corpus \cite{hermans2015enron}, on how users
-	employ certain functions or commands. Researchers have applied such questions
-	to other contexts as well, such as Murphy and colleague's study into how Java
-	developers use Eclipse and what commands they use most often
-	\cite{murphy2006java}.  Others focus on the documentation of the API itself:
-	Robillard and DeLine, for example conducted a series of surveys and interviews
-	to diagnose common problems with learning APIs, and they found that code
-	examples, one of the focuses of this tool, is one of the most important aids to
-	have in learning a new system \cite{robillard2011field}.
+	faults. \cite{abreu2014smelling}.\par
+
+	Implicit in this study is an exploration of how users interact with the Excel
+	API. Previous research, such as the first study on the Enron spreadsheet corpus
+	\cite{hermans2015enron}, on how users employ certain functions or commands.
+	Researchers have applied such questions to other contexts as well, such as
+	Murphy and colleague's study into how Java developers use Eclipse and what
+	commands they use most often \cite{murphy2006java}.  Others focus on the
+	documentation of the API itself: Robillard and DeLine, for example conducted a
+	series of surveys and interviews to diagnose common problems with learning
+	APIs, and they found that code examples, one of the focuses of this tool, is
+	one of the most important aids to have in learning a new system
+	\cite{robillard2011field}.
 
@@
 	however, to understand the interaction, we will start rather from the
-	beginning. \par When the user first approaches the tree for a given top-level
-	function -- that is, a function nested within none other -- only a few nodes
-	are visible, as shown in figure \ref{fig:startpic}. \par
+	beginning. \par
+
+	When the user first approaches the tree for a given top-level function -- that
+	is, a function nested within none other -- only a few nodes are visible, as
+	shown in figure \ref{fig:startpic}. \par
 
@@
 	specifications in the
-	API.\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2} \par Knowing that it is the first argument which contains the conditionals, we click on the square labeled "1" to explore.
-To save space, when more than 10 unique arguments have been observed in any position, the tool displays only the first ten, with an option to display the rest.
-The results are shown below:
+	API.\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2} \par
+
+	Knowing that it is the first argument which contains the conditionals, we click
+	on the square labeled "1" to explore. To save space, when more than 10 unique
+	arguments have been observed in any position, the tool displays only the first
+	ten, with an option to display the rest. The results are shown below:
 
@@
 	ISNA and AND, with simple equality being the most common and some use as ABS
-	being the least seen of everything actually used. \par From here, we can
-	further explore the common options among these functions. Clicking on the "="
-	node will yield two arguments, it being a binary operator, and expanding each
-	of them will peer into the range of common values of equality comparison, which
-	Figure \ref{fig:fullpic} shows. \par For both sides of the equal sign, the
-	operator has certain types of arguments which predominate over the others: on
-	the left side is most often a reference to another cell; on the right, a string
-	or number literal, which makes sense for the case of confirming a value in
-	another cell before assigning this one. Furthermore, if the concept is
-	difficult to imagine is practice, a tooltip accompanies each function node in
-	the tree, providing a concrete example of a function that uses this structure
-	and where it can be found. If this single instance is not enough, then the user
-	also has the option to double-click the individual function node, which will
-	open up a new tab with a table of many more examples from dataset.
+	being the least seen of everything actually used. \par
+
+	From here, we can further explore the common options among these functions.
+	Clicking on the "=" node will yield two arguments, it being a binary operator,
+	and expanding each of them will peer into the range of common values of
+	equality comparison, which Figure \ref{fig:fullpic} shows. \par
+
+	For both sides of the equal sign, the operator has certain types of arguments
+	which predominate over the others: on the left side is most often a reference
+	to another cell; on the right, a string or number literal, which makes sense
+	for the case of confirming a value in another cell before assigning this one.
+	Furthermore, if the concept is difficult to imagine is practice, a tooltip
+	accompanies each function node in the tree, providing a concrete example of a
+	function that uses this structure and where it can be found. If this single
+	instance is not enough, then the user also has the option to double-click the
+	individual function node, which will open up a new tab with a table of many
+	more examples from dataset.
 
@@
 		even direct users to the exact cell in the spreadsheets where the formula was
-		used, contextualizing the functions. \end{itemize} \par Likewise, to bound our
-	scope, we outlined a few goals to specifically avoid accomplishing with this:
-	\begin{itemize} \item [!1] \textbf{Do not try to directly explain what a
-			function does.} Though the tool tries to foster tries understanding by linking
-		pattern to example, it won't provide a precise description of what a function
-		accomplishes. The tool's user must infer this. \item [!2] \textbf{Do not create
-			new formulas.} This is essentially an exploratory tool, not a generative one.
-		It should not produce any information other than new views of the original
-		data. \item [!3] \textbf{Do not visualize individual formulas.} Though there is
-		room to explore the place of a single function in the group, the tool must
-		design the core visualization around the entire body of data, not the other way
-		around. \end{itemize}
+		used, contextualizing the functions. \end{itemize} \par
+
+	Likewise, to bound our scope, we outlined a few goals to specifically avoid
+	accomplishing with this: \begin{itemize} \item [!1] \textbf{Do not try to
+			directly explain what a function does.} Though the tool tries to foster tries
+		understanding by linking pattern to example, it won't provide a precise
+		description of what a function accomplishes. The tool's user must infer this.
+		\item [!2] \textbf{Do not create new formulas.} This is essentially an
+		exploratory tool, not a generative one. It should not produce any information
+		other than new views of the original data. \item [!3] \textbf{Do not visualize
+			individual formulas.} Though there is room to explore the place of a single
+		function in the group, the tool must design the core visualization around the
+		entire body of data, not the other way around. \end{itemize}
 
@@
 	function and the number of possible functions observed as an argument in a
-	function. \par Guided by the goals in section A, we faced a number of decision
-	points, a sample of which we describe below, before we arrived at the design
-	shown above. \begin{itemize} \item \textit{Copied formulas}: Excel allows users
-		to spread a formula over an area, repeating the same task in each cell with
-		minor adjustments. Without checking for this, the analysis may not reveal the
+	function. \par
+
+	Guided by the goals in section A, we faced a number of decision points, a
+	sample of which we describe below, before we arrived at the design shown above.
+	\begin{itemize} \item \textit{Copied formulas}: Excel allows users to spread a
+		formula over an area, repeating the same task in each cell with minor
+		adjustments. Without checking for this, the analysis may not reveal the
 		functions most commonly used together but rather the formulas most often
@@
 		be analyzed only as a nested function or would it also be valid to analyze the
-		nested function on its own?  \par For example, in the pictured IF function, we
-		found that people often use another IF statement as the second or third
-		arguments of the top-level IF. If we only consider functions exactly where
-		they're found embedded in the formula, then information about the same function
-		-- IF, in this case -- will be scattered across different trees with no way to
-		aggregate them. If we record every instance of a function by ignoring their
-		context -- that is, including an IF embedded within a SUM function in the same
-		node as the top-level IF -- then the tool will represent some functions in
-		multiple nodes to capture every possible level of nesting. Both approaches have
-		benefits and drawbacks, and so we included both. \item \textit{Pattern
-			density}: How should the tool quantitatively order its elements: by a
-		function's raw frequency or by the unity of patterns it leads to? For example,
-		if SUM has for its first argument two possibilities, one which itself contains
-		1000 unique argument possibilities with 1 occurrence each (high frequency, low
-		pattern density) and another seen with 2 argument possibilities of 100
-		occurrences each (low frequency, high pattern density), which would be more
-		interesting to emphasize? The answer depends on the nuances of the questions,
-		but for simplicity, I've shown the former. \item \textit{Non-functions}: How
-		should the tool represent everything in the formula that isn't a function:
-		numbers, string literals, errors, references, etc? Since these don't accept
-		arguments, they will adorn the tree as leaves, and their precise content won't
-		affect the functions around them as long as their types are known. As such, in
-		the visualization, all of these nodes are replaced and aggregated under their
+		nested function on its own?
+
+		\par For example, in the pictured IF function, we found that people often use
+		another IF statement as the second or third arguments of the top-level IF. If
+		we only consider functions exactly where they're found embedded in the
+		formula, then information about the same function -- IF, in this case -- will
+		be scattered across different trees with no way to aggregate them. If we
+		record every instance of a function by ignoring their context -- that is,
+		including an IF embedded within a SUM function in the same node as the
+		top-level IF -- then the tool will represent some functions in multiple nodes
+		to capture every possible level of nesting. Both approaches have benefits and
+		drawbacks, and so we included both. \item \textit{Pattern density}: How should
+		the tool quantitatively order its elements: by a function's raw frequency or
+		by the unity of patterns it leads to? For example, if SUM has for its first
+		argument two possibilities, one which itself contains 1000 unique argument
+		possibilities with 1 occurrence each (high frequency, low pattern density) and
+		another seen with 2 argument possibilities of 100 occurrences each (low
+		frequency, high pattern density), which would be more interesting to
+		emphasize? The answer depends on the nuances of the questions, but for
+		simplicity, I've shown the former. \item \textit{Non-functions}: How should
+		the tool represent everything in the formula that isn't a function: numbers,
+		string literals, errors, references, etc? Since these don't accept arguments,
+		they will adorn the tree as leaves, and their precise content won't affect the
+		functions around them as long as their types are known. As such, in the
+		visualization, all of these nodes are replaced and aggregated under their
 		types and represented as empty white nodes. \item \textit{Optional arguments}:
 		How should the tool handle functions which accept a variable number of
-		arguments? SUM, for example, can have anywhere from 1 to 255, and IF can accept
-		either 2 or 3.
+		arguments? SUM, for example, can have anywhere from 1 to 255, and IF can
+		accept either 2 or 3.
 		\footnote{https://support.office.com/en-us/article/Excel-functions-by-category-5f91f4e9-7b42-46d2-9bd1-63f26a86c0eb} Without prior evidence, it's possible that, when people use optional arguments, they use different kinds of types and functions for arguments versus the cases when they ignore optional arguments.
@@
 
-	\subsection{Bad Smells} Fowler's (?) seminal description of code smells
+	\subsection{Bad Smells} Fowler's description of code smells \cite{fowler2009refactoring}
 	underscored an important point of code quality: between perfect code and
@@
 	attention and earned wide-ranging applicability, eventually making it to the
-	art of spreadsheet design. Since then, Hermans and others catalog the odors of
-	spreadsheets, often built off Fowler's (?) original specifications to
-	articulate the subtle problems in spreadsheet design. \par Collected, some of
-	the intra-spreadsheet smells fall well within the purview of this visualization
-	tool. Some such smells can be found in a figure [FIGURE]. \par The smells
-	described above, then, entail a corresponding structure visible in the
-	visualization: the deeper a branch runs, or the taller the range of arguments,
-	the more it emits the stench of suboptimal design. \par To be sure, these rank
-	occurrences must be leveraged with their prevalence across the dataset. One
-	person's anomaly, though perhaps still interesting, will not be as impactful as
-	a smell of thousands. \par Some examples are meaningful not for the space they
-	take up but for how they clash with the expectations around a function. For
-	example, Excel offers a number of functions that accept any number arguments
-	given to them, up to a resource-defined limit. SUM and CONCATENATE are two such
-	functions: adding more arguments simply adds or appends that element in the
-	same way as every previous argument. Strange cases were found, then, in the
-	cases where these functions were used with only one argument. \par Hermans, in
-	her paper on the nuances of VLOOKUP and its common misuses, explore the problem
-	of the final, optional argument. A tool there helped, but how might a
-	visualization such as this illuminated the same?
+	art of spreadsheet design.
+
+	Since then, spreadsheet researchers have taken the concept, if not the specific
+	smells themselves, and applied them to spreadsheet programming
+	\cite{hermans2012detecting} \cite{cunha2012towards} \cite{jansen2015code}
+	\cite{asavametha2012detecting} . While some of the smells lie beyond the 
+	scope of the tool, such as those characterizing inter-worksheet connections,
+	some have structures which create distinctive features within the tree,
+	leading to easy detection through visualization: \par
+
+	\begin{itemize}
+		\item \textit{Long Method}: Also called "Multiple Operations" in \cite{hermans2012detecting},
+		this refers to situations where numerous functions and operators are used all within the same
+		cell, creating a formula that tends to extend beyond a compact viewing space and makes it
+		difficult to understand. In the visualization, since each nested and combined function creates
+		yet another level of depth within the tree, these constructions can result in long, horizontal 
+		chains of nodes, as seen in figure \ref{"fig:longsum"}.
+		\item \textit{Long Parameter List}: [tall, vertical towers of blue nodes]
+		\item \textit{Conditional Complexity}: [IF nodes within IF nodes]
+	\end{itemize}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{longsum}
+		\label{"fig:longsum"}
+		\caption{The horizontal length of a tree may indicate complex or redundant design.}
+	\end{figure*}
+
+	Some examples are meaningful not for the space they take up but for how they
+	clash with the expectations around a function. For example, Excel offers a
+	number of functions that accept any number arguments given to them, up to a
+	resource-defined limit. SUM and CONCATENATE are two such functions: adding more
+	arguments simply adds or appends that element in the same way as every previous
+	argument. Strange cases were found, then, in the cases where these functions
+	were used with only one argument. \par
+
+	%Lookup example
+	Otherwise, the LOOKUP functions are particularly notorious for their confusing
+	mechanisms and, as such, have warranted some especial attention with regards to
+	spreadsheet design. In a recent study, Hermans, Aivaloglou, and Jansen probed
+	the Enron dataset for uses of VLOOKUP and HLOOKUP specifically.
+	The issue at hand was the optional fourth argument: when omitted or set to TRUE,
+	the function attempts to return a value from another column by matching two values
+	approximately, but when set to FALSE, the match must be exact. Furthermore, exact
+	matching works only with sorted columns or rows; if the programmer neglects to sort
+	values before calling the *LOOKUP function, they may acquire inaccurate results \cite{hermans2015detecting}. \par
+
+	Given access to the same dataset, how might this tool approach the issue? 
+	On the surface, the tool supports easy quantification through the tooltips
+	displayed for each node, as shown in figure \ref{"fig:vhlookups"}, answering
+	the question, "How often do spreadsheet programmers use this function?". But, 
+	more to the point, the tool's distinction between the numbers of arguments
+	for a single function lets the user compare frequencies of three-argument 
+	forms with the four-argument. The visualization does not, however, discern
+	between the different values for booleans in the tree, much less whether 
+	the spreadsheet columns are ordered -- but the linking of examples to patterns
+	allows quick insight into which files are at risk for the problems they outlined. \par
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=.5\textwidth]{vlookup}
+		\includegraphics[width=.225\textwidth]{vlookupbox}
+		\includegraphics[width=.225\textwidth]{hlookupbox}
+		\includegraphics[width=.5\textwidth]{hlookup}
+		\label{"fig:vhlookups"}
+		\caption{VLOOKUP and HLOOKUP with four arguments. Numbers
+			not expected to correspond perfectly with \cite{hermans2015detecting}.}
+	\end{figure}
+
+	Also at hand are issues with the standard LOOKUP function. Unlike the two 
+	variations above, LOOKUP accepts either two or three arguments, depending
+	on which API-defined form the programmer uses: the vector form or
+	the array form, the primary difference being whether the second parameter
+	is a one-column/-row range or a two-dimensional array. The array form, as 
+	it happens, is strongly discouraged by the API in favor of the V/HLOOKUP,
+	a notion that might also be leveraged in the pursuit in good spreadsheet 
+	design.
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=.5\textwidth]{lookup-2}
+		\includegraphics[width=.5\textwidth]{lookup-3}
+		\label{"fig:lookups"}
+		\caption{LOOKUP with two (6 occurrences) and three (1648) arguments.}
+	\end{figure}
 
@@
 	since we wanted a range of views and backgrounds despite the persona, we
-	readily accepted this interpretive wiggle room. \par We clarified, furthermore,
-	that these notes could be directed either at the quality of the data conveyed
-	by the tool or at the tool's conveyance itself. Since the tool's philosophy was
-	based in exploration, we decided that it would not have been appropriate to
-	restrict what people were to look for, letting them find interesting stories of
-	formula construction for themselves. Additionally, either kind of comment -- on
-	data or on tool -- would direct us back to the central evaluation; a user's
-	silence, or lack of any interesting findings, would tacitly indicate that
-	perhaps the tool does not convey information well enough. \par Still, several
-	limitations cropped up during the study that complicate the evaluation. For one
-	thing, though the source of the data was not explicitly stated at the outset of
-	the session, several users studied the file names (unchanged as they were) to
-	deduce its roots in finance, if not Enron itself. Because of these notorious
-	connotations, then, some were inclined from this moment of discovery to orient
-	their exploration around finance-related functions, potentially limiting their
-	findings or perceived users for the tool -- though some also said that, without
-	this essential context, they could not have properly explored a dataset in the
-	first place. Comments like these point out the trade-offs of unguided
-	exploration, too: though it might not restrict them to a single purpose, it
-	might, at the same time, not afford them any mindset at all with which to
-	interpret the data. Another potential problem is that the data which users
-	explored was processed and created before we had fully completed the tool,
-	meaning some of the counts and patterns in the trees were inaccurate. However,
-	we decided that this was not a pressing concern, being that we were primarily
-	with whether any interesting reports could be made at all, not with whether
-	these reports were 100\% accurate assessments of reality. \par Nevertheless,
-	these user studies were a formative moment in evaluating the tool's
-	performance, generating a number of directions or corrections in the process.
-	We present an overview of responses below, with the four participants recorded
-	simply as P1 through P4. \par \subsection{Positive Responses} The inclusion of
-	formula examples, grounded in and linking back to the originating spreadsheets,
-	proved to be an especial draw to the tool. After all, none of the participants
-	professed themselves to be experts with Excel, their self-reported
-	proficiencies ranging from "fairly familiar" (P2) to "not extremely familiar"
-	(P4); even if they were experts, it would likely be unreasonable to expect an
-	evenly distributed familiarity with the 100+ function trees available.
-	Nevertheless, the list of actual formulas accessible through a node's
-	double-click allowed the users a way to find examples of formulas with exactly
-	the configuration they wanted. For example, as P1 explored the VLOOKUP
-	function, even though they knew the official API more verbosely explained its
-	signature, they said they could use the tool to collect more examples than the
-	documentation offers. \par Furthermore, it offers a simple way of finding
-	examples where certain functions were used together. though a standard
-	text-search tool might yield the same results for a function alone,
-	combinations can require more complex text queries, whereas here, the
-	information is already captured in nodes. [This paragraph contrasts it with
-	previous approaches, but lacks compelling evidence -- a lot of "mights"] \par
+	readily accepted this interpretive wiggle room. \par
+
+	We clarified, furthermore, that these notes could be directed either at the
+	quality of the data conveyed by the tool or at the tool's conveyance itself.
+	Since the tool's philosophy was based in exploration, we decided that it would
+	not have been appropriate to restrict what people were to look for, letting
+	them find interesting stories of formula construction for themselves.
+	Additionally, either kind of comment -- on data or on tool -- would direct us
+	back to the central evaluation; a user's silence, or lack of any interesting
+	findings, would tacitly indicate that perhaps the tool does not convey
+	information well enough. \par
+
+	Still, several limitations cropped up during the study that complicate the
+	evaluation. For one thing, though the source of the data was not explicitly
+	stated at the outset of the session, several users studied the file names
+	(unchanged as they were) to deduce its roots in finance, if not Enron itself.
+	Because of these notorious connotations, then, some were inclined from this
+	moment of discovery to orient their exploration around finance-related
+	functions, potentially limiting their findings or perceived users for the tool
+	-- though some also said that, without this essential context, they could not
+	have properly explored a dataset in the first place. Comments like these point
+	out the trade-offs of unguided exploration, too: though it might not restrict
+	them to a single purpose, it might, at the same time, not afford them any
+	mindset at all with which to interpret the data. Another potential problem is
+	that the data which users explored was processed and created before we had
+	fully completed the tool, meaning some of the counts and patterns in the trees
+	were inaccurate. However, we decided that this was not a pressing concern,
+	being that we were primarily with whether any interesting reports could be made
+	at all, not with whether these reports were 100\% accurate assessments of
+	reality. \par
+
+	Nevertheless, these user studies were a formative moment in evaluating the
+	tool's performance, generating a number of directions or corrections in the
+	process. We present an overview of responses below, with the four participants
+	recorded simply as P1 through P4. \par
+
+	\subsection{Positive Responses} The inclusion of formula examples, grounded in
+	and linking back to the originating spreadsheets, proved to be an especial draw
+	to the tool. After all, none of the participants professed themselves to be
+	experts with Excel, their self-reported proficiencies ranging from "fairly
+	familiar" (P2) to "not extremely familiar" (P4); even if they were experts, it
+	would likely be unreasonable to expect an evenly distributed familiarity with
+	the 100+ function trees available. Nevertheless, the list of actual formulas
+	accessible through a node's double-click allowed the users a way to find
+	examples of formulas with exactly the configuration they wanted. For example,
+	as P1 explored the VLOOKUP function, even though they knew the official API
+	more verbosely explained its signature, they said they could use the tool to
+	collect more examples than the documentation offers. \par
+
+	Furthermore, it offers a simple way of finding examples where certain functions
+	were used together. though a standard text-search tool might yield the same
+	results for a function alone, combinations can require more complex text
+	queries, whereas here, the information is already captured in nodes. [This
+	paragraph contrasts it with previous approaches, but lacks compelling evidence
+	-- a lot of "mights"] \par
+
 	\begin{wrapfigure}{l}{.12\textwidth} \centering \includegraphics{SUM}
-		\label{"fig:sum"} \end{wrapfigure} The discovery of errors and bad design,
-	whether by purpose or accident, produced the more jarring events of the study,
-	and as such, most users commented on the tool's ability to locate these
-	problems in spreadsheet design. This was often supported by the distinctive
-	visual signatures of certain bad practices: multiple arguments produce towers
-	of nodes, deep function nesting stretches the tree horizontally, and so on. As
-	such, the participants remarked on the problems quickly after opening: P3,
-	exploring the example for a 27-argument SUM (with SUM's initial appearance
-	pictured left), diagnosed the situation with either incompetency or just plain
-	weirdness; P2, meanwhile, decided that the spreadsheet's author "was having a
-	bad day" when writing an AVERAGE with 18 distinct arguments. Aside from these
-	implicit cues, there are also nodes which refer to formula errors, prefixed
-	with \#s, which P4 said could be useful if marked well. Furthermore, once these
-	errors are found, the participants could then open the offending spreadsheets,
-	discovering that, even in context, some of these formulas remained
-	incomprehensible, posing problems for mere functioning and maintainability.
-	[Hermanns discussed in one of her paper the transfer scenarios -- would go well
-	here.] The tool, then, aggregates these issues in a single place, accessible to
-	either the unguided user and the ones who know exactly where to find these
-	issues. \par The detection of bad design, however, is certainly not limited to
-	a visualization tool, and some users remarked that a tool which printed a list
-	of errors could suffice just as well for that purpose. However, they also
-	remarked that this visual interface better supports the case when searching for
-	new and unknown brands of bad smell.
+		\label{"fig:sum"} \end{wrapfigure}
+
+	The discovery of errors and bad design, whether by purpose or accident,
+	produced the more jarring events of the study, and as such, most users
+	commented on the tool's ability to locate these problems in spreadsheet design.
+	This was often supported by the distinctive visual signatures of certain bad
+	practices: multiple arguments produce towers of nodes, deep function nesting
+	stretches the tree horizontally, and so on. As such, the participants remarked
+	on the problems quickly after opening: P3, exploring the example for a
+	27-argument SUM (with SUM's initial appearance pictured left), diagnosed the
+	situation with either incompetency or just plain weirdness; P2, meanwhile,
+	decided that the spreadsheet's author "was having a bad day" when writing an
+	AVERAGE with 18 distinct arguments. Aside from these implicit cues, there are
+	also nodes which refer to formula errors, prefixed with \#s, which P4 said
+	could be useful if marked well. Furthermore, once these errors are found, the
+	participants could then open the offending spreadsheets, discovering that, even
+	in context, some of these formulas remained incomprehensible, posing problems
+	for the spreadsheet transfer scenarios as outlined by Hermans \cite{hermans2011supporting}.
+	The tool, then, aggregates
+	these issues in a single place, accessible to either the unguided user and the
+	ones who know exactly where to find these issues. \par
+
+	The detection of bad design, however, is certainly not limited to a
+	visualization tool, and some users remarked that a tool which printed a list of
+	errors could suffice just as well for that purpose. However, they also remarked
+	that this visual interface better supports the case when searching for new and
+	unknown brands of bad smell.
 
@@
 	design from it. Right now, we can't be sure; the tool would have to be
-
 	supplemented with a distinguishing eye, informed on bad design already, and
 	supplying the tool with this would take it beyond a design-agnostic view. [More
-	on this in the conclusion.] \par Furthermore, just because a user can
-	exhaustively explore every variation of how a function was used doesn't mean
-	they will learn exactly what it does. P1, in their exploration, examined
-	functions that they hadn't used before, such as KURT and PV, and described
-	precisely what types of arguments it accepted and how many. However, even after
-	exploring the spreadsheets, they could not accurately describe what the
-	functions produced without consulting the official documentation. Whether
-	through reticence of the tool or obscurity of the functions themselves, the
-	exploratory environment is not enough for independent education. However,
-	unlike the previous problem, this can be addressed, perhaps, by guiding the
-	user directly to such documentation from within the tool without violating any
-	design concerns. \par A threat to the exploratory philosophy may also mount
-	from the problem of too much data, particularly in the popular functions, like
-	SUM and IF. We had added some precautions before the study: for any position in
-	the tree, for example, only the ten most common functions were displayed
-	without clicking on the expansion arrow \includegraphics[scale=.35]{arrow}.
-	Nevertheless, P3 remarked that they specifically avoided the most popular
-	functions, anticipating a flood of nodes from which they could salvage nothing
-	interesting -- which might not have been a bad prediction, considering that the
-	SUM is built from 910 nodes and IF, at least 18000 [double-check these with
-	refined data]. P2 corroborated this by explaining how they gravitated toward
-	specific examples over the plane of nodes but complicates it further by also
-	deeming the tool at its best when it shows either every possibility of an
-	side-by-side (for comparison) or nothing on that branch at all, a balance that
-	is hard to strike with node-dense trees. \par Throughout the study, it became
-	apparent that some of the concepts, particularly optional arguments, were
-	easily lost in the representation. To illustrate this, consider the following
-	two trees: \par \includegraphics[width = .46\textwidth]{comparison} The
-	difference is, perhaps, too subtle: on the left, the tree contains instances of
-	AND functions with any number of arguments, up to four; on the right, the tree
-	contains only instances with exactly four arguments. In other words, an
-	instance of "=AND(A1, B2, C3, D4)" would be found in both trees, while
-	"=AND(A1, B2)" would be found in only the left. Though the users naturally did
-	not explicitly report misinterpreting the icons, it became clear in their
-	out-loud thoughts that they viewed each box as a fundamentally different set of
-	possibilities in formula construction rather than just a specific parameter.
-	Though we clarified the meanings when these misunderstandings became apparent,
-	these events point to a failure in the tool to properly indicate every function
-	with clarity.   \par
+	on this in the conclusion.] \par
+
+	Furthermore, just because a user can exhaustively explore every variation of
+	how a function was used doesn't mean they will learn exactly what it does. P1,
+	in their exploration, examined functions that they hadn't used before, such as
+	KURT and PV, and described precisely what types of arguments it accepted and
+	how many. However, even after exploring the spreadsheets, they could not
+	accurately describe what the functions produced without consulting the official
+	documentation. Whether through reticence of the tool or obscurity of the
+	functions themselves, the exploratory environment is not enough for independent
+	education. However, unlike the previous problem, this can be addressed,
+	perhaps, by guiding the user directly to such documentation from within the
+	tool without violating any design concerns. \par
+
+	A threat to the exploratory philosophy may also mount from the problem of too
+	much data, particularly in the popular functions, like SUM and IF. We had added
+	some precautions before the study: for any position in the tree, for example,
+	only the ten most common functions were displayed without clicking on the
+	expansion arrow \includegraphics[scale=.35]{arrow}. Nevertheless, P3 remarked
+	that they specifically avoided the most popular functions, anticipating a flood
+	of nodes from which they could salvage nothing interesting -- which might not
+	have been a bad prediction, considering that the SUM is built from 910 nodes
+	and IF, at least 18000 [double-check these with refined data]. P2 corroborated
+	this by explaining how they gravitated toward specific examples over the plane
+	of nodes but complicates it further by also deeming the tool at its best when
+	it shows either every possibility of an side-by-side (for comparison) or
+	nothing on that branch at all, a balance that is hard to strike with node-dense
+	trees. \par
+
+	\begin{figure}
+		\centering 
+		\includegraphics{longIF}
+		\label{"fig:longif"}
+		\caption{The many possibilities of IF, argument 3, demonstrate the problem of
+			having too many options.}
+	 \end{figure}
+
+	Throughout the study, it became apparent that some of the concepts,
+	particularly optional arguments, were easily lost in the representation. To
+	illustrate this, consider the following two trees: \par
+
+	\includegraphics[width = .46\textwidth]{comparison}
+
+	The difference is, perhaps, too subtle: on the left, the tree contains
+	instances of AND functions with any number of arguments, up to four; on the
+	right, the tree contains only instances with exactly four arguments. In other
+	words, an instance of "=AND(A1, B2, C3, D4)" would be found in both trees,
+	while "=AND(A1, B2)" would be found in only the left. Though the users
+	naturally did not explicitly report misinterpreting the icons, it became clear
+	in their out-loud thoughts that they viewed each box as a fundamentally
+	different set of possibilities in formula construction rather than just a
+	specific parameter. Though we clarified the meanings when these
+	misunderstandings became apparent, these events point to a failure in the tool
+	to properly indicate every function with clarity.   \par
 
@@
 	trade-offs in which we found no acceptable way to win the best of both worlds,
-	and necessary compromises were made. \par Because the data collection depends
-	on POI's formula parser, it affords no leeway or partial information from a
-	formula; it either processes it perfectly or throws it out. As such, the
-	visualization inhibits insight into anything with syntactical errors or
-	third-party functions that can't be evaluated without additional tools. Note,
-	however, that this does not include standard Excel errors like \#REF! and
-	\#DIV/0, which the parser handles well. This poses more egregious problems,
-	however, when POI does not support the parsing of certain functions, such as
-	EOMONTH (as obscure as it may be), preventing the healthy growth of those
-	trees. \par Many functions have an expected order of arguments, but some, like
-	SUM and MATCH, can be reordered in various ways and maintain their value.
-	However, the representation that this tool uses reinforces for all functions
-	that the order is important, even in these exceptions. Future work could design
-	a new family of tree to accommodate these loose cases, however, by bucketing
+	and necessary compromises were made. \par
+
+	Because the data collection depends on POI's formula parser, it affords no
+	leeway or partial information from a formula; it either processes it perfectly
+	or throws it out. As such, the visualization inhibits insight into anything
+	with syntactical errors or third-party functions that can't be evaluated
+	without additional tools. Note, however, that this does not include standard
+	Excel errors like \#REF! and \#DIV/0, which the parser handles well. This poses
+	more egregious problems, however, when POI does not support the parsing of
+	certain functions, such as EOMONTH (as obscure as it may be), preventing the
+	healthy growth of those trees. \par
+
+	Many functions have an expected order of arguments, but some, like SUM and
+	MATCH, can be reordered in various ways and maintain their value. However, the
+	representation that this tool uses reinforces for all functions that the order
+	is important, even in these exceptions. Future work could design a new family
+	of tree to accommodate these loose cases, however, by bucketing
 	order-insignificant arguments together; this, of course, would still have to
-	address the profusion of co-presented data. \par A larger and related problem
-	is the loss of argument combination. In the example in section B, we saw how
-	the tools conveys which arguments are used most often on each side of an equals
-	sign, but it does not encode how these whether references were actually
-	compared to strings and numbers the most or whether it corresponded more to all
-	the arguments beneath those two
+	address the profusion of co-presented data. \par
 
-	\section{Conclusion} Why design agnostic?
+	A larger and related problem is the loss of argument combination. For example,
+	figure \ref{"fig:index"} shows the situation of the INDEX tree, wherein each
+	argument position has a few distinct possibilities. While it is easy to break down,
+	for each position, which argument types are most common (ranges, MATCH, and numbers,
+	respectively), the tree is silent on whether MATCH functions are used together
+	in the second and third arguments, among other concerns. Though these argument
+	combinations could be pieced together by manually inspecting the lists of examples,
+	it is nevertheless inconvenient, though not outside the realm of future improvement.
 
-	[to be filled in]
+	\begin{figure}
+		\centering
+		\includegraphics[width=.5\textwidth]{index}
+		\label{"fig:index"}
+		\caption{A difficult question: how often is MATCH used in both the second
+			and third arguments?}
+	\end{figure}
 
-	-extensible to other spreadsheets? % conference papers do not normally have an
-	% appendix
+	%To be sure, though, there is still plenty of work to improve this tool. One activity
+	%it does not support well now is that of comparison: for all of it's ability to spit
+	%out numbers and quantify patterns,
+
+	\section{Future Work}
+	For these user and case studies, we relied solely on Enron's spreadsheets to
+	find our results. However, Enron's focus on finances and energy represents only one context
+	in which people use spreadsheets. Other corpora, like EUSES and Fuse, draw from other 
+	domains and industries, and, as Jansen found in his comparison
+	of spreadsheets Enron and EUSES, different companies rely on different functions.
+	Though the use of a single corpora nevertheless suffices for evaluation, 
+	we may yet be able to find more interesting applications and uses for the tool
+	in other types of spreadsheet. \par
+
+	Additionally, Excel is only one of many different spreadsheet products available, 
+	chosen for this project because of its prevalence. But other spreadsheets, such as
+	Gnumeric\footnote{http://www.gnumeric.org/} or Google Sheets \footnote{https://www.google.com/sheets/about/}
+	represent other approaches to spreadsheet systems. Even within identical domains,
+	there's no guarantee that practices and functions will hold across these varied
+	offerings. This, then, warrants further analysis, in which good visualization might
+	serve well. \par
+
+	\section{Conclusion} 
+	This paper presents a tool to support the exploration of function combinations
+	throughout a given spreadsheet dataset. By taking a agnostic approach to design
+	quality, it attempts to convey the dataset's spreadsheet practices as is: the
+	common along with the anomalous, and the well-designed along with the odorous.
+	As seen in the user and case studies, this allows it to take on several potential
+	roles at once, such as an environment for search out bad code smells as well as
+	a repository for examples for learning new techniques. \par
+
+	To be sure, we still have a lot of room for improvement. Though the exploratory
+	philosophy fostered certain goals well, such as the ability to discover new
+	problematic smells without knowing beforehand what they are, it also hindered
+	the project in others. Some users, for example, found the trees of popular 
+	functions to be too crowded to explore well, or that their intention to use
+	the tool to examine the good or the bad design exclusively was not fully
+	supported by a tool that claimed to know neither. Many of the problems, however,
+	were not essential to this design conflict and will be overcome in future
+	iterations of design by refining icons and improving maneuverability. \par
+
+	Either way, the visualization of these large datasets represents an important
+	step in improving practice overall. By taking these voluminous oceans of data
+	offered in spreadsheet corpora and rendering them comprehensible through
+	images, we seek to draw attention to valuable information that would otherwise
+	go unnoticed.
 

### 2016-04-20 src/core/FormulaToken.java

@@ -5,6 +5,7 @@ import org.apache.poi.ss.formula.FormulaParsingWorkbook;
 import org.apache.poi.ss.formula.FormulaRenderingWorkbook;
 import org.apache.poi.ss.formula.ptg.AreaPtgBase;
 import org.apache.poi.ss.formula.ptg.BoolPtg;
+import org.apache.poi.ss.formula.ptg.ErrPtg;
 import org.apache.poi.ss.formula.ptg.IntPtg;
 import org.apache.poi.ss.formula.ptg.NamePtg;
 import org.apache.poi.ss.formula.ptg.NumberPtg;
@@ -105,8 +106,12 @@ public class FormulaToken {
       type = "~STR~";
     else if (tok instanceof BoolPtg)                              //TRUE
       type = "~BOOL~";
-    else                                                          //errors, for example
-      type = "~OTHER~";
+    else if (tok instanceof ErrPtg)
+      type = "~ERROR~";
+    else {                                                        
+      type = "~OTHER~"; //TODO
+      System.out.println(tok.toFormulaString() + " " + tok.getClass());
+    }
     
     return type;
   }

### 2016-04-20 src/viz/treeMaker.js

@@ -130,7 +130,7 @@ d3.json(src, function(error, json) {
 
     scale = d3.scale.log()
         .domain([1, root.frequency])
-        .range([3, 20])
+        .range([3, 30])
         .nice();
 
     root.children.forEach(function(c) {
@@ -254,7 +254,7 @@ function update(src) {
         d.y0 = d.y;
     });
 
-    center(src);
+    //center(src);
 }
 
 /**
@@ -398,6 +398,12 @@ function mouseover(d) {
             else if (d.children) return empty_hover; //Get gray.
             else return empty_col; //Don't change if no children.
         });
+
+    /*d3.selectAll("svg g").style("fill-opacity", ".25");
+    (function opaqueTree(c) {
+      d3.select("#n" + c.id).style("fill-opacity", 1);
+      if (c.parent) opaqueTree(c.parent);
+    })(d);*/
 }
 
 /**
@@ -421,6 +427,8 @@ function mouseleave(d) {
         .style("fill", function(d) {
             return d._children ? circle_col : (d.children ? circle_empty : empty_col);
         });
+
+    //d3.selectAll("svg g").style("fill-opacity", "1");
 }
 
 function rect_mouseover(d) {

### 2016-04-21 doc/paper.tex
Progress from yesterday. Fixes #34, fixes #37, fixes #40, fixes #41, fixes #43, fixes #44, fixes #45

@@
 
+\usepackage{textcomp}
+\newcommand{\toolname}{Perquimans?!}
 \begin{document} \title{A Tool for Visualizing Patterns of Spreadsheet Function
@@
 	% affiliations
-	\author{\IEEEauthorblockN{Justin A. Middleton} \IEEEauthorblockA{North Carolina
-			State University\\ Raleigh, North Carolina}}
+	\author{
+		\IEEEauthorblockN{Justin A. Middleton, Emerson Murphy-Hill} 
+		\IEEEauthorblockA{North Carolina
+			State University\\ Raleigh, North Carolina, USA}		
+	}
 
@@
 	\maketitle
+
+	\begin{figure*}[t] \includegraphics[width = \textwidth]{IFargslabel} \caption{A
+			picture of the tool.} \centering \label{fig:fullpic} \end{figure*}
 
@@
 
-	\section{Introduction} Business and research alike owe a lot to spreadsheets, the
-	tabular interface that offers users a structured way to store and manipulate
-	potentially huge bodies of data. Their allure is in their versatility: while
-	the novice can still work without a deep knowledge of programming, they can
-	learn to expedite their work by building programs out of several available
-	functions \cite{nardi1990spreadsheet}. As such, it should not be surprising
-	that when Scaffidi and colleagues estimated that over 50 million U.S. workers
-	could be using them by 2012, with 25 million of them writing programs
-	\cite{scaffidi2005estimating}. \par
+	\section{Introduction} Spreadsheets surround us, ordering the ever-growing
+	flood of data that we produce. They serve key roles in industry, where as much
+	as 95\% of U.S. financial firms use them daily \cite{panko2008sarbanes}, and academia,
+	where teachers can use them to track research and students' grades, not to
+	mention many other lines of work \cite{ko2011state}. It's this flexibility that
+	grants them their allure: while a novice can still work without much experience,
+	spreadsheets offer hundreds of specialized functions to fulfill a wide range of
+	advanced needs, from complex statistics to text manipulation
+	\cite{nardi1990spreadsheet}. As such, it should be no surprise that tens of
+	millions of workers rely on these programs every day
+	\cite{scaffidi2005estimating}.
 
-	Considering this ubiquity, it's crucial to understand how people are actually
-	using spreadsheets. After all, failures in their practice can be ruinous, as
-	demonstrated in EuSpRIG's many horror stories of spreadsheets gone wrong. In
-	2013, for example, they detail the influence of an economics paper on debt and
-	national growth which shaped many political initiates around it, only to
-	discover that the spreadsheets used in the data analysis contained an error
-	that reversed the findings. The other stories, likewise, do not augur well if
-	shoddy spreadsheet practices persist
-	\footnote{http://www.eusprig.org/horror-stories.htm}. \par
+	However, this ubiquity is not without danger: as more people adopt these tools
+	and make larger and more complex sheets, the cost of failure grows too. To
+	stress this, the European Spreadsheet Risks Interest Group (EuSpRIG) documents
+	many horror stories of spreadsheets gone terribly
+	wrong\footnote{http://www.eusprig.org/horror-stories.htm}. One such story tells
+	of a 2013 economics paper which drew stark connections between debt and
+	national growth. Its findings shaped many political initiatives throughout the
+	United States and Europe. However, other researchers soon discovered that a
+	critical coding error in the research spreadsheets hampered the results and
+	that, by correcting this error, they completely reversed the findings! And this
+	is only one of several accounts; even if most spreadsheet errors are relatively
+	benign, poor spreadsheet practice can risk millions, if not billions, of
+	dollars \cite{powell2009impact}.
 
-	Fortunately, many spreadsheet researchers have assembled and released a number
-	of spreadsheet corpora to inform work of how people actually use these tools.
-	Collections like EUSES \cite{fisher2005euses}, FUSE \cite{barik2015fuse}, and
-	the Enron corpus \cite{hermans2015enron} have already enabled fruitful work
-	across the field. Hermans and colleagues, for example, used the EUSES corpus in
-	2011 to inform and evaluate their work on exploring code smells, or inelegant
-	places in code that suggest the need for refactoring, between worksheets
-	\cite{hermans2012detecting}. Furthermore, these corpora have been compared
-	and cross-referenced, such as in Jansen's contrast on Enron and EUSES, to
-	gather insight in how different domains use spreadsheets differently 
-	\cite{jansen2015enron}, or in Aivaloglou and colleague's evaluation of a
-	spreadsheet grammar \cite{aivaloglou2015grammar}.\par
+	From these stories, we can see the dire importance of understanding how people
+	actually use spreadsheets, if only to avoid disasters. Fortunately, spreadsheet
+	researchers have supported this by amassing spreadsheet collections from
+	diverse sources, industrial to academic. Collections like EUSES
+	\cite{fisher2005euses}, Fuse \cite{barik2015fuse}, and the Enron corpus
+	\cite{hermans2015enron} have already fueled productive research across the
+	field, such as in Hermans' \cite{hermans2012detecting} or Jansen's
+	\cite{jansen2015code} search for code smells\footnote{Or, instances of
+		inelegant code that do not necessarily cause problems alone but nevertheless
+		suggest a need for refactoring to prevent future problems. More on this in
+		section IV.} in spreadsheet environments or Aivaloglou and colleague's work on
+	making a grammar to capture every possible spreadsheet program in Excel
+	\cite{aivaloglou2015grammar}. Additionally, some research has focused simply on
+	comparing these collections, as Jansen did in 2015, to discover variation in
+	spreadsheet techniques over time and location \cite{jansen2015enron}.
 
-	A tool, then, that empowers users of any intention to explore these datasets
-	would be rife with potential. On a simple level, the tool could provide
-	concrete statistics on which functions are used in practice most (or least)
-	often for a given dataset. Beyond this, though, it could also inform future
-	work on recommending functions through an understanding of this patterns, or it
-	could guide API improvement by suggesting functions to add or prune based how
-	people actually use them. Furthermore, if the tool maintains the connection
-	between its broad patterns and the actual instances of formulae in workbooks,
-	it could serve as a boon to educators not only by showing which functions and
-	combinations are most practical to learn but also by offering a bounty of
-	instructive, and real, examples \par
+	Considering the sheer value of spreadsheets and all of these resources to describe
+	their use, it becomes necessary that we design tools to make sense of it all. Tools,
+	then, that empower people to explore datasets are rife with the potential to improve
+	the current design of spreadsheets themselves and educate new generations of spreadsheets 
+	users on how to work best.
 
-	This paper contributes a tool, informed by some of the aforementioned
-	spreadsheet corpora, that seeks to accomplish these tasks by offering an
-	interactive interface for exploring how people combine functions. It seeks to
-	balance several needs, such as capturing these patterns in a broad enough
-	overview while still be specific enough lead back to the precise places in
-	spreadsheets where these patterns are realized. Along with the tool, then, is
-	also a discussion of the various goals which the tool seeks to fulfill and the
-	trade-offs that we negotiated at each point. All of this culminates in an
-	evaluation of the tool through a study of possible cases to which the tool
-	might apply.
+	This paper contributes such a tool, \toolname, that attempts to fulfill this by building on the aforementioned
+	spreadsheet corpora. Working with spreadsheets in Excel, \toolname focuses primarily
+	on the functions, like SUM and IF and hundreds more, which are the building blocks
+	of formula and programs which determine values across a spreadsheet. The tool creates
+	an interactive, exploratory visualization which captures how people combine these functions
+	in a selected collection of spreadsheets, quantifying the broad patterns of function nesting
+	while also being specific enough to find anomalous formulae and link them
+	back to the specific cell in spreadsheets where they originate. \par
 
-	\section{Related Work} This tool comes from a line of spreadsheet visualization
-	tools before it, each with a different focus. Some tools, such as Igarashi and
-	colleague's fluid visualizations \cite{igarashi1998fluid}, seek to visualize
-	the hidden formulas within a spreadsheet by imposing the dataflow graphs over
-	the cells. Likewise, Clermont \cite{clermont2003scalable} (and Hipfl
-	\cite{hipfl2008using}, who extended his work) explored various ways of
-	visualizing groups of related cells through similar functions, neighbors, or
-	references. Others focus on creating visualizations outside of the sheets:
-	Hermans and colleagues address a spreadsheet programmer's information needs
-	through their work on the tools GyroSAT \cite{hermans2011supporting} and Breviz
-	\cite{hermans2011breviz} to make dataflow diagrams of individual spreadsheets.
-	These, however, tend to focus on individual spreadsheets and not bodies of
-	them. \par
+	Alongside the tool, we discuss several of the key decisions we faced during design,
+	such as what to do with redundant formulae in a sheet or how to represent optional
+	arguments, and we describe how our overall design goals both helped and hindered this
+	process. We then apply the tool to a number of case studies to evaluate how much it
+	could contribute to several different contexts:
 
-	Nevertheless, other studies and tools focus more on evaluating the content of
-	the cells therein. Badame, for example, implements a number of Excel formula
-	refactorings and uses Euses in part to evaluate it
-	\cite{badame2012refactoring}. Hermans, leveraging her work with the
-	aforementioned dataflow diagrams, approached the same dataset to assess the
-	prevalence of common inter-worksheet smells, such as feature envy and
-	inappropriate intimacy \cite{hermans2012detecting}. Cunha and colleagues,
-	likewise, constructed and refined a catalogue of smells and implemented the
-	SmellSheet Detective tool to detect bad smells in chosen spreadsheets
-	\cite{cunha2012towards}, which Abreu and colleagues later extended to detect
-	faults. \cite{abreu2014smelling}.\par
+	\begin{itemize}
+		\item API improvement
+		\item Detection of code smells
+		\item Spreadsheet education
+	\end{itemize}
 
-	Implicit in this study is an exploration of how users interact with the Excel
-	API. Previous research, such as the first study on the Enron spreadsheet corpus
-	\cite{hermans2015enron}, on how users employ certain functions or commands.
-	Researchers have applied such questions to other contexts as well, such as
-	Murphy and colleague's study into how Java developers use Eclipse and what
-	commands they use most often \cite{murphy2006java}.  Others focus on the
-	documentation of the API itself: Robillard and DeLine, for example conducted a
-	series of surveys and interviews to diagnose common problems with learning
-	APIs, and they found that code examples, one of the focuses of this tool, is
-	one of the most important aids to have in learning a new system
-	\cite{robillard2011field}.
+	To round out that discussion, we also conducted a user study to judge how usable 
+	and intuitive the tool actually is. This grounds the discussion of its potential uses
+	while also underscoring some of its inherent limitations and setting the way
+	for future extensions and improvements upon the concept.
+
+	\section{Related Work} Given humanity's affinity for visual information,
+	visualizations have long been prized for their ability to communicate
+	information quickly and efficient \cite{baeza1999modern}; the visualization of
+	spreadsheets, therefore, has offered much room for research. Several previous
+	tools work within a spreadsheet, seeking to clarify the connections between the
+	visible values in cells, the formulae that produce them, and the dependencies
+	between cells that inform them. Igarashi and colleague's fluid visualizations
+	\cite{igarashi1998fluid}, for example, do this by imposing lines, color, and
+	animation over the spreadsheet to visually explain these tangled connections.
+	Likewise, Clermont explored ways of grouping cells by color and border that
+	were related through similar functions, neighbors, or references
+	\cite{clermont2003scalable}, and Hipfl extended this work by incorporating the
+	layouts and labels of spreadsheets \cite{hipfl2008using}. Other tools focus on
+	creating visualizations external to the sheets. Hermans and colleagues address a
+	spreadsheet programmer's information by making dataflow diagrams from individual sheets
+	through the tools GyroSAT \cite{hermans2011supporting} and Breviz \cite{hermans2011breviz}. 
+	\toolname is among the latter class, creating standalone visualizations about spreadsheets. In contrast to Hermans' work, though, our work focuses on representing
+	functions and how they comprise complex formula, rather than exploring the data
+	structures of any particular spreadsheet.  \par
+
+	Many other tools inspect the structure of formulas but often from the
+	perspective of finding bad design.  Following Fowler's initial description of
+	code smells in object-oriented design \cite{fowler2009refactoring}, many
+	researchers have applied similar observations to spreadsheets and have
+	cataloged classes of problematic formulae \cite{hermans2012detecting}
+	\cite{cunha2012towards} \cite{asavametha2012detecting}, often accompanying them
+	with detection tools \cite{abreu2014smelling} and investigations \cite{jansen2015code}.
+For example, Hermans, leveraging her work with the aforementioned dataflow diagrams, has worked with assessing common inter-worksheet smells, such as feature envy and
+	inappropriate intimacy, wherein references between worksheets (rather
+	than cells) in a file suggest a problem. \cite{hermans2012detectinginter}. Other
+	tools, like Badam's Excel refactoring \cite{badame2012refactoring}, are concerned
+	more with understanding the formula in the service of changing them. 	
+	However, these studies define standards of poor design and orient their searches
+	around them. Though \toolname supports the search for bad design, as we will see, 
+	the tool itself takes a much more agnostic approach in presentation, offering 
+	examples without regard for design quality. \par
+
+	Implicit in this study is an exploration of the Excel API and how people use
+	it. Previous research, such as the first study on the Enron spreadsheets
+	\cite{hermans2015enron} or in its comparison with the EUSUS corpus
+	\cite{jansen2015enron}, quantify how ofter users employ certain functions but
+	not how they combine them. Researchers have applied such questions to other
+	contexts as well, such as Murphy and colleague's study into how Java developers
+	use Eclipse and what commands they use most often \cite{murphy2006java}. 
+	Others focus on the documentation of the API itself: Robillard and DeLine, for
+	example conducted a series of surveys and interviews to diagnose common
+	problems with learning APIs, and they found that code examples, one of the
+	focuses of this tool, is one of the most important aids to have in learning a
+	new system \cite{robillard2011field}. Though this paper applies the tool to the
+	Enron corpus specifically, the tool itself is not limited to this; it can be 
+	readily applied to any collection of Excel spreadsheets a user gives it.
 
@@
 
-	\centerline{\includegraphics{start}}
+	\begin{figure}
+		\centering
+		\includegraphics{start}
+		\label{fig:startpic}
+		\caption{How the IF tree looks at the start}
+	\end{figure}
 
@@
 	more examples from dataset.
-
-	\begin{figure*}[t] \includegraphics[width = \textwidth]{IFargslabel} \caption{A
-			picture of the tool.} \centering \label{fig:fullpic} \end{figure*}
 

### 2016-04-21 doc/paper.tex
Reordering section 3. Fixes #53.

@@
 
-	\section{Approach/Methodology} \subsection{Walkthrough of Tool} Before
+	\section{Approach/Methodology}
+
+	\subsection{Design Goals} In visualizing the spreadsheet data, I outlined a few
+	core goals for what the tool should accomplish: \begin{itemize} \item [1]
+		\textbf{Draw an interactive interface to explore observed function
+			combinations.} The combination space for all Excel functions is massive, let
+		alone the space for observed formulas. Working from data with actual referents
+		in practice, the tool must aid the user in navigating this space. \item [2]
+		\textbf{Emphasize the quantitative patterns in formula construction.} The tool,
+		accommodating datasets of a few spreadsheets to millions, should address the
+		questions of how often the end users employed a certain function and where they
+		used it. In this way, it must show precise metrics, such as frequency of  use
+		and depth of function nesting, of the dataset it conveys. \item [3]
+		\textbf{Promote a qualitative understanding of the patterns.} Lest these
+		patterns remain abstract, the tool should supplement its observations with
+		concrete instances of relevant formulas from the corpus. Ideally, it should
+		even direct users to the exact cell in the spreadsheets where the formula was
+		used, contextualizing the functions. \end{itemize} \par
+
+	Likewise, to bound our scope, we outlined a few goals to specifically avoid
+	accomplishing with this: \begin{itemize} \item [!1] \textbf{Do not try to
+			directly explain what a function does.} Though the tool tries to foster tries
+		understanding by linking pattern to example, it won't provide a precise
+		description of what a function accomplishes. The tool's user must infer this.
+		\item [!2] \textbf{Do not create new formulas.} This is essentially an
+		exploratory tool, not a generative one. It should not produce any information
+		other than new views of the original data. \item [!3] \textbf{Do not visualize
+			individual formulas.} Though there is room to explore the place of a single
+		function in the group, the tool must design the core visualization around the
+		entire body of data, not the other way around. \end{itemize}
+
+	\subsection{Walkthrough of Tool} Before
 	discussing the minutiae of how the tool was developed, it will help first to
@@
 	more examples from dataset.
-
-	\subsection{Design Goals} In visualizing the spreadsheet data, I outlined a few
-	core goals for what the tool should accomplish: \begin{itemize} \item [1]
-		\textbf{Draw an interactive interface to explore observed function
-			combinations.} The combination space for all Excel functions is massive, let
-		alone the space for observed formulas. Working from data with actual referents
-		in practice, the tool must aid the user in navigating this space. \item [2]
-		\textbf{Emphasize the quantitative patterns in formula construction.} The tool,
-		accommodating datasets of a few spreadsheets to millions, should address the
-		questions of how often the end users employed a certain function and where they
-		used it. In this way, it must show precise metrics, such as frequency of  use
-		and depth of function nesting, of the dataset it conveys. \item [3]
-		\textbf{Promote a qualitative understanding of the patterns.} Lest these
-		patterns remain abstract, the tool should supplement its observations with
-		concrete instances of relevant formulas from the corpus. Ideally, it should
-		even direct users to the exact cell in the spreadsheets where the formula was
-		used, contextualizing the functions. \end{itemize} \par
-
-	Likewise, to bound our scope, we outlined a few goals to specifically avoid
-	accomplishing with this: \begin{itemize} \item [!1] \textbf{Do not try to
-			directly explain what a function does.} Though the tool tries to foster tries
-		understanding by linking pattern to example, it won't provide a precise
-		description of what a function accomplishes. The tool's user must infer this.
-		\item [!2] \textbf{Do not create new formulas.} This is essentially an
-		exploratory tool, not a generative one. It should not produce any information
-		other than new views of the original data. \item [!3] \textbf{Do not visualize
-			individual formulas.} Though there is room to explore the place of a single
-		function in the group, the tool must design the core visualization around the
-		entire body of data, not the other way around. \end{itemize}
 

### 2016-04-21 doc/paper.tex
Methodology work. Fixes #63, fixes #64.

@@
 
-\usepackage{textcomp}
-\newcommand{\toolname}{Perquimans?!}
-\begin{document} \title{A Tool for Visualizing Patterns of Spreadsheet Function
-		Combinations}
+\usepackage{textcomp} \newcommand{\toolname}{Perquimans?!} \begin{document}
+	\title{A Tool for Visualizing Patterns of Spreadsheet Function Combinations}
 
@@
 	% affiliations
-	\author{
-		\IEEEauthorblockN{Justin A. Middleton, Emerson Murphy-Hill} 
-		\IEEEauthorblockA{North Carolina
-			State University\\ Raleigh, North Carolina, USA}		
-	}
+	\author{ \IEEEauthorblockN{Justin A. Middleton, Emerson Murphy-Hill}
+		\IEEEauthorblockA{North Carolina State University\\ Raleigh, North Carolina,
+			USA} }
 
@@
 	flood of data that we produce. They serve key roles in industry, where as much
-	as 95\% of U.S. financial firms use them daily \cite{panko2008sarbanes}, and academia,
-	where teachers can use them to track research and students' grades, not to
-	mention many other lines of work \cite{ko2011state}. It's this flexibility that
-	grants them their allure: while a novice can still work without much experience,
-	spreadsheets offer hundreds of specialized functions to fulfill a wide range of
-	advanced needs, from complex statistics to text manipulation
-	\cite{nardi1990spreadsheet}. As such, it should be no surprise that tens of
-	millions of workers rely on these programs every day
+	as 95\% of U.S. financial firms use them daily \cite{panko2008sarbanes}, and
+	academia, where teachers can use them to track research and students' grades,
+	not to mention many other lines of work \cite{ko2011state}. It's this
+	flexibility that grants them their allure: while a novice can still work
+	without much experience, spreadsheets offer hundreds of specialized functions
+	to fulfill a wide range of advanced needs, from complex statistics to text
+	manipulation \cite{nardi1990spreadsheet}. As such, it should be no surprise
+	that tens of millions of workers rely on these programs every day
 	\cite{scaffidi2005estimating}.
@@
 
-	Considering the sheer value of spreadsheets and all of these resources to describe
-	their use, it becomes necessary that we design tools to make sense of it all. Tools,
-	then, that empower people to explore datasets are rife with the potential to improve
-	the current design of spreadsheets themselves and educate new generations of spreadsheets 
-	users on how to work best.
+	Considering the sheer value of spreadsheets and all of these resources to
+	describe their use, it becomes necessary that we design tools to make sense of
+	it all. Tools, then, that empower people to explore datasets are rife with the
+	potential to improve the current design of spreadsheets themselves and educate
+	new generations of spreadsheets users on how to work best.
 
-	This paper contributes such a tool, \toolname, that attempts to fulfill this by building on the aforementioned
-	spreadsheet corpora. Working with spreadsheets in Excel, \toolname focuses primarily
-	on the functions, like SUM and IF and hundreds more, which are the building blocks
-	of formula and programs which determine values across a spreadsheet. The tool creates
-	an interactive, exploratory visualization which captures how people combine these functions
-	in a selected collection of spreadsheets, quantifying the broad patterns of function nesting
-	while also being specific enough to find anomalous formulae and link them
-	back to the specific cell in spreadsheets where they originate. \par
+	This paper contributes such a tool, \toolname, that attempts to fulfill this by
+	building on the aforementioned spreadsheet corpora. Working with spreadsheets
+	in Excel, \toolname focuses primarily on the functions, like SUM and IF and
+	hundreds more, which are the building blocks of formula and programs which
+	determine values across a spreadsheet. The tool creates an interactive,
+	exploratory visualization which captures how people combine these functions in
+	a selected collection of spreadsheets, quantifying the broad patterns of
+	function nesting while also being specific enough to find anomalous formulae
+	and link them back to the specific cell in spreadsheets where they originate.
+	\par
 
-	Alongside the tool, we discuss several of the key decisions we faced during design,
-	such as what to do with redundant formulae in a sheet or how to represent optional
-	arguments, and we describe how our overall design goals both helped and hindered this
-	process. We then apply the tool to a number of case studies to evaluate how much it
-	could contribute to several different contexts:
+	Alongside the tool, we discuss several of the key decisions we faced during
+	design, such as what to do with redundant formulae in a sheet or how to
+	represent optional arguments, and we describe how our overall design goals both
+	helped and hindered this process. We then apply the tool to a number of case
+	studies to evaluate how much it could contribute to several different contexts:
 
-	\begin{itemize}
-		\item API improvement
-		\item Detection of code smells
-		\item Spreadsheet education
-	\end{itemize}
+	\begin{itemize} \item API improvement \item Detection of code smells \item
+		Spreadsheet education \end{itemize}
 
-	To round out that discussion, we also conducted a user study to judge how usable 
-	and intuitive the tool actually is. This grounds the discussion of its potential uses
-	while also underscoring some of its inherent limitations and setting the way
-	for future extensions and improvements upon the concept.
+	To round out that discussion, we also conducted a user study to judge how
+	usable and intuitive the tool actually is. This grounds the discussion of its
+	potential uses while also underscoring some of its inherent limitations and
+	setting the way for future extensions and improvements upon the concept.
 
@@
 	layouts and labels of spreadsheets \cite{hipfl2008using}. Other tools focus on
-	creating visualizations external to the sheets. Hermans and colleagues address a
-	spreadsheet programmer's information by making dataflow diagrams from individual sheets
-	through the tools GyroSAT \cite{hermans2011supporting} and Breviz \cite{hermans2011breviz}. 
-	\toolname is among the latter class, creating standalone visualizations about spreadsheets. In contrast to Hermans' work, though, our work focuses on representing
-	functions and how they comprise complex formula, rather than exploring the data
-	structures of any particular spreadsheet.  \par
+	creating visualizations external to the sheets. Hermans and colleagues address
+	a spreadsheet programmer's information by making dataflow diagrams from
+	individual sheets through the tools GyroSAT \cite{hermans2011supporting} and
+	Breviz \cite{hermans2011breviz}. \toolname is among the latter class, creating
+	standalone visualizations about spreadsheets. In contrast to Hermans' work,
+	though, our work focuses on representing functions and how they comprise
+	complex formula, rather than exploring the data structures of any particular
+	spreadsheet.  \par
 
@@
 	\cite{cunha2012towards} \cite{asavametha2012detecting}, often accompanying them
-	with detection tools \cite{abreu2014smelling} and investigations \cite{jansen2015code}.
-For example, Hermans, leveraging her work with the aforementioned dataflow diagrams, has worked with assessing common inter-worksheet smells, such as feature envy and
-	inappropriate intimacy, wherein references between worksheets (rather
-	than cells) in a file suggest a problem. \cite{hermans2012detectinginter}. Other
-	tools, like Badam's Excel refactoring \cite{badame2012refactoring}, are concerned
-	more with understanding the formula in the service of changing them. 	
-	However, these studies define standards of poor design and orient their searches
-	around them. Though \toolname supports the search for bad design, as we will see, 
-	the tool itself takes a much more agnostic approach in presentation, offering 
-	examples without regard for design quality. \par
+	with detection tools \cite{abreu2014smelling} and investigations
+	\cite{jansen2015code}. For example, Hermans, leveraging her work with the
+	aforementioned dataflow diagrams, has worked with assessing common
+	inter-worksheet smells, such as feature envy and inappropriate intimacy,
+	wherein references between worksheets (rather than cells) in a file suggest a
+	problem. \cite{hermans2012detectinginter}. Other tools, like Badam's Excel
+	refactoring \cite{badame2012refactoring}, are concerned more with understanding
+	the formula in the service of changing them. However, these studies define
+	standards of poor design and orient their searches around them. Though
+	\toolname supports the search for bad design, as we will see, the tool itself
+	takes a much more agnostic approach in presentation, offering examples without
+	regard for design quality. \par
 
@@
 	contexts as well, such as Murphy and colleague's study into how Java developers
-	use Eclipse and what commands they use most often \cite{murphy2006java}. 
-	Others focus on the documentation of the API itself: Robillard and DeLine, for
-	example conducted a series of surveys and interviews to diagnose common
-	problems with learning APIs, and they found that code examples, one of the
-	focuses of this tool, is one of the most important aids to have in learning a
-	new system \cite{robillard2011field}. Though this paper applies the tool to the
-	Enron corpus specifically, the tool itself is not limited to this; it can be 
-	readily applied to any collection of Excel spreadsheets a user gives it.
+	use Eclipse and what commands they use most often \cite{murphy2006java}. Others
+	focus on the documentation of the API itself: Robillard and DeLine, for example
+	conducted a series of surveys and interviews to diagnose common problems with
+	learning APIs, and they found that code examples, one of the focuses of this
+	tool, is one of the most important aids to have in learning a new system
+	\cite{robillard2011field}. Though this paper applies the tool to the Enron
+	corpus specifically, the tool itself is not limited to this; it can be readily
+	applied to any collection of Excel spreadsheets a user gives it.
 
@@
 
-	\subsection{Design Goals} In visualizing the spreadsheet data, I outlined a few
-	core goals for what the tool should accomplish: \begin{itemize} \item [1]
-		\textbf{Draw an interactive interface to explore observed function
-			combinations.} The combination space for all Excel functions is massive, let
-		alone the space for observed formulas. Working from data with actual referents
-		in practice, the tool must aid the user in navigating this space. \item [2]
-		\textbf{Emphasize the quantitative patterns in formula construction.} The tool,
-		accommodating datasets of a few spreadsheets to millions, should address the
-		questions of how often the end users employed a certain function and where they
-		used it. In this way, it must show precise metrics, such as frequency of  use
-		and depth of function nesting, of the dataset it conveys. \item [3]
-		\textbf{Promote a qualitative understanding of the patterns.} Lest these
-		patterns remain abstract, the tool should supplement its observations with
-		concrete instances of relevant formulas from the corpus. Ideally, it should
-		even direct users to the exact cell in the spreadsheets where the formula was
-		used, contextualizing the functions. \end{itemize} \par
+	\subsection{Design Goals} In visualizing the spreadsheet data, we outlined the
+	core goals for what the tool should accomplish. Furthermore, with these goals,
+	we also considered the likely challenges of achieving those goals and 
+	particular outcomes which we considered beyond the scope of the research. We present
+	both sides of these goals below:
 
-	Likewise, to bound our scope, we outlined a few goals to specifically avoid
-	accomplishing with this: \begin{itemize} \item [!1] \textbf{Do not try to
-			directly explain what a function does.} Though the tool tries to foster tries
-		understanding by linking pattern to example, it won't provide a precise
-		description of what a function accomplishes. The tool's user must infer this.
-		\item [!2] \textbf{Do not create new formulas.} This is essentially an
-		exploratory tool, not a generative one. It should not produce any information
-		other than new views of the original data. \item [!3] \textbf{Do not visualize
-			individual formulas.} Though there is room to explore the place of a single
-		function in the group, the tool must design the core visualization around the
-		entire body of data, not the other way around. \end{itemize}
+	\begin{itemize}
 
-	\subsection{Walkthrough of Tool} Before
-	discussing the minutiae of how the tool was developed, it will help first to
-	give a basic example of how the tool can be used and how to interpret its
-	symbols. One such example might be to find the answer to this question:
-	\textit{ What kinds of functions do people use to define the condition in an IF
-		function?} The final visualization is available in figure \ref{fig:fullpic};
-	however, to understand the interaction, we will start rather from the
-	beginning. \par
+		\item [1] \textbf{Provide an interactive environment for unguided exploration.}
+
+		%The combination space for all Excel functions is massive, let
+		%alone the space for observed formulas. Working from data with actual referents
+		%in practice, the tool must aid the user in navigating this space.
+
+		\item [!1] \textbf{Do not make judgments about good and bad design.}
+
+		%Though
+		%the tool tries to foster tries understanding by linking pattern to example, it
+		%won't provide a precise description of what a function accomplishes. The tool's
+		%user must infer this.
+
+		\item [2] \textbf{Emphasize the quantitative patterns in formula construction.}
+
+		%The tool, accommodating datasets of a few spreadsheets to millions, should
+		%address the questions of how often the end users employed a certain function
+		%and where they used it. In this way, it must show precise metrics, such as
+		%frequency of  use and depth of function nesting, of the dataset it conveys.
+
+		\item [!2] \textbf{Do not overwhelm with numbers.}
+
+		%This is essentially an
+		%exploratory tool, not a generative one. It should not produce any information
+		%other than new views of the original data.
+
+		\item [3] \textbf{Promote a qualitative understanding of the patterns.}
+
+		%Lest
+		%these patterns remain abstract, the tool should supplement its observations
+		%with concrete instances of relevant formulas from the corpus. Ideally, it
+		%should even direct users to the exact cell in the spreadsheets where the
+		%formula was used, contextualizing the functions.
+
+		\item [!3] \textbf{Do not attempt to explain formulae.}
+
+		%Though there is room
+		%to explore the place of a single function in the group, the tool must design
+		%the core visualization around the entire body of data, not the other way
+		%around.
+
+	\end{itemize}
+
+	\subsection{Walkthrough of Tool} Before discussing the minutiae of how the tool
+	was developed, it will help first to give a basic example of how the tool can
+	be used and how to interpret its symbols. One such example might be to find the
+	answer to this question: \textit{ What kinds of functions do people use to
+		define the condition in an IF function?} The final visualization is available
+	in figure \ref{fig:fullpic}; however, to understand the interaction, we will
+	start rather from the beginning. \par
 
@@
 
-	\begin{figure}
-		\centering
-		\includegraphics{start}
-		\label{fig:startpic}
-		\caption{How the IF tree looks at the start}
-	\end{figure}
+	\begin{figure} \centering \includegraphics{start} \label{fig:startpic}
+		\caption{How the IF tree looks at the start} \end{figure}
 
@@
 
-	\subsection{Bad Smells} Fowler's description of code smells \cite{fowler2009refactoring}
-	underscored an important point of code quality: between perfect code and
-	bug-crippled spaghetti,  there is a spectrum of code designs which, by
-	themselves, are not faulty but nevertheless suggest problems and
-	vulnerabilities in code design. Code smells, as we call them, soon commanded
-	attention and earned wide-ranging applicability, eventually making it to the
-	art of spreadsheet design.
+	\subsection{Bad Smells} Fowler's description of code smells
+	\cite{fowler2009refactoring} underscored an important point of code quality:
+	between perfect code and bug-crippled spaghetti,  there is a spectrum of code
+	designs which, by themselves, are not faulty but nevertheless suggest problems
+	and vulnerabilities in code design. Code smells, as we call them, soon
+	commanded attention and earned wide-ranging applicability, eventually making it
+	to the art of spreadsheet design.
 
@@
 	\cite{hermans2012detecting} \cite{cunha2012towards} \cite{jansen2015code}
-	\cite{asavametha2012detecting} . While some of the smells lie beyond the 
-	scope of the tool, such as those characterizing inter-worksheet connections,
-	some have structures which create distinctive features within the tree,
-	leading to easy detection through visualization: \par
+	\cite{asavametha2012detecting} . While some of the smells lie beyond the scope
+	of the tool, such as those characterizing inter-worksheet connections, some
+	have structures which create distinctive features within the tree, leading to
+	easy detection through visualization: \par
 
-	\begin{itemize}
-		\item \textit{Long Method}: Also called "Multiple Operations" in \cite{hermans2012detecting},
-		this refers to situations where numerous functions and operators are used all within the same
-		cell, creating a formula that tends to extend beyond a compact viewing space and makes it
-		difficult to understand. In the visualization, since each nested and combined function creates
-		yet another level of depth within the tree, these constructions can result in long, horizontal 
-		chains of nodes, as seen in figure \ref{"fig:longsum"}.
-		\item \textit{Long Parameter List}: [tall, vertical towers of blue nodes]
-		\item \textit{Conditional Complexity}: [IF nodes within IF nodes]
-	\end{itemize}
+	\begin{itemize} \item \textit{Long Method}: Also called "Multiple Operations"
+		in \cite{hermans2012detecting}, this refers to situations where numerous
+		functions and operators are used all within the same cell, creating a formula
+		that tends to extend beyond a compact viewing space and makes it difficult to
+		understand. In the visualization, since each nested and combined function
+		creates yet another level of depth within the tree, these constructions can
+		result in long, horizontal chains of nodes, as seen in figure
+		\ref{"fig:longsum"}. \item \textit{Long Parameter List}: [tall, vertical towers
+		of blue nodes] \item \textit{Conditional Complexity}: [IF nodes within IF
+		nodes] \end{itemize}
 
-	\begin{figure*}
-		\centering
-		\includegraphics[width=\textwidth]{longsum}
-		\label{"fig:longsum"}
-		\caption{The horizontal length of a tree may indicate complex or redundant design.}
-	\end{figure*}
+	\begin{figure*} \centering \includegraphics[width=\textwidth]{longsum}
+		\label{"fig:longsum"} \caption{The horizontal length of a tree may indicate
+			complex or redundant design.} \end{figure*}
 
@@
 	spreadsheet design. In a recent study, Hermans, Aivaloglou, and Jansen probed
-	the Enron dataset for uses of VLOOKUP and HLOOKUP specifically.
-	The issue at hand was the optional fourth argument: when omitted or set to TRUE,
-	the function attempts to return a value from another column by matching two values
-	approximately, but when set to FALSE, the match must be exact. Furthermore, exact
-	matching works only with sorted columns or rows; if the programmer neglects to sort
-	values before calling the *LOOKUP function, they may acquire inaccurate results \cite{hermans2015detecting}. \par
+	the Enron dataset for uses of VLOOKUP and HLOOKUP specifically. The issue at
+	hand was the optional fourth argument: when omitted or set to TRUE, the
+	function attempts to return a value from another column by matching two values
+	approximately, but when set to FALSE, the match must be exact. Furthermore,
+	exact matching works only with sorted columns or rows; if the programmer
+	neglects to sort values before calling the *LOOKUP function, they may acquire
+	inaccurate results \cite{hermans2015detecting}. \par
 
-	Given access to the same dataset, how might this tool approach the issue? 
-	On the surface, the tool supports easy quantification through the tooltips
+	Given access to the same dataset, how might this tool approach the issue? On
+	the surface, the tool supports easy quantification through the tooltips
 	displayed for each node, as shown in figure \ref{"fig:vhlookups"}, answering
 	the question, "How often do spreadsheet programmers use this function?". But,
-	more to the point, the tool's distinction between the numbers of arguments
-	for a single function lets the user compare frequencies of three-argument 
-	forms with the four-argument. The visualization does not, however, discern
-	between the different values for booleans in the tree, much less whether 
-	the spreadsheet columns are ordered -- but the linking of examples to patterns
-	allows quick insight into which files are at risk for the problems they outlined. \par
+	more to the point, the tool's distinction between the numbers of arguments for
+	a single function lets the user compare frequencies of three-argument forms
+	with the four-argument. The visualization does not, however, discern between
+	the different values for booleans in the tree, much less whether the
+	spreadsheet columns are ordered -- but the linking of examples to patterns
+	allows quick insight into which files are at risk for the problems they
+	outlined. \par
 
-	\begin{figure}
-		\centering
-		\includegraphics[width=.5\textwidth]{vlookup}
+	\begin{figure} \centering \includegraphics[width=.5\textwidth]{vlookup}
 		\includegraphics[width=.225\textwidth]{vlookupbox}
 		\includegraphics[width=.225\textwidth]{hlookupbox}
-		\includegraphics[width=.5\textwidth]{hlookup}
-		\label{"fig:vhlookups"}
-		\caption{VLOOKUP and HLOOKUP with four arguments. Numbers
-			not expected to correspond perfectly with \cite{hermans2015detecting}.}
-	\end{figure}
+		\includegraphics[width=.5\textwidth]{hlookup} \label{"fig:vhlookups"}
+		\caption{VLOOKUP and HLOOKUP with four arguments. Numbers not expected to
+			correspond perfectly with \cite{hermans2015detecting}.} \end{figure}
 
 	Also at hand are issues with the standard LOOKUP function. Unlike the two
-	variations above, LOOKUP accepts either two or three arguments, depending
-	on which API-defined form the programmer uses: the vector form or
-	the array form, the primary difference being whether the second parameter
-	is a one-column/-row range or a two-dimensional array. The array form, as 
-	it happens, is strongly discouraged by the API in favor of the V/HLOOKUP,
-	a notion that might also be leveraged in the pursuit in good spreadsheet 
-	design.
+	variations above, LOOKUP accepts either two or three arguments, depending on
+	which API-defined form the programmer uses: the vector form or the array form,
+	the primary difference being whether the second parameter is a one-column/-row
+	range or a two-dimensional array. The array form, as it happens, is strongly
+	discouraged by the API in favor of the V/HLOOKUP, a notion that might also be
+	leveraged in the pursuit in good spreadsheet design.
 
-	\begin{figure}
-		\centering
-		\includegraphics[width=.5\textwidth]{lookup-2}
-		\includegraphics[width=.5\textwidth]{lookup-3}
-		\label{"fig:lookups"}
+	\begin{figure} \centering \includegraphics[width=.5\textwidth]{lookup-2}
+		\includegraphics[width=.5\textwidth]{lookup-3} \label{"fig:lookups"}
 		\caption{LOOKUP with two (6 occurrences) and three (1648) arguments.}
@@
 	in context, some of these formulas remained incomprehensible, posing problems
-	for the spreadsheet transfer scenarios as outlined by Hermans \cite{hermans2011supporting}.
-	The tool, then, aggregates
-	these issues in a single place, accessible to either the unguided user and the
-	ones who know exactly where to find these issues. \par
+	for the spreadsheet transfer scenarios as outlined by Hermans
+	\cite{hermans2011supporting}. The tool, then, aggregates these issues in a
+	single place, accessible to either the unguided user and the ones who know
+	exactly where to find these issues. \par
 
@@
 
-	\begin{figure}
-		\centering 
-		\includegraphics{longIF}
-		\label{"fig:longif"}
+	\begin{figure} \centering \includegraphics{longIF} \label{"fig:longif"}
 		\caption{The many possibilities of IF, argument 3, demonstrate the problem of
-			having too many options.}
-	 \end{figure}
+			having too many options.} \end{figure}
 
@@
 	figure \ref{"fig:index"} shows the situation of the INDEX tree, wherein each
-	argument position has a few distinct possibilities. While it is easy to break down,
-	for each position, which argument types are most common (ranges, MATCH, and numbers,
-	respectively), the tree is silent on whether MATCH functions are used together
-	in the second and third arguments, among other concerns. Though these argument
-	combinations could be pieced together by manually inspecting the lists of examples,
-	it is nevertheless inconvenient, though not outside the realm of future improvement.
+	argument position has a few distinct possibilities. While it is easy to break
+	down, for each position, which argument types are most common (ranges, MATCH,
+	and numbers, respectively), the tree is silent on whether MATCH functions are
+	used together in the second and third arguments, among other concerns. Though
+	these argument combinations could be pieced together by manually inspecting the
+	lists of examples, it is nevertheless inconvenient, though not outside the
+	realm of future improvement.
 
-	\begin{figure}
-		\centering
-		\includegraphics[width=.5\textwidth]{index}
-		\label{"fig:index"}
-		\caption{A difficult question: how often is MATCH used in both the second
-			and third arguments?}
-	\end{figure}
+	\begin{figure} \centering \includegraphics[width=.5\textwidth]{index}
+		\label{"fig:index"} \caption{A difficult question: how often is MATCH used in
+			both the second and third arguments?} \end{figure}
 
-	%To be sure, though, there is still plenty of work to improve this tool. One activity
-	%it does not support well now is that of comparison: for all of it's ability to spit
+	%To be sure, though, there is still plenty of work to improve this tool. One
+	% activity
+	%it does not support well now is that of comparison: for all of it's ability to
+	% spit
 	%out numbers and quantify patterns,
 
-	\section{Future Work}
-	For these user and case studies, we relied solely on Enron's spreadsheets to
-	find our results. However, Enron's focus on finances and energy represents only one context
-	in which people use spreadsheets. Other corpora, like EUSES and Fuse, draw from other 
-	domains and industries, and, as Jansen found in his comparison
-	of spreadsheets Enron and EUSES, different companies rely on different functions.
-	Though the use of a single corpora nevertheless suffices for evaluation, 
-	we may yet be able to find more interesting applications and uses for the tool
-	in other types of spreadsheet. \par
+	\section{Future Work} For these user and case studies, we relied solely on
+	Enron's spreadsheets to find our results. However, Enron's focus on finances
+	and energy represents only one context in which people use spreadsheets. Other
+	corpora, like EUSES and Fuse, draw from other domains and industries, and, as
+	Jansen found in his comparison of spreadsheets Enron and EUSES, different
+	companies rely on different functions. Though the use of a single corpora
+	nevertheless suffices for evaluation, we may yet be able to find more
+	interesting applications and uses for the tool in other types of spreadsheet.
+	\par
 
-	Additionally, Excel is only one of many different spreadsheet products available, 
-	chosen for this project because of its prevalence. But other spreadsheets, such as
-	Gnumeric\footnote{http://www.gnumeric.org/} or Google Sheets \footnote{https://www.google.com/sheets/about/}
-	represent other approaches to spreadsheet systems. Even within identical domains,
-	there's no guarantee that practices and functions will hold across these varied
-	offerings. This, then, warrants further analysis, in which good visualization might
-	serve well. \par
+	Additionally, Excel is only one of many different spreadsheet products
+	available, chosen for this project because of its prevalence. But other
+	spreadsheets, such as Gnumeric\footnote{http://www.gnumeric.org/} or Google
+	Sheets \footnote{https://www.google.com/sheets/about/} represent other
+	approaches to spreadsheet systems. Even within identical domains, there's no
+	guarantee that practices and functions will hold across these varied offerings.
+	This, then, warrants further analysis, in which good visualization might serve
+	well. \par
 
-	\section{Conclusion} 
-	This paper presents a tool to support the exploration of function combinations
-	throughout a given spreadsheet dataset. By taking a agnostic approach to design
-	quality, it attempts to convey the dataset's spreadsheet practices as is: the
-	common along with the anomalous, and the well-designed along with the odorous.
-	As seen in the user and case studies, this allows it to take on several potential
-	roles at once, such as an environment for search out bad code smells as well as
-	a repository for examples for learning new techniques. \par
+	\section{Conclusion} This paper presents a tool to support the exploration of
+	function combinations throughout a given spreadsheet dataset. By taking a
+	agnostic approach to design quality, it attempts to convey the dataset's
+	spreadsheet practices as is: the common along with the anomalous, and the
+	well-designed along with the odorous. As seen in the user and case studies,
+	this allows it to take on several potential roles at once, such as an
+	environment for search out bad code smells as well as a repository for examples
+	for learning new techniques. \par
 
@@
 	the project in others. Some users, for example, found the trees of popular
-	functions to be too crowded to explore well, or that their intention to use
-	the tool to examine the good or the bad design exclusively was not fully
-	supported by a tool that claimed to know neither. Many of the problems, however,
-	were not essential to this design conflict and will be overcome in future
-	iterations of design by refining icons and improving maneuverability. \par
+	functions to be too crowded to explore well, or that their intention to use the
+	tool to examine the good or the bad design exclusively was not fully supported
+	by a tool that claimed to know neither. Many of the problems, however, were not
+	essential to this design conflict and will be overcome in future iterations of
+	design by refining icons and improving maneuverability. \par
 

### 2016-04-21 doc/paper.tex
Fixes #46

@@
 	we also considered the likely challenges of achieving those goals and
-	particular outcomes which we considered beyond the scope of the research. We present
-	both sides of these goals below:
+	particular outcomes which we considered beyond the scope of the research. We
+	present both sides of these goals below:
 
@@
 
-		\item [1] \textbf{Provide an interactive environment for unguided exploration.}
+		\item [1] \textbf{Provide an interactive environment for free exploration.}
+		There are a lot of data in some of these collections, and the user should be
+		able to pick for themselves which to explore while ignoring the rest. Furthermore,
+		this exploration should not be designed around answering one specific question
+		but rather be open-ended.
 
-		%The combination space for all Excel functions is massive, let
-		%alone the space for observed formulas. Working from data with actual referents
-		%in practice, the tool must aid the user in navigating this space.
+		\item [!1] \textbf{Do not make judgments about good and bad design.} Though
+		users may certainly approach the tool with the intention of finding particular
+		formulae, \toolname will not prioritize any on metrics of good or bad
+		practice. Rather, it will present them agnostically, referring only to
+		frequency.
 
-		\item [!1] \textbf{Do not make judgments about good and bad design.}
+		\item [2] \textbf{Emphasize the quantitative patterns in formula
+			construction.} \toolname should address the questions of how often the
+		spreadsheet programmers used a certain function and where they used it. In
+		this way, it must show precise metrics, such as frequency of use and depth of
+		function nesting, of the dataset it conveys.
 
-		%Though
-		%the tool tries to foster tries understanding by linking pattern to example, it
-		%won't provide a precise description of what a function accomplishes. The tool's
-		%user must infer this.
-
-		\item [2] \textbf{Emphasize the quantitative patterns in formula construction.}
-
-		%The tool, accommodating datasets of a few spreadsheets to millions, should
-		%address the questions of how often the end users employed a certain function
-		%and where they used it. In this way, it must show precise metrics, such as
-		%frequency of  use and depth of function nesting, of the dataset it conveys.
-
-		\item [!2] \textbf{Do not overwhelm with numbers.}
-
-		%This is essentially an
-		%exploratory tool, not a generative one. It should not produce any information
-		%other than new views of the original data.
+		\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
+		especially, we anticipated some particularly dense trees. Though
+		everything should be accessible in accordance with Goal 1, we should design in
+		a way that reduces noise.
 
 		\item [3] \textbf{Promote a qualitative understanding of the patterns.}
+		\toolname should supplement its observations with concrete instances of
+		relevant formulas from the corpus. Ideally, it should even direct users to the
+		exact cell in the spreadsheets where the formula was used, contextualizing the
+		functions.
 
-		%Lest
-		%these patterns remain abstract, the tool should supplement its observations
-		%with concrete instances of relevant formulas from the corpus. Ideally, it
-		%should even direct users to the exact cell in the spreadsheets where the
-		%formula was used, contextualizing the functions.
-
-		\item [!3] \textbf{Do not attempt to explain formulae.}
-
-		%Though there is room
-		%to explore the place of a single function in the group, the tool must design
-		%the core visualization around the entire body of data, not the other way
-		%around.
+		\item [!3] \textbf{Do not attempt to explain formulae.} Though \toolname tries
+		to foster understanding by linking pattern to example, it should not provide
+		a precise description of what a complex formula accomplishes. The tool's user
+		must infer this on their own.
 
@@
 
-	\subsection{Walkthrough of Tool} Before discussing the minutiae of how the tool
+	Though we kept these guidelines in mind through the development of \toolname, we
+	nevertheless reached a number of points in which these principles conflicted. For
+	a discussion of these decisions, see section \ref{ssec:decisions}.
+
+	\subsection{Walkthrough of the Tool} Before discussing the minutiae of how the tool
 	was developed, it will help first to give a basic example of how the tool can
@@
 
-	\centerline{\includegraphics[width=.43\textwidth]{IFexpand}}
+	\begin{figure}
+		\centering
+		\includegraphics[width=.43\textwidth]{IFexpand}
+		\label{fig:expandif}
+		\caption{First argument of the IF tree}
+	\end{figure}
 
@@
 
-	\subsection{Design Decisions} Early in the process, we decided that the tree
+	\subsection{Design Decisions} \label{ssec:decisions}
+	Early in the process, we decided that the tree
 	form would be a suitable fit to represent the parent-child or caller-callee

### 2016-04-21 doc/paper.tex
Fixes #42

@@
 
-	Many other tools inspect the structure of formulas but often from the
+	Many other tools inspect the structure of formulae but often from the
 	perspective of finding bad design.  Following Fowler's initial description of
@@
 		\toolname should supplement its observations with concrete instances of
-		relevant formulas from the corpus. Ideally, it should even direct users to the
+		relevant formulae from the corpus. Ideally, it should even direct users to the
 		exact cell in the spreadsheets where the formula was used, contextualizing the
@@
 	form would be a suitable fit to represent the parent-child or caller-callee
-	relationships inherent in the data, given the composition of formulas as
+	relationships inherent in the data, given the composition of formulae as
 	functions and their arguments (which could be yet more functions). By adapting
@@
 	sample of which we describe below, before we arrived at the design shown above.
-	\begin{itemize} \item \textit{Copied formulas}: Excel allows users to spread a
+	\begin{itemize} \item \textit{Copied formulae}: Excel allows users to spread a
 		formula over an area, repeating the same task in each cell with minor
 		adjustments. Without checking for this, the analysis may not reveal the
-		functions most commonly used together but rather the formulas most often
-		applied to large areas. To combat this, we converted formulas from their native
-		A1 format to the relative R1C1, in which copied formulas should be identical,
-		and reduced the records to unique R1C1 formulas per sheet. \item
+		functions most commonly used together but rather the formulae most often
+		applied to large areas. To combat this, we converted formulae from their native
+		A1 format to the relative R1C1, in which copied formulae should be identical,
+		and reduced the records to unique R1C1 formulae per sheet. \item
 		\textit{Importance of depth}: When a function appears within another, should it
@@
 		the formula text into an ordered set of individual tokens, which the tool then
-		parses into the tree-like form by which it is recorded. When all formulas have
+		parses into the tree-like form by which it is recorded. When all formulae have
 		been analyzed like this, it produces JSON files for each top-level function in
@@
 	would likely be unreasonable to expect an evenly distributed familiarity with
-	the 100+ function trees available. Nevertheless, the list of actual formulas
+	the 100+ function trees available. Nevertheless, the list of actual formulae
 	accessible through a node's double-click allowed the users a way to find
-	examples of formulas with exactly the configuration they wanted. For example,
+	examples of formulae with exactly the configuration they wanted. For example,
 	as P1 explored the VLOOKUP function, even though they knew the official API
@@
 	participants could then open the offending spreadsheets, discovering that, even
-	in context, some of these formulas remained incomprehensible, posing problems
+	in context, some of these formulae remained incomprehensible, posing problems
 	for the spreadsheet transfer scenarios as outlined by Hermans

### 2016-04-22 doc/paper.tex
Methodology stuff. Fixes #49, fixes #50, fixes #51, fixes #52, fixes #55, fixes #56, fixes #57, fixes #58, fixes #59, fixes #60

@@
 	\begin{figure*}[t] \includegraphics[width = \textwidth]{IFargslabel} \caption{A
-			picture of the tool.} \centering \label{fig:fullpic} \end{figure*}
+			picture of \toolname} \centering \label{fig:fullpic} \end{figure*}
 
@@
 
-	\section{Approach/Methodology}
+	\section{Approach}
 
-	\subsection{Design Goals} In visualizing the spreadsheet data, we outlined the
+	\subsection{Design Goals} \label{goals} In visualizing the spreadsheet data, we outlined the
 	core goals for what the tool should accomplish. Furthermore, with these goals,
@@
 
-	\subsection{Walkthrough of the Tool} Before discussing the minutiae of how the tool
-	was developed, it will help first to give a basic example of how the tool can
-	be used and how to interpret its symbols. One such example might be to find the
-	answer to this question: \textit{ What kinds of functions do people use to
-		define the condition in an IF function?} The final visualization is available
-	in figure \ref{fig:fullpic}; however, to understand the interaction, we will
-	start rather from the beginning. \par
+	\subsection{Walkthrough of the Tool} Before discussing the minutiae of tool's development,
+	though, we will give a basic example of how to use the tool. For this, we will answer this question: \textit{ What kinds of functions do people use to
+		define the condition in an IF function?} Thefull  visualization that answers this 
+	is available in figure \ref{fig:fullpic}; however, to understand the interaction, we will
+	start from the beginning. \par
+
+	First, a word on the IF function. In Excel, it serves as one of the logical functions: given
+	a condition as the first argument that evaluates to either true or false, it takes on
+	the value of either the second or third argument, respectively. Or, as the documentation
+	writes out, "IF(Something is True, then do something, otherwise do something 
+	else)"\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}.
+	Furthermore, the third argument is optional; if left out, the function will return a default
+	"FALSE" value if necessary. Examples of this function in practice can be seen in \ref{fig:ifexample}.
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=.5\textwidth]{ifExample}
+		\label{fig:ifexample}
+		\caption{Configurations of the IF function}
+	\end{figure}
 
@@
 
-	\begin{figure} \centering \includegraphics{start} \label{fig:startpic}
+	\begin{figure}[h] \centering \includegraphics{start} \label{fig:startpic}
 		\caption{How the IF tree looks at the start} \end{figure}
 
-	The visualization so far comprises two types of node: the circle, which
+	The visualization so far comprises two types of node: the circle \includegraphics{glossary-greenonly}, which
 	represents a discrete function in the formula and is size according to its
-	relative frequency (the top-level node, by definition, will be the largest);
-	and the numbered squares, which represent the positions of arguments within its
-	parent function. From this, we can infer that, of the times it was observed, IF
+	frequency relative to the number of times to root function appeared\footnote{The root node, by definition, will
+		always be the largest node in a tree.};
+	and the numbered squares \includegraphics{glossary-blue}, which represent the positions of arguments within its
+	parent function. From this, we can confirm that, of the times it was observed, IF
 	can have at most three arguments passed into it, which corresponds with its
@@
 	arguments have been observed in any position, the tool displays only the first
-	ten, with an option to display the rest. The results are shown below:
+	ten, with an option to display the rest as the arrow \includegraphics{glossary-arrow}.
 
-	\begin{figure}
+	\begin{figure}[h]
 		\centering
@@
 
-	As expected, we see that IF contains as its first argument a number of
-	comparison operators, such as = and <=, and boolean-returning functions, like
+	We see that IF contains as its first argument a number of
+	comparison operators, such as = and $\le$, and boolean-returning functions, like
 	ISNA and AND, with simple equality being the most common and some use as ABS
@@
 	From here, we can further explore the common options among these functions.
-	Clicking on the "=" node will yield two arguments, it being a binary operator,
+	Clicking on the "=" node will yield two arguments
 	and expanding each of them will peer into the range of common values of
@@
 
+	\subsection{Icon Glossary}
+
+	From these images, we can provide a quick glossary of images within the visualization
+	to aid interpretation.
+	\begin{itemize}
+		\item \includegraphics{glossary-green} - \textbf{Function nodes} are green
+		circles labeled with the function name. Their size is determined by their
+		relative frequency, scaled logarithmically, to the frequency of the root node
+		in the tree. They may have any number of arguments, including zero, as
+		determined by the API.
+
+		\item \vspace{.25cm}\includegraphics{glossary-leaf} - \textbf{Value nodes} are white circles
+		with a generic label. They represent elements of a formula which are which
+		accept no arguments, like references (A1), ranges (A1:A10)\footnote{That is,
+			only if both sides of a references are cell references. If either side is a
+			function that returns a cell reference, like INDIRECT, then the colon should
+			be a function node.}, numbers, boolean values, strings, and errors. Functions
+		with zero arguments, like NOW, however, should still be considered function
+		nodes.
+
+		\item  \vspace{.25cm} \includegraphics{glossary-blue} - \textbf{Argument nodes} are dark blue
+		squares labeled with a number. The number is the position of an argument
+		within the function in the parent node. In \ref{fig:expandif} for example,
+		argument node 1 shows every function or value that was seen in the first
+		argument.
+
+		\item  \vspace{.25cm} \includegraphics{glossary-solidline} - \textbf{Solid lines} represent a
+		function's ownership of its various arguments. As such, they connect the
+		function nodes to argument nodes.
+
+		\item  \vspace{.25cm} \includegraphics{glossary-fadingline} - \textbf{Fading lines} represent
+		the possibility of an argument position to have several different possible
+		functions or values. As such, they connect argument nodes to function or value
+		nodes.
+
+		\item  \vspace{.25cm} \includegraphics{glossary-arrow} - \textbf{Expansion arrows} appear
+		within an argument node when there are over 10 possible functions or values in
+		an argument position. By default, only the first 10 will be shown along with
+		this arrow; clicking this will show the rest as well.
+
+		\item  \vspace{.25cm} \includegraphics[scale=.75]{glossary-lightblue} - \textbf{Optional
+			argument trees} are variations of trees that show only formulae with a
+		specific number of arguments, allowing the user to control for the presence of
+		optional arguments. By default, trees with dark blue nodes contain every type
+		of formula without regard how many arguments they have -- for example,
+		single-argument ANDs could appear alongside 4-argument ANDs. See Figure
+		\ref{fig:optional} to see it visualized.
+	\end{itemize}
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width = .46\textwidth]{comparison}
+		\includegraphics[]{comparison-ss}
+		\label{fig:optional}
+		\caption{The contents of each type of tree.}
+	\end{figure}
+
+	\subsection{Implementation Details} The final visualization is the
+	product of two discrete processes: \begin{itemize} \item \textit{Collection}:
+		Given a set of Excel sheets, the tool, written in Java, uses Apache
+		POI\footnote{https://poi.apache.org/} to identify and iterate over every cell
+		containing a valid formula. Afterward, it calls POI's formula parser to break
+		the formula text into an ordered set of individual tokens, which the tool then
+		parses into the tree-like form. When all formulae have
+		been analyzed like this, it produces JSON files for each top-level function in
+		the set.
+
+		\item \textit{Presentation}: The JSON files, meanwhile, feed into the
+		presentation code, implemented in Javascript with much help from the
+		visualization library D3\footnote{https://d3js.org/}. We chose D3 primarily for
+		its accessibility: given the JSON, the visualization can be simply
+		embedded into a webpage accessible through a browser. \end{itemize} A
+	demonstration of the tool can be found at https://github.com/DeveloperLiberationFront/Excel-Function-Visualizer.
+
 	\subsection{Design Decisions} \label{ssec:decisions}
-	Early in the process, we decided that the tree
-	form would be a suitable fit to represent the parent-child or caller-callee
-	relationships inherent in the data, given the composition of formulae as
-	functions and their arguments (which could be yet more functions). By adapting
+	Early in the design, we chose the tree form for its inherent ability to
+	represent the loose parent-children relationship of formulae as
+	functions and their arguments, which could be yet more functions. By adapting
 	this structure to accommodate a broad range of possibilities for nested
-	functions, the branching factor depends on both the number of arguments in a
+	functions, the branching factor depends alternatively on the number of arguments in a
 	function and the number of possible functions observed as an argument in a
@@
 	sample of which we describe below, before we arrived at the design shown above.
-	\begin{itemize} \item \textit{Copied formulae}: Excel allows users to spread a
+	\begin{itemize}
+
+%			\begin{itemize}
+%				
+%				\item [1] \textbf{Provide an interactive environment for free exploration.}
+%				There are a lot of data in some of these collections, and the user should be
+%				able to pick for themselves which to explore while ignoring the rest. Furthermore,
+%				this exploration should not be designed around answering one specific question
+%				but rather be open-ended.
+%				
+%				\item [!1] \textbf{Do not make judgments about good and bad design.} Though
+%				users may certainly approach the tool with the intention of finding particular
+%				formulae, \toolname will not prioritize any on metrics of good or bad
+%				practice. Rather, it will present them agnostically, referring only to
+%				frequency.
+%				
+%				\item [2] \textbf{Emphasize the quantitative patterns in formula
+%					construction.} \toolname should address the questions of how often the
+%				spreadsheet programmers used a certain function and where they used it. In
+%				this way, it must show precise metrics, such as frequency of use and depth of
+%				function nesting, of the dataset it conveys.
+%				
+%				\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
+%				especially, we anticipated some particularly dense trees. Though
+%				everything should be accessible in accordance with Goal 1, we should design in
+%				a way that reduces noise.
+%				
+%				\item [3] \textbf{Promote a qualitative understanding of the patterns.}
+%				\toolname should supplement its observations with concrete instances of
+%				relevant formulae from the corpus. Ideally, it should even direct users to the
+%				exact cell in the spreadsheets where the formula was used, contextualizing the
+%				functions.
+%				
+%				\item [!3] \textbf{Do not attempt to explain formulae.} Though \toolname tries
+%				to foster understanding by linking pattern to example, it should not provide
+%				a precise description of what a complex formula accomplishes. The tool's user
+%				must infer this on their own.
+%				
+%			\end{itemize}
+
+		\item \textit{Copied formulae}: Excel allows users to spread a
 		formula over an area, repeating the same task in each cell with minor
@@
 		A1 format to the relative R1C1, in which copied formulae should be identical,
-		and reduced the records to unique R1C1 formulae per sheet. \item
-		\textit{Importance of depth}: When a function appears within another, should it
+		and considered only each R1C1 formulae once per worksheet.
+
+		\item \textit{Importance of depth}: When a function appears within another, should it
 		be analyzed only as a nested function or would it also be valid to analyze the
-		nested function on its own?
+		nested function on its own? \par
 
-		\par For example, in the pictured IF function, we found that people often use
+		\ \ For example, in the pictured IF function, we found that people often use
 		another IF statement as the second or third arguments of the top-level IF. If
@@
 		top-level IF -- then the tool will represent some functions in multiple nodes
-		to capture every possible level of nesting. Both approaches have benefits and
-		drawbacks, and so we included both. \item \textit{Pattern density}: How should
-		the tool quantitatively order its elements: by a function's raw frequency or
-		by the unity of patterns it leads to? For example, if SUM has for its first
-		argument two possibilities, one which itself contains 1000 unique argument
-		possibilities with 1 occurrence each (high frequency, low pattern density) and
-		another seen with 2 argument possibilities of 100 occurrences each (low
-		frequency, high pattern density), which would be more interesting to
-		emphasize? The answer depends on the nuances of the questions, but for
-		simplicity, I've shown the former. \item \textit{Non-functions}: How should
-		the tool represent everything in the formula that isn't a function: numbers,
-		string literals, errors, references, etc? Since these don't accept arguments,
-		they will adorn the tree as leaves, and their precise content won't affect the
-		functions around them as long as their types are known. As such, in the
-		visualization, all of these nodes are replaced and aggregated under their
-		types and represented as empty white nodes. \item \textit{Optional arguments}:
-		How should the tool handle functions which accept a variable number of
-		arguments? SUM, for example, can have anywhere from 1 to 255, and IF can
-		accept either 2 or 3.
-		\footnote{https://support.office.com/en-us/article/Excel-functions-by-category-5f91f4e9-7b42-46d2-9bd1-63f26a86c0eb} Without prior evidence, it's possible that, when people use optional arguments, they use different kinds of types and functions for arguments versus the cases when they ignore optional arguments.
-To account for this, we separate and analyze the different quantities of arguments observed for each function; the tool, however, uses as default all of the options collapsed into a single representation.
+		to capture every possible level of nesting. For now, we only include the first,
+		with the latter to be added as an option in the future.
+
 	\end{itemize}
-
-	\subsection{Implementation Details} We can view the final visualization as the
-	product of two discrete processes: \begin{itemize} \item \textit{Collection}:
-		Given a set of Excel sheets, the tool, written mostly in Java, uses Apache
-		POI\footnote{https://poi.apache.org/} to identify and iterate over every cell
-		containing a valid formula. Afterward, it calls POI's formula parser to break
-		the formula text into an ordered set of individual tokens, which the tool then
-		parses into the tree-like form by which it is recorded. When all formulae have
-		been analyzed like this, it produces JSON files for each top-level function in
-		the set. \item \textit{Presentation}: The JSON files, meanwhile, feed into the
-		presentation code, implemented in Javascript with much help from the
-		visualization library D3\footnote{https://d3js.org/}. We chose D3 primarily for
-		its accessibility: given the JSON, the visualization can be rather simply
-		embedded into a webpage accessible through a browser. \end{itemize} A
-	demonstration of the tool can be found at [LINK HERE].
 
@@
 
-	\begin{figure*} \centering \includegraphics[width=\textwidth]{longsum}
+	\begin{figure*}[h] \centering \includegraphics[width=\textwidth]{longsum}
 		\label{"fig:longsum"} \caption{The horizontal length of a tree may indicate
@@
 	the surface, the tool supports easy quantification through the tooltips
-	displayed for each node, as shown in figure \ref{"fig:vhlookups"}, answering
+	displayed for each node, as shown in figure \ref{fig:vhlookups}, answering
 	the question, "How often do spreadsheet programmers use this function?". But,
@@
 
-	\begin{figure} \centering \includegraphics[width=.5\textwidth]{vlookup}
+	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
 		\includegraphics[width=.225\textwidth]{vlookupbox}
 		\includegraphics[width=.225\textwidth]{hlookupbox}
-		\includegraphics[width=.5\textwidth]{hlookup} \label{"fig:vhlookups"}
+		\includegraphics[width=.5\textwidth]{hlookup} \label{fig:vhlookups}
 		\caption{VLOOKUP and HLOOKUP with four arguments. Numbers not expected to
@@
 
-	\begin{figure} \centering \includegraphics[width=.5\textwidth]{lookup-2}
-		\includegraphics[width=.5\textwidth]{lookup-3} \label{"fig:lookups"}
+	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
+		\includegraphics[width=.5\textwidth]{lookup-3} \label{fig:lookups}
 		\caption{LOOKUP with two (6 occurrences) and three (1648) arguments.}
@@
 	\begin{wrapfigure}{l}{.12\textwidth} \centering \includegraphics{SUM}
-		\label{"fig:sum"} \end{wrapfigure}
+		\label{fig:sum} \end{wrapfigure}
 
@@
 
-	\begin{figure} \centering \includegraphics{longIF} \label{"fig:longif"}
+	\begin{figure} \centering \includegraphics[scale=.5]{longIF} \label{fig:longif}
 		\caption{The many possibilities of IF, argument 3, demonstrate the problem of
@@
 	A larger and related problem is the loss of argument combination. For example,
-	figure \ref{"fig:index"} shows the situation of the INDEX tree, wherein each
+	figure \ref{fig:index} shows the situation of the INDEX tree, wherein each
 	argument position has a few distinct possibilities. While it is easy to break
@@
 	\begin{figure} \centering \includegraphics[width=.5\textwidth]{index}
-		\label{"fig:index"} \caption{A difficult question: how often is MATCH used in
+		\label{fig:index} \caption{A difficult question: how often is MATCH used in
 			both the second and third arguments?} \end{figure}

### 2016-04-22 doc/paper.tex
Actually fixing the quotes this time.

@@
 
-	\subsection{Design Goals} \label{goals} In visualizing the spreadsheet data, we outlined the
-	core goals for what the tool should accomplish. Furthermore, with these goals,
-	we also considered the likely challenges of achieving those goals and
-	particular outcomes which we considered beyond the scope of the research. We
-	present both sides of these goals below:
+	\subsection{Design Goals} \label{goals} In visualizing the spreadsheet data, we
+	outlined the core goals for what the tool should accomplish. Furthermore, with
+	these goals, we also considered the likely challenges of achieving those goals
+	and particular outcomes which we considered beyond the scope of the research.
+	We present both sides of these goals below:
 
@@
 		There are a lot of data in some of these collections, and the user should be
-		able to pick for themselves which to explore while ignoring the rest. Furthermore,
-		this exploration should not be designed around answering one specific question
-		but rather be open-ended.
+		able to pick for themselves which to explore while ignoring the rest.
+		Furthermore, this exploration should not be designed around answering one
+		specific question but rather be open-ended.
 
@@
 		\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
-		especially, we anticipated some particularly dense trees. Though
-		everything should be accessible in accordance with Goal 1, we should design in
-		a way that reduces noise.
+		especially, we anticipated some particularly dense trees. Though everything
+		should be accessible in accordance with Goal 1, we should design in a way that
+		reduces noise.
 
@@
 		\item [!3] \textbf{Do not attempt to explain formulae.} Though \toolname tries
-		to foster understanding by linking pattern to example, it should not provide
-		a precise description of what a complex formula accomplishes. The tool's user
+		to foster understanding by linking pattern to example, it should not provide a
+		precise description of what a complex formula accomplishes. The tool's user
 		must infer this on their own.
@@
 
-	Though we kept these guidelines in mind through the development of \toolname, we
-	nevertheless reached a number of points in which these principles conflicted. For
-	a discussion of these decisions, see section \ref{ssec:decisions}.
+	Though we kept these guidelines in mind through the development of \toolname,
+	we nevertheless reached a number of points in which these principles
+	conflicted. For a discussion of these decisions, see section
+	\ref{ssec:decisions}.
 
-	\subsection{Walkthrough of the Tool} Before discussing the minutiae of tool's development,
-	though, we will give a basic example of how to use the tool. For this, we will answer this question: \textit{ What kinds of functions do people use to
-		define the condition in an IF function?} Thefull  visualization that answers this 
-	is available in figure \ref{fig:fullpic}; however, to understand the interaction, we will
-	start from the beginning. \par
+	\subsection{Walkthrough of the Tool} Before discussing the minutiae of tool's
+	development, though, we will give a basic example of how to use the tool. For
+	this, we will answer this question: \textit{ What kinds of functions do people
+		use to define the condition in an IF function?} Thefull  visualization that
+	answers this is available in figure \ref{fig:fullpic}; however, to understand
+	the interaction, we will start from the beginning. \par
 
-	First, a word on the IF function. In Excel, it serves as one of the logical functions: given
-	a condition as the first argument that evaluates to either true or false, it takes on
-	the value of either the second or third argument, respectively. Or, as the documentation
-	writes out, "IF(Something is True, then do something, otherwise do something 
+	First, a word on the IF function. In Excel, it serves as one of the logical
+	functions: given a condition as the first argument that evaluates to either
+	true or false, it takes on the value of either the second or third argument,
+	respectively. Or, as the documentation writes out, "IF(Something is True, then
+	do something, otherwise do something
 	else)"\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}.
-	Furthermore, the third argument is optional; if left out, the function will return a default
-	"FALSE" value if necessary. Examples of this function in practice can be seen in \ref{fig:ifexample}.
+Furthermore, the third argument is optional; if left out, the function will return a default "FALSE" value if necessary.
+Examples of this function in practice can be seen in \ref{fig:ifexample}.
 
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=.5\textwidth]{ifExample}
-		\label{fig:ifexample}
-		\caption{Configurations of the IF function}
-	\end{figure}
+	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{ifExample}
+		\label{fig:ifexample} \caption{Configurations of the IF function} \end{figure}
 
@@
 
-	The visualization so far comprises two types of node: the circle \includegraphics{glossary-greenonly}, which
-	represents a discrete function in the formula and is size according to its
-	frequency relative to the number of times to root function appeared\footnote{The root node, by definition, will
-		always be the largest node in a tree.};
-	and the numbered squares \includegraphics{glossary-blue}, which represent the positions of arguments within its
-	parent function. From this, we can confirm that, of the times it was observed, IF
-	can have at most three arguments passed into it, which corresponds with its
-	specifications in the
-	API.\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2} \par
+	The visualization so far comprises two types of node: the circle
+	\includegraphics{glossary-greenonly}, which represents a discrete function in
+	the formula and is size according to its frequency relative to the number of
+	times to root function appeared\footnote{The root node, by definition, will
+		always be the largest node in a tree.}; and the numbered squares
+	\includegraphics{glossary-blue}, which represent the positions of arguments
+	within its parent function. From this, we can confirm that, of the times it was
+	observed, IF can have at most three arguments passed into it, which corresponds
+	with its specifications in the
+	API\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}. \par
 
 	Knowing that it is the first argument which contains the conditionals, we click
-	on the square labeled "1" to explore. To save space, when more than 10 unique
+	on the square labeled ``1" to explore. To save space, when more than 10 unique
 	arguments have been observed in any position, the tool displays only the first
-	ten, with an option to display the rest as the arrow \includegraphics{glossary-arrow}.
+	ten, with an option to display the rest by clicking the arrow
+	\includegraphics{glossary-arrow}.
 
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=.43\textwidth]{IFexpand}
-		\label{fig:expandif}
-		\caption{First argument of the IF tree}
-	\end{figure}
+	\begin{figure}[h] \centering \includegraphics[width=.43\textwidth]{IFexpand}
+		\label{fig:expandif} \caption{First argument of the IF tree} \end{figure}
 
-	We see that IF contains as its first argument a number of
-	comparison operators, such as = and $\le$, and boolean-returning functions, like
-	ISNA and AND, with simple equality being the most common and some use as ABS
-	being the least seen of everything actually used. \par
+	We see that IF contains a number of comparison operators as its first argument,
+	such as = and $\le$, and boolean-returning functions, like ISNA and AND, with
+	simple equality being the most common and some use as ABS being the least seen
+	of everything actually used. \par
 
 	From here, we can further explore the common options among these functions.
-	Clicking on the "=" node will yield two arguments
-	and expanding each of them will peer into the range of common values of
-	equality comparison, which Figure \ref{fig:fullpic} shows. \par
+	Clicking on the ``=" node will yield two arguments and expanding each of them
+	will peer into the range of common values of equality comparison, which Figure
+	\ref{fig:fullpic} shows. \par
 
@@
 
-	From these images, we can provide a quick glossary of images within the visualization
-	to aid interpretation.
-	\begin{itemize}
-		\item \includegraphics{glossary-green} - \textbf{Function nodes} are green
-		circles labeled with the function name. Their size is determined by their
-		relative frequency, scaled logarithmically, to the frequency of the root node
-		in the tree. They may have any number of arguments, including zero, as
-		determined by the API.
+	From these images, we can provide a quick glossary of images within the
+	visualization to aid interpretation. \begin{itemize} \item
+		\includegraphics{glossary-green} - \textbf{Function nodes} are green circles
+		labeled with the function name. Their size is determined by their relative
+		frequency, scaled logarithmically, to the frequency of the root node in the
+		tree. They may have any number of arguments, including zero, as determined by
+		the API.
 
-		\item \vspace{.25cm}\includegraphics{glossary-leaf} - \textbf{Value nodes} are white circles
-		with a generic label. They represent elements of a formula which are which
-		accept no arguments, like references (A1), ranges (A1:A10)\footnote{That is,
-			only if both sides of a references are cell references. If either side is a
-			function that returns a cell reference, like INDIRECT, then the colon should
-			be a function node.}, numbers, boolean values, strings, and errors. Functions
-		with zero arguments, like NOW, however, should still be considered function
-		nodes.
+		\item \vspace{.25cm}\includegraphics{glossary-leaf} - \textbf{Value nodes} are
+		white circles with a generic label. They represent elements of a formula which
+		are which accept no arguments, like references (A1), ranges
+		(A1:A10)\footnote{That is, only if both sides of a references are cell
+			references. If either side is a function that returns a cell reference, like
+			INDIRECT, then the colon should be a function node.}, numbers, boolean values,
+		strings, and errors. Functions with zero arguments, like NOW, however, should
+		still be considered function nodes.
 
-		\item  \vspace{.25cm} \includegraphics{glossary-blue} - \textbf{Argument nodes} are dark blue
-		squares labeled with a number. The number is the position of an argument
-		within the function in the parent node. In \ref{fig:expandif} for example,
-		argument node 1 shows every function or value that was seen in the first
-		argument.
+		\item  \vspace{.25cm} \includegraphics{glossary-blue} - \textbf{Argument
+			nodes} are dark blue squares labeled with a number. The number is the position
+		of an argument within the function in the parent node. In \ref{fig:expandif}
+		for example, argument node 1 shows every function or value that was seen in
+		the first argument.
 
-		\item  \vspace{.25cm} \includegraphics{glossary-solidline} - \textbf{Solid lines} represent a
-		function's ownership of its various arguments. As such, they connect the
-		function nodes to argument nodes.
+		\item  \vspace{.25cm} \includegraphics{glossary-solidline} - \textbf{Solid
+			lines} represent a function's ownership of its various arguments. As such,
+		they connect the function nodes to argument nodes.
 
-		\item  \vspace{.25cm} \includegraphics{glossary-fadingline} - \textbf{Fading lines} represent
-		the possibility of an argument position to have several different possible
-		functions or values. As such, they connect argument nodes to function or value
-		nodes.
+		\item  \vspace{.25cm} \includegraphics{glossary-fadingline} - \textbf{Fading
+			lines} represent the possibility of an argument position to have several
+		different possible functions or values. As such, they connect argument nodes
+		to function or value nodes.
 
-		\item  \vspace{.25cm} \includegraphics{glossary-arrow} - \textbf{Expansion arrows} appear
-		within an argument node when there are over 10 possible functions or values in
-		an argument position. By default, only the first 10 will be shown along with
-		this arrow; clicking this will show the rest as well.
+		\item  \vspace{.25cm} \includegraphics{glossary-arrow} - \textbf{Expansion
+			arrows} appear within an argument node when there are over 10 possible
+		functions or values in an argument position. By default, only the first 10
+		will be shown along with this arrow; clicking this will show the rest as well.
 
-		\item  \vspace{.25cm} \includegraphics[scale=.75]{glossary-lightblue} - \textbf{Optional
-			argument trees} are variations of trees that show only formulae with a
-		specific number of arguments, allowing the user to control for the presence of
-		optional arguments. By default, trees with dark blue nodes contain every type
-		of formula without regard how many arguments they have -- for example,
-		single-argument ANDs could appear alongside 4-argument ANDs. See Figure
-		\ref{fig:optional} to see it visualized.
-	\end{itemize}
+		\item  \vspace{.25cm} \includegraphics[scale=.75]{glossary-lightblue} -
+		\textbf{Optional argument trees} are variations of trees that show only
+		formulae with a specific number of arguments, allowing the user to control for
+		the presence of optional arguments. By default, trees with dark blue nodes
+		contain every type of formula without regard how many arguments they have --
+		for example, single-argument ANDs could appear alongside 4-argument ANDs. See
+		Figure \ref{fig:optional} to see it visualized. \end{itemize}
 
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width = .46\textwidth]{comparison}
-		\includegraphics[]{comparison-ss}
-		\label{fig:optional}
-		\caption{The contents of each type of tree.}
-	\end{figure}
+	\begin{figure}[h] \centering \includegraphics[width =
+		.46\textwidth]{comparison} \includegraphics[]{comparison-ss}
+		\label{fig:optional} \caption{The contents of each type of tree.} \end{figure}
 
-	\subsection{Implementation Details} The final visualization is the
-	product of two discrete processes: \begin{itemize} \item \textit{Collection}:
-		Given a set of Excel sheets, the tool, written in Java, uses Apache
+	\subsection{Implementation Details} The final visualization is the product of
+	two discrete processes: \begin{itemize} \item \textit{Collection}: Given a set
+		of Excel sheets, the tool, written in Java, uses Apache
 		POI\footnote{https://poi.apache.org/} to identify and iterate over every cell
@@
 		the formula text into an ordered set of individual tokens, which the tool then
-		parses into the tree-like form. When all formulae have
-		been analyzed like this, it produces JSON files for each top-level function in
-		the set.
+		parses into the tree-like form. When all formulae have been analyzed like this,
+		it produces JSON files for each top-level function in the set.
 
@@
 		presentation code, implemented in Javascript with much help from the
-		visualization library D3\footnote{https://d3js.org/}. We chose D3 primarily for
-		its accessibility: given the JSON, the visualization can be simply
+		visualization library D3\footnote{https://d3js.org/}. We chose D3 primarily
+		for its accessibility: given the JSON, the visualization can be simply
 		embedded into a webpage accessible through a browser. \end{itemize} A
-	demonstration of the tool can be found at https://github.com/DeveloperLiberationFront/Excel-Function-Visualizer.
+	demonstration of the tool can be found at
+	https://github.com/DeveloperLiberationFront/Excel-Function-Visualizer.
 
-	\subsection{Design Decisions} \label{ssec:decisions}
-	Early in the design, we chose the tree form for its inherent ability to
-	represent the loose parent-children relationship of formulae as
-	functions and their arguments, which could be yet more functions. By adapting
-	this structure to accommodate a broad range of possibilities for nested
-	functions, the branching factor depends alternatively on the number of arguments in a
-	function and the number of possible functions observed as an argument in a
-	function. \par
+	\subsection{Design Decisions} \label{ssec:decisions} Early in the design, we
+	chose the tree form for its inherent ability to represent the loose
+	parent-children relationship of formulae as functions and their arguments,
+	which could be yet more functions. By adapting this structure to accommodate a
+	broad range of possibilities for nested functions, the branching factor depends
+	alternatively on the number of arguments in a function and the number of
+	possible functions observed as an argument in a function. \par
 
@@
 		%
-%				\item [1] \textbf{Provide an interactive environment for free exploration.}
-%				There are a lot of data in some of these collections, and the user should be
-%				able to pick for themselves which to explore while ignoring the rest. Furthermore,
-%				this exploration should not be designed around answering one specific question
+		%				\item [1] \textbf{Provide an interactive environment for free
+		% exploration.}
+		%				There are a lot of data in some of these collections, and the user should
+		% be
+		%				able to pick for themselves which to explore while ignoring the rest.
+		% Furthermore,
+		%				this exploration should not be designed around answering one specific
+		% question
 		%				but rather be open-ended.
 		%
-%				\item [!1] \textbf{Do not make judgments about good and bad design.} Though
-%				users may certainly approach the tool with the intention of finding particular
+		%				\item [!1] \textbf{Do not make judgments about good and bad design.}
+		% Though
+		%				users may certainly approach the tool with the intention of finding
+		% particular
 		%				formulae, \toolname will not prioritize any on metrics of good or bad
@@
 		%					construction.} \toolname should address the questions of how often the
-%				spreadsheet programmers used a certain function and where they used it. In
-%				this way, it must show precise metrics, such as frequency of use and depth of
+		%				spreadsheet programmers used a certain function and where they used it.
+		% In
+		%				this way, it must show precise metrics, such as frequency of use and
+		% depth
+		% of
 		%				function nesting, of the dataset it conveys.
@@
 		%				especially, we anticipated some particularly dense trees. Though
-%				everything should be accessible in accordance with Goal 1, we should design in
+		%				everything should be accessible in accordance with Goal 1, we should
+		% design
+		% in
 		%				a way that reduces noise.
@@
 		%				\toolname should supplement its observations with concrete instances of
-%				relevant formulae from the corpus. Ideally, it should even direct users to the
-%				exact cell in the spreadsheets where the formula was used, contextualizing the
+		%				relevant formulae from the corpus. Ideally, it should even direct users
+		% to
+		% the
+		%				exact cell in the spreadsheets where the formula was used,
+		% contextualizing
+		% the
 		%				functions.
 		%
-%				\item [!3] \textbf{Do not attempt to explain formulae.} Though \toolname tries
-%				to foster understanding by linking pattern to example, it should not provide
-%				a precise description of what a complex formula accomplishes. The tool's user
+		%				\item [!3] \textbf{Do not attempt to explain formulae.} Though \toolname
+		% tries
+		%				to foster understanding by linking pattern to example, it should not
+		% provide
+		%				a precise description of what a complex formula accomplishes. The tool's
+		% user
 		%				must infer this on their own.
@@
 
-		\item \textit{Copied formulae}: Excel allows users to spread a
-		formula over an area, repeating the same task in each cell with minor
-		adjustments. Without checking for this, the analysis may not reveal the
-		functions most commonly used together but rather the formulae most often
-		applied to large areas. To combat this, we converted formulae from their native
-		A1 format to the relative R1C1, in which copied formulae should be identical,
-		and considered only each R1C1 formulae once per worksheet.
+		\item \textit{Copied formulae}: Excel allows users to spread a formula over an
+		area, repeating the same task in each cell with minor adjustments. Without
+		checking for this, the analysis may not reveal the functions most commonly
+		used together but rather the formulae most often applied to large areas. To
+		combat this, we converted formulae from their native A1 format to the relative
+		R1C1, in which copied formulae should be identical, and considered only each
+		R1C1 formulae once per worksheet.
 
-		\item \textit{Importance of depth}: When a function appears within another, should it
-		be analyzed only as a nested function or would it also be valid to analyze the
-		nested function on its own? \par
+		\item \textit{Importance of depth}: When a function appears within another,
+		should it be analyzed only as a nested function or would it also be valid to
+		analyze the nested function on its own? \par
 
@@
 		top-level IF -- then the tool will represent some functions in multiple nodes
-		to capture every possible level of nesting. For now, we only include the first,
-		with the latter to be added as an option in the future.
+		to capture every possible level of nesting. For now, we only include the
+		first, with the latter to be added as an option in the future.
 
@@
 	the surface, the tool supports easy quantification through the tooltips
-	displayed for each node, as shown in figure \ref{fig:vhlookups}, answering
-	the question, "How often do spreadsheet programmers use this function?". But,
-	more to the point, the tool's distinction between the numbers of arguments for
-	a single function lets the user compare frequencies of three-argument forms
-	with the four-argument. The visualization does not, however, discern between
-	the different values for booleans in the tree, much less whether the
-	spreadsheet columns are ordered -- but the linking of examples to patterns
-	allows quick insight into which files are at risk for the problems they
-	outlined. \par
+	displayed for each node, as shown in figure \ref{fig:vhlookups}, answering the
+	question, "How often do spreadsheet programmers use this function?". But, more
+	to the point, the tool's distinction between the numbers of arguments for a
+	single function lets the user compare frequencies of three-argument forms with
+	the four-argument. The visualization does not, however, discern between the
+	different values for booleans in the tree, much less whether the spreadsheet
+	columns are ordered -- but the linking of examples to patterns allows quick
+	insight into which files are at risk for the problems they outlined. \par
 

### 2016-04-22 doc/paper.tex
Case study rewording. Fixes #75, fixes #76.

@@
 
-	\section{Related Work} Given humanity's affinity for visual information,
+	\section{Related Work} \label{related-work} Given humanity's affinity for visual information,
 	visualizations have long been prized for their ability to communicate
@@
 	for the case of confirming a value in another cell before assigning this one.
-	Furthermore, if the concept is difficult to imagine is practice, a tooltip
-	accompanies each function node in the tree, providing a concrete example of a
-	function that uses this structure and where it can be found. If this single
-	instance is not enough, then the user also has the option to double-click the
-	individual function node, which will open up a new tab with a table of many
-	more examples from dataset.
+	Furthermore, a tooltip accompanies each function node in the tree, providing a
+	concrete example of a function that uses this structure and where it can be
+	found. If this single instance is not enough, then the user also has the option
+	to double-click the individual function node, which will open up a new tab with
+	a table of many more examples from dataset.
 
@@
 
+		%Can I incorporate these again?
 		%			\begin{itemize}
@@
 	\section{Case Study} The obvious question to pose to any visualization is this:
-	Why does it matter that we see this way? In other words, it is not enough to
-	prove that something can be visualized; instead we must also demonstrate what
+	What do the images tell us that the text could not? It is not enough to
+	prove that something can be visualized; we must also demonstrate what
 	we can be gained from any particular visualization. As such, we raised a few
 	tasks in the introduction in which we thought the tool could help: identifying
-	places for API improvement, detecting bad smells or common programmer
-	misunderstanding, and guiding spreadsheet education. To demonstrate the tool's
-	applicability, then, we sought out places in the tree which best exemplify
-	these respective concerns.
+	places for API improvement, detecting bad smells, and guiding spreadsheet education. To demonstrate the tool's
+	applicability, we sought out places in the tree which best exemplify
+	these tasks.
 
@@
 	between perfect code and bug-crippled spaghetti,  there is a spectrum of code
-	designs which, by themselves, are not faulty but nevertheless suggest problems
-	and vulnerabilities in code design. Code smells, as we call them, soon
-	commanded attention and earned wide-ranging applicability, eventually making it
-	to the art of spreadsheet design.
+	designs which, by themselves, are not faulty but nevertheless suggest vulnerabilities in code design. 	
+	Since then, researchers have applied these concepts to spreadsheet programming, as 
+	discussed in section \ref{related-work}. While some of the smells lie beyond the scope
+	of the tool, such as those characterizing inter-worksheet connections, others
+	have structures which create distinctive features within the tree, leading to
+	easy detection through our visualization: \par
 
-	Since then, spreadsheet researchers have taken the concept, if not the specific
-	smells themselves, and applied them to spreadsheet programming
-	\cite{hermans2012detecting} \cite{cunha2012towards} \cite{jansen2015code}
-	\cite{asavametha2012detecting} . While some of the smells lie beyond the scope
-	of the tool, such as those characterizing inter-worksheet connections, some
-	have structures which create distinctive features within the tree, leading to
-	easy detection through visualization: \par
+	\begin{itemize}
 
-	\begin{itemize} \item \textit{Long Method}: Also called "Multiple Operations"
+		\item \textit{Long Method}: Also called "Multiple Operations"
 		in \cite{hermans2012detecting}, this refers to situations where numerous
-		functions and operators are used all within the same cell, creating a formula
-		that tends to extend beyond a compact viewing space and makes it difficult to
-		understand. In the visualization, since each nested and combined function
+		functions and operators are used within a single formula. As a result, the formula
+		tends to be prohibitively complex. In the visualization, since each nested and combined function
 		creates yet another level of depth within the tree, these constructions can
 		result in long, horizontal chains of nodes, as seen in figure
-		\ref{"fig:longsum"}. \item \textit{Long Parameter List}: [tall, vertical towers
-		of blue nodes] \item \textit{Conditional Complexity}: [IF nodes within IF
+		\ref{"fig:longsum"}.
+
+		\item \textit{Long Parameter List}: [tall, vertical towers
+		of blue nodes]
+
+		\item \textit{Conditional Complexity}: [IF nodes within IF
 		nodes] \end{itemize}

### 2016-04-23 doc/paper.tex
User study. Fixes #71, fixes #72, fixes #73, fixes #74, fixes #75, fixes #76, fixes #77.

@@
 
+	\subsection{API Improvement}
+
 	\subsection{Bad Smells} Fowler's description of code smells
 	\cite{fowler2009refactoring} underscored an important point of code quality:
-	between perfect code and bug-crippled spaghetti,  there is a spectrum of code
+	between elegant, efficient code and bug-crippled spaghetti, there is a spectrum of code
 	designs which, by themselves, are not faulty but nevertheless suggest vulnerabilities in code design. 	
@@
 
-		\item \textit{Long Method}: Also called "Multiple Operations"
-		in \cite{hermans2012detecting}, this refers to situations where numerous
-		functions and operators are used within a single formula. As a result, the formula
-		tends to be prohibitively complex. In the visualization, since each nested and combined function
-		creates yet another level of depth within the tree, these constructions can
-		result in long, horizontal chains of nodes, as seen in figure
-		\ref{"fig:longsum"}.
+		\item \textit{Multiple Operations}: A single formula comprises numerous
+		functions and operators. \cite{hermans2012detecting}. As a result, the formula
+		tends to be prohibitively complex. In the visualization, since each nested and
+		combined function creates yet another level of depth within the tree, these
+		constructions can result in long, horizontal chains of nodes, as seen in
+		figure \ref{"fig:longsum"}.
 
-		\item \textit{Long Parameter List}: [tall, vertical towers
-		of blue nodes]
+		\item \textit{Long Parameter List}: A function uses numerous arguments, making
+		it harder to understand \cite{asavametha2012detecting}. This is not a problem
+		for many functions which have a limited number of arguments that it accepts. However,
+		for functions that accept arguments indefinitely, such as SUM and CONCATENATE, it creates
+		tall towers of argument nodes from a single function node.
 
-		\item \textit{Conditional Complexity}: [IF nodes within IF
-		nodes] \end{itemize}
+		\item \textit{Conditional Complexity}: A logical function, particularly IF, nests
+		several other logical functions inside of it, reducing code readability \cite{hermans2012detecting}. 
+		These can be traced manually in the trees for the logical functions. IF, for example,
+		will have several more IF function nodes within its second or third arguments, which
+		in turn might have more of the same nested within them.
+
+	\end{itemize}
 
@@
 
-	Some examples are meaningful not for the space they take up but for how they
-	clash with the expectations around a function. For example, Excel offers a
+	Some code issues are meaningful not for the space they occupy but for how they
+	clash with a function's expectations. For example, Excel offers a
 	number of functions that accept any number arguments given to them, up to a
-	resource-defined limit. SUM and CONCATENATE are two such functions: adding more
-	arguments simply adds or appends that element in the same way as every previous
-	argument. Strange cases were found, then, in the cases where these functions
-	were used with only one argument. \par
+	resource-defined limit. SUM, for example, simply adds every argument given to it.
+	This also means that it can accept only one argument, and when the user does so,
+	they pass in a range of cells over 90\% of the time. However, using the tool,
+	we isolated an instance where the programmer used a single-argument SUM where the 
+	argument was a series of 32 contiguous cells added with the + operation -- 
+	``SUM(C6+C7+C8+C9+C10+C11+C12+C13+...+C37)" -- representing a technically
+	valid but unusual and problematic design.\par
 
@@
 
-	\section{User Study} Midway through production, we conducted a brief,
-	four-participant user study in order to gauge how well we were capturing the
-	initial design goals. The study was, in general, a flexible and exploratory
-	affair: rather than giving the users any specific tasks or pointed questions,
-	we asked instead that they choose for themselves which trees to explore and
-	report anything that they deemed interesting. Specifically, given trees rooted
-	in the Enron dataset and at least 20 to thirty minutes, the participants
-	situated themselves within the persona of a consultant asked to evaluate a
-	company's spreadsheet practice, which could be arranged around questions like
-	which functions on which the employees most depended, which sheets presented
-	the most anomalous or dangerous designs, and so on. Interpretation of
-	"spreadsheet practice" can certainly vary from participant to participant, but
-	since we wanted a range of views and backgrounds despite the persona, we
-	readily accepted this interpretive wiggle room. \par
+	\section{User Study} During development, we conducted a brief, four-participant
+	user study in order to detect conflicts between our design and the goals in
+	section \ref{goals}. We designed the study to be exploratory; given trees based
+	in the Enron dataset and at least twenty minutes, we asked the participants to
+	adopt the persona of a consultant evaluating a company's spreadsheet
+	practice, allowing for questions like which functions on which the employees
+	most depended or which sheets or employees presented the most anomalous or
+	dangerous designs. Though we instructed them on how to use the tool and
+	suggested that they visit one of the most populous trees in the set, we put
+	aside any specific tasks or questions and let them choose their own paths.
+	Though interpretation of the phrase ``spreadsheet practice" can certainly vary
+	from participant to participant, we readily accepted this interpretive
+	flexibility since we wanted a range of views and backgrounds despite the
+	persona. \par
 
@@
 
-	\begin{wrapfigure}{l}{.12\textwidth} \centering \includegraphics{SUM}
-		\label{fig:sum} \end{wrapfigure}
+	\begin{wrapfigure}{L}{.25\textwidth} \centering \includegraphics{SUM}
+		\label{fig:sum} \caption{An abundance of parameters in SUM} \end{wrapfigure}
 
@@
 
-	\begin{figure} \centering \includegraphics[scale=.5]{longIF} \label{fig:longif}
+	\begin{wrapfigure}{R}{.25\textwidth} \centering \includegraphics[scale=.5]{longIF} \label{fig:longif}
 		\caption{The many possibilities of IF, argument 3, demonstrate the problem of
-			having too many options.} \end{figure}
+			having too many options.} \end{wrapfigure}
 
@@
 
-	\includegraphics[width = .46\textwidth]{comparison}
+	[MOVED]
 

### 2016-04-23 doc/paper.tex
More user study. Fixes #78, fixes #79, fixes #80.

@@
 	flexibility since we wanted a range of views and backgrounds despite the
-	persona. \par
-
-	We clarified, furthermore, that these notes could be directed either at the
-	quality of the data conveyed by the tool or at the tool's conveyance itself.
-	Since the tool's philosophy was based in exploration, we decided that it would
-	not have been appropriate to restrict what people were to look for, letting
-	them find interesting stories of formula construction for themselves.
-	Additionally, either kind of comment -- on data or on tool -- would direct us
-	back to the central evaluation; a user's silence, or lack of any interesting
-	findings, would tacitly indicate that perhaps the tool does not convey
-	information well enough. \par
+	persona. We clarified, furthermore, that their observations could be directed either at the
+	quality of the data conveyed by the tool or at the tool's design itself. \par
 

### 2016-04-23 doc/paper.tex
Reordering user study. Fixes #83

@@
 
-	Still, several limitations cropped up during the study that complicate the
-	evaluation. For one thing, though the source of the data was not explicitly
-	stated at the outset of the session, several users studied the file names
-	(unchanged as they were) to deduce its roots in finance, if not Enron itself.
-	Because of these notorious connotations, then, some were inclined from this
-	moment of discovery to orient their exploration around finance-related
-	functions, potentially limiting their findings or perceived users for the tool
-	-- though some also said that, without this essential context, they could not
-	have properly explored a dataset in the first place. Comments like these point
-	out the trade-offs of unguided exploration, too: though it might not restrict
-	them to a single purpose, it might, at the same time, not afford them any
-	mindset at all with which to interpret the data. Another potential problem is
-	that the data which users explored was processed and created before we had
-	fully completed the tool, meaning some of the counts and patterns in the trees
-	were inaccurate. However, we decided that this was not a pressing concern,
-	being that we were primarily with whether any interesting reports could be made
-	at all, not with whether these reports were 100\% accurate assessments of
-	reality. \par
-
 	Nevertheless, these user studies were a formative moment in evaluating the
@@
 
-	\subsection{Positive Responses} The inclusion of formula examples, grounded in
-	and linking back to the originating spreadsheets, proved to be an especial draw
-	to the tool. After all, none of the participants professed themselves to be
-	experts with Excel, their self-reported proficiencies ranging from "fairly
-	familiar" (P2) to "not extremely familiar" (P4); even if they were experts, it
-	would likely be unreasonable to expect an evenly distributed familiarity with
-	the 100+ function trees available. Nevertheless, the list of actual formulae
-	accessible through a node's double-click allowed the users a way to find
-	examples of formulae with exactly the configuration they wanted. For example,
-	as P1 explored the VLOOKUP function, even though they knew the official API
-	more verbosely explained its signature, they said they could use the tool to
-	collect more examples than the documentation offers. \par
-
-	Furthermore, it offers a simple way of finding examples where certain functions
-	were used together. though a standard text-search tool might yield the same
-	results for a function alone, combinations can require more complex text
-	queries, whereas here, the information is already captured in nodes. [This
-	paragraph contrasts it with previous approaches, but lacks compelling evidence
-	-- a lot of "mights"] \par
-
-	\begin{wrapfigure}{L}{.25\textwidth} \centering \includegraphics{SUM}
+	\subsection{Use in Smell Tracking}
+	\begin{wrapfigure}{O}{.25\textwidth} \centering \includegraphics{SUM}
 		\label{fig:sum} \caption{An abundance of parameters in SUM} \end{wrapfigure}
@@
 
-	\subsection{Negative Responses} Some interaction with the tool underlined how a
-	lack of contextual information may limit the tool. For example, the benefits
-	described in the previous sections imply a hidden complication: if the tool
-	educates through example but doesn't explicitly distinguish between good design
-	and bad design, how can we be sure that people won't inadvertently learn bad
-	design from it. Right now, we can't be sure; the tool would have to be
-	supplemented with a distinguishing eye, informed on bad design already, and
-	supplying the tool with this would take it beyond a design-agnostic view. [More
-	on this in the conclusion.] \par
+	\subsection{Use in Education}
+	The inclusion of formula examples, grounded in
+	and linking back to the originating spreadsheets, proved to be an especial draw
+	to the tool. After all, none of the participants professed themselves to be
+	experts with Excel, their self-reported proficiencies ranging from "fairly
+	familiar" (P2) to "not extremely familiar" (P4); even if they were experts, it
+	would likely be unreasonable to expect an evenly distributed familiarity with
+	the 100+ function trees available. Nevertheless, the list of actual formulae
+	accessible through a node's double-click allowed the users a way to find
+	examples of formulae with exactly the configuration they wanted. For example,
+	as P1 explored the VLOOKUP function, even though they knew the official API
+	more verbosely explained its signature, they said they could use the tool to
+	collect more examples than the documentation offers. \par
+
+	Furthermore, it offers a simple way of finding examples where certain functions
+	were used together. though a standard text-search tool might yield the same
+	results for a function alone, combinations can require more complex text
+	queries, whereas here, the information is already captured in nodes. [This
+	paragraph contrasts it with previous approaches, but lacks compelling evidence
+	-- a lot of "mights"] \par
 
@@
 
-	A threat to the exploratory philosophy may also mount from the problem of too
-	much data, particularly in the popular functions, like SUM and IF. We had added
-	some precautions before the study: for any position in the tree, for example,
-	only the ten most common functions were displayed without clicking on the
-	expansion arrow \includegraphics[scale=.35]{arrow}. Nevertheless, P3 remarked
-	that they specifically avoided the most popular functions, anticipating a flood
-	of nodes from which they could salvage nothing interesting -- which might not
-	have been a bad prediction, considering that the SUM is built from 910 nodes
-	and IF, at least 18000 [double-check these with refined data]. P2 corroborated
-	this by explaining how they gravitated toward specific examples over the plane
-	of nodes but complicates it further by also deeming the tool at its best when
-	it shows either every possibility of an side-by-side (for comparison) or
-	nothing on that branch at all, a balance that is hard to strike with node-dense
-	trees. \par
+	\subsection{Study Limitations}
 
-	\begin{wrapfigure}{R}{.25\textwidth} \centering \includegraphics[scale=.5]{longIF} \label{fig:longif}
-		\caption{The many possibilities of IF, argument 3, demonstrate the problem of
-			having too many options.} \end{wrapfigure}
+	Still, several limitations cropped up during the study that complicate the
+	evaluation. For one thing, though the source of the data was not explicitly
+	stated at the outset of the session, several users studied the file names
+	(unchanged as they were) to deduce its roots in finance, if not Enron itself.
+	Because of these notorious connotations, then, some were inclined from this
+	moment of discovery to orient their exploration around finance-related
+	functions, potentially limiting their findings or perceived users for the tool
+	-- though some also said that, without this essential context, they could not
+	have properly explored a dataset in the first place. Comments like these point
+	out the trade-offs of unguided exploration, too: though it might not restrict
+	them to a single purpose, it might, at the same time, not afford them any
+	mindset at all with which to interpret the data. Another potential problem is
+	that the data which users explored was processed and created before we had
+	fully completed the tool, meaning some of the counts and patterns in the trees
+	were inaccurate. However, we decided that this was not a pressing concern,
+	being that we were primarily with whether any interesting reports could be made
+	at all, not with whether these reports were 100\% accurate assessments of
+	reality. \par
 
@@
 	particularly optional arguments, were easily lost in the representation. To
-	illustrate this, consider the following two trees: \par
-
-	[MOVED]
-
+	illustrate this, consider the following two trees.	
 	The difference is, perhaps, too subtle: on the left, the tree contains
@@
 	realm of future improvement.
+
+	\begin{wrapfigure}{O}{.25\textwidth} 
+		\centering 
+		\includegraphics[width=.25\textwidth]{longIF} 
+		\label{fig:longif}
+		\caption{The many possibilities of IF, argument 3, demonstrate the problem of
+			having too many options.} 
+	\end{wrapfigure}
+
+	A threat to the exploratory philosophy may also mount from the problem of too
+	much data, particularly in the popular functions, like SUM and IF. We had added
+	some precautions before the study: for any position in the tree, for example,
+	only the ten most common functions were displayed without clicking on the
+	expansion arrow \includegraphics[scale=.35]{arrow}. Nevertheless, P3 remarked
+	that they specifically avoided the most popular functions, anticipating a flood
+	of nodes from which they could salvage nothing interesting -- which might not
+	have been a bad prediction, considering that the SUM is built from 910 nodes
+	and IF, at least 18000 [double-check these with refined data]. P2 corroborated
+	this by explaining how they gravitated toward specific examples over the plane
+	of nodes but complicates it further by also deeming the tool at its best when
+	it shows either every possibility of an side-by-side (for comparison) or
+	nothing on that branch at all, a balance that is hard to strike with node-dense
+	trees. \par
 

### 2016-04-23 doc/paper.tex
User study stuff. Fixes #92, fixes #93, fixes #97, fixes #95, fixes #94, fixes #98, fixes #99, fixes #100, fixes #101, fixes #103, fixes #104, fixes #105, fixes #106, fixes #107.

@@
 
-	\subsection{Bad Smells} Fowler's description of code smells
+	\subsection{Bad Smells} \label{badsmells} Fowler's description of code smells
 	\cite{fowler2009refactoring} underscored an important point of code quality:
@@
 	\begin{wrapfigure}{O}{.25\textwidth} \centering \includegraphics{SUM}
-		\label{fig:sum} \caption{An abundance of parameters in SUM} \end{wrapfigure}
+		\label{fig:sum} \caption{An abundance of parameters in SUM. Encountering this, P4
+			remarked, "Woah."} \end{wrapfigure}
 
-	The discovery of errors and bad design, whether by purpose or accident,
-	produced the more jarring events of the study, and as such, most users
-	commented on the tool's ability to locate these problems in spreadsheet design.
-	This was often supported by the distinctive visual signatures of certain bad
-	practices: multiple arguments produce towers of nodes, deep function nesting
-	stretches the tree horizontally, and so on. As such, the participants remarked
-	on the problems quickly after opening: P3, exploring the example for a
-	27-argument SUM (with SUM's initial appearance pictured left), diagnosed the
-	situation with either incompetency or just plain weirdness; P2, meanwhile,
-	decided that the spreadsheet's author "was having a bad day" when writing an
-	AVERAGE with 18 distinct arguments. Aside from these implicit cues, there are
-	also nodes which refer to formula errors, prefixed with \#s, which P4 said
-	could be useful if marked well. Furthermore, once these errors are found, the
-	participants could then open the offending spreadsheets, discovering that, even
-	in context, some of these formulae remained incomprehensible, posing problems
-	for the spreadsheet transfer scenarios as outlined by Hermans
-	\cite{hermans2011supporting}. The tool, then, aggregates these issues in a
-	single place, accessible to either the unguided user and the ones who know
-	exactly where to find these issues. \par
+	The participants were most vocal about their findings when they discovered, by
+	purpose or accident, instances of heinous design in the dataset. Many times,
+	they noted these examples shortly after opening a new tree, suggesting that the
+	distinctive visual signatures as discussed in section \ref{badsmells} was a
+	salient force in their exploration. For example, when P3 encountered the
+	initial design of the SUM tree, as seen in figure \ref{fig:sum}, they readily
+	diagnosed that either a spreadsheet author was "totally incompetent, or [the
+	formula was] just some that's weird." Other than these visual cues, value
+	errors, prefixed with \#s, also appear in the tree where they are found, 
+	which P4 said could be useful for tracking these problems if marked well.
+
+	Additionally, because the files in the Enron set had name with the author
+	as a prefix, P2 commented that they could use the tool in a company
+	setting to follow up with repeat offenders. For instance, they first
+	encountered a particular author's name when investigating an AVERAGE function
+	with 18 distinct arguments for which our participant could not discern any
+	logical order, even after opening the source spreadsheet; the same name
+	popped up again as P2 looked at a RATE function relying on several hard-coded
+	values. P2 said that, if they were a manager or project leader, this recurrence
+	was a sign to talk to the author personally and figure out why
+	these problems were there, as to prevent more in the future. They also added
+	that these problems would grow worse if this particular author left the company
+	and no one remained who understood these formulae, a concern that aligns with
+	Hermans' transfer scenarios \cite{hermans2011supporting}.
 
@@
 	that this visual interface better supports the case when searching for new and
-	unknown brands of bad smell.
-
-	Because the exploratory design makes no qualitative judgment and visualizes
-	benign designs with the problematic, it therefore allows for flexible
-	interpretation of what is an issue; that is, a user might not realize a certain
-	design is suboptimal until they see it in the tree and, at the point, find
-	every instance of it.
+	unknown brands of bad smell. Because the exploratory design makes no
+	qualitative judgment and visualizes benign designs with the problematic, it
+	therefore allows for flexible interpretation of what is a smell; that is, a
+	user might not realize a certain design is suboptimal until they see it in the
+	tree and, at the point, find specific examples of where it occurs in the
+	spreadsheets.
 

### 2016-04-23 doc/paper.tex
User study stuff. Fixes #110, fixes #112

@@
 	formula was] just some that's weird." Other than these visual cues, value
-	errors, prefixed with \#s, also appear in the tree where they are found, 
+	errors, prefixed with \#s, also appear in the tree, 
 	which P4 said could be useful for tracking these problems if marked well.
@@
 
-	\subsection{Use in Education}
-	The inclusion of formula examples, grounded in
-	and linking back to the originating spreadsheets, proved to be an especial draw
-	to the tool. After all, none of the participants professed themselves to be
-	experts with Excel, their self-reported proficiencies ranging from "fairly
-	familiar" (P2) to "not extremely familiar" (P4); even if they were experts, it
-	would likely be unreasonable to expect an evenly distributed familiarity with
-	the 100+ function trees available. Nevertheless, the list of actual formulae
-	accessible through a node's double-click allowed the users a way to find
-	examples of formulae with exactly the configuration they wanted. For example,
-	as P1 explored the VLOOKUP function, even though they knew the official API
-	more verbosely explained its signature, they said they could use the tool to
-	collect more examples than the documentation offers. \par
+	\subsection{Use in Education} Users found \toolname's inclusion of examples
+	to be especially useful since none of the them considered themselves to be
+	experts of Excel, their self-reported proficiencies ranging from "fairly
+	familiar" (P2) to "not extremely familiar" (P4). For example, as P1 explored
+	the VLOOKUP function, they said they could use the tool to collect more
+	examples than the documentation offers even though they knew the documentation more verbosely
+	explained its function signature. Furthermore, in the process of exploring trees,
+	P1 and P3 also gravitated towards some functions they had not used before, such as
+	PV and IPMT, looking for new features in Excel to explore and learn. \par
 
-	Furthermore, it offers a simple way of finding examples where certain functions
-	were used together. though a standard text-search tool might yield the same
+	Additionally, \toolname offers a simple way of finding examples where certain functions
+	were used together. Though a standard text-search tool might yield the same
 	results for a function alone, combinations can require more complex text
-	queries, whereas here, the information is already captured in nodes. [This
-	paragraph contrasts it with previous approaches, but lacks compelling evidence
-	-- a lot of "mights"] \par
+	queries, whereas here, the information is already captured in nodes.  \par
 
-	Furthermore, just because a user can exhaustively explore every variation of
-	how a function was used doesn't mean they will learn exactly what it does. P1,
-	in their exploration, examined functions that they hadn't used before, such as
-	KURT and PV, and described precisely what types of arguments it accepted and
-	how many. However, even after exploring the spreadsheets, they could not
+	However, we found that even though a user can explore all of a function's configurations, this
+	does not mean that they will learn exactly what it does. P1,
+	examining unfamiliar functions like
+	KURT and PV, could describe precisely what types of arguments it accepted and
+	how many. But even after exploring the spreadsheets for context, they could not
 	accurately describe what the functions produced without consulting the official
 	documentation. Whether through reticence of the tool or obscurity of the
-	functions themselves, the exploratory environment is not enough for independent
-	education. However, unlike the previous problem, this can be addressed,
-	perhaps, by guiding the user directly to such documentation from within the
-	tool without violating any design concerns. \par
+	functions themselves, the exploratory environment is not enough to teach users
+	\textit{when} to use a function. However, we could address this in future designs,
+	perhaps, by linking directly to such documentation from within the
+	tool without violating any design concerns in \ref{goals}. \par
 

### 2016-04-23 doc/paper.tex
Redesign of limitations.

@@
 
-	\begin{itemize} \item API improvement \item Detection of code smells \item
+	\begin{itemize} \item Detection of code smells \item
 		Spreadsheet education \end{itemize}
@@
 
-	\section{Related Work} \label{related-work} Given humanity's affinity for visual information,
-	visualizations have long been prized for their ability to communicate
-	information quickly and efficient \cite{baeza1999modern}; the visualization of
-	spreadsheets, therefore, has offered much room for research. Several previous
-	tools work within a spreadsheet, seeking to clarify the connections between the
-	visible values in cells, the formulae that produce them, and the dependencies
-	between cells that inform them. Igarashi and colleague's fluid visualizations
-	\cite{igarashi1998fluid}, for example, do this by imposing lines, color, and
-	animation over the spreadsheet to visually explain these tangled connections.
-	Likewise, Clermont explored ways of grouping cells by color and border that
-	were related through similar functions, neighbors, or references
-	\cite{clermont2003scalable}, and Hipfl extended this work by incorporating the
-	layouts and labels of spreadsheets \cite{hipfl2008using}. Other tools focus on
-	creating visualizations external to the sheets. Hermans and colleagues address
-	a spreadsheet programmer's information by making dataflow diagrams from
-	individual sheets through the tools GyroSAT \cite{hermans2011supporting} and
-	Breviz \cite{hermans2011breviz}. \toolname is among the latter class, creating
-	standalone visualizations about spreadsheets. In contrast to Hermans' work,
-	though, our work focuses on representing functions and how they comprise
-	complex formula, rather than exploring the data structures of any particular
-	spreadsheet.  \par
+	\section{Related Work} \label{related-work} Given humanity's affinity for
+	visual information, visualizations have long been prized for their ability to
+	communicate information quickly and efficient \cite{baeza1999modern}; the
+	visualization of spreadsheets, therefore, has offered much room for research.
+	Several previous tools work within a spreadsheet, seeking to clarify the
+	connections between the visible values in cells, the formulae that produce
+	them, and the dependencies between cells that inform them. Igarashi and
+	colleague's fluid visualizations \cite{igarashi1998fluid}, for example, do this
+	by imposing lines, color, and animation over the spreadsheet to visually
+	explain these tangled connections. Likewise, Clermont explored ways of grouping
+	cells by color and border that were related through similar functions,
+	neighbors, or references \cite{clermont2003scalable}, and Hipfl extended this
+	work by incorporating the layouts and labels of spreadsheets
+	\cite{hipfl2008using}. Other tools focus on creating visualizations external to
+	the sheets. Hermans and colleagues address a spreadsheet programmer's
+	information by making dataflow diagrams from individual sheets through the
+	tools GyroSAT \cite{hermans2011supporting} and Breviz \cite{hermans2011breviz}.
+	\toolname is among the latter class, creating standalone visualizations about
+	spreadsheets. In contrast to Hermans' work, though, our work focuses on
+	representing functions and how they comprise complex formula, rather than
+	exploring the data structures of any particular spreadsheet.  \par
 
@@
 	\section{Case Study} The obvious question to pose to any visualization is this:
-	What do the images tell us that the text could not? It is not enough to
-	prove that something can be visualized; we must also demonstrate what
-	we can be gained from any particular visualization. As such, we raised a few
-	tasks in the introduction in which we thought the tool could help: identifying
-	places for API improvement, detecting bad smells, and guiding spreadsheet education. To demonstrate the tool's
-	applicability, we sought out places in the tree which best exemplify
-	these tasks.
-
-	\subsection{API Improvement}
+	What do the images tell us that the text could not? It is not enough to prove
+	that something can be visualized; we must also demonstrate what we can be
+	gained from any particular visualization. As such, we raised a few tasks in the
+	introduction in which we thought the tool could help: identifying places for
+	API improvement, detecting bad smells, and guiding spreadsheet education. To
+	demonstrate the tool's applicability, we sought out places in the tree which
+	best exemplify these tasks.
 
@@
 	\cite{fowler2009refactoring} underscored an important point of code quality:
-	between elegant, efficient code and bug-crippled spaghetti, there is a spectrum of code
-	designs which, by themselves, are not faulty but nevertheless suggest vulnerabilities in code design. 	
-	Since then, researchers have applied these concepts to spreadsheet programming, as 
-	discussed in section \ref{related-work}. While some of the smells lie beyond the scope
-	of the tool, such as those characterizing inter-worksheet connections, others
-	have structures which create distinctive features within the tree, leading to
-	easy detection through our visualization: \par
+	between elegant, efficient code and bug-crippled spaghetti, there is a spectrum
+	of code designs which, by themselves, are not faulty but nevertheless suggest
+	vulnerabilities in code design. Since then, researchers have applied these
+	concepts to spreadsheet programming, as discussed in section
+	\ref{related-work}. While some of the smells lie beyond the scope of the tool,
+	such as those characterizing inter-worksheet connections, others have
+	structures which create distinctive features within the tree, leading to easy
+	detection through our visualization: \par
 
@@
 		it harder to understand \cite{asavametha2012detecting}. This is not a problem
-		for many functions which have a limited number of arguments that it accepts. However,
-		for functions that accept arguments indefinitely, such as SUM and CONCATENATE, it creates
-		tall towers of argument nodes from a single function node.
+		for many functions which have a limited number of arguments that it accepts.
+		However, for functions that accept arguments indefinitely, such as SUM and
+		CONCATENATE, it creates tall towers of argument nodes from a single function
+		node.
 
-		\item \textit{Conditional Complexity}: A logical function, particularly IF, nests
-		several other logical functions inside of it, reducing code readability \cite{hermans2012detecting}. 
-		These can be traced manually in the trees for the logical functions. IF, for example,
-		will have several more IF function nodes within its second or third arguments, which
-		in turn might have more of the same nested within them.
+		\item \textit{Conditional Complexity}: A logical function, particularly IF,
+		nests several other logical functions inside of it, reducing code readability
+		\cite{hermans2012detecting}. These can be traced manually in the trees for the
+		logical functions. IF, for example, will have several more IF function nodes
+		within its second or third arguments, which in turn might have more of the
+		same nested within them.
 
@@
 	Some code issues are meaningful not for the space they occupy but for how they
-	clash with a function's expectations. For example, Excel offers a
-	number of functions that accept any number arguments given to them, up to a
-	resource-defined limit. SUM, for example, simply adds every argument given to it.
-	This also means that it can accept only one argument, and when the user does so,
-	they pass in a range of cells over 90\% of the time. However, using the tool,
-	we isolated an instance where the programmer used a single-argument SUM where the 
-	argument was a series of 32 contiguous cells added with the + operation -- 
-	``SUM(C6+C7+C8+C9+C10+C11+C12+C13+...+C37)" -- representing a technically
-	valid but unusual and problematic design.\par
+	clash with a function's expectations. For example, Excel offers a number of
+	functions that accept any number arguments given to them, up to a
+	resource-defined limit. SUM, for example, simply adds every argument given to
+	it. This also means that it can accept only one argument, and when the user
+	does so, they pass in a range of cells over 90\% of the time. However, using
+	the tool, we isolated an instance where the programmer used a single-argument
+	SUM where the argument was a series of 32 contiguous cells added with the +
+	operation -- ``SUM(C6+C7+C8+C9+C10+C11+C12+C13+...+C37)" -- representing a
+	technically valid but unusual and problematic design.\par
 
@@
 	in the Enron dataset and at least twenty minutes, we asked the participants to
-	adopt the persona of a consultant evaluating a company's spreadsheet
-	practice, allowing for questions like which functions on which the employees
-	most depended or which sheets or employees presented the most anomalous or
-	dangerous designs. Though we instructed them on how to use the tool and
-	suggested that they visit one of the most populous trees in the set, we put
-	aside any specific tasks or questions and let them choose their own paths.
-	Though interpretation of the phrase ``spreadsheet practice" can certainly vary
-	from participant to participant, we readily accepted this interpretive
-	flexibility since we wanted a range of views and backgrounds despite the
-	persona. We clarified, furthermore, that their observations could be directed either at the
-	quality of the data conveyed by the tool or at the tool's design itself. \par
+	adopt the persona of a consultant evaluating a company's spreadsheet practice,
+	allowing for questions like which functions on which the employees most
+	depended or which sheets or employees presented the most anomalous or dangerous
+	designs. Though we instructed them on how to use the tool and suggested that
+	they visit one of the most populous trees in the set, we put aside any specific
+	tasks or questions and let them choose their own paths. Though interpretation
+	of the phrase ``spreadsheet practice" can certainly vary from participant to
+	participant, we readily accepted this interpretive flexibility since we wanted
+	a range of views and backgrounds despite the persona. We clarified,
+	furthermore, that their observations could be directed either at the quality of
+	the data conveyed by the tool or at the tool's design itself. \par
 
@@
 
-	\subsection{Use in Smell Tracking}
-	\begin{wrapfigure}{O}{.25\textwidth} \centering \includegraphics{SUM}
-		\label{fig:sum} \caption{An abundance of parameters in SUM. Encountering this, P4
-			remarked, "Woah."} \end{wrapfigure}
+	\subsection{Use in Smell Tracking} \begin{wrapfigure}{O}{.25\textwidth}
+		\centering \includegraphics{SUM} \label{fig:sum} \caption{An abundance of
+			parameters in SUM. Encountering this, P4 remarked, "Woah."} \end{wrapfigure}
 
@@
 	formula was] just some that's weird." Other than these visual cues, value
-	errors, prefixed with \#s, also appear in the tree, 
-	which P4 said could be useful for tracking these problems if marked well.
+	errors, prefixed with \#s, also appear in the tree, which P4 said could be
+	useful for tracking these problems if marked well.
 
-	Additionally, because the files in the Enron set had name with the author
-	as a prefix, P2 commented that they could use the tool in a company
-	setting to follow up with repeat offenders. For instance, they first
-	encountered a particular author's name when investigating an AVERAGE function
-	with 18 distinct arguments for which our participant could not discern any
-	logical order, even after opening the source spreadsheet; the same name
-	popped up again as P2 looked at a RATE function relying on several hard-coded
-	values. P2 said that, if they were a manager or project leader, this recurrence
-	was a sign to talk to the author personally and figure out why
-	these problems were there, as to prevent more in the future. They also added
-	that these problems would grow worse if this particular author left the company
-	and no one remained who understood these formulae, a concern that aligns with
-	Hermans' transfer scenarios \cite{hermans2011supporting}.
+	Additionally, because the files in the Enron set had name with the author as a
+	prefix, P2 commented that they could use the tool in a company setting to
+	follow up with repeat offenders. For instance, they first encountered a
+	particular author's name when investigating an AVERAGE function with 18
+	distinct arguments for which our participant could not discern any logical
+	order, even after opening the source spreadsheet; the same name popped up again
+	as P2 looked at a RATE function relying on several hard-coded values. P2 said
+	that, if they were a manager or project leader, this recurrence was a sign to
+	talk to the author personally and figure out why these problems were there, as
+	to prevent more in the future. They also added that these problems would grow
+	worse if this particular author left the company and no one remained who
+	understood these formulae, a concern that aligns with Hermans' transfer
+	scenarios \cite{hermans2011supporting}.
 
@@
 
-	\subsection{Use in Education} Users found \toolname's inclusion of examples
-	to be especially useful since none of the them considered themselves to be
-	experts of Excel, their self-reported proficiencies ranging from "fairly
-	familiar" (P2) to "not extremely familiar" (P4). For example, as P1 explored
-	the VLOOKUP function, they said they could use the tool to collect more
-	examples than the documentation offers even though they knew the documentation more verbosely
-	explained its function signature. Furthermore, in the process of exploring trees,
-	P1 and P3 also gravitated towards some functions they had not used before, such as
-	PV and IPMT, looking for new features in Excel to explore and learn. \par
+	\subsection{Use in Education} Users found \toolname's inclusion of examples to
+	be especially useful since none of the them considered themselves to be experts
+	of Excel, their self-reported proficiencies ranging from "fairly familiar" (P2)
+	to "not extremely familiar" (P4). For example, as P1 explored the VLOOKUP
+	function, they said they could use the tool to collect more examples than the
+	documentation offers even though they knew the documentation more verbosely
+	explained its function signature. Furthermore, in the process of exploring
+	trees, P1 and P3 also gravitated towards some functions they had not used
+	before, such as PV and IPMT, looking for new features in Excel to explore and
+	learn. \par
 
-	Additionally, \toolname offers a simple way of finding examples where certain functions
-	were used together. Though a standard text-search tool might yield the same
-	results for a function alone, combinations can require more complex text
-	queries, whereas here, the information is already captured in nodes.  \par
+	Additionally, \toolname offers a simple way of finding examples where certain
+	functions were used together. Though a standard text-search tool might yield
+	the same results for a function alone, combinations can require more complex
+	text queries, whereas here, the information is already captured in nodes.  \par
 
-	However, we found that even though a user can explore all of a function's configurations, this
-	does not mean that they will learn exactly what it does. P1,
-	examining unfamiliar functions like
-	KURT and PV, could describe precisely what types of arguments it accepted and
-	how many. But even after exploring the spreadsheets for context, they could not
-	accurately describe what the functions produced without consulting the official
-	documentation. Whether through reticence of the tool or obscurity of the
-	functions themselves, the exploratory environment is not enough to teach users
-	\textit{when} to use a function. However, we could address this in future designs,
-	perhaps, by linking directly to such documentation from within the
-	tool without violating any design concerns in \ref{goals}. \par
+	However, we found that even though a user can explore all of a function's
+	configurations, this does not mean that they will learn exactly what it does.
+	P1, examining unfamiliar functions like KURT and PV, could describe precisely
+	what types of arguments it accepted and how many. But even after exploring the
+	spreadsheets for context, they could not accurately describe what the functions
+	produced without consulting the official documentation. Whether through
+	reticence of the tool or obscurity of the functions themselves, the exploratory
+	environment is not enough to teach users \textit{when} to use a function.
+	However, we could address this in future designs, perhaps, by linking directly
+	to such documentation from within the tool without violating any design
+	concerns in \ref{goals}. \par
 
 	\subsection{Study Limitations}
-
-	Still, several limitations cropped up during the study that complicate the
-	evaluation. For one thing, though the source of the data was not explicitly
-	stated at the outset of the session, several users studied the file names
-	(unchanged as they were) to deduce its roots in finance, if not Enron itself.
-	Because of these notorious connotations, then, some were inclined from this
-	moment of discovery to orient their exploration around finance-related
-	functions, potentially limiting their findings or perceived users for the tool
-	-- though some also said that, without this essential context, they could not
+	Though we did not start the study by telling that the data source came from Enron, 
+	two users studied the file names
+	to deduce its roots in finance, if not Enron itself.
+	Because of these notorious connotations, then, they might have been inclined from this
+	information to orient their exploration around finance-related
+	functions, potentially limiting their findings or perceived users for the tool. Though,
+	one also said that, without this essential context, they could not
 	have properly explored a dataset in the first place. Comments like these point
@@
 	them to a single purpose, it might, at the same time, not afford them any
-	mindset at all with which to interpret the data. Another potential problem is
-	that the data which users explored was processed and created before we had
+	mindset at all with which to interpret the data. \par
+
+	Furthermore, the data which users explored was processed and created before we had
 	fully completed the tool, meaning some of the counts and patterns in the trees
 	were inaccurate. However, we decided that this was not a pressing concern,
-	being that we were primarily with whether any interesting reports could be made
+	being that we were primarily concerned with whether any interesting reports could be made
 	at all, not with whether these reports were 100\% accurate assessments of
@@
 
-	Throughout the study, it became apparent that some of the concepts,
-	particularly optional arguments, were easily lost in the representation. To
-	illustrate this, consider the following two trees.	
-	The difference is, perhaps, too subtle: on the left, the tree contains
-	instances of AND functions with any number of arguments, up to four; on the
-	right, the tree contains only instances with exactly four arguments. In other
-	words, an instance of "=AND(A1, B2, C3, D4)" would be found in both trees,
-	while "=AND(A1, B2)" would be found in only the left. Though the users
-	naturally did not explicitly report misinterpreting the icons, it became clear
-	in their out-loud thoughts that they viewed each box as a fundamentally
-	different set of possibilities in formula construction rather than just a
-	specific parameter. Though we clarified the meanings when these
-	misunderstandings became apparent, these events point to a failure in the tool
-	to properly indicate every function with clarity.   \par
+	Throughout the study, we noticed that users misunderstood some of the icons
+	and, as such, their early discoveries were inaccurate. For example, P1 interpreted
+	the numbers on the argument boxes to mean that all of the box's children had exactly
+	that many arguments -- that is, clicking on the dark blue ``1" would return all the single-argument functions
+	instead of the first argument of a function -- and P2 initially took the solid lines to mean
+	different paths in formula construction rather than different arguments of the same function. 
+	Though the users naturally did not explicitly report misinterpreting
+	the icons, these misunderstandings became clear in their early evaluations of the
+	spreadsheet practice. Though we clarified the meanings when
+	these misunderstandings became apparent, these events point to a failure in the
+	tool to properly indicate every function with clarity.   \par
 
-	\section{Limitations} Beyond the negative responses in the user study, a few
-	more inherent limitations beset the tool. These largely resulted from
-	trade-offs in which we found no acceptable way to win the best of both worlds,
-	and necessary compromises were made. \par
+	\section{Discussion} 	
+	We began these studies with the intention of evaluating our progress towards the
+	goals in section \ref{goals}. Working from these results, we noted many places
+	where the tool aligned well or fell short.
 
-	Because the data collection depends on POI's formula parser, it affords no
-	leeway or partial information from a formula; it either processes it perfectly
-	or throws it out. As such, the visualization inhibits insight into anything
-	with syntactical errors or third-party functions that can't be evaluated
-	without additional tools. Note, however, that this does not include standard
-	Excel errors like \#REF! and \#DIV/0, which the parser handles well. This poses
-	more egregious problems, however, when POI does not support the parsing of
-	certain functions, such as EOMONTH (as obscure as it may be), preventing the
+	\subsection{Unbiased Exploration}	
+	The first goal -- that of full exploration -- is threatened by the presence of certain
+	formulae that the tool does not display, such as those with nonstandard functions. 
+	Because the data collection depends on POI's formula parser, it does not
+	allow for any partial parsing of a formula; it either processes a formula perfectly
+	or throws it out. As such, the visualization does not display anything
+	with syntactical errors or third-party functions that POI cannot parse. This poses
+	larger problems, however, when POI does not support the parsing of
+	certain functions, such as EOMONTH, preventing the
 	healthy growth of those trees. \par
 
-	Many functions have an expected order of arguments, but some, like SUM and
-	MATCH, can be reordered in various ways and maintain their value. However, the
-	representation that this tool uses reinforces for all functions that the order
-	is important, even in these exceptions. Future work could design a new family
-	of tree to accommodate these loose cases, however, by bucketing
-	order-insignificant arguments together; this, of course, would still have to
-	address the profusion of co-presented data. \par
+	Participants also asked for more options to quickly navigate the tree. For example,
+	P2 asked for the ability to expand the entire tree at once and icons that better
+	communicated the presence of optional arguments and their quantities. The more 
+	familiar participants grew with the tool, the faster they wanted to explore, yet
+	it supported expert navigation up to the point of expanding all of a node's children
+	up to one level. \par
 
-	A larger and related problem is the loss of argument combination. For example,
-	figure \ref{fig:index} shows the situation of the INDEX tree, wherein each
-	argument position has a few distinct possibilities. While it is easy to break
-	down, for each position, which argument types are most common (ranges, MATCH,
-	and numbers, respectively), the tree is silent on whether MATCH functions are
-	used together in the second and third arguments, among other concerns. Though
-	these argument combinations could be pieced together by manually inspecting the
-	lists of examples, it is nevertheless inconvenient, though not outside the
-	realm of future improvement.
+	Other than that, we did avoid designing anything that intentionally evaluated
+	formula designs. Nevertheless, \toolname inadvertently emphasizes bad design of
+	certain types, such as all of those in section \ref{badsmells} marked by their
+	visual signatures. Even so, our participants found the discovery of bad smell
+	to be the most interesting aspect about it, to the point where they could
+	imagine business scenarios in which micromanagers use it to ensure
+	precise design parameters across a department's spreadsheets! To design in that
+	direction, however, would mean a reevaluation of this design goal, since
+	intentionally guiding users toward known smells may guide them away from
+	new, unmarked ones.
 
-	\begin{wrapfigure}{O}{.25\textwidth} 
-		\centering 
-		\includegraphics[width=.25\textwidth]{longIF} 
-		\label{fig:longif}
-		\caption{The many possibilities of IF, argument 3, demonstrate the problem of
-			having too many options.} 
-	\end{wrapfigure}
+	\subsection{Uncluttered Quantification}
 
-	A threat to the exploratory philosophy may also mount from the problem of too
-	much data, particularly in the popular functions, like SUM and IF. We had added
-	some precautions before the study: for any position in the tree, for example,
-	only the ten most common functions were displayed without clicking on the
-	expansion arrow \includegraphics[scale=.35]{arrow}. Nevertheless, P3 remarked
-	that they specifically avoided the most popular functions, anticipating a flood
-	of nodes from which they could salvage nothing interesting -- which might not
-	have been a bad prediction, considering that the SUM is built from 910 nodes
-	and IF, at least 18000 [double-check these with refined data]. P2 corroborated
-	this by explaining how they gravitated toward specific examples over the plane
-	of nodes but complicates it further by also deeming the tool at its best when
-	it shows either every possibility of an side-by-side (for comparison) or
-	nothing on that branch at all, a balance that is hard to strike with node-dense
-	trees. \par
+	We realized early that some of the popular functions would present a problem: 
+	some would have thousands of variations in large datasets, and showing all of
+	these variations at once would hopelessly overwhelm the user. We therefore
+	made a number of choices, such as the expansion arrows and the use of generic
+	types in place of specific primitive values, that would reduce the variation
+	to something more manageable.
 
-	\begin{figure} \centering \includegraphics[width=.5\textwidth]{index}
-		\label{fig:index} \caption{A difficult question: how often is MATCH used in
-			both the second and third arguments?} \end{figure}
+	Nevertheless, during the user study, P3 remarked that they specifically avoided
+	the most popular functions, anticipating a flood of nodes from which they could
+	salvage nothing interesting -- which might not have been a bad prediction,
+	considering that the SUM is built from 910 function and argument nodes stemming
+	the root and IF, at least 18000. P2 corroborated this by explaining how they
+	gravitated toward exploring specific examples in particular value nodes over
+	navigating the full crowd of the tree, but they complicate it further by also
+	saying that the tool at its best when it shows either every possibility of an
+	argument side-by-side (for comparison) or nothing on that branch at all, a
+	balance that is hard to strike with node-dense trees.
 
-	%To be sure, though, there is still plenty of work to improve this tool. One
-	% activity
-	%it does not support well now is that of comparison: for all of it's ability to
-	% spit
-	%out numbers and quantify patterns,
+	A threat to our goals, then, arises from the problem of too much data,
+	particularly in the popular functions, like SUM and IF. Despite our
+	precautions, balancing the desire to show every single possibility of design
+	with the desire not to overwhelm remains a challenge. \par
+
+	\subsection{Informative Qualification}
 
@@
 	well. \par
+
+	A larger and related problem is the loss of argument combination. For example,
+	figure \ref{fig:index} shows the situation of the INDEX tree, wherein each
+	argument position has a few distinct possibilities. While it is easy to break
+	down, for each position, which argument types are most common (ranges, MATCH,
+	and numbers, respectively), the tree is silent on whether MATCH functions are
+	used together in the second and third arguments, among other concerns. Though
+	these argument combinations could be pieced together by manually inspecting the
+	lists of examples, it is nevertheless inconvenient, though not outside the
+	realm of future improvement. \par
+
+	\begin{wrapfigure}{O}{.25\textwidth} \centering
+		\includegraphics[width=.25\textwidth]{longIF} \label{fig:longif} \caption{The
+			many possibilities of IF, argument 3, demonstrate the problem of having too
+			many options.} \end{wrapfigure}
+
+	Further contextual information.
+
+	\begin{figure} \centering \includegraphics[width=.5\textwidth]{index}
+		\label{fig:index} \caption{A difficult question: how often is MATCH used in
+			both the second and third arguments?} \end{figure}
+
+	Redesign.
 

### 2016-04-24 doc/paper.tex
Case study stuff!!!!!!!!

@@
 
-	\subsection{Walkthrough of the Tool} Before discussing the minutiae of tool's
+	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing the minutiae of tool's
 	development, though, we will give a basic example of how to use the tool. For
@@
 
-	\subsection{Education} Learning by example has long been a cornerstone of
-	effective teacher techniques: by showing the student a concrete example of
-	something, rather than dwelling in the realm of abstract description,
-	comprehension increases [I'm sure there's a cite out there somewhere.] This is
-	no different in software, where every explanation of a tricky programming
-	concept is much untangled by the illustrative stub. Even APIs, researchers have
-	found, by the inclusion of an in-practice example of the function described.
-	Spreadsheet programming, then, should not be essentially different: examples of
-	spreadsheet functions in use
+	\subsection{Education} When Robillard and Deline researched common obstacles
+	for programmers learning new APIs, they concluded that one of the most important
+	elements of a good API was the use of code examples to demonstrate function use.
+	These examples, furthermore, come in a variety of forms: small snippets
+	or tutorials that show only the intended function, sample applications that
+	incorporate the function in a broader context, or even production code that
+	employs the function but was not initially intended to be an illustrative 
+	example \cite{robillard2011field}. Of these categories, \toolname aligns
+	entirely with the last; when a user chooses to explore a particular function
+	node, they will see examples of that formula as it was used in a working 
+	environment, with the specifics depending on the dataset the tool is using. \par
+
+	Furthermore, Robillard and Deline's study makes the case for examples that show
+	"API usage patterns involving more than one method call" \cite{robillard2011field}.
+	Examples that show only a single function, they find, are too simple, whereas those
+	demonstrating the interaction of functions will equip users for more complex tasks. 
+	\toolname is especially suited for this focus on combination; consider again
+	the question in the walkthrough (Section \ref{sec:walkthrough}), asking
+	which functions and operations are used as conditions in IF. The design of this
+	tool emphasizes the connection, then, between what functions like ISNA and AND
+	return and what IF accepts, and specific examples for any of these combinations
+	are only a click away.
 

### 2016-04-25 doc/paper.tex
Changes to entire paper. Too many issues fixed to list here.

@@
 \usepackage{textcomp} \newcommand{\toolname}{Perquimans?!} \begin{document}
-	\title{A Tool for Visualizing Patterns of Spreadsheet Function Combinations}
+	\title{\toolname: A Tool for Visualizing Patterns of Spreadsheet Function Combinations}
 
@@
 		of functions and operations to manipulate data, but it can be difficult to
-		understand how programmers actually use these in practice. Furthermore, users
-		can combine several functions into a complex formula, complicating matters for
-		both researchers and practitioners who want to study formulae to improve
-		spreadsheet practices. Therefore, we developed a tool that visualizes patterns
-		of function combination in spreadsheets as an interactive tree of
-		possibilities. Using spreadsheets from the public spreadsheet corpora, we then
-		apply to the tool to real datasets and demonstrate its ability to capture the
-		most common and most anomalous patterns of function combination and their
-		contexts in actual workbooks. \end{abstract}
+		understand how programmers actually use these functions in practice.
+		Furthermore, users can combine several functions into a complex formula,
+		complicating matters for both researchers and practitioners who want to study
+		formulae to improve spreadsheet practices. Therefore, we developed \toolname, a
+		tool that visualizes patterns of function combination in spreadsheets as an
+		interactive tree of possibilities, capable of capturing both the most common
+		and most anomalous patterns of function combination and their contexts in
+		actual workbooks. Using spreadsheets from the Enron corpus, we conduct both a
+		case study and several user studies to explore \toolname's various
+		applications, particularly those in flexible smell detection and spreadsheet
+		education. \end{abstract}
 
@@
 	helped and hindered this process. We then apply the tool to a number of case
-	studies to evaluate how much it could contribute to several different contexts:
-
-	\begin{itemize} \item Detection of code smells \item
-		Spreadsheet education \end{itemize}
+	studies to evaluate how much it could contribute to several different contexts,
+	most notably code smell detection and spreadsheet education.
 
@@
 
-	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing the minutiae of tool's
-	development, though, we will give a basic example of how to use the tool. For
-	this, we will answer this question: \textit{ What kinds of functions do people
-		use to define the condition in an IF function?} Thefull  visualization that
-	answers this is available in figure \ref{fig:fullpic}; however, to understand
-	the interaction, we will start from the beginning. \par
+	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing
+	the minutiae of tool's development, though, we will give a basic example of how
+	to use the tool. For this, we will answer this question: \textit{ What kinds of
+		functions do people use to define the condition in an IF function?} Thefull
+	visualization that answers this is available in figure \ref{fig:fullpic};
+	however, to understand the interaction, we will start from the beginning. \par
 
@@
 	gained from any particular visualization. As such, we raised a few tasks in the
-	introduction in which we thought the tool could help: identifying places for
-	API improvement, detecting bad smells, and guiding spreadsheet education. To
+	introduction in which we thought the tool could help: detecting bad smells and guiding spreadsheet education. To
 	demonstrate the tool's applicability, we sought out places in the tree which
@@
 
+	\subsection{Education} When Robillard and Deline researched common obstacles
+	for programmers learning new APIs, they concluded that one of the most
+	important elements of a good API was the use of code examples to demonstrate
+	function use. These examples, furthermore, come in a variety of forms: small
+	snippets or tutorials that show only the intended function, sample applications
+	that incorporate the function in a broader context, or even production code
+	that employs the function but was not initially intended to be an illustrative
+	example \cite{robillard2011field}. Of these categories, \toolname aligns
+	entirely with the last; when a user chooses to explore a particular function
+	node, they will see examples of that formula as it was used in a working
+	environment, with the specifics depending on the dataset the tool is using.
+	\par
+
+	Furthermore, Robillard and Deline's study makes the case for examples that show
+	"API usage patterns involving more than one method call"
+	\cite{robillard2011field}. Examples that show only a single function, they
+	find, are too simple, whereas those demonstrating the interaction of functions
+	will equip users for more complex tasks. \toolname is especially suited for
+	this focus on combination; consider again the question in the walkthrough
+	(Section \ref{sec:walkthrough}), asking which functions and operations are used
+	as conditions in IF. The design of this tool emphasizes the connection, then,
+	between what functions like ISNA and AND return and what IF accepts, and
+	specific examples for any of these combinations are only a click away.
+
 	%Lookup example
-	Otherwise, the LOOKUP functions are particularly notorious for their confusing
-	mechanisms and, as such, have warranted some especial attention with regards to
-	spreadsheet design. In a recent study, Hermans, Aivaloglou, and Jansen probed
-	the Enron dataset for uses of VLOOKUP and HLOOKUP specifically. The issue at
-	hand was the optional fourth argument: when omitted or set to TRUE, the
-	function attempts to return a value from another column by matching two values
-	approximately, but when set to FALSE, the match must be exact. Furthermore,
-	exact matching works only with sorted columns or rows; if the programmer
-	neglects to sort values before calling the *LOOKUP function, they may acquire
-	inaccurate results \cite{hermans2015detecting}. \par
+	For a deeper example, the LOOKUP functions are particularly notorious for their
+	confusing mechanisms and, as such, have warranted some extra attention with
+	regards to spreadsheet design. In short, these functions are for "when you need
+	to look in a single row or column and find a value from the same position in a
+	second row or
+	column"\footnote{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}. Examples of each can be found in Figure \ref{fig:lookupexample}.
 
-	Given access to the same dataset, how might this tool approach the issue? On
-	the surface, the tool supports easy quantification through the tooltips
-	displayed for each node, as shown in figure \ref{fig:vhlookups}, answering the
-	question, "How often do spreadsheet programmers use this function?". But, more
-	to the point, the tool's distinction between the numbers of arguments for a
-	single function lets the user compare frequencies of three-argument forms with
-	the four-argument. The visualization does not, however, discern between the
-	different values for booleans in the tree, much less whether the spreadsheet
-	columns are ordered -- but the linking of examples to patterns allows quick
-	insight into which files are at risk for the problems they outlined. \par
+	\begin{figure} \centering \includegraphics[width=.5\textwidth]{lookupexample}
+		\label{fig:lookupexample} \caption{Demonstrations of LOOKUP and VLOOKUP}
+	\end{figure}
 
-	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
-		\includegraphics[width=.225\textwidth]{vlookupbox}
-		\includegraphics[width=.225\textwidth]{hlookupbox}
-		\includegraphics[width=.5\textwidth]{hlookup} \label{fig:vhlookups}
-		\caption{VLOOKUP and HLOOKUP with four arguments. Numbers not expected to
-			correspond perfectly with \cite{hermans2015detecting}.} \end{figure}
+	LOOKUP has two forms: vector and array. In either case, the first argument is
+	the value which you are trying to match in another column. If the formula is in
+	the vector form, that column is the second argument, so in Figure
+	\ref{fig:lookupexample}, the formula in cell D2 (\textit{=LOOKUP(3, A2:A6,
+		B2:B6)}) will search for the value of 3 between cells A2 and A6. The value the
+	formula returns then comes from the corresponding cell in the optional third
+	argument's column; since the lookup values matches the value in cell A4, it
+	returns the value from cell B4. The array form of the LOOKUP works the same
+	way, except that the second argument is a two-dimensional table where it
+	matches values in the table's first column and returns values from the
+	last\footnote{ Depending on the dimensions of the lookup table, the function
+		may substitute rows for columns.}.
 
-	Also at hand are issues with the standard LOOKUP function. Unlike the two
-	variations above, LOOKUP accepts either two or three arguments, depending on
-	which API-defined form the programmer uses: the vector form or the array form,
-	the primary difference being whether the second parameter is a one-column/-row
-	range or a two-dimensional array. The array form, as it happens, is strongly
-	discouraged by the API in favor of the V/HLOOKUP, a notion that might also be
-	leveraged in the pursuit in good spreadsheet design.
+	VLOOKUP works closely with this array form, except the user defines in its
+	third argument which column from which to return values. In \textit{=VLOOKUP(3,
+		A2:B6, 2)}, the argument ``2" tells to return the value from the second column,
+	which is \textit{B2:B6} here. Furthermore, it also accepts a boolean value for
+	an optional argument: when set to FALSE, it returns only exact matches, and
+	when TRUE or left out, it approximates the match to the closest value beneath
+	it. We demonstrate this in Figure \ref{fig:lookupexample} in the bottom two
+	VLOOKUP functions, one returning ``Friday" and the other an error. HLOOKUP
+	works identically but focuses on rows instead of columns.
+
+	All of these variations may seem daunting to a beginner, but \toolname can
+	help. Because of its design, users can distinguish between forms of the same
+	function, as seen in Figure \ref{fig:lookups} where the one can explore both
+	the frequency with which the spreadsheet programmers used these different forms
+	-- three-argument vector form much more than the array form -- and then
+	retrieve examples of every configuration in the dataset. The same goes for the
+	V/HLOOKUP functions, as shown partially in Figure \ref{fig:vhlookups}
 
@@
 		\includegraphics[width=.5\textwidth]{lookup-3} \label{fig:lookups}
-		\caption{LOOKUP with two (6 occurrences) and three (1648) arguments.}
-	\end{figure}
+		\caption{LOOKUP with two and three arguments.} \end{figure}
 
-	\subsection{Education} When Robillard and Deline researched common obstacles
-	for programmers learning new APIs, they concluded that one of the most important
-	elements of a good API was the use of code examples to demonstrate function use.
-	These examples, furthermore, come in a variety of forms: small snippets
-	or tutorials that show only the intended function, sample applications that
-	incorporate the function in a broader context, or even production code that
-	employs the function but was not initially intended to be an illustrative 
-	example \cite{robillard2011field}. Of these categories, \toolname aligns
-	entirely with the last; when a user chooses to explore a particular function
-	node, they will see examples of that formula as it was used in a working 
-	environment, with the specifics depending on the dataset the tool is using. \par
+	Furthermore, these examples are good as well for exploring how it might bridge
+	issues of bad design with education. In a recent study, Hermans, Aivaloglou,
+	and Jansen probed the Enron dataset for uses of VLOOKUP and HLOOKUP
+	specifically. The issue at hand was the optional fourth argument, which
+	requires that rows are sorted lest it return inaccurate results
+	\cite{hermans2015detecting}. For someone seeking to increase awareness of this
+	problem, it first allows them to answer the question of significance -- "How
+	often do spreadsheet programmers use this function, with these particular
+	parameters?" Though \toolname does not discernd whether neighboring columns are
+	sorted, it can nevertheless guide the educator to several examples in
+	production where this problem surfaces. \par
 
-	Furthermore, Robillard and Deline's study makes the case for examples that show
-	"API usage patterns involving more than one method call" \cite{robillard2011field}.
-	Examples that show only a single function, they find, are too simple, whereas those
-	demonstrating the interaction of functions will equip users for more complex tasks. 
-	\toolname is especially suited for this focus on combination; consider again
-	the question in the walkthrough (Section \ref{sec:walkthrough}), asking
-	which functions and operations are used as conditions in IF. The design of this
-	tool emphasizes the connection, then, between what functions like ISNA and AND
-	return and what IF accepts, and specific examples for any of these combinations
-	are only a click away.
+	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
+		\includegraphics[width=.5\textwidth]{hlookup} \label{fig:vhlookups}
+		\caption{VLOOKUP and HLOOKUP with four arguments.} \end{figure}
 
-	\section{User Study} During development, we conducted a brief, four-participant
-	user study in order to detect conflicts between our design and the goals in
-	section \ref{goals}. We designed the study to be exploratory; given trees based
-	in the Enron dataset and at least twenty minutes, we asked the participants to
-	adopt the persona of a consultant evaluating a company's spreadsheet practice,
-	allowing for questions like which functions on which the employees most
-	depended or which sheets or employees presented the most anomalous or dangerous
-	designs. Though we instructed them on how to use the tool and suggested that
-	they visit one of the most populous trees in the set, we put aside any specific
-	tasks or questions and let them choose their own paths. Though interpretation
-	of the phrase ``spreadsheet practice" can certainly vary from participant to
-	participant, we readily accepted this interpretive flexibility since we wanted
-	a range of views and backgrounds despite the persona. We clarified,
-	furthermore, that their observations could be directed either at the quality of
-	the data conveyed by the tool or at the tool's design itself. \par
+	\section{User Study} \label{sec:userstudy} During development, we conducted a
+	brief, four-participant user study in order to detect conflicts between our
+	design and the goals in section \ref{goals}. We designed the study to be
+	exploratory; given trees based in the Enron dataset and at least twenty
+	minutes, we asked the participants to adopt the persona of a consultant
+	evaluating a company's spreadsheet practice, allowing for questions like which
+	functions on which the employees most depended or which sheets or employees
+	presented the most anomalous or dangerous designs. Though we instructed them on
+	how to use the tool and suggested that they visit one of the most populous
+	trees in the set, we put aside any specific tasks or questions and let them
+	choose their own paths. Though interpretation of the phrase ``spreadsheet
+	practice" can certainly vary from participant to participant, we readily
+	accepted this interpretive flexibility since we wanted a range of views and
+	backgrounds despite the persona. We clarified, furthermore, that their
+	observations could be directed either at the quality of the data conveyed by
+	the tool or at the tool's design itself. \par
 
@@
 
-	\subsection{Study Limitations}
-	Though we did not start the study by telling that the data source came from Enron, 
-	two users studied the file names
-	to deduce its roots in finance, if not Enron itself.
-	Because of these notorious connotations, then, they might have been inclined from this
-	information to orient their exploration around finance-related
-	functions, potentially limiting their findings or perceived users for the tool. Though,
-	one also said that, without this essential context, they could not
-	have properly explored a dataset in the first place. Comments like these point
-	out the trade-offs of unguided exploration, too: though it might not restrict
-	them to a single purpose, it might, at the same time, not afford them any
-	mindset at all with which to interpret the data. \par
+	\subsection{Study Limitations} Though we did not start the study by telling
+	that the data source came from Enron, two users studied the file names to
+	deduce its roots in finance, if not Enron itself. Because of these notorious
+	connotations, then, they might have been inclined from this information to
+	orient their exploration around finance-related functions, potentially limiting
+	their findings or perceived users for the tool. Though, one also said that,
+	without this essential context, they could not have properly explored a dataset
+	in the first place. Comments like these point out the trade-offs of unguided
+	exploration, too: though it might not restrict them to a single purpose, it
+	might, at the same time, not afford them any mindset at all with which to
+	interpret the data. \par
 
-	Furthermore, the data which users explored was processed and created before we had
-	fully completed the tool, meaning some of the counts and patterns in the trees
-	were inaccurate. However, we decided that this was not a pressing concern,
-	being that we were primarily concerned with whether any interesting reports could be made
-	at all, not with whether these reports were 100\% accurate assessments of
-	reality. \par
+	Furthermore, the data which users explored was processed and created before we
+	had fully completed the tool, meaning some of the counts and patterns in the
+	trees were inaccurate. However, we decided that this was not a pressing
+	concern, being that we were primarily concerned with whether any interesting
+	reports could be made at all, not with whether these reports were 100\%
+	accurate assessments of reality. \par
 
 	Throughout the study, we noticed that users misunderstood some of the icons
-	and, as such, their early discoveries were inaccurate. For example, P1 interpreted
-	the numbers on the argument boxes to mean that all of the box's children had exactly
-	that many arguments -- that is, clicking on the dark blue ``1" would return all the single-argument functions
-	instead of the first argument of a function -- and P2 initially took the solid lines to mean
-	different paths in formula construction rather than different arguments of the same function. 
-	Though the users naturally did not explicitly report misinterpreting
-	the icons, these misunderstandings became clear in their early evaluations of the
-	spreadsheet practice. Though we clarified the meanings when
+	and, as such, their early discoveries were inaccurate. For example, P1
+	interpreted the numbers on the argument boxes to mean that all of the box's
+	children had exactly that many arguments -- that is, clicking on the dark blue
+	``1" would return all the single-argument functions instead of the first
+	argument of a function -- and P2 initially took the solid lines to mean
+	different paths in formula construction rather than different arguments of the
+	same function. Though the users naturally did not explicitly report
+	misinterpreting the icons, these misunderstandings became clear in their early
+	evaluations of the spreadsheet practice. Though we clarified the meanings when
 	these misunderstandings became apparent, these events point to a failure in the
@@
 
-	\section{Discussion} 	
-	We began these studies with the intention of evaluating our progress towards the
-	goals in section \ref{goals}. Working from these results, we noted many places
-	where the tool aligned well or fell short.
+	\section{Discussion} We began these studies with the intention of evaluating
+	our progress towards the goals in section \ref{goals}. Working from these
+	results, we noted many places where the tool aligned well or fell short.
 
-	\subsection{Unbiased Exploration}	
-	The first goal -- that of full exploration -- is threatened by the presence of certain
-	formulae that the tool does not display, such as those with nonstandard functions. 
-	Because the data collection depends on POI's formula parser, it does not
-	allow for any partial parsing of a formula; it either processes a formula perfectly
-	or throws it out. As such, the visualization does not display anything
-	with syntactical errors or third-party functions that POI cannot parse. This poses
-	larger problems, however, when POI does not support the parsing of
-	certain functions, such as EOMONTH, preventing the
-	healthy growth of those trees. \par
+	\subsection{Unbiased Exploration} The first goal -- that of full exploration --
+	is threatened by the presence of certain formulae that the tool does not
+	display, such as those with nonstandard functions. Because the data collection
+	depends on POI's formula parser, it does not allow for any partial parsing of a
+	formula; it either processes a formula perfectly or throws it out. As such, the
+	visualization does not display anything with syntactical errors or third-party
+	functions that POI cannot parse. This poses larger problems, however, when POI
+	does not support the parsing of certain functions, such as EOMONTH, preventing
+	the healthy growth of those trees. \par
 
-	Participants also asked for more options to quickly navigate the tree. For example,
-	P2 asked for the ability to expand the entire tree at once and icons that better
-	communicated the presence of optional arguments and their quantities. The more 
-	familiar participants grew with the tool, the faster they wanted to explore, yet
-	it supported expert navigation up to the point of expanding all of a node's children
-	up to one level. \par
+	Participants also asked for more options to quickly navigate the tree. For
+	example, P2 asked for the ability to expand the entire tree at once and icons
+	that better communicated the presence of optional arguments and their
+	quantities. The more familiar participants grew with the tool, the faster they
+	wanted to explore, yet it supported expert navigation up to the point of
+	expanding all of a node's children up to one level. \par
 
@@
 	to be the most interesting aspect about it, to the point where they could
-	imagine business scenarios in which micromanagers use it to ensure
-	precise design parameters across a department's spreadsheets! To design in that
+	imagine business scenarios in which micromanagers use it to ensure precise
+	design parameters across a department's spreadsheets! To design in that
 	direction, however, would mean a reevaluation of this design goal, since
-	intentionally guiding users toward known smells may guide them away from
-	new, unmarked ones.
+	intentionally guiding users toward known smells may guide them away from new,
+	unmarked ones.
 
@@
 	some would have thousands of variations in large datasets, and showing all of
-	these variations at once would hopelessly overwhelm the user. We therefore
-	made a number of choices, such as the expansion arrows and the use of generic
-	types in place of specific primitive values, that would reduce the variation
-	to something more manageable.
+	these variations at once would hopelessly overwhelm the user. We therefore made
+	a number of choices, such as the expansion arrows and the use of generic types
+	in place of specific primitive values, that would reduce the variation to
+	something more manageable.
 
@@
 
-	\subsection{Informative Qualification}
+	\subsection{Informative Qualification} As we found in the case study, the tool
+	excels at making formula examples available throughout a tree. Though the tool
+	cannot outright explain what a formula does function-by-function, users
+	nevertheless found it valuable for the way it offers them with numerous
+	practical examples of functions previously unknown or confusing to them,
+	especially within the LOOKUP family. In the user study (Section
+	\ref{sec:userstudy}), furthermore, we also observed how a participant used the
+	repeated instance of a spreadsheet author's name to identify a potential
+	problem with a particular designer rather than a design itself, demonstrating
+	its use on several levels. \par
+
+	However, the benefits described in the previous sections imply a hidden
+	complication: if the tool educates through example but does not explicitly
+	distinguish between good design and bad design, how can we be sure that people
+	won’t inadvertently learn bad design from it? In the user study, we discussed
+	its use in education and smell detection by bringing up the issues surrounding
+	the LOOKUP functions; this discussion, though, presupposes a distinguishing eye
+	that knew which examples practiced good design and which exhibited the common
+	errors. But a beginner might not know the difference. Robillard and Deline, in
+	their study, remarked that good API examples should demonstrate best practices,
+	but, right now, we have no way to assure this with \toolname. As with the
+	problems in achieving unbiased exploration, correcting for this danger may
+	entail a reevaluation of design goals.
 
 	\section{Future Work} For these user and case studies, we relied solely on
-	Enron's spreadsheets to find our results. However, Enron's focus on finances
-	and energy represents only one context in which people use spreadsheets. Other
-	corpora, like EUSES and Fuse, draw from other domains and industries, and, as
-	Jansen found in his comparison of spreadsheets Enron and EUSES, different
+	Enron's spreadsheets. However, Enron's focus on finances and energy represents
+	only one context in which people use spreadsheets. Other corpora, like EUSES
+	and Fuse, draw from other domains and industries, and, as Jansen found in his
+	comparison of spreadsheets Enron and EUSES \cite{jansen2015enron}, different
 	companies rely on different functions. Though the use of a single corpora
@@
 	spreadsheets, such as Gnumeric\footnote{http://www.gnumeric.org/} or Google
-	Sheets \footnote{https://www.google.com/sheets/about/} represent other
+	Sheets\footnote{https://www.google.com/sheets/about/} represent other
 	approaches to spreadsheet systems. Even within identical domains, there's no
@@
 
-	A larger and related problem is the loss of argument combination. For example,
-	figure \ref{fig:index} shows the situation of the INDEX tree, wherein each
-	argument position has a few distinct possibilities. While it is easy to break
-	down, for each position, which argument types are most common (ranges, MATCH,
-	and numbers, respectively), the tree is silent on whether MATCH functions are
-	used together in the second and third arguments, among other concerns. Though
-	these argument combinations could be pieced together by manually inspecting the
-	lists of examples, it is nevertheless inconvenient, though not outside the
-	realm of future improvement. \par
-
-	\begin{wrapfigure}{O}{.25\textwidth} \centering
-		\includegraphics[width=.25\textwidth]{longIF} \label{fig:longif} \caption{The
-			many possibilities of IF, argument 3, demonstrate the problem of having too
-			many options.} \end{wrapfigure}
-
-	Further contextual information.
-
 	\begin{figure} \centering \includegraphics[width=.5\textwidth]{index}
@@
 
-	Redesign.
+	Though our focus was specifically on function combination, there are several
+	other elements of a formula's context that we do no currently consider. For
+	example, \toolname does not current capture argument combination; in
+	\ref{fig:index}, it is impossible to state how often the function MATCH
+	occurred in both the second and third arguments or whether they were more often
+	paired with references. Furthermore, it is easy to open a tree and see what is
+	used inside of a specific function, but finding information on what a function
+	is used inside of takes considerably more work -- we see again in
+	\ref{fig:index} that MATCH is used inside INDEX, but we cannot know which
+	functions have INDEX inside them without searching every other tree. More
+	distant concerns might be exploring which functions often occur in adjacent
+	cells in the sheet -- whenever INDEX occurs, which functions are seen most
+	often in the cells around it?
+
+	%\begin{wrapfigure}{O}{.25\textwidth} \centering
+	%	\includegraphics[width=.25\textwidth]{longIF} \label{fig:longif} \caption{The
+	%		many possibilities of IF, argument 3, demonstrate the problem of having too
+	%		many options.} \end{wrapfigure}
 
@@
 
-	To be sure, we still have a lot of room for improvement. Though the exploratory
-	philosophy fostered certain goals well, such as the ability to discover new
-	problematic smells without knowing beforehand what they are, it also hindered
-	the project in others. Some users, for example, found the trees of popular
-	functions to be too crowded to explore well, or that their intention to use the
-	tool to examine the good or the bad design exclusively was not fully supported
-	by a tool that claimed to know neither. Many of the problems, however, were not
+	The design of the tool still has much room for improvement. Though the
+	exploratory philosophy fostered certain goals well, such as the ability to
+	discover new problematic smells without knowing beforehand what they are, it
+	hindered others. Some users, for example, found the trees of popular functions
+	to be too crowded to explore well, or that their intention to use the tool to
+	examine the good or the bad design exclusively was not fully supported by a
+	tool that claimed to know neither. Many of the problems, however, were not
 	essential to this design conflict and will be overcome in future iterations of
@@
 	offered in spreadsheet corpora and rendering them comprehensible through
-	images, we seek to draw attention to valuable information that would otherwise
+	visualization, we seek to draw attention to valuable information that would otherwise
 	go unnoticed.

### 2016-04-26 doc/paper.tex
Last night revisions. Fixes #127, fixes #107, fixes #108, fixes #109, fixes #110.

@@
 %
-%\usepackage{cite}
+\usepackage{cite}
 % cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
 % The latest version can be obtained at:
@@
 \ifCLASSINFOpdf \usepackage[pdftex]{graphicx} \usepackage{wrapfig} % declare the
-% path(s) where your graphic files are
 \graphicspath{{pic/}} % and their extensions so you won't have to specify these
-% with
-% every instance of \includegraphics
 \DeclareGraphicsExtensions{.png} \else % or other class option (dvipsone,
@@
 % correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
+% \hyphenation{op-tical net-works semi-conduc-tor}
 
-\usepackage{textcomp} \newcommand{\toolname}{Perquimans?!} \begin{document}
-	\title{\toolname: A Tool for Visualizing Patterns of Spreadsheet Function Combinations}
+\usepackage{textcomp}
+
+\newcommand{\toolname}{Perquimans }
+\newcommand{\toolnameend}{Perquimans}
+\newcommand{\toolnameposs}{Perquimans' }
+
+\begin{document}
+	\title{\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations}
 
@@
 	\author{ \IEEEauthorblockN{Justin A. Middleton, Emerson Murphy-Hill}
-		\IEEEauthorblockA{North Carolina State University\\ Raleigh, North Carolina,
-			USA} }
+		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ 
+			\{jamiddl2, ermurph3\}@ncsu.edu }}
 
@@
 	% in the abstract
-	\begin{abstract} Spreadsheet environments often come equipped with an abundance
-		of functions and operations to manipulate data, but it can be difficult to
-		understand how programmers actually use these functions in practice.
-		Furthermore, users can combine several functions into a complex formula,
-		complicating matters for both researchers and practitioners who want to study
-		formulae to improve spreadsheet practices. Therefore, we developed \toolname, a
-		tool that visualizes patterns of function combination in spreadsheets as an
-		interactive tree of possibilities, capable of capturing both the most common
-		and most anomalous patterns of function combination and their contexts in
-		actual workbooks. Using spreadsheets from the Enron corpus, we conduct both a
-		case study and several user studies to explore \toolname's various
-		applications, particularly those in flexible smell detection and spreadsheet
-		education. \end{abstract}
+	\begin{abstract} 
+		Spreadsheet environments often come equipped with an abundance of functions
+		and operations to manipulate data, which users can combine into a complex
+		formulae for more sophisticated programs. However, anticipating these
+		combinations is difficult, complicating matters for both researchers and
+		practitioners who want to study formulae to improve spreadsheet practices.
+		Therefore, we developed \toolnameend, a tool that analyzes spreadsheet corpora to
+		visualize patterns of function
+		combination as an interactive tree, capable
+		of representing both the most common and most anomalous patterns of formula construction and their contexts in actual workbooks. Using spreadsheets from
+		the Enron corpus, we conduct both a case study and a user study to
+		explore \toolnameposs various applications, particularly those in flexible smell
+		detection and spreadsheet education.
+
+	\end{abstract}
 

### 2016-04-26 doc/paper.tex
Intro paragraph 1. Fixes #111, fixes #112, fixes #113

@@
 		practitioners who want to study formulae to improve spreadsheet practices.
-		Therefore, we developed \toolnameend, a tool that analyzes spreadsheet corpora to
-		visualize patterns of function
-		combination as an interactive tree, capable
-		of representing both the most common and most anomalous patterns of formula construction and their contexts in actual workbooks. Using spreadsheets from
-		the Enron corpus, we conduct both a case study and a user study to
-		explore \toolnameposs various applications, particularly those in flexible smell
+		Therefore, we developed \toolnameend, a tool that analyzes spreadsheet corpora
+		to visualize patterns of function combination as an interactive tree, capable
+		of representing both the most common and most anomalous patterns of formula
+		construction and their contexts in actual workbooks. Using spreadsheets from
+		the Enron corpus, we conduct both a case study and a user study to explore
+		\toolnameposs various applications, particularly those in flexible smell
 		detection and spreadsheet education.
@@
 
-	\section{Introduction} Spreadsheets surround us, ordering the ever-growing
-	flood of data that we produce. They serve key roles in industry, where as much
-	as 95\% of U.S. financial firms use them daily \cite{panko2008sarbanes}, and
-	academia, where teachers can use them to track research and students' grades,
-	not to mention many other lines of work \cite{ko2011state}. It's this
-	flexibility that grants them their allure: while a novice can still work
-	without much experience, spreadsheets offer hundreds of specialized functions
-	to fulfill a wide range of advanced needs, from complex statistics to text
-	manipulation \cite{nardi1990spreadsheet}. As such, it should be no surprise
-	that tens of millions of workers rely on these programs every day
-	\cite{scaffidi2005estimating}.
+	\section{Introduction} Spreadsheets surround us. They serve key roles in
+	industry, where as much as 95\% of U.S. financial firms use them daily
+	\cite{panko2008sarbanes}, and academia, where teachers can use them to track
+	research and students' grades, not to mention many other applications
+	\cite{ko2011state}. It's this flexibility that grants them their allure: while
+	a novice can still work without much experience, spreadsheets offer hundreds of
+	specialized functions to fulfill a wide range of advanced needs, from complex
+	statistics to text manipulation \cite{nardi1990spreadsheet}. As such, it should
+	be no surprise that tens of millions of workers rely on these programs every
+	day \cite{scaffidi2005estimating}.
 

### 2016-04-26 doc/paper.tex
Intro. Fixes #114, fixes #115, fixes #116, fixes #117, fixes #118, fixes #119, fixes #120.

@@
 	However, this ubiquity is not without danger: as more people adopt these tools
-	and make larger and more complex sheets, the cost of failure grows too. To
-	stress this, the European Spreadsheet Risks Interest Group (EuSpRIG) documents
-	many horror stories of spreadsheets gone terribly
+	and make larger and more complex sheets, the cost of failure grows too. For examples
+	of this, the European Spreadsheet Risks Interest Group (EuSpRIG) documents
+	many horror stories of spreadsheets gone 
 	wrong\footnote{http://www.eusprig.org/horror-stories.htm}. One such story tells
-	of a 2013 economics paper which drew stark connections between debt and
+	of a 2013 economics paper which drew connections between debt and
 	national growth. Its findings shaped many political initiatives throughout the
 	United States and Europe. However, other researchers soon discovered that a
-	critical coding error in the research spreadsheets hampered the results and
-	that, by correcting this error, they completely reversed the findings! And this
+	critical selection error in the research spreadsheets hampered the results and
+	that, by correcting this error, the findings reversed completely! And this
 	is only one of several accounts; even if most spreadsheet errors are relatively
@@
 	\cite{hermans2015enron} have already fueled productive research across the
-	field, such as in Hermans' \cite{hermans2012detecting} or Jansen's
-	\cite{jansen2015code} search for code smells\footnote{Or, instances of
-		inelegant code that do not necessarily cause problems alone but nevertheless
-		suggest a need for refactoring to prevent future problems. More on this in
-		section IV.} in spreadsheet environments or Aivaloglou and colleague's work on
-	making a grammar to capture every possible spreadsheet program in Excel
-	\cite{aivaloglou2015grammar}. Additionally, some research has focused simply on
-	comparing these collections, as Jansen did in 2015, to discover variation in
-	spreadsheet techniques over time and location \cite{jansen2015enron}.
+	field, such as in Hermans' \cite{hermans2012detecting} and Jansen's
+	\cite{jansen2015code} search for code smells in spreadsheet environments or
+	Aivaloglou and colleague's work on making a grammar to capture every possible
+	spreadsheet program in Excel \cite{aivaloglou2015grammar}. Additionally, some
+	research has focused on comparing these collections, as Jansen did in
+	2015, to discover variation in spreadsheet techniques over time and location
+	\cite{jansen2015enron}.
 
-	Considering the sheer value of spreadsheets and all of these resources to
+	Considering the value of spreadsheets and all of these resources to
 	describe their use, it becomes necessary that we design tools to make sense of

### 2016-04-26 doc/paper.tex
Prep for SVG/PDF images.

@@
 \usepackage{textcomp} 
+\usepackage{svg}
 
@@
 	statistics to text manipulation \cite{nardi1990spreadsheet}. As such, it should
-	be no surprise that tens of millions of workers rely on these programs every
-	day \cite{scaffidi2005estimating}.
+	be no surprise that tens of millions of workers rely on these programs daily \cite{scaffidi2005estimating}.
 
-	However, this ubiquity is not without danger: as more people adopt these tools
-	and make larger and more complex sheets, the cost of failure grows too. For examples
-	of this, the European Spreadsheet Risks Interest Group (EuSpRIG) documents
+	However, this ubiquity is not without danger; as more people adopt these tools
+	and make larger and more complex sheets, the cost of failure grows too. To illustrate this, the European Spreadsheet Risks Interest Group (EuSpRIG) documents
 	many horror stories of spreadsheets gone 
-	wrong\footnote{http://www.eusprig.org/horror-stories.htm}. One such story tells
+	wrong\footnote{http://www.eusprig.org/horror-stories.htm}. One story tells
 	of a 2013 economics paper which drew connections between debt and
@@
 
-	This paper contributes such a tool, \toolname, that attempts to fulfill this by
+	This paper contributes such a tool, \toolname, that attempts to fulfill this
+	need for better exploration by
 	building on the aforementioned spreadsheet corpora. Working with spreadsheets
 	in Excel, \toolname focuses primarily on the functions, like SUM and IF and
-	hundreds more, which are the building blocks of formula and programs which
+	hundreds more, which are the building blocks of formula and programs that
 	determine values across a spreadsheet. The tool creates an interactive,
@@
 
-	To round out that discussion, we also conducted a user study to judge how
+	To better understand how people might use \toolnameend, we also conducted a user study to judge how
 	usable and intuitive the tool actually is. This grounds the discussion of its

### 2016-04-26 doc/paper.tex
Full paper work. Fixes #136, fixes #128, fixes #129, fixes #130, fixes #131, fixes 134, fixes #135, fixes #139, fixes #143, fixes #144, fixes #149, fixes #150, fixes #152, fixes #166, fixes #168, fixes #174, fixes #176, fixes #189, fixes #191, fixes #192...and maybe some others.

@@
 \usepackage{textcomp} 
-\usepackage{svg}
+%\usepackage{svg}
+%\setsvg{inkscape = inkscape -z -D, svgpath = svgs/}
 
@@
 
-	\begin{figure*}[t] \includegraphics[width = \textwidth]{IFargslabel} \caption{A
-			picture of \toolname} \centering \label{fig:fullpic} \end{figure*}
+	\begin{figure*}[t] \centering \includegraphics[scale=.6]{IFargslabel} \caption{A
+			picture of \toolname displaying the common arguments to the IF function's first 
+			parameter} \centering \label{fig:fullpic} \end{figure*}
 
@@
 
-	\section{Related Work} \label{related-work} Given humanity's affinity for
-	visual information, visualizations have long been prized for their ability to
+	\section{Related Work} \label{related-work} Visualizations have long been prized for their ability to
 	communicate information quickly and efficient \cite{baeza1999modern}; the
@@
 	the sheets. Hermans and colleagues address a spreadsheet programmer's
-	information by making dataflow diagrams from individual sheets through the
+	information needs by making dataflow diagrams from individual sheets through the
 	tools GyroSAT \cite{hermans2011supporting} and Breviz \cite{hermans2011breviz}.
 	\toolname is among the latter class, creating standalone visualizations about
-	spreadsheets. In contrast to Hermans' work, though, our work focuses on
+	spreadsheets. In contrast to Hermans' work, our work focuses on
 	representing functions and how they comprise complex formula, rather than
@@
 	wherein references between worksheets (rather than cells) in a file suggest a
-	problem. \cite{hermans2012detectinginter}. Other tools, like Badam's Excel
+	problem \cite{hermans2012detectinginter}. Other tools, like Badam's Excel
 	refactoring \cite{badame2012refactoring}, are concerned more with understanding
-	the formula in the service of changing them. However, these studies define
+	the formula in service of changing them. However, these studies define
 	standards of poor design and orient their searches around them. Though
@@
 		\item [1] \textbf{Provide an interactive environment for free exploration.}
-		There are a lot of data in some of these collections, and the user should be
+		There are a lot of data in some of these spreadsheet corpora, and the user should be
 		able to pick for themselves which to explore while ignoring the rest.
@@
 		formulae, \toolname will not prioritize any on metrics of good or bad
-		practice. Rather, it will present them agnostically, referring only to
-		frequency.
+		practice.
 
@@
 		spreadsheet programmers used a certain function and where they used it. In
-		this way, it must show precise metrics, such as frequency of use and depth of
+		this way, it must show metrics, such as frequency of use and depth of
 		function nesting, of the dataset it conveys.
@@
 	we nevertheless reached a number of points in which these principles
-	conflicted. For a discussion of these decisions, see section
+	conflicted. For a discussion of these decisions, see Section
 	\ref{ssec:decisions}.
@@
 	to use the tool. For this, we will answer this question: \textit{ What kinds of
-		functions do people use to define the condition in an IF function?} Thefull
-	visualization that answers this is available in figure \ref{fig:fullpic};
+		functions do people use to define the condition in an IF function?} The full
+	visualization that answers this is available in Figure~\ref{fig:fullpic};
 	however, to understand the interaction, we will start from the beginning. \par
@@
 	Furthermore, the third argument is optional; if left out, the function will return a default "FALSE" value if necessary.
-Examples of this function in practice can be seen in \ref{fig:ifexample}.
+Examples of this function in practice can be seen in Figure~\ref{fig:ifexample}.
 
 	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{ifExample}
-		\label{fig:ifexample} \caption{Configurations of the IF function} \end{figure}
+		\caption{Configurations of the IF function} \label{fig:ifexample} \end{figure}
 
@@
 	is, a function nested within none other -- only a few nodes are visible, as
-	shown in figure \ref{fig:startpic}. \par
+	shown in Figure \ref{fig:startpic}. \par
 
-	\begin{figure}[h] \centering \includegraphics{start} \label{fig:startpic}
-		\caption{How the IF tree looks at the start} \end{figure}
+	\begin{figure}[h] \centering \includegraphics[scale=.5]{start} 
+		\caption{How the IF tree looks at the start} \label{fig:startpic} \end{figure}
 
-	The visualization so far comprises two types of node: the circle
+	The visualization so far comprises two types of nodes: the circle
 	\includegraphics{glossary-greenonly}, which represents a discrete function in
@@
 
-	\begin{figure}[h] \centering \includegraphics[width=.43\textwidth]{IFexpand}
-		\label{fig:expandif} \caption{First argument of the IF tree} \end{figure}
+	\begin{figure}[h] \centering \includegraphics[scale=.4]{IFexpand}
+		 \caption{First argument of the IF tree} \label{fig:expandif} \end{figure}
 
@@
 			nodes} are dark blue squares labeled with a number. The number is the position
-		of an argument within the function in the parent node. In \ref{fig:expandif}
+		of an argument within the function in the parent node. In Figure \ref{fig:expandif}
 		for example, argument node 1 shows every function or value that was seen in
@@
 		.46\textwidth]{comparison} \includegraphics[]{comparison-ss}
-		\label{fig:optional} \caption{The contents of each type of tree.} \end{figure}
+		\caption{The contents of each type of tree.} \label{fig:optional} \end{figure}
 
@@
 
-	Guided by the goals in section A, we faced a number of decision points, a
+	Guided by the goals in Section \ref{goals}, we faced a number of decision points, a
 	sample of which we describe below, before we arrived at the design shown above.
@@
 	vulnerabilities in code design. Since then, researchers have applied these
-	concepts to spreadsheet programming, as discussed in section
+	concepts to spreadsheet programming, as discussed in Section
 	\ref{related-work}. While some of the smells lie beyond the scope of the tool,
@@
 		\item \textit{Multiple Operations}: A single formula comprises numerous
-		functions and operators. \cite{hermans2012detecting}. As a result, the formula
+		functions and operators \cite{hermans2012detecting}. As a result, the formula
 		tends to be prohibitively complex. In the visualization, since each nested and
@@
 		constructions can result in long, horizontal chains of nodes, as seen in
-		figure \ref{"fig:longsum"}.
+		Figure \ref{fig:longsum}.
 
@@
 	\begin{figure*}[h] \centering \includegraphics[width=\textwidth]{longsum}
-		\label{"fig:longsum"} \caption{The horizontal length of a tree may indicate
-			complex or redundant design.} \end{figure*}
+		 \caption{The horizontal length of a tree may indicate
+			complex or redundant design.} \label{fig:longsum} \end{figure*}
 
@@
 	\begin{figure} \centering \includegraphics[width=.5\textwidth]{lookupexample}
-		\label{fig:lookupexample} \caption{Demonstrations of LOOKUP and VLOOKUP}
+		 \caption{Demonstrations of LOOKUP and VLOOKUP} \label{fig:lookupexample}
 	\end{figure}
@@
 	retrieve examples of every configuration in the dataset. The same goes for the
-	V/HLOOKUP functions, as shown partially in Figure \ref{fig:vhlookups}
+	V/HLOOKUP functions, as shown partially in Figure \ref{fig:vhlookups}.
 
 	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
-		\includegraphics[width=.5\textwidth]{lookup-3} \label{fig:lookups}
-		\caption{LOOKUP with two and three arguments.} \end{figure}
+		\includegraphics[width=.5\textwidth]{lookup-3}
+		\caption{LOOKUP with two and three arguments}  \label{fig:lookups} \end{figure}
 
@@
 	often do spreadsheet programmers use this function, with these particular
-	parameters?" Though \toolname does not discernd whether neighboring columns are
+	parameters?" Though \toolname does not discern whether neighboring columns are
 	sorted, it can nevertheless guide the educator to several examples in
@@
 	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
-		\includegraphics[width=.5\textwidth]{hlookup} \label{fig:vhlookups}
-		\caption{VLOOKUP and HLOOKUP with four arguments.} \end{figure}
+		\includegraphics[width=.5\textwidth]{hlookup} 
+		\caption{VLOOKUP and HLOOKUP with four arguments} \label{fig:vhlookups}\end{figure}
 
@@
 	brief, four-participant user study in order to detect conflicts between our
-	design and the goals in section \ref{goals}. We designed the study to be
+	design and the goals in Section \ref{goals}. We designed the study to be
 	exploratory; given trees based in the Enron dataset and at least twenty
@@
 	\subsection{Use in Smell Tracking} \begin{wrapfigure}{O}{.25\textwidth}
-		\centering \includegraphics{SUM} \label{fig:sum} \caption{An abundance of
-			parameters in SUM. Encountering this, P4 remarked, "Woah."} \end{wrapfigure}
+		\centering \includegraphics{SUM}  \caption{An abundance of
+			parameters in SUM. Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}
 
@@
 	they noted these examples shortly after opening a new tree, suggesting that the
-	distinctive visual signatures as discussed in section \ref{badsmells} was a
+	distinctive visual signatures as discussed in Section \ref{badsmells} was a
 	salient force in their exploration. For example, when P3 encountered the
-	initial design of the SUM tree, as seen in figure \ref{fig:sum}, they readily
+	initial design of the SUM tree, as seen in Figure \ref{fig:sum}, they readily
 	diagnosed that either a spreadsheet author was "totally incompetent, or [the
@@
 	to such documentation from within the tool without violating any design
-	concerns in \ref{goals}. \par
+	concerns in Section \ref{goals}. \par
 
@@
 	\section{Discussion} We began these studies with the intention of evaluating
-	our progress towards the goals in section \ref{goals}. Working from these
+	our progress towards the goals in Section \ref{goals}. Working from these
 	results, we noted many places where the tool aligned well or fell short.
@@
 	formula designs. Nevertheless, \toolname inadvertently emphasizes bad design of
-	certain types, such as all of those in section \ref{badsmells} marked by their
+	certain types, such as all of those in Section \ref{badsmells} marked by their
 	visual signatures. Even so, our participants found the discovery of bad smell
@@
 	distinguish between good design and bad design, how can we be sure that people
-	won’t inadvertently learn bad design from it? In the user study, we discussed
+	will not inadvertently learn bad design from it? In the user study, we discussed
 	its use in education and smell detection by bringing up the issues surrounding
@@
 	\begin{figure} \centering \includegraphics[width=.5\textwidth]{index}
-		\label{fig:index} \caption{A difficult question: how often is MATCH used in
-			both the second and third arguments?} \end{figure}
+		 \caption{A difficult question: how often is MATCH used in
+			both the second and third arguments?} \label{fig:index} \end{figure}
 
@@
 	other elements of a formula's context that we do no currently consider. For
-	example, \toolname does not current capture argument combination; in
+	example, \toolname does not current capture argument combination; in Figure
 	\ref{fig:index}, it is impossible to state how often the function MATCH
@@
 	used inside of a specific function, but finding information on what a function
-	is used inside of takes considerably more work -- we see again in
+	is used inside of takes considerably more work -- we see again in Figure
 	\ref{fig:index} that MATCH is used inside INDEX, but we cannot know which
@@
 	\section{Conclusion} This paper presents a tool to support the exploration of
-	function combinations throughout a given spreadsheet dataset. By taking a
+	function combinations throughout a given spreadsheet dataset. By taking an
 	agnostic approach to design quality, it attempts to convey the dataset's

### 2016-04-26 src/viz/treeMaker.js

@@ -30,7 +30,7 @@ var margin = {
     rect_col = "#519393",
     rect_hover = "#284E5E",
 
-    alternate_rect = "#B1BEC4",
+    alternate_rect = "#69787F",
 
     expand_col = "#CFE5A7",
     expand_hover = "#BBCE96",
@@ -130,7 +130,7 @@ d3.json(src, function(error, json) {
 
     scale = d3.scale.log()
         .domain([1, root.frequency])
-        .range([3, 30])
+        .range([5, 25])
         .nice();
 
     root.children.forEach(function(c) {
@@ -364,10 +364,10 @@ function mouseover(d) {
         ii = "</i>",
         br = "<br/>",
         func = "func: " + b + d.function+bb + br,
-        freq = "count: " + d.frequency.toLocaleString()
-          + " (" + (100 * d.frequency / (d.parent || d).frequency).toFixed(2) + "%)"
-          + " [" + (100 * d.frequency / root.frequency).toFixed(3) + "%]"+ br,
-        depth = "depth: " + (d.depth/2) + " (" + d.max_depth + ")" + br,
+        freq = "count: " + d.frequency.toLocaleString() + br;
+          //+ " (" + (100 * d.frequency / (d.parent || d).frequency).toFixed(2) + "%)"
+          //+ " [" + (100 * d.frequency / root.frequency).toFixed(3) + "%]"+ br,
+        depth = "depth: " + (d.depth/2) + br; //+ " of max " + d.max_depth + br,
         id = d.example;
 
     var hovered = d3.select("#n" + d.id);

### 2016-04-26 src/viz/windowMaker.js

@@ -9,7 +9,7 @@ function newWindow(d) {
         return; //TODO: A bigger problem is limiting the number of examples.
 
     var win = window.open("", "_blank");
-    win.document.write("Hey! You clicked: " + d.function)
+    win.document.write("You clicked: " + d.function + "<br/><br/>")
     win.focus;
 
     var childrenExamples = {};

### 2016-04-26 doc/paper.tex
More paper work. Fixes #122, fixes #132, fixes #133, fixes #140, fixes #141, fixes #145, fixes #146.

@@
 	\section{Introduction} Spreadsheets surround us. They serve key roles in
-	industry, where as much as 95\% of U.S. financial firms use them daily
-	\cite{panko2008sarbanes}, and academia, where teachers can use them to track
-	research and students' grades, not to mention many other applications
-	\cite{ko2011state}. It's this flexibility that grants them their allure: while
+	industry, where as much as 95\% of U.S. financial firms use them daily~\cite{panko2008sarbanes}, and academia, where teachers can use them to track
+	research and students' grades, not to mention many other applications~\cite{ko2011state}. It's this flexibility that grants them their allure: while
 	a novice can still work without much experience, spreadsheets offer hundreds of
 	specialized functions to fulfill a wide range of advanced needs, from complex
-	statistics to text manipulation \cite{nardi1990spreadsheet}. As such, it should
-	be no surprise that tens of millions of workers rely on these programs daily \cite{scaffidi2005estimating}.
+	statistics to text manipulation~\cite{nardi1990spreadsheet}. As such, it should
+	be no surprise that tens of millions of workers rely on these programs daily~\cite{scaffidi2005estimating}.
 
@@
 	benign, poor spreadsheet practice can risk millions, if not billions, of
-	dollars \cite{powell2009impact}.
+	dollars~\cite{powell2009impact}.
 
 	From these stories, we can see the dire importance of understanding how people
-	actually use spreadsheets, if only to avoid disasters. Fortunately, spreadsheet
+	actually use spreadsheets. Fortunately, spreadsheet
 	researchers have supported this by amassing spreadsheet collections from
-	diverse sources, industrial to academic. Collections like EUSES
-	\cite{fisher2005euses}, Fuse \cite{barik2015fuse}, and the Enron corpus
-	\cite{hermans2015enron} have already fueled productive research across the
-	field, such as in Hermans' \cite{hermans2012detecting} and Jansen's
-	\cite{jansen2015code} search for code smells in spreadsheet environments or
+	diverse sources, industrial to academic. Collections like EUSES~\cite{fisher2005euses}, 
+	Fuse~\cite{barik2015fuse}, and the Enron corpus~\cite{hermans2015enron} have already fueled productive research across the
+	field, such as in Hermans'~\cite{hermans2012detecting} and Jansen's~\cite{jansen2015code} search for code smells in spreadsheet environments or
 	Aivaloglou and colleague's work on making a grammar to capture every possible
-	spreadsheet program in Excel \cite{aivaloglou2015grammar}. Additionally, some
+	spreadsheet program in Excel~\cite{aivaloglou2015grammar}. Additionally, some
 	research has focused on comparing these collections, as Jansen did in
-	2015, to discover variation in spreadsheet techniques over time and location
-	\cite{jansen2015enron}.
+	2015, to discover variation in spreadsheet techniques over time and location~\cite{jansen2015enron}.
 
 	Considering the value of spreadsheets and all of these resources to
-	describe their use, it becomes necessary that we design tools to make sense of
-	it all. Tools, then, that empower people to explore datasets are rife with the
-	potential to improve the current design of spreadsheets themselves and educate
+	describe their use, it becomes necessary that we design tools to better enable the
+	exploration of these datasets and simplify the complex concepts that occur in
+	spreadsheet design. One such concept is that of formula construction; functions
+	are an important part of using spreadsheets efficiently, yet the number of their potential
+	combinations quickly becomes massive when you consider that there are hundreds of them.
+	Tools, then, that empower people to explore questions about which functions are used together 
+	in practice have the potential to improve the current design of spreadsheets themselves and educate
 	new generations of spreadsheets users on how to work best.
@@
 
-	\section{Related Work} \label{related-work} Visualizations have long been prized for their ability to
-	communicate information quickly and efficient \cite{baeza1999modern}; the
+	\section{Related Work} \label{related-work} Visualizations excel for their ability to
+	communicate information quickly and efficiently~\cite{baeza1999modern}; the
 	visualization of spreadsheets, therefore, has offered much room for research.
@@
 	them, and the dependencies between cells that inform them. Igarashi and
-	colleague's fluid visualizations \cite{igarashi1998fluid}, for example, do this
+	colleague's fluid visualizations~\cite{igarashi1998fluid}, for example, do this
 	by imposing lines, color, and animation over the spreadsheet to visually
@@
 	cells by color and border that were related through similar functions,
-	neighbors, or references \cite{clermont2003scalable}, and Hipfl extended this
-	work by incorporating the layouts and labels of spreadsheets
-	\cite{hipfl2008using}. Other tools focus on creating visualizations external to
+	neighbors, or references~\cite{clermont2003scalable}, and Hipfl extended this
+	work by incorporating the layouts and labels of spreadsheets~\cite{hipfl2008using}. Other tools focus on creating visualizations external to
 	the sheets. Hermans and colleagues address a spreadsheet programmer's
 	information needs by making dataflow diagrams from individual sheets through the
-	tools GyroSAT \cite{hermans2011supporting} and Breviz \cite{hermans2011breviz}.
+	tools GyroSAT~\cite{hermans2011supporting} and Breviz~\cite{hermans2011breviz}.
 	\toolname is among the latter class, creating standalone visualizations about
-	spreadsheets. In contrast to Hermans' work, our work focuses on
+	spreadsheets instead of drawing connections inside the spreadsheet itself. In contrast to Hermans' work, our work focuses on
 	representing functions and how they comprise complex formula, rather than
@@
 	perspective of finding bad design.  Following Fowler's initial description of
-	code smells in object-oriented design \cite{fowler2009refactoring}, many
+	code smells in object-oriented design~\cite{fowler2009refactoring}, many
 	researchers have applied similar observations to spreadsheets and have
-	cataloged classes of problematic formulae \cite{hermans2012detecting}
-	\cite{cunha2012towards} \cite{asavametha2012detecting}, often accompanying them
-	with detection tools \cite{abreu2014smelling} and investigations
-	\cite{jansen2015code}. For example, Hermans, leveraging her work with the
+	cataloged classes of problematic formulae~\cite{hermans2012detecting}~\cite{cunha2012towards}~\cite{asavametha2012detecting}, often accompanying them
+	with detection tools~\cite{abreu2014smelling} and investigations into real datasets~\cite{jansen2015code}. For example, Hermans, leveraging her work with the
 	aforementioned dataflow diagrams, has worked with assessing common
@@
 	wherein references between worksheets (rather than cells) in a file suggest a
-	problem \cite{hermans2012detectinginter}. Other tools, like Badam's Excel
-	refactoring \cite{badame2012refactoring}, are concerned more with understanding
+	problem~\cite{hermans2012detectinginter}. Other tools, like Badam's Excel
+	refactoring~\cite{badame2012refactoring}, are concerned more with understanding
 	the formula in service of changing them. However, these studies define
@@
 	Implicit in this study is an exploration of the Excel API and how people use
-	it. Previous research, such as the first study on the Enron spreadsheets
-	\cite{hermans2015enron} or in its comparison with the EUSUS corpus
-	\cite{jansen2015enron}, quantify how ofter users employ certain functions but
+	it.
+Previous research, such as the first study on the Enron spreadsheets~\cite{hermans2015enron} or in its comparison with the EUSUS corpus~\cite{jansen2015enron}, quantify how ofter users employ certain functions but
 	not how they combine them. Researchers have applied such questions to other
 	contexts as well, such as Murphy and colleague's study into how Java developers
-	use Eclipse and what commands they use most often \cite{murphy2006java}. Others
+	use Eclipse and what commands they use most often~\cite{murphy2006java}. Others
 	focus on the documentation of the API itself: Robillard and DeLine, for example
@@
 	learning APIs, and they found that code examples, one of the focuses of this
-	tool, is one of the most important aids to have in learning a new system
-	\cite{robillard2011field}. Though this paper applies the tool to the Enron
+	tool, is one of the most important aids to have in learning a new system~\cite{robillard2011field}. Though this paper applies the tool to the Enron
 	corpus specifically, the tool itself is not limited to this; it can be readily
@@
 	\subsection{Design Goals} \label{goals} In visualizing the spreadsheet data, we
-	outlined the core goals for what the tool should accomplish. Furthermore, with
+	follow a few core goals for what the tool should accomplish. Furthermore, with
 	these goals, we also considered the likely challenges of achieving those goals
@@
 		Furthermore, this exploration should not be designed around answering one
-		specific question but rather be open-ended.
+		specific question but rather helping to answer a variety of questions.
 
 		\item [!1] \textbf{Do not make judgments about good and bad design.} Though
-		users may certainly approach the tool with the intention of finding particular
+		users may certainly approach the tool with the intention of exploring particular
 		formulae, \toolname will not prioritize any on metrics of good or bad
@@
 			construction.} \toolname should address the questions of how often the
-		spreadsheet programmers used a certain function and where they used it. In
-		this way, it must show metrics, such as frequency of use and depth of
+		spreadsheet programmers used a certain function and where they used it. To do
+		this, it must show metrics, such as frequency of use and depth of
 		function nesting, of the dataset it conveys.
@@
 		\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
-		especially, we anticipated some particularly dense trees. Though everything
+		especially, we anticipated that we'd have to show a lot of related data
+		at once. Though everything
 		should be accessible in accordance with Goal 1, we should design in a way that
@@
 	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing
-	the minutiae of tool's development, though, we will give a basic example of how
+	the minutiae of tool's development, we will give a basic example of how
 	to use the tool. For this, we will answer this question: \textit{ What kinds of

### 2016-04-26 doc/paper.tex
Fixes #142.

@@
 		users may certainly approach the tool with the intention of exploring particular
-		formulae, \toolname will not prioritize any on metrics of good or bad
+		formulae, a formula visualization tool will not prioritize any on metrics of good or bad
 		practice.
@@
 		\item [2] \textbf{Emphasize the quantitative patterns in formula
-			construction.} \toolname should address the questions of how often the
+			construction.} The tool should address the questions of how often the
 		spreadsheet programmers used a certain function and where they used it. To do
@@
 		\item [3] \textbf{Promote a qualitative understanding of the patterns.}
-		\toolname should supplement its observations with concrete instances of
+		The tool should supplement its observations with concrete instances of
 		relevant formulae from the corpus. Ideally, it should even direct users to the
@@
 
-		\item [!3] \textbf{Do not attempt to explain formulae.} Though \toolname tries
+		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool will
 		to foster understanding by linking pattern to example, it should not provide a

### 2016-04-26 doc/paper.tex
Delirium at 2:30am. Fixes #154, fixes #155, fixes #156, fixes #157, fixes #158, fixes #159 (hopefully)

@@
 	\maketitle
-
-	\begin{figure*}[t] \centering \includegraphics[scale=.6]{IFargslabel} \caption{A
-			picture of \toolname displaying the common arguments to the IF function's first 
-			parameter} \centering \label{fig:fullpic} \end{figure*}
 
@@
 	to use the tool. For this, we will answer this question: \textit{ What kinds of
-		functions do people use to define the condition in an IF function?} The full
-	visualization that answers this is available in Figure~\ref{fig:fullpic};
-	however, to understand the interaction, we will start from the beginning. \par
+		functions do people use to define the condition in an IF function?} \par
 
@@
 	the formula and is size according to its frequency relative to the number of
-	times to root function appeared\footnote{The root node, by definition, will
-		always be the largest node in a tree.}; and the numbered squares
+	times to root function appeared; and the numbered squares
 	\includegraphics{glossary-blue}, which represent the positions of arguments
@@
 
+	\begin{figure*}[t] \centering \includegraphics[scale=.5]{IFargslabel} \caption{A
+			picture of \toolname displaying the common arguments to the IF function's first 
+			parameter} \centering \label{fig:fullpic} \end{figure*}
+
 	For both sides of the equal sign, the operator has certain types of arguments
@@
 	Furthermore, a tooltip accompanies each function node in the tree, providing a
-	concrete example of a function that uses this structure and where it can be
-	found. If this single instance is not enough, then the user also has the option
+	concrete example of a function that uses this structure. If this single instance is not enough, then the user also has the option
 	to double-click the individual function node, which will open up a new tab with
@@
 
-	\subsection{Icon Glossary}
+	\subsection{Glyph Glossary}
 
-	From these images, we can provide a quick glossary of images within the
+	From these images, we can provide a quick glossary of glyphs within the
 	visualization to aid interpretation. \begin{itemize} \item
@@
 		white circles with a generic label. They represent elements of a formula which
-		are which accept no arguments, like references (A1), ranges
-		(A1:A10)\footnote{That is, only if both sides of a references are cell
-			references. If either side is a function that returns a cell reference, like
-			INDIRECT, then the colon should be a function node.}, numbers, boolean values,
-		strings, and errors. Functions with zero arguments, like NOW, however, should
-		still be considered function nodes.
+		accept no arguments, like references (A1), ranges (A1:A10), numbers, boolean
+		values, strings, and errors. However, \toolname treats still functions with
+		zero arguments, like NOW, as function nodes.
 
@@
 		\item  \vspace{.25cm} \includegraphics{glossary-solidline} - \textbf{Solid
-			lines} represent a function's ownership of its various arguments. As such,
+			lines} represent a function's acceptance of its parameters. As such,
 		they connect the function nodes to argument nodes.
@@
 		\item  \vspace{.25cm} \includegraphics{glossary-fadingline} - \textbf{Fading
-			lines} represent the possibility of an argument position to have several
-		different possible functions or values. As such, they connect argument nodes
-		to function or value nodes.
+			lines} represents how a formula author can use several different possible
+		functions or values within a single argument position. As such, they connect
+		argument nodes to function or value nodes.
 
@@
 		\textbf{Optional argument trees} are variations of trees that show only
-		formulae with a specific number of arguments, allowing the user to control for
-		the presence of optional arguments. By default, trees with dark blue nodes
-		contain every type of formula without regard how many arguments they have --
-		for example, single-argument ANDs could appear alongside 4-argument ANDs. See
-		Figure \ref{fig:optional} to see it visualized. \end{itemize}
+		formulae with a specific number of arguments. For example, the function AND can
+		take any number of arguments, up to 255. By default, the tree shows data from
+		AND functions with any number of argument, but these trees, marked with a darker
+		blue color, can show how AND was used when \textit{only} two arguments were passed into 
+		it, or \textit{only} four, and so on. See
+		Figure \ref{fig:optional} for how the data between tree types differs. \end{itemize}
 
@@
 		.46\textwidth]{comparison} \includegraphics[]{comparison-ss}
-		\caption{The contents of each type of tree.} \label{fig:optional} \end{figure}
+		\caption{The contents of the default tree (left) and the optional argument trees (right)} \label{fig:optional} \end{figure}
 
-	\subsection{Implementation Details} The final visualization is the product of
+	\subsection{Implementation Details} The visualization is the product of
 	two discrete processes: \begin{itemize} \item \textit{Collection}: Given a set
@@
 	\subsection{Design Decisions} \label{ssec:decisions} Early in the design, we
-	chose the tree form for its inherent ability to represent the loose
+	chose the tree form for its inherent ability to represent the
 	parent-children relationship of formulae as functions and their arguments,
@@
 
-	Guided by the goals in Section \ref{goals}, we faced a number of decision points, a
-	sample of which we describe below, before we arrived at the design shown above.
+	Guided by the goals in Section \ref{goals}, we faced a number of decisions in how
+	to represent the data in the visualization. Below, I've outlined those that had
+	the largest impact in the values that appear in the tree.
 	\begin{itemize}
-
-		%Can I incorporate these again?
-		%			\begin{itemize}
-		%
-		%				\item [1] \textbf{Provide an interactive environment for free
-		% exploration.}
-		%				There are a lot of data in some of these collections, and the user should
-		% be
-		%				able to pick for themselves which to explore while ignoring the rest.
-		% Furthermore,
-		%				this exploration should not be designed around answering one specific
-		% question
-		%				but rather be open-ended.
-		%
-		%				\item [!1] \textbf{Do not make judgments about good and bad design.}
-		% Though
-		%				users may certainly approach the tool with the intention of finding
-		% particular
-		%				formulae, \toolname will not prioritize any on metrics of good or bad
-		%				practice. Rather, it will present them agnostically, referring only to
-		%				frequency.
-		%
-		%				\item [2] \textbf{Emphasize the quantitative patterns in formula
-		%					construction.} \toolname should address the questions of how often the
-		%				spreadsheet programmers used a certain function and where they used it.
-		% In
-		%				this way, it must show precise metrics, such as frequency of use and
-		% depth
-		% of
-		%				function nesting, of the dataset it conveys.
-		%
-		%				\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
-		%				especially, we anticipated some particularly dense trees. Though
-		%				everything should be accessible in accordance with Goal 1, we should
-		% design
-		% in
-		%				a way that reduces noise.
-		%
-		%				\item [3] \textbf{Promote a qualitative understanding of the patterns.}
-		%				\toolname should supplement its observations with concrete instances of
-		%				relevant formulae from the corpus. Ideally, it should even direct users
-		% to
-		% the
-		%				exact cell in the spreadsheets where the formula was used,
-		% contextualizing
-		% the
-		%				functions.
-		%
-		%				\item [!3] \textbf{Do not attempt to explain formulae.} Though \toolname
-		% tries
-		%				to foster understanding by linking pattern to example, it should not
-		% provide
-		%				a precise description of what a complex formula accomplishes. The tool's
-		% user
-		%				must infer this on their own.
-		%
-		%			\end{itemize}
 

### 2016-04-26 doc/paper.tex
Fixes #61.

@@
 	the minutiae of tool's development, we will give a basic example of how
-	to use the tool. For this, we will answer this question: \textit{ What kinds of
+	to use the tool. For this, we will work from the visualization built on the Enron
+	corpus to answer this question: \textit{ What kinds of
 		functions do people use to define the condition in an IF function?} \par

### 2016-04-26 doc/paper.tex
Studies revision. Fixes #178, fixes #177, fixes #175, fixes #173, fixes #172, fixes #171, fixes #169.

@@
 %
-\usepackage{cite}
-% cite.sty was written by Donald Arseneau
+\usepackage{cite} % cite.sty was written by Donald Arseneau
 % The latest version can be obtained at:
@@
 
-\usepackage{textcomp} 
-%\usepackage{svg}
+\usepackage{textcomp} %\usepackage{svg}
 %\setsvg{inkscape = inkscape -z -D, svgpath = svgs/}
 
-\newcommand{\toolname}{Perquimans }
-\newcommand{\toolnameend}{Perquimans}
+\newcommand{\toolname}{Perquimans } \newcommand{\toolnameend}{Perquimans}
 \newcommand{\toolnameposs}{Perquimans' }
 
-\begin{document}
-	\title{\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations}
+\begin{document} \title{\toolnameend: A Tool for Visualizing Patterns of
+		Spreadsheet Function Combinations}
 
@@
 	\author{ \IEEEauthorblockN{Justin A. Middleton, Emerson Murphy-Hill}
-		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ 
-			\{jamiddl2, ermurph3\}@ncsu.edu }}
+		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ \{jamiddl2,
+			ermurph3\}@ncsu.edu }}
 
@@
 	% in the abstract
-	\begin{abstract} 
-		Spreadsheet environments often come equipped with an abundance of functions
-		and operations to manipulate data, which users can combine into a complex
-		formulae for more sophisticated programs. However, anticipating these
+	\begin{abstract} Spreadsheet environments often come equipped with an abundance
+		of functions and operations to manipulate data, which users can combine into a
+		complex formulae for more sophisticated programs. However, anticipating these
 		combinations is difficult, complicating matters for both researchers and
@@
 	\section{Introduction} Spreadsheets surround us. They serve key roles in
-	industry, where as much as 95\% of U.S. financial firms use them daily~\cite{panko2008sarbanes}, and academia, where teachers can use them to track
-	research and students' grades, not to mention many other applications~\cite{ko2011state}. It's this flexibility that grants them their allure: while
-	a novice can still work without much experience, spreadsheets offer hundreds of
-	specialized functions to fulfill a wide range of advanced needs, from complex
-	statistics to text manipulation~\cite{nardi1990spreadsheet}. As such, it should
-	be no surprise that tens of millions of workers rely on these programs daily~\cite{scaffidi2005estimating}.
+	industry, where as much as 95\% of U.S. financial firms use them
+	daily~\cite{panko2008sarbanes}, and academia, where teachers can use them to
+	track research and students' grades, not to mention many other
+	applications~\cite{ko2011state}. It's this flexibility that grants them their
+	allure: while a novice can still work without much experience, spreadsheets
+	offer hundreds of specialized functions to fulfill a wide range of advanced
+	needs, from complex statistics to text
+	manipulation~\cite{nardi1990spreadsheet}. As such, it should be no surprise
+	that tens of millions of workers rely on these programs
+	daily~\cite{scaffidi2005estimating}.
 
 	However, this ubiquity is not without danger; as more people adopt these tools
-	and make larger and more complex sheets, the cost of failure grows too. To illustrate this, the European Spreadsheet Risks Interest Group (EuSpRIG) documents
-	many horror stories of spreadsheets gone 
-	wrong\footnote{http://www.eusprig.org/horror-stories.htm}. One story tells
-	of a 2013 economics paper which drew connections between debt and
-	national growth. Its findings shaped many political initiatives throughout the
-	United States and Europe. However, other researchers soon discovered that a
-	critical selection error in the research spreadsheets hampered the results and
-	that, by correcting this error, the findings reversed completely! And this
-	is only one of several accounts; even if most spreadsheet errors are relatively
-	benign, poor spreadsheet practice can risk millions, if not billions, of
+	and make larger and more complex sheets, the cost of failure grows too. To
+	illustrate this, the European Spreadsheet Risks Interest Group (EuSpRIG)
+	documents many horror stories of spreadsheets gone
+	wrong\footnote{http://www.eusprig.org/horror-stories.htm}. One story tells of a
+	2013 economics paper which drew connections between debt and national growth.
+	Its findings shaped many political initiatives throughout the United States and
+	Europe. However, other researchers soon discovered that a critical selection
+	error in the research spreadsheets hampered the results and that, by correcting
+	this error, the findings reversed completely! And this is only one of several
+	accounts; even if most spreadsheet errors are relatively benign, poor
+	spreadsheet practice can risk millions, if not billions, of
 	dollars~\cite{powell2009impact}.
@@
 	From these stories, we can see the dire importance of understanding how people
-	actually use spreadsheets. Fortunately, spreadsheet
-	researchers have supported this by amassing spreadsheet collections from
-	diverse sources, industrial to academic. Collections like EUSES~\cite{fisher2005euses}, 
-	Fuse~\cite{barik2015fuse}, and the Enron corpus~\cite{hermans2015enron} have already fueled productive research across the
-	field, such as in Hermans'~\cite{hermans2012detecting} and Jansen's~\cite{jansen2015code} search for code smells in spreadsheet environments or
-	Aivaloglou and colleague's work on making a grammar to capture every possible
-	spreadsheet program in Excel~\cite{aivaloglou2015grammar}. Additionally, some
-	research has focused on comparing these collections, as Jansen did in
-	2015, to discover variation in spreadsheet techniques over time and location~\cite{jansen2015enron}.
+	actually use spreadsheets. Fortunately, spreadsheet researchers have supported
+	this by amassing spreadsheet collections from diverse sources, industrial to
+	academic. Collections like EUSES~\cite{fisher2005euses},
+	Fuse~\cite{barik2015fuse}, and the Enron corpus~\cite{hermans2015enron} have
+	already fueled productive research across the field, such as in
+	Hermans'~\cite{hermans2012detecting} and Jansen's~\cite{jansen2015code} search
+	for code smells in spreadsheet environments or Aivaloglou and colleague's work
+	on making a grammar to capture every possible spreadsheet program in
+	Excel~\cite{aivaloglou2015grammar}. Additionally, some research has focused on
+	comparing these collections, as Jansen did in 2015, to discover variation in
+	spreadsheet techniques over time and location~\cite{jansen2015enron}.
 
-	Considering the value of spreadsheets and all of these resources to
-	describe their use, it becomes necessary that we design tools to better enable the
+	Considering the value of spreadsheets and all of these resources to describe
+	their use, it becomes necessary that we design tools to better enable the
 	exploration of these datasets and simplify the complex concepts that occur in
 	spreadsheet design. One such concept is that of formula construction; functions
-	are an important part of using spreadsheets efficiently, yet the number of their potential
-	combinations quickly becomes massive when you consider that there are hundreds of them.
-	Tools, then, that empower people to explore questions about which functions are used together 
-	in practice have the potential to improve the current design of spreadsheets themselves and educate
+	are an important part of using spreadsheets efficiently, yet the number of
+	their potential combinations quickly becomes massive when you consider that
+	there are hundreds of them. Tools, then, that empower people to explore
+	questions about which functions are used together in practice have the
+	potential to improve the current design of spreadsheets themselves and educate
 	new generations of spreadsheets users on how to work best.
@@
 	This paper contributes such a tool, \toolname, that attempts to fulfill this
-	need for better exploration by
-	building on the aforementioned spreadsheet corpora. Working with spreadsheets
-	in Excel, \toolname focuses primarily on the functions, like SUM and IF and
-	hundreds more, which are the building blocks of formula and programs that
-	determine values across a spreadsheet. The tool creates an interactive,
-	exploratory visualization which captures how people combine these functions in
-	a selected collection of spreadsheets, quantifying the broad patterns of
-	function nesting while also being specific enough to find anomalous formulae
-	and link them back to the specific cell in spreadsheets where they originate.
-	\par
+	need for better exploration by building on the aforementioned spreadsheet
+	corpora. Working with spreadsheets in Excel, \toolname focuses primarily on the
+	functions, like SUM and IF and hundreds more, which are the building blocks of
+	formula and programs that determine values across a spreadsheet. The tool
+	creates an interactive, exploratory visualization which captures how people
+	combine these functions in a selected collection of spreadsheets, quantifying
+	the broad patterns of function nesting while also being specific enough to find
+	anomalous formulae and link them back to the specific cell in spreadsheets
+	where they originate. \par
 
@@
 
-	To better understand how people might use \toolnameend, we also conducted a user study to judge how
-	usable and intuitive the tool actually is. This grounds the discussion of its
-	potential uses while also underscoring some of its inherent limitations and
-	setting the way for future extensions and improvements upon the concept.
+	To better understand how people might use \toolnameend, we also conducted a
+	user study to judge how usable and intuitive the tool actually is. This grounds
+	the discussion of its potential uses while also underscoring some of its
+	inherent limitations and setting the way for future extensions and improvements
+	upon the concept.
 
-	\section{Related Work} \label{related-work} Visualizations excel for their ability to
-	communicate information quickly and efficiently~\cite{baeza1999modern}; the
-	visualization of spreadsheets, therefore, has offered much room for research.
-	Several previous tools work within a spreadsheet, seeking to clarify the
-	connections between the visible values in cells, the formulae that produce
-	them, and the dependencies between cells that inform them. Igarashi and
-	colleague's fluid visualizations~\cite{igarashi1998fluid}, for example, do this
-	by imposing lines, color, and animation over the spreadsheet to visually
-	explain these tangled connections. Likewise, Clermont explored ways of grouping
-	cells by color and border that were related through similar functions,
-	neighbors, or references~\cite{clermont2003scalable}, and Hipfl extended this
-	work by incorporating the layouts and labels of spreadsheets~\cite{hipfl2008using}. Other tools focus on creating visualizations external to
-	the sheets. Hermans and colleagues address a spreadsheet programmer's
-	information needs by making dataflow diagrams from individual sheets through the
-	tools GyroSAT~\cite{hermans2011supporting} and Breviz~\cite{hermans2011breviz}.
+	\section{Related Work} \label{related-work} Visualizations excel for their
+	ability to communicate information quickly and
+	efficiently~\cite{baeza1999modern}; the visualization of spreadsheets,
+	therefore, has offered much room for research. Several previous tools work
+	within a spreadsheet, seeking to clarify the connections between the visible
+	values in cells, the formulae that produce them, and the dependencies between
+	cells that inform them. Igarashi and colleague's fluid
+	visualizations~\cite{igarashi1998fluid}, for example, do this by imposing
+	lines, color, and animation over the spreadsheet to visually explain these
+	tangled connections. Likewise, Clermont explored ways of grouping cells by
+	color and border that were related through similar functions, neighbors, or
+	references~\cite{clermont2003scalable}, and Hipfl extended this work by
+	incorporating the layouts and labels of spreadsheets~\cite{hipfl2008using}.
+	Other tools focus on creating visualizations external to the sheets. Hermans
+	and colleagues address a spreadsheet programmer's information needs by making
+	dataflow diagrams from individual sheets through the tools
+	GyroSAT~\cite{hermans2011supporting} and Breviz~\cite{hermans2011breviz}.
 	\toolname is among the latter class, creating standalone visualizations about
-	spreadsheets instead of drawing connections inside the spreadsheet itself. In contrast to Hermans' work, our work focuses on
-	representing functions and how they comprise complex formula, rather than
-	exploring the data structures of any particular spreadsheet.  \par
+	spreadsheets instead of drawing connections inside the spreadsheet itself. In
+	contrast to Hermans' work, our work focuses on representing functions and how
+	they comprise complex formula, rather than exploring the data structures of any
+	particular spreadsheet.  \par
 
@@
 	researchers have applied similar observations to spreadsheets and have
-	cataloged classes of problematic formulae~\cite{hermans2012detecting}~\cite{cunha2012towards}~\cite{asavametha2012detecting}, often accompanying them
-	with detection tools~\cite{abreu2014smelling} and investigations into real datasets~\cite{jansen2015code}. For example, Hermans, leveraging her work with the
-	aforementioned dataflow diagrams, has worked with assessing common
-	inter-worksheet smells, such as feature envy and inappropriate intimacy,
-	wherein references between worksheets (rather than cells) in a file suggest a
-	problem~\cite{hermans2012detectinginter}. Other tools, like Badam's Excel
-	refactoring~\cite{badame2012refactoring}, are concerned more with understanding
-	the formula in service of changing them. However, these studies define
-	standards of poor design and orient their searches around them. Though
-	\toolname supports the search for bad design, as we will see, the tool itself
-	takes a much more agnostic approach in presentation, offering examples without
-	regard for design quality. \par
+	cataloged classes of problematic
+	formulae~\cite{hermans2012detecting}~\cite{cunha2012towards}~\cite{asavametha2012detecting}, often accompanying them with detection tools~\cite{abreu2014smelling} and investigations into real datasets~\cite{jansen2015code}.
+For example, Hermans, leveraging her work with the aforementioned dataflow diagrams, has worked with assessing common inter-worksheet smells, such as feature envy and inappropriate intimacy, wherein references between worksheets (rather than cells) in a file suggest a problem~\cite{hermans2012detectinginter}.
+Other tools, like Badam's Excel refactoring~\cite{badame2012refactoring}, are concerned more with understanding the formula in service of changing them.
+However, these studies define standards of poor design and orient their searches around them.
+Though \toolname supports the search for bad design, as we will see, the tool itself takes a much more agnostic approach in presentation, offering examples without regard for design quality.
+\par
 
 	Implicit in this study is an exploration of the Excel API and how people use
-	it.
-Previous research, such as the first study on the Enron spreadsheets~\cite{hermans2015enron} or in its comparison with the EUSUS corpus~\cite{jansen2015enron}, quantify how ofter users employ certain functions but
-	not how they combine them. Researchers have applied such questions to other
-	contexts as well, such as Murphy and colleague's study into how Java developers
-	use Eclipse and what commands they use most often~\cite{murphy2006java}. Others
-	focus on the documentation of the API itself: Robillard and DeLine, for example
-	conducted a series of surveys and interviews to diagnose common problems with
-	learning APIs, and they found that code examples, one of the focuses of this
-	tool, is one of the most important aids to have in learning a new system~\cite{robillard2011field}. Though this paper applies the tool to the Enron
-	corpus specifically, the tool itself is not limited to this; it can be readily
-	applied to any collection of Excel spreadsheets a user gives it.
+	it. Previous research, such as the first study on the Enron
+	spreadsheets~\cite{hermans2015enron} or in its comparison with the EUSUS
+	corpus~\cite{jansen2015enron}, quantify how ofter users employ certain
+	functions but not how they combine them. Researchers have applied such
+	questions to other contexts as well, such as Murphy and colleague's study into
+	how Java developers use Eclipse and what commands they use most
+	often~\cite{murphy2006java}. Others focus on the documentation of the API
+	itself: Robillard and DeLine, for example conducted a series of surveys and
+	interviews to diagnose common problems with learning APIs, and they found that
+	code examples, one of the focuses of this tool, is one of the most important
+	aids to have in learning a new system~\cite{robillard2011field}. Though this
+	paper applies the tool to the Enron corpus specifically, the tool itself is not
+	limited to this; it can be readily applied to any collection of Excel
+	spreadsheets a user gives it.
 
@@
 		\item [1] \textbf{Provide an interactive environment for free exploration.}
-		There are a lot of data in some of these spreadsheet corpora, and the user should be
-		able to pick for themselves which to explore while ignoring the rest.
-		Furthermore, this exploration should not be designed around answering one
-		specific question but rather helping to answer a variety of questions.
+		There are a lot of data in some of these spreadsheet corpora, and the user
+		should be able to pick for themselves which to explore while ignoring the
+		rest. Furthermore, this exploration should not be designed around answering
+		one specific question but rather helping to answer a variety of questions.
 
 		\item [!1] \textbf{Do not make judgments about good and bad design.} Though
-		users may certainly approach the tool with the intention of exploring particular
-		formulae, a formula visualization tool will not prioritize any on metrics of good or bad
-		practice.
+		users may certainly approach the tool with the intention of exploring
+		particular formulae, a formula visualization tool will not prioritize any on
+		metrics of good or bad practice.
 
@@
 		spreadsheet programmers used a certain function and where they used it. To do
-		this, it must show metrics, such as frequency of use and depth of
-		function nesting, of the dataset it conveys.
+		this, it must show metrics, such as frequency of use and depth of function
+		nesting, of the dataset it conveys.
 
 		\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
-		especially, we anticipated that we'd have to show a lot of related data
-		at once. Though everything
-		should be accessible in accordance with Goal 1, we should design in a way that
-		reduces noise.
+		especially, we anticipated that we'd have to show a lot of related data at
+		once. Though everything should be accessible in accordance with Goal 1, we
+		should design in a way that reduces noise.
 
-		\item [3] \textbf{Promote a qualitative understanding of the patterns.}
-		The tool should supplement its observations with concrete instances of
-		relevant formulae from the corpus. Ideally, it should even direct users to the
-		exact cell in the spreadsheets where the formula was used, contextualizing the
+		\item [3] \textbf{Promote a qualitative understanding of the patterns.} The
+		tool should supplement its observations with concrete instances of relevant
+		formulae from the corpus. Ideally, it should even direct users to the exact
+		cell in the spreadsheets where the formula was used, contextualizing the
 		functions.
@@
 	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing
-	the minutiae of tool's development, we will give a basic example of how
-	to use the tool. For this, we will work from the visualization built on the Enron
-	corpus to answer this question: \textit{ What kinds of
-		functions do people use to define the condition in an IF function?} \par
+	the minutiae of tool's development, we will give a basic example of how to use
+	the tool. For this, we will work from the visualization built on the Enron
+	corpus to answer this question: \textit{ What kinds of functions do people use
+		to define the condition in an IF function?} \par
 
@@
 
-	\begin{figure}[h] \centering \includegraphics[scale=.5]{start} 
-		\caption{How the IF tree looks at the start} \label{fig:startpic} \end{figure}
+	\begin{figure}[h] \centering \includegraphics[scale=.5]{start} \caption{How the
+			IF tree looks at the start} \label{fig:startpic} \end{figure}
 
@@
 
-	\begin{figure*}[t] \centering \includegraphics[scale=.5]{IFargslabel} \caption{A
-			picture of \toolname displaying the common arguments to the IF function's first 
-			parameter} \centering \label{fig:fullpic} \end{figure*}
+	\begin{figure*}[t] \centering \includegraphics[scale=.5]{IFargslabel}
+		\caption{A picture of \toolname displaying the common arguments to the IF
+			function's first parameter} \centering \label{fig:fullpic} \end{figure*}
 
@@
 	Furthermore, a tooltip accompanies each function node in the tree, providing a
-	concrete example of a function that uses this structure. If this single instance is not enough, then the user also has the option
-	to double-click the individual function node, which will open up a new tab with
-	a table of many more examples from dataset.
+	concrete example of a function that uses this structure. If this single
+	instance is not enough, then the user also has the option to double-click the
+	individual function node, which will open up a new tab with a table of many
+	more examples from dataset.
 
@@
 			nodes} are dark blue squares labeled with a number. The number is the position
-		of an argument within the function in the parent node. In Figure \ref{fig:expandif}
-		for example, argument node 1 shows every function or value that was seen in
-		the first argument.
+		of an argument within the function in the parent node. In Figure
+		\ref{fig:expandif} for example, argument node 1 shows every function or value
+		that was seen in the first argument.
 
 		\item  \vspace{.25cm} \includegraphics{glossary-solidline} - \textbf{Solid
-			lines} represent a function's acceptance of its parameters. As such,
-		they connect the function nodes to argument nodes.
+			lines} represent a function's acceptance of its parameters. As such, they
+		connect the function nodes to argument nodes.
 
@@
 		\textbf{Optional argument trees} are variations of trees that show only
-		formulae with a specific number of arguments. For example, the function AND can
-		take any number of arguments, up to 255. By default, the tree shows data from
-		AND functions with any number of argument, but these trees, marked with a darker
-		blue color, can show how AND was used when \textit{only} two arguments were passed into 
-		it, or \textit{only} four, and so on. See
-		Figure \ref{fig:optional} for how the data between tree types differs. \end{itemize}
+		formulae with a specific number of arguments. For example, the function AND
+		can take any number of arguments, up to 255. By default, the tree shows data
+		from AND functions with any number of argument, but these trees, marked with a
+		darker blue color, can show how AND was used when \textit{only} two arguments
+		were passed into it, or \textit{only} four, and so on. See
+		Figure~\ref{fig:optional} for how the data between tree types differs.
+	\end{itemize}
 
 	\begin{figure}[h] \centering \includegraphics[width =
-		.46\textwidth]{comparison} \includegraphics[]{comparison-ss}
-		\caption{The contents of the default tree (left) and the optional argument trees (right)} \label{fig:optional} \end{figure}
+		.46\textwidth]{comparison} \includegraphics[]{comparison-ss} \caption{The
+			contents of the default tree (left) and the optional argument trees (right)}
+		\label{fig:optional} \end{figure}
 
-	\subsection{Implementation Details} The visualization is the product of
-	two discrete processes: \begin{itemize} \item \textit{Collection}: Given a set
-		of Excel sheets, the tool, written in Java, uses Apache
+	\subsection{Implementation Details} The visualization is the product of two
+	discrete processes: \begin{itemize} \item \textit{Collection}: Given a set of
+		Excel sheets, the tool, written in Java, uses Apache
 		POI\footnote{https://poi.apache.org/} to identify and iterate over every cell
@@
 	\subsection{Design Decisions} \label{ssec:decisions} Early in the design, we
-	chose the tree form for its inherent ability to represent the
-	parent-children relationship of formulae as functions and their arguments,
-	which could be yet more functions. By adapting this structure to accommodate a
-	broad range of possibilities for nested functions, the branching factor depends
-	alternatively on the number of arguments in a function and the number of
-	possible functions observed as an argument in a function. \par
+	chose the tree form for its inherent ability to represent the parent-children
+	relationship of formulae as functions and their arguments, which could be yet
+	more functions. By adapting this structure to accommodate a broad range of
+	possibilities for nested functions, the branching factor depends alternatively
+	on the number of arguments in a function and the number of possible functions
+	observed as an argument in a function. \par
 
-	Guided by the goals in Section \ref{goals}, we faced a number of decisions in how
-	to represent the data in the visualization. Below, I've outlined those that had
-	the largest impact in the values that appear in the tree.
-	\begin{itemize}
+	Guided by the goals in Section \ref{goals}, we faced a number of decisions in
+	how to represent the data in the visualization. Below, I've outlined those that
+	had the largest impact in the values that appear in the tree. \begin{itemize}
 
@@
 	gained from any particular visualization. As such, we raised a few tasks in the
-	introduction in which we thought the tool could help: detecting bad smells and guiding spreadsheet education. To
-	demonstrate the tool's applicability, we sought out places in the tree which
-	best exemplify these tasks.
+	introduction in which we thought the tool could help: detecting bad smells and
+	guiding spreadsheet education. To demonstrate the tool's applicability, we
+	sought out places in the tree which best exemplify these tasks.
 
-	\subsection{Bad Smells} \label{badsmells} Fowler's description of code smells
-	\cite{fowler2009refactoring} underscored an important point of code quality:
-	between elegant, efficient code and bug-crippled spaghetti, there is a spectrum
-	of code designs which, by themselves, are not faulty but nevertheless suggest
-	vulnerabilities in code design. Since then, researchers have applied these
-	concepts to spreadsheet programming, as discussed in Section
-	\ref{related-work}. While some of the smells lie beyond the scope of the tool,
-	such as those characterizing inter-worksheet connections, others have
+	\subsection{Bad Smells} \label{badsmells} Fowler's description of code
+	smells~\cite{fowler2009refactoring} underscored an important point of code
+	quality: between elegant, efficient code and bug-crippled spaghetti, there is a
+	spectrum of code designs which, by themselves, are not faulty but nevertheless
+	suggest vulnerabilities in code design. Since then, researchers have applied
+	these concepts to spreadsheet programming, as discussed in
+	Section~\ref{related-work}. While some of the smells lie beyond the scope of
+	the tool, such as those characterizing inter-worksheet connections, others have
 	structures which create distinctive features within the tree, leading to easy
@@
 		\item \textit{Multiple Operations}: A single formula comprises numerous
-		functions and operators \cite{hermans2012detecting}. As a result, the formula
+		functions and operators~\cite{hermans2012detecting}. As a result, the formula
 		tends to be prohibitively complex. In the visualization, since each nested and
@@
 		constructions can result in long, horizontal chains of nodes, as seen in
-		Figure \ref{fig:longsum}.
+		Figure~\ref{fig:longsum}.
 
 		\item \textit{Long Parameter List}: A function uses numerous arguments, making
-		it harder to understand \cite{asavametha2012detecting}. This is not a problem
+		it harder to understand~\cite{asavametha2012detecting}. This is not a problem
 		for many functions which have a limited number of arguments that it accepts.
@@
 		\item \textit{Conditional Complexity}: A logical function, particularly IF,
-		nests several other logical functions inside of it, reducing code readability
-		\cite{hermans2012detecting}. These can be traced manually in the trees for the
-		logical functions. IF, for example, will have several more IF function nodes
-		within its second or third arguments, which in turn might have more of the
-		same nested within them.
+		nests several other logical functions inside of it, reducing code
+		readability~\cite{hermans2012detecting}. These can be traced manually in the
+		trees for the logical functions. IF, for example, will have several more IF
+		function nodes within its second or third arguments, which in turn might have
+		more of the same nested within them.
 
@@
 	\begin{figure*}[h] \centering \includegraphics[width=\textwidth]{longsum}
-		 \caption{The horizontal length of a tree may indicate
-			complex or redundant design.} \label{fig:longsum} \end{figure*}
+		\caption{The horizontal length of a tree may indicate complex or redundant
+			design} \label{fig:longsum} \end{figure*}
 
@@
 
+	However, because \toolname makes no judgments beforehand about which designs to
+	emphasize as good or bad, the tool can be used to find strange or suboptimal
+	designs that exist outside these obvious categories. Consider the second
+	argument of the ``='' operator, already shown expanded in
+	Figure~\ref{fig:fullpic}: among the top five argument types for the position in
+	an IF function were boolean values. This corresponds to designs in which
+	conditions already in a boolean form were then checked against "=TRUE" or
+	"=FALSE", such as in the formula \textit{IF(Formulas!C77=TRUE, "Yes")}, which
+	appears in one of the sheets. Though this practice does not break anything in
+	itself, it nevertheless represents redundant operations in formula design and
+	indicates a possible misunderstanding of how the IF function works over the
+	hundreds of examples of this boolean comparison that our tool can return.
+
 	\subsection{Education} When Robillard and Deline researched common obstacles
@@
 	important elements of a good API was the use of code examples to demonstrate
-	function use. These examples, furthermore, come in a variety of forms: small
+	function use. Examples in APIs, furthermore, come in a variety of forms: small
 	snippets or tutorials that show only the intended function, sample applications
@@
 	that employs the function but was not initially intended to be an illustrative
-	example \cite{robillard2011field}. Of these categories, \toolname aligns
+	example~\cite{robillard2011field}. Of these categories, \toolname aligns
 	entirely with the last; when a user chooses to explore a particular function
@@
 	Furthermore, Robillard and Deline's study makes the case for examples that show
-	"API usage patterns involving more than one method call"
+	``API usage patterns involving more than one method call"
 	\cite{robillard2011field}. Examples that show only a single function, they
@@
 	%Lookup example
-	For a deeper example, the LOOKUP functions are particularly notorious for their
-	confusing mechanisms and, as such, have warranted some extra attention with
-	regards to spreadsheet design. In short, these functions are for "when you need
-	to look in a single row or column and find a value from the same position in a
-	second row or
-	column"\footnote{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}. Examples of each can be found in Figure \ref{fig:lookupexample}.
+	For a deeper example, the LOOKUP functions are some of the most popular in
+	Excel yet come with a number of important but silent requirements for proper
+	use, and, as such, they have warranted some extra attention with regards to
+	spreadsheet design. In short, these functions are for "when you need to look in
+	a single row or column and find a value from the same position in a second row
+	or column"\footnote{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}.
+Examples of their use can be found in Figure \ref{fig:lookupexample}, and we will cover each type
+	in more depth to better understand the visualizations for these functions.
 
-	\begin{figure} \centering \includegraphics[width=.5\textwidth]{lookupexample}
+	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookupexample}
 		\caption{Demonstrations of LOOKUP and VLOOKUP} \label{fig:lookupexample}
@@
 	the value which you are trying to match in another column. If the formula is in
-	the vector form, that column is the second argument, so in Figure
-	\ref{fig:lookupexample}, the formula in cell D2 (\textit{=LOOKUP(3, A2:A6,
+	the vector form, that column is the second argument, so in Figure~\ref{fig:lookupexample}, 
+	the formula in cell D2 (\textit{=LOOKUP(3, A2:A6,
 		B2:B6)}) will search for the value of 3 between cells A2 and A6. The value the
@@
 	way, except that the second argument is a two-dimensional table where it
-	matches values in the table's first column and returns values from the
-	last\footnote{ Depending on the dimensions of the lookup table, the function
-		may substitute rows for columns.}.
+	matches values in the table's first column and returns values from the last.
+	Also, depending on the dimensions of the lookup table, the function may
+	substitute rows for columns.
 
@@
 	when TRUE or left out, it approximates the match to the closest value beneath
-	it. We demonstrate this in Figure \ref{fig:lookupexample} in the bottom two
+	it. We demonstrate this in Figure~\ref{fig:lookupexample} in the bottom two
 	VLOOKUP functions, one returning ``Friday" and the other an error. HLOOKUP
@@
 	help. Because of its design, users can distinguish between forms of the same
-	function, as seen in Figure \ref{fig:lookups} where the one can explore both
+	function, as seen in Figure~\ref{fig:lookups} where the one can explore both
 	the frequency with which the spreadsheet programmers used these different forms
@@
 	retrieve examples of every configuration in the dataset. The same goes for the
-	V/HLOOKUP functions, as shown partially in Figure \ref{fig:vhlookups}.
+	V/HLOOKUP functions, as shown partially in Figure~\ref{fig:vhlookups}.
 
 	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
-		\includegraphics[width=.5\textwidth]{lookup-3}
-		\caption{LOOKUP with two and three arguments}  \label{fig:lookups} \end{figure}
+		\includegraphics[width=.5\textwidth]{lookup-3} \caption{LOOKUP with two and
+			three arguments}  \label{fig:lookups} \end{figure}
 
@@
 	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
-		\includegraphics[width=.5\textwidth]{hlookup} 
-		\caption{VLOOKUP and HLOOKUP with four arguments} \label{fig:vhlookups}\end{figure}
+		\includegraphics[width=.5\textwidth]{hlookup} \caption{VLOOKUP and HLOOKUP with
+			four arguments} \label{fig:vhlookups}\end{figure}
 
 	\section{User Study} \label{sec:userstudy} During development, we conducted a
-	brief, four-participant user study in order to detect conflicts between our
+	brief, four-participant user study to detect conflicts between our
 	design and the goals in Section \ref{goals}. We designed the study to be
@@
 	\subsection{Use in Smell Tracking} \begin{wrapfigure}{O}{.25\textwidth}
-		\centering \includegraphics{SUM}  \caption{An abundance of
-			parameters in SUM. Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}
+		\centering \includegraphics{SUM}  \caption{An abundance of parameters in SUM.
+			Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}
 
@@
 	diagnosed that either a spreadsheet author was "totally incompetent, or [the
-	formula was] just some that's weird." Other than these visual cues, value
+	formula was] just something that's weird." Other than these visual cues, value
 	errors, prefixed with \#s, also appear in the tree, which P4 said could be
@@
 	distinguish between good design and bad design, how can we be sure that people
-	will not inadvertently learn bad design from it? In the user study, we discussed
-	its use in education and smell detection by bringing up the issues surrounding
-	the LOOKUP functions; this discussion, though, presupposes a distinguishing eye
-	that knew which examples practiced good design and which exhibited the common
-	errors. But a beginner might not know the difference. Robillard and Deline, in
-	their study, remarked that good API examples should demonstrate best practices,
-	but, right now, we have no way to assure this with \toolname. As with the
-	problems in achieving unbiased exploration, correcting for this danger may
-	entail a reevaluation of design goals.
+	will not inadvertently learn bad design from it? In the user study, we
+	discussed its use in education and smell detection by bringing up the issues
+	surrounding the LOOKUP functions; this discussion, though, presupposes a
+	distinguishing eye that knew which examples practiced good design and which
+	exhibited the common errors. But a beginner might not know the difference.
+	Robillard and Deline, in their study, remarked that good API examples should
+	demonstrate best practices, but, right now, we have no way to assure this with
+	\toolname. As with the problems in achieving unbiased exploration, correcting
+	for this danger may entail a reevaluation of design goals.
 
@@
 	\begin{figure} \centering \includegraphics[width=.5\textwidth]{index}
-		 \caption{A difficult question: how often is MATCH used in
-			both the second and third arguments?} \label{fig:index} \end{figure}
+		\caption{A difficult question: how often is MATCH used in both the second and
+			third arguments?} \label{fig:index} \end{figure}
 
@@
 	offered in spreadsheet corpora and rendering them comprehensible through
-	visualization, we seek to draw attention to valuable information that would otherwise
-	go unnoticed.
+	visualization, we seek to draw attention to valuable information that would
+	otherwise go unnoticed.
 

### 2016-04-26 doc/paper.tex
Fixes #170.

@@
 	important elements of a good API was the use of code examples to demonstrate
-	function use. Examples in APIs, furthermore, come in a variety of forms: small
+	function use~\cite{robillard2011field}. Examples in APIs, furthermore, come in a variety of forms: small
 	snippets or tutorials that show only the intended function, sample applications
@@
 	that employs the function but was not initially intended to be an illustrative
-	example~\cite{robillard2011field}. Of these categories, \toolname aligns
+	example. Of these categories, \toolname aligns
 	entirely with the last; when a user chooses to explore a particular function
@@
 	Furthermore, Robillard and Deline's study makes the case for examples that show
-	``API usage patterns involving more than one method call"
-	\cite{robillard2011field}. Examples that show only a single function, they
+	``API usage patterns involving more than one method call"~\cite{robillard2011field}. Examples that show only a single function, they
 	find, are too simple, whereas those demonstrating the interaction of functions

### 2016-04-26 doc/paper.tex
Fixes #179, fixes #180.

@@
 	observations could be directed either at the quality of the data conveyed by
-	the tool or at the tool's design itself. \par
-
-	Nevertheless, these user studies were a formative moment in evaluating the
-	tool's performance, generating a number of directions or corrections in the
-	process. We present an overview of responses below, with the four participants
+	the tool or at the tool's design itself. We present an overview of responses below, with the four participants
 	recorded simply as P1 through P4. \par
 
-	\subsection{Use in Smell Tracking} \begin{wrapfigure}{O}{.25\textwidth}
-		\centering \includegraphics{SUM}  \caption{An abundance of parameters in SUM.
-			Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}
+	\subsection{Use in Smell Tracking}
 
@@
 	useful for tracking these problems if marked well.
+
+	\begin{wrapfigure}{O}{.25\textwidth}
+		\centering \includegraphics{SUM}  \caption{An abundance of parameters in SUM.
+			Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}
 
@@
 	that this visual interface better supports the case when searching for new and
-	unknown brands of bad smell. Because the exploratory design makes no
+	previously unknown smells. Because the exploratory design makes no
 	qualitative judgment and visualizes benign designs with the problematic, it

### 2016-04-26 doc/paper.tex
Got paper to 10 pages.

@@
 	studies to evaluate how much it could contribute to several different contexts,
-	most notably code smell detection and spreadsheet education.
-
-	To better understand how people might use \toolnameend, we also conducted a
+	most notably code smell detection and spreadsheet education. To better understand how people might use \toolnameend, we also conducted a
 	user study to judge how usable and intuitive the tool actually is. This grounds
@@
 
-	\begin{figure}[h] \centering \includegraphics[scale=.5]{start} \caption{How the
+	\begin{figure}[h] \centering \includegraphics[scale=.4]{start} \caption{How the
 			IF tree looks at the start} \label{fig:startpic} \end{figure}
@@
 	on the square labeled ``1" to explore. To save space, when more than 10 unique
-	arguments have been observed in any position, the tool displays only the first
+	arguments were found in a position, the tool displays only the first
 	ten, with an option to display the rest by clicking the arrow
@@
 	simple equality being the most common and some use as ABS being the least seen
-	of everything actually used. \par
-
-	From here, we can further explore the common options among these functions.
+	of everything actually used. From here, we can further explore the common options among these functions.
 	Clicking on the ``=" node will yield two arguments and expanding each of them
@@
 		tree. They may have any number of arguments, including zero, as determined by
-		the API.
+		the API. Users can select any of these nodes to view the examples from the 
+		provided dataset that use this function in the node's position in the tree.
 
@@
 		values, strings, and errors. However, \toolname treats still functions with
-		zero arguments, like NOW, as function nodes.
+		zero arguments, like NOW, as function nodes. Like function nodes, these also 
+		contain examples.
 
@@
 		for its accessibility: given the JSON, the visualization can be simply
-		embedded into a webpage accessible through a browser. \end{itemize} A
-	demonstration of the tool can be found at
+		embedded into a webpage accessible through a browser. \end{itemize} The code and a
+	demonstration of \toolname can be found at
 	https://github.com/DeveloperLiberationFront/Excel-Function-Visualizer.
@@
 	Guided by the goals in Section \ref{goals}, we faced a number of decisions in
-	how to represent the data in the visualization. Below, I've outlined those that
+	how to visualize the data. Below, we've outlined those that
 	had the largest impact in the values that appear in the tree. \begin{itemize}
@@
 
-	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
-		\includegraphics[width=.5\textwidth]{lookup-3} \caption{LOOKUP with two and
+	\begin{figure}[h] \centering \includegraphics[scale=.75]{lookup-2}
+		\includegraphics[scale=.75]{lookup-3} \caption{LOOKUP with two and
 			three arguments}  \label{fig:lookups} \end{figure}
@@
 
-	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
-		\includegraphics[width=.5\textwidth]{hlookup} \caption{VLOOKUP and HLOOKUP with
+	\begin{figure}[h] \centering \includegraphics[scale=.75]{vlookup}
+		\includegraphics[scale=.75]{hlookup} \caption{VLOOKUP and HLOOKUP with
 			four arguments} \label{fig:vhlookups}\end{figure}
@@
 	Additionally, \toolname offers a simple way of finding examples where certain
-	functions were used together. Though a standard text-search tool might yield
+	functions were used together, demonstrated when P4 took special interest in how people
+	frequently used MATCH as the second argument of INDEX or how they used date functions
+	like DATE and MONTH as lookup values in VLOOKUP. Though a standard text-search tool might yield
 	the same results for a function alone, combinations can require more complex
@@
 	to such documentation from within the tool without violating any design
-	concerns in Section \ref{goals}. \par
+	concerns in Section~\ref{goals}. \par
 
@@
 	orient their exploration around finance-related functions, potentially limiting
-	their findings or perceived users for the tool. Though, one also said that,
-	without this essential context, they could not have properly explored a dataset
+	their findings or perceived users for the tool. However, one participant also said that,
+	without this essential context, they could not have intelligently explored a dataset
 	in the first place. Comments like these point out the trade-offs of unguided
@@
 	Furthermore, the data which users explored was processed and created before we
-	had fully completed the tool, meaning some of the counts and patterns in the
+	had fully ensured that the tool could extract all of the useful data from the 
+	spreadsheets, meaning some of the counts and patterns in the
 	trees were inaccurate. However, we decided that this was not a pressing
@@
 	these misunderstandings became apparent, these events point to a failure in the
-	tool to properly indicate every function with clarity.   \par
+	tool to indicate every function clearly.   \par
 
-	\section{Discussion} We began these studies with the intention of evaluating
+	\section{Limitations} We began these studies with the intention of evaluating
 	our progress towards the goals in Section \ref{goals}. Working from these
@@
 
-	Participants also asked for more options to quickly navigate the tree. For
-	example, P2 asked for the ability to expand the entire tree at once and icons
-	that better communicated the presence of optional arguments and their
-	quantities. The more familiar participants grew with the tool, the faster they
-	wanted to explore, yet it supported expert navigation up to the point of
-	expanding all of a node's children up to one level. \par
-
 	Other than that, we did avoid designing anything that intentionally evaluated
 	formula designs. Nevertheless, \toolname inadvertently emphasizes bad design of
-	certain types, such as all of those in Section \ref{badsmells} marked by their
+	certain types, such as all of those in Section~\ref{badsmells} marked by their
 	visual signatures. Even so, our participants found the discovery of bad smell
@@
 
-	We realized early that some of the popular functions would present a problem:
-	some would have thousands of variations in large datasets, and showing all of
+	We realized early that some of the popular functions would have thousands of variations in large datasets, and showing all of
 	these variations at once would hopelessly overwhelm the user. We therefore made
@@
 	the most popular functions, anticipating a flood of nodes from which they could
-	salvage nothing interesting -- which might not have been a bad prediction,
-	considering that the SUM is built from 910 function and argument nodes stemming
-	the root and IF, at least 18000. P2 corroborated this by explaining how they
+	salvage nothing interesting. P2 corroborated this by explaining how they
 	gravitated toward exploring specific examples in particular value nodes over
-	navigating the full crowd of the tree, but they complicate it further by also
+	navigating the full, crowded tree, but they complicate it further by also
 	saying that the tool at its best when it shows either every possibility of an
@@
 	\subsection{Informative Qualification} As we found in the case study, the tool
-	excels at making formula examples available throughout a tree. Though the tool
-	cannot outright explain what a formula does function-by-function, users
-	nevertheless found it valuable for the way it offers them with numerous
-	practical examples of functions previously unknown or confusing to them,
-	especially within the LOOKUP family. In the user study (Section
-	\ref{sec:userstudy}), furthermore, we also observed how a participant used the
-	repeated instance of a spreadsheet author's name to identify a potential
-	problem with a particular designer rather than a design itself, demonstrating
-	its use on several levels. \par
-
+	excels at making formula examples available throughout a tree. 	
 	However, the benefits described in the previous sections imply a hidden
@@
 	distinguishing eye that knew which examples practiced good design and which
-	exhibited the common errors. But a beginner might not know the difference.
+	exhibited the common errors. A beginner might not know the difference.
 	Robillard and Deline, in their study, remarked that good API examples should
@@
 
-	\begin{figure} \centering \includegraphics[width=.5\textwidth]{index}
+	\begin{figure} \centering \includegraphics[scale=.75]{index}
 		\caption{A difficult question: how often is MATCH used in both the second and

### 2016-04-26 doc/paper.tex
done? typo checking

@@
 	\begin{abstract} Spreadsheet environments often come equipped with an abundance
-		of functions and operations to manipulate data, which users can combine into a
-		complex formulae for more sophisticated programs. However, anticipating these
+		of functions and operations to manipulate data, which users can combine into
+		complex formulae. However, anticipating these
 		combinations is difficult, complicating matters for both researchers and
@@
 	are an important part of using spreadsheets efficiently, yet the number of
-	their potential combinations quickly becomes massive when you consider that
+	potential combinations between them quickly becomes massive when you consider that
 	there are hundreds of them. Tools, then, that empower people to explore
@@
 		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool will
-		to foster understanding by linking pattern to example, it should not provide a
-		precise description of what a complex formula accomplishes. The tool's user
-		must infer this on their own.
+		to foster understanding by linking pattern to example, it will not try to be
+		an explanatory tool that articulates what a complex formula accomplishes. Rather,
+		we will provide the structure and context, and the user	must infer this on their own.
 
@@
 
-	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{ifExample}
+	\begin{figure}[h] \centering \includegraphics[scale=.9]{ifExample}
 		\caption{Configurations of the IF function} \label{fig:ifexample} \end{figure}
@@
 
-	\begin{figure}[h] \centering \includegraphics[scale=.75]{lookup-2}
-		\includegraphics[scale=.75]{lookup-3} \caption{LOOKUP with two and
+	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
+		\includegraphics[width=.5\textwidth]{lookup-3} \caption{LOOKUP with two and
 			three arguments}  \label{fig:lookups} \end{figure}
@@
 
-	\begin{figure}[h] \centering \includegraphics[scale=.75]{vlookup}
-		\includegraphics[scale=.75]{hlookup} \caption{VLOOKUP and HLOOKUP with
+	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
+		\includegraphics[width=.5\textwidth]{hlookup} \caption{VLOOKUP and HLOOKUP with
 			four arguments} \label{fig:vhlookups}\end{figure}
@@
 	\begin{wrapfigure}{O}{.25\textwidth}
-		\centering \includegraphics{SUM}  \caption{An abundance of parameters in SUM.
+		\centering \includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters in SUM.
 			Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}
@@
 
-	\begin{figure} \centering \includegraphics[scale=.75]{index}
+	\begin{figure} \centering \includegraphics[width=.4\textwidth]{index}
 		\caption{A difficult question: how often is MATCH used in both the second and

### 2016-05-24 doc/paper.tex
Various changes for getting the info out.

@@
 
-	This paper contributes such a tool, \toolname, that attempts to fulfill this
+	This paper contributes such a tool, \toolnameend, that attempts to fulfill this
 	need for better exploration by building on the aforementioned spreadsheet
@@
 	functions, like SUM and IF and hundreds more, which are the building blocks of
-	formula and programs that determine values across a spreadsheet. The tool
+	formulae that determine values across a spreadsheet. The tool
 	creates an interactive, exploratory visualization which captures how people
@@
 	spreadsheets instead of drawing connections inside the spreadsheet itself. In
-	contrast to Hermans' work, our work focuses on representing functions and how
-	they comprise complex formula, rather than exploring the data structures of any
+	contrast to the other visualization work, our work focuses on representing functions and how
+	they combine into complex formula, rather than exploring the data structures of any
 	particular spreadsheet.  \par
@@
 For example, Hermans, leveraging her work with the aforementioned dataflow diagrams, has worked with assessing common inter-worksheet smells, such as feature envy and inappropriate intimacy, wherein references between worksheets (rather than cells) in a file suggest a problem~\cite{hermans2012detectinginter}.
-Other tools, like Badam's Excel refactoring~\cite{badame2012refactoring}, are concerned more with understanding the formula in service of changing them.
+Other tools, like Badame's Excel refactoring~\cite{badame2012refactoring}, are concerned more with understanding the formula in service of changing them.
 However, these studies define standards of poor design and orient their searches around them.
@@
 	spreadsheets~\cite{hermans2015enron} or in its comparison with the EUSUS
-	corpus~\cite{jansen2015enron}, quantify how ofter users employ certain
+	corpus~\cite{jansen2015enron}, quantifies how ofter users employ certain
 	functions but not how they combine them. Researchers have applied such
@@
 	\subsection{Design Goals} \label{goals} In visualizing the spreadsheet data, we
-	follow a few core goals for what the tool should accomplish. Furthermore, with
+	set out a few core goals for what the tool should accomplish. Furthermore, with
 	these goals, we also considered the likely challenges of achieving those goals
@@
 		\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
-		especially, we anticipated that we'd have to show a lot of related data at
+		especially, we anticipate that we'll have to show a lot of related data at
 		once. Though everything should be accessible in accordance with Goal 1, we
@@
 	with its specifications in the
-	API\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}. \par
+	API. \par
 
 	Knowing that it is the first argument which contains the conditionals, we click
-	on the square labeled ``1" to explore. To save space, when more than 10 unique
-	arguments were found in a position, the tool displays only the first
+	on the square labeled ``1" to explore. To save space, when the tool finds more than 10 unique
+	arguments in a position, it displays only the first
 	ten, with an option to display the rest by clicking the arrow
@@
 		\item  \vspace{.25cm} \includegraphics{glossary-solidline} - \textbf{Solid
-			lines} represent a function's acceptance of its parameters. As such, they
+			lines} represent a function's list of parameters. As such, they
 		connect the function nodes to argument nodes.
@@
 		can take any number of arguments, up to 255. By default, the tree shows data
-		from AND functions with any number of argument, but these trees, marked with a
-		darker blue color, can show how AND was used when \textit{only} two arguments
+		from AND functions with any number of arguments, but these trees, which have argument nodes of a lighter blue color, can show how AND was used when \textit{only} two arguments
 		were passed into it, or \textit{only} four, and so on. See
@@
 		for its accessibility: given the JSON, the visualization can be simply
-		embedded into a webpage accessible through a browser. \end{itemize} The code and a
+		embedded into a webpage accessible through a browser. \end{itemize} A
 	demonstration of \toolname can be found at
@@
 	emphasize as good or bad, the tool can be used to find strange or suboptimal
-	designs that exist outside these obvious categories. Consider the second
+	designs that exist outside these readily visible categories. Consider the second
 	argument of the ``='' operator, already shown expanded in
@@
 
-	\begin{wrapfigure}{O}{.25\textwidth}
-		\centering \includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters in SUM.
-			Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}
+	\begin{wrapfigure}{L}{.25\textwidth}
+		\centering \includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters in SUM, which was a commonly noted smell in the user study} \label{fig:sum} \end{wrapfigure}
 
@@
 	distinct arguments for which our participant could not discern any logical
-	order, even after opening the source spreadsheet; the same name popped up again
+	order even after opening the source spreadsheet; the same name popped up again
 	as P2 looked at a RATE function relying on several hard-coded values. P2 said
@@
 	demonstrate best practices, but, right now, we have no way to assure this with
-	\toolname. As with the problems in achieving unbiased exploration, correcting
+	\toolnameend. As with the problems in achieving unbiased exploration, correcting
 	for this danger may entail a reevaluation of design goals.
@@
 	this allows it to take on several potential roles at once, such as an
-	environment for search out bad code smells as well as a repository for examples
+	environment for investigating code smells as well as a repository for examples
 	for learning new techniques. \par

### 2016-05-24 src/core/ArgumentNode.java

@@ -55,6 +55,14 @@ public class ArgumentNode extends Node {
   }
   
   @Override
+  public Node[] getChildren() {
+    if (children == null)
+      setChildren();
+    
+    return children;
+  }
+  
+  @Override
   public String toString() {
     return position + "";
   }

### 2016-05-24 src/core/FunctionNode.java

@@ -24,6 +24,8 @@ public class FunctionNode extends Node {
   
   private int shortestExampleLen = Integer.MAX_VALUE;
   
+  //Ensures that it's not a unary/binary operator.
+  //TODO: + can be either unary or binary...
   private static Matcher nonvariadicFuncs = Pattern.compile("[\\+\\-\\*/\\^&]").matcher("");
     
   /**
@@ -125,16 +127,20 @@ public class FunctionNode extends Node {
     return quantityNode;
   }
   
+  /**
+   * When this function is called, the array "children" should be set to null, while "all_quantities"
+   * is the map used to keep track of the children. We just want to convert the map to the array.
+   * 
+   * If this function also has specific quantities, we need to set the children for those nodes too.
+   * TODO: There's got to be a better way at representing/explaining optional arguments...
+   */
   @Override
   public void setChildren() {
-    //TODO: Other kinds of children too!
     children = all_quantities.values().stream().toArray(ArgumentNode[]::new);
     
     for (ArgumentNode arg : all_quantities.values())
       arg.setChildren();
     
-    //Map<Integer, QuantityOfArgumentsNode> sortedQuantities = new LinkedHashMap<Integer, QuantityOfArgumentsNode>();
-    //Integer[] vals = specific_quantities.keySet().stream().toArray(Integer[]::new);
     if (specific_quantities != null) {
       if (specific_quantities.size() > 1)
         for (QuantityOfArgumentsNode node : specific_quantities.values())
@@ -144,15 +150,17 @@ public class FunctionNode extends Node {
     }
   }
   
+  public Node[] getChildren() {
+    if (children == null) 
+      setChildren();
+    
+    return children;
+  }
+  
   public String getFunction() {
     return function;
   }
   
-  /**
-   * Using {@link #toTreeString(StringBuilder, int)}, this returns a string
-   * which conveys the hierarchical nature of the formulas and displays the
-   * frequency of each kind of argument.
-   */
   @Override
   public String toString() {
     return function; 

### 2016-05-24 src/core/LeafNode.java

@@ -41,6 +41,11 @@ public class LeafNode extends Node {
   public void setChildren() {
     // Nothing    
   }
+  
+  public static final Node[] NO_CHILDREN = {};
+  public Node[] getChildren() {
+    return NO_CHILDREN;
+  }
 
   @Override
   public String toString() {

### 2016-05-24 src/core/Node.java

@@ -9,6 +9,8 @@ public abstract class Node implements Comparable<Node> {
   public abstract void add(int ex, FormulaToken token);
 
   public abstract void setChildren();
+  
+  public abstract Node[] getChildren();
 
   /**
    * Record this type of function as being used one more time.

### 2016-05-24 src/core/QuantityOfArgumentsNode.java

@@ -58,4 +58,11 @@ public class QuantityOfArgumentsNode extends Node {
   public String toString() {
     return quantity + "";
   }
+
+  @Override
+  public Node[] getChildren() {
+    // TODO Not really needed for the frequency argument...but had
+    //      to add for interface consistency.
+    return children;
+  }
 }

### 2016-05-24 src/viz/treeMaker.js

@@ -30,7 +30,7 @@ var margin = {
     rect_col = "#519393",
     rect_hover = "#284E5E",
 
-    alternate_rect = "#69787F",
+    alternate_rect = "#B1BEC4",
 
     expand_col = "#CFE5A7",
     expand_hover = "#BBCE96",

### 2016-05-24 src/viz/windowMaker.js

@@ -33,14 +33,21 @@ function newWindow(d) {
 
     var table = d3.select(win.document.body)
         .append("table")
-        .style("width", "75%");
+        .style("width", "75%")
+        .style("border", "1px solid black");
 
-    var cols = table.append("colgroup");
-    cols.append("col").attr("span", "1").style("width", "60%");
-    cols.append("col").attr("span", "1").style("width", "30%");
-    cols.append("col").attr("span", "1").style("width", "10%");
+    //var cols = table.append("colgroup");
+    //cols.append("col").attr("span", "1").style("width", "60%");
+    //cols.append("col").attr("span", "1").style("width", "30%");
+    //cols.append("col").attr("span", "1").style("width", "10%");
 
-    var rows = table.selectAll("tr")
+    var headers = table.append("thead").append("tr");
+    headers.style("border-bottom-style", "1px solid black");
+    headers.append("th").html("Formula");
+    headers.append("th").html("File");
+    headers.append("th").html("Sheet and Cell");
+
+    var rows = table.append("tbody").selectAll("tr")
         .data(childrenExamples)
         .enter()
         .append("tr");
@@ -49,7 +56,7 @@ function newWindow(d) {
         var row = d3.select(this);
 
         if (i % 2 == 0)
-            row.attr("color", "#eee");
+            row.style("background-color", "#ddd");
 
         d3.json("examples.php?id=" + d, function(error, data) {
             var formula, file, location;
@@ -64,9 +71,9 @@ function newWindow(d) {
                 file = "<a href=\"localhost:8000/sheets/ENRON/" + file + "#" + location + "\">" + file + "</a>";
             }
 
-            row.append("td").html(formula);
-            row.append("td").html(file);
-            row.append("td").html(location);
+            row.append("td").style("width", "600px").style("word-wrap", "break-word").style("padding", "5px").html(formula.replace(/,/g, ", "));
+            row.append("td").style("width", "200px").style("word-wrap", "break-word").style("padding", "5px").html(file);
+            row.append("td").style("width", "100px").style("word-wrap", "break-word").style("padding", "5px").html(location);
         });
     });
 }

### 2016-08-08 src/core/FormulaToken.java
Viz work, anonymous acks.

@@ -92,10 +92,16 @@ public class FormulaToken {
   }
   
   public String toR1C1String(CellReference cell) {
-    return toR1C1String(this.token, cell);
+    return this.toR1C1String(this.token, cell);
   }
   
-  private String toR1C1String(Ptg tok, CellReference cell) {
+  /**
+   * 
+   * @param tok
+   * @param cell
+   * @return
+   */
+  public String toR1C1String(Ptg tok, CellReference cell) {
     String original = tok.toFormulaString();
     String relative = "";
     
@@ -248,6 +254,10 @@ public class FormulaToken {
   
   public int getOrigLen() {
     return origLen;
+  }
+  
+  public Ptg getPtg() {
+    return token;
   }
   
   public String toString() {

### 2016-08-08 src/core/OperationToken.java

@@ -6,6 +6,8 @@ import java.util.regex.Pattern;
 
 import org.apache.poi.ss.formula.ptg.AttrPtg;
 import org.apache.poi.ss.formula.ptg.OperationPtg;
+import org.apache.poi.ss.formula.ptg.Ptg;
+import org.apache.poi.ss.util.CellReference;
 
 public class OperationToken extends FormulaToken {
   private FormulaToken[] children;          //The arguments of this function.
@@ -25,13 +27,14 @@ public class OperationToken extends FormulaToken {
   public OperationToken(OperationPtg tok, FormulaToken[] args) {
     int len = args.length;
     if (tok.getNumberOfOperands() != len) {
-      throw new UnsupportedOperationException("OperationToken: not enough arguments to the operation.");
+      throw new UnsupportedOperationException("OperationToken: not enough arguments "
+          + "to the operation.");
     }   
     
     this.token = tok;
     
-    String[] sArgs = Arrays.stream(args).map(s -> s.toString()).toArray(String[]::new);
-    this.tokenStr = tok.toFormulaString(sArgs);
+    String[] strArgs = Arrays.stream(args).map(s -> s.toString()).toArray(String[]::new);
+    this.tokenStr = tok.toFormulaString(strArgs);
     this.op = extractOp(tok, len);
         
     addChildren(len, args);
@@ -46,7 +49,8 @@ public class OperationToken extends FormulaToken {
    */
   public OperationToken(AttrPtg tok, FormulaToken... args) {
     if (args.length != 1) {
-      throw new UnsupportedOperationException("OperationToken: not enough arguments to the operation.");
+      throw new UnsupportedOperationException("OperationToken: not enough arguments "
+          + "to the operation.");
     } 
     
     this.token = tok;  
@@ -122,5 +126,31 @@ public class OperationToken extends FormulaToken {
     }
     
     return sb;
+  }
+  
+  /**
+   * 
+   * @param tok
+   * @param cell
+   * @return
+   */
+  public String toR1C1String(Ptg tok, CellReference cell) {
+    String[] strArgs = new String[children.length];
+    
+    for (int i = 0; i < children.length; ++i) {
+      FormulaToken child = children[i];
+      strArgs[i] = child.toR1C1String(cell);
+    }
+    
+    if (tok instanceof OperationPtg) {
+      OperationPtg opTok = (OperationPtg) tok;      
+      return opTok.toFormulaString(strArgs);
[…]

### 2016-08-08 src/core/Parser.java

@@ -31,7 +31,7 @@ import utils.POIUtils;
  * @since 28 July 2016
  */
 public class Parser {
-  private static FormulaToken.Mode mode = FormulaToken.Mode.NO_CHANGE;
+  private static FormulaToken.Mode mode = FormulaToken.Mode.REPLACE;
   public static final XSSFEvaluationWorkbook BLANK 
       = XSSFEvaluationWorkbook.create(POIUtils.getWorkbook("./src/utils/sum.xlsx"));
 

### 2016-08-08 src/scripts/ExceptionCatcher.java

@@ -55,7 +55,7 @@ public class ExceptionCatcher {
       Exception ex = buffer.get(str);
       try {
         write.write(str + " : ");
-        write.write(ex + ", " + ex.getMessage());
+        write.write(ex + ", " + ex.getMessage() + "\n");
       } catch (IOException ex2) {
         System.err.println("Unable to print " + str + ":" + ex.getMessage());
       }

### 2016-08-08 src/scripts/Orchard.java

@@ -17,6 +17,7 @@ import core.FunctionNode;
 
 public class Orchard {
   private final Map<String, FunctionNode> trees = new HashMap<String, FunctionNode>();
+  private int totalFormulae = 0;
   
   /**
    * 
@@ -27,7 +28,10 @@ public class Orchard {
     if (!trees.containsKey(toplevel)) {
       trees.put(toplevel, new FunctionNode(toplevel));
     }
-    trees.get(toplevel).add(trees.size(), formula);  //TODO: NO MORE DB MEANS NO MORE ID
+    trees.get(toplevel).add(trees.size(), formula);  
+    //TODO: NO MORE DB MEANS NO MORE ID
+    
+    ++totalFormulae;
   }
   
   /**
@@ -69,8 +73,9 @@ public class Orchard {
       
       BufferedWriter write;
       try {
-        write = new BufferedWriter(new FileWriter("./src/viz/json/j" + fileFunc + ".json"));
+        write = new BufferedWriter(new FileWriter(outputDirectory + "j" + fileFunc + ".json"));
         write.write(gson.toJson(allFuncs.get(func)));
+        write.flush();
         write.close();
       } catch (IOException ex) {
         System.err.println("Unable to print JSON for " + func);
@@ -82,11 +87,14 @@ public class Orchard {
     Collections.sort(list);
     
     try {
-      BufferedWriter write = new BufferedWriter(new FileWriter("./src/viz/json/index.json"));
+      BufferedWriter write = new BufferedWriter(new FileWriter(outputDirectory + "index.json"));
       write.write(gson.toJson(list));
+      write.flush();
       write.close();
     } catch (IOException ex) {
       System.err.println("Unable to print index file.");
     }
+    
+    System.out.println("Formulae added: " + totalFormulae);
   }
 }

### 2016-08-08 src/scripts/SheetAnalysis.java

@@ -12,6 +12,10 @@ import org.apache.poi.openxml4j.opc.OPCPackage;
 import org.apache.poi.openxml4j.opc.PackageAccess;
 import org.apache.poi.ss.formula.FormulaParseException;
 import org.apache.poi.ss.formula.FormulaParsingWorkbook;
+import org.apache.poi.ss.formula.ptg.ErrPtg;
+import org.apache.poi.ss.formula.ptg.OperandPtg;
+import org.apache.poi.ss.formula.ptg.Ptg;
+import org.apache.poi.ss.formula.ptg.ScalarConstantPtg;
 import org.apache.poi.ss.usermodel.Cell;
 import org.apache.poi.ss.usermodel.Row;
 import org.apache.poi.ss.usermodel.Sheet;
@@ -20,6 +24,7 @@ import org.apache.poi.xssf.usermodel.XSSFEvaluationWorkbook;
 import org.apache.poi.xssf.usermodel.XSSFWorkbook;
 
 import core.FormulaToken;
+import core.OperationToken;
 import core.Parser;
 
 /**
@@ -30,7 +35,7 @@ import core.Parser;
  */
 public class SheetAnalysis {
   private static final String INPUT_DIRECTORY = "./sheets/ENRON/";
-  private static final String OUTPUT_DIRECTORY = "./src/viz/json";
+  private static final String OUTPUT_DIRECTORY = "./src/viz/smalljson/";
   
   /**
    * Ingests spreadsheets and outputs JSON files that describe the frequencies
@@ -67,8 +72,8 @@ public class SheetAnalysis {
     directoriesToAnalyze.add(sheetDirectory);                   
                                                                 
     while (!directoriesToAnalyze.isEmpty()) {
-      
-      for (File file : sheetDirectory.listFiles()) {
+      File directory = directoriesToAnalyze.remove();
+      for (File file : directory.listFiles()) {
         System.out.print(file + ": ");
         if (file.getName().endsWith(".ignore")) {
           continue;
@@ -113,6 +118,8 @@ public class SheetAnalysis {
                   formula = Parser.parseFormula(formulaStr, parse, i);
                   r1c1 = formula.toR1C1String(cellRef);                  
                 } catch (Exception ex) {
+                  System.err.println(formulaStr + " : " + ex.getMessage());
+                  //ex.printStackTrace();
                   catcher.addFormula(formulaStr, ex);
                   continue;
                 }
@@ -123,7 +130,9 @@ public class SheetAnalysis {
[…]

### 2016-08-08 src/viz/treeMaker.js

@@ -118,7 +118,7 @@ function getQueryVariable(variable) {
 /**
  * Initialize the tree with only one level down expanded.
  */
-var src = "json/j" + getQueryVariable("file") + ".json"; //If python server started in tree folder
+var src = "smalljson/j" + getQueryVariable("file") + ".json"; //If python server started in tree folder
 var root;
 d3.json(src, function(error, json) {
     if (error) throw error;

### 2016-08-08 doc/paper.tex
Viz work, anonymous acks.
Unscalability comments -- fixes #145

@@
 	diagnosed that either a spreadsheet author was "totally incompetent, or [the
-	formula was] just something that's weird." Other than these visual cues, value
+	formula was] just something that's weird." Even though the visualization struggles
+	to scale well for this formula, it calls clearly to a problem in the underlying
+	spreadsheets -- awkward formulae make awkward trees. Other than these visual cues, value
 	errors, prefixed with \#s, also appear in the tree, which P4 said could be
@@
 
-	Additionally, because the files in the Enron set had name with the author as a
-	prefix, P2 commented that they could use the tool in a company setting to
+	Additionally, because the Enron files had names with the author as a
+	prefix, P2 commented that companies could use the tool to
 	follow up with repeat offenders. For instance, they first encountered a
@@
 	visualization tool, and some users remarked that a tool which printed a list of
-	errors could suffice just as well for that purpose. However, they also remarked
-	that this visual interface better supports the case when searching for new and
-	previously unknown smells. Because the exploratory design makes no
+	errors could work just as well for that purpose. However, they also said
+	that this visual interface is better when searching for new smells. 
+	Because the exploratory design makes no
 	qualitative judgment and visualizes benign designs with the problematic, it
-	therefore allows for flexible interpretation of what is a smell; that is, a
-	user might not realize a certain design is suboptimal until they see it in the
+	allows for flexible interpretation of what a smell is; that is, a
+	user might not realize a certain design is poor until they see it in the
 	tree and, at the point, find specific examples of where it occurs in the
@@
 	are those of the author(s) and do not necessarily reflect the views of the LAS
-	and/or any agency or entity of the United States Government.
+	and/or any agency or entity of the United States Government. I also thank the
+	anonymous reviewers who advised the direction of this paper.
 

### 2016-08-08 doc/paper.tex
Fixes 146 but bears revision.

@@
 	relationship of formulae as functions and their arguments, which could be yet
-	more functions. By adapting this structure to accommodate a broad range of
+	more functions. By adapting this structure for a broad range of
 	possibilities for nested functions, the branching factor depends alternatively
@@
 	observed as an argument in a function. \par
+
+	Another of our options was to represent the call trees as simple text hierarchies. 
+	Though this might work well for a single, uncomplicated call structure, we did not
+	do this because our tool combined many of these call trees into a more complicated 
+	structure. To capture the different relationships in the tree and to quantify the
+	frequency of arguments, we would need to be more verbose in our description. As such, we
+	decided that visualizing some dimensions was quicker than writing them out. 
+	\par
 

### 2016-08-08 doc/paper.tex
Fixes #147

@@
 	The detection of bad design, however, is certainly not limited to a
-	visualization tool, and some users remarked that a tool which printed a list of
-	errors could work just as well for that purpose. However, they also said
-	that this visual interface is better when searching for new smells. 
-	Because the exploratory design makes no
-	qualitative judgment and visualizes benign designs with the problematic, it
-	allows for flexible interpretation of what a smell is; that is, a
-	user might not realize a certain design is poor until they see it in the
-	tree and, at the point, find specific examples of where it occurs in the
-	spreadsheets.
+	visualization tool. Some users remarked that a tool which printed a list of
+	errors could work just as well for that purpose, and smell checkers can and
+	have been directly built into spreadsheets to point out bad design.
+	However, users also said that this visual interface is better when searching
+	for new smells. Because the exploratory design makes no qualitative judgment
+	and visualizes benign designs with the problematic, it allows for flexible
+	interpretation of what a smell is; that is, a user might not realize a certain
+	design is poor until they see it in the tree and, at the point, find specific
+	examples of where it occurs in the spreadsheets.
 

### 2016-08-09 doc/paper.tex
Sentence level correction. Fixes #156.

@@
 	Fuse~\cite{barik2015fuse}, and the Enron corpus~\cite{hermans2015enron} have
-	already fueled productive research across the field, such as in
-	Hermans'~\cite{hermans2012detecting} and Jansen's~\cite{jansen2015code} search
-	for code smells in spreadsheet environments or Aivaloglou and colleague's work
-	on making a grammar to capture every possible spreadsheet program in
-	Excel~\cite{aivaloglou2015grammar}. Additionally, some research has focused on
-	comparing these collections, as Jansen did in 2015, to discover variation in
-	spreadsheet techniques over time and location~\cite{jansen2015enron}.
+	already fueled productive research across the field, such as in the search for
+	code smells in spreadsheet environments~\cite{hermans2012detecting}~\cite{jansen2015code} or the creation of grammars to capture every possible
+	spreadsheet program in Excel~\cite{aivaloglou2015grammar}. Additionally, some
+	research has focused on comparing these collections, as Jansen did in 2015, to
+	discover variation in spreadsheet techniques over time and
+	location~\cite{jansen2015enron}.
 
@@
 	contrast to the other visualization work, our work focuses on representing functions and how
-	they combine into complex formula, rather than exploring the data structures of any
+	they combine into complex formulae, rather than exploring the data structures of any
 	particular spreadsheet.  \par
@@
 	spreadsheets~\cite{hermans2015enron} or in its comparison with the EUSUS
-	corpus~\cite{jansen2015enron}, quantifies how ofter users employ certain
+	corpus~\cite{jansen2015enron}, quantifies how often users employ certain
 	functions but not how they combine them. Researchers have applied such
@@
 
-		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool will
+		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool is meant
 		to foster understanding by linking pattern to example, it will not try to be
@@
 	true or false, it takes on the value of either the second or third argument,
-	respectively. Or, as the documentation writes out, "IF(Something is True, then
+	respectively. Or, as the documentation writes out, ``IF(Something is True, then
 	do something, otherwise do something
 	else)"\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}.
-Furthermore, the third argument is optional; if left out, the function will return a default "FALSE" value if necessary.
+Furthermore, the third argument is optional; if left out, the function will return a default ``FALSE" value if necessary.
 Examples of this function in practice can be seen in Figure~\ref{fig:ifexample}.
@@
 	the formula and is size according to its frequency relative to the number of
-	times to root function appeared; and the numbered squares
+	times the root function appeared; and the numbered squares
 	\includegraphics{glossary-blue}, which represent the positions of arguments
@@
 	such as = and $\le$, and boolean-returning functions, like ISNA and AND, with
-	simple equality being the most common and some use as ABS being the least seen
-	of everything actually used. From here, we can further explore the common options among these functions.
-	Clicking on the ``=" node will yield two arguments and expanding each of them
+	simple equality being the most common and ABS being the least. From here, we
+	can further explore the common options among these functions. Clicking on the
+	``=" node will yield two arguments and expanding each of them
 	will peer into the range of common values of equality comparison, which Figure
@@
 	What do the images tell us that the text could not? It is not enough to prove
-	that something can be visualized; we must also demonstrate what we can be
-	gained from any particular visualization. As such, we raised a few tasks in the
+	that something can be visualized; we must also demonstrate what we can
+	gain from any particular visualization. As such, we raised a few tasks in the
 	introduction in which we thought the tool could help: detecting bad smells and
@@
 	an IF function were boolean values. This corresponds to designs in which
-	conditions already in a boolean form were then checked against "=TRUE" or
-	"=FALSE", such as in the formula \textit{IF(Formulas!C77=TRUE, "Yes")}, which
+	conditions already in a boolean form were then checked against ``=TRUE" or
+	``=FALSE", such as in the formula \textit{IF(Formulas!C77=TRUE, ``Yes")}, which
 	appears in one of the sheets. Though this practice does not break anything in
@@
 	use, and, as such, they have warranted some extra attention with regards to
-	spreadsheet design. In short, these functions are for "when you need to look in
+	spreadsheet design. In short, these functions are for ``when you need to look in
 	a single row or column and find a value from the same position in a second row
@@
 	help. Because of its design, users can distinguish between forms of the same
-	function, as seen in Figure~\ref{fig:lookups} where the one can explore both
+	function, as seen in Figure~\ref{fig:lookups} where one can explore both
 	the frequency with which the spreadsheet programmers used these different forms
@@
 	Furthermore, these examples are good as well for exploring how it might bridge
-	issues of bad design with education. In a recent study, Hermans, Aivaloglou,
-	and Jansen probed the Enron dataset for uses of VLOOKUP and HLOOKUP
-	specifically. The issue at hand was the optional fourth argument, which
-	requires that rows are sorted lest it return inaccurate results
-	\cite{hermans2015detecting}. For someone seeking to increase awareness of this
-	problem, it first allows them to answer the question of significance -- "How
-	often do spreadsheet programmers use this function, with these particular
+	issues of bad design with education. In a recent study, Hermans and colleagues
+	probed the Enron dataset for uses of VLOOKUP and HLOOKUP
+	specifically~\cite{hermans2015detecting}. The issue at hand was the optional
+	fourth argument, which requires that rows are sorted lest it return inaccurate
+	results. For someone seeking to increase awareness of this problem, it first
+	allows them to answer the question of significance -- ``How often do
+	spreadsheet programmers use this function, with these particular
 	parameters?" Though \toolname does not discern whether neighboring columns are
@@
 	initial design of the SUM tree, as seen in Figure \ref{fig:sum}, they readily
-	diagnosed that either a spreadsheet author was "totally incompetent, or [the
+	diagnosed that either a spreadsheet author was ``totally incompetent, or [the
 	formula was] just something that's weird." Even though the visualization struggles
@@
 	be especially useful since none of the them considered themselves to be experts
-	of Excel, their self-reported proficiencies ranging from "fairly familiar" (P2)
-	to "not extremely familiar" (P4). For example, as P1 explored the VLOOKUP
+	of Excel, their self-reported proficiencies ranging from ``fairly familiar" (P2)
+	to ``not extremely familiar" (P4). For example, as P1 explored the VLOOKUP
 	function, they said they could use the tool to collect more examples than the

### 2016-08-09 doc/paper.tex
Future work revision, combining two paragraphs.

@@
 		of functions and operations to manipulate data, which users can combine into
-		complex formulae. However, anticipating these
-		combinations is difficult, complicating matters for both researchers and
-		practitioners who want to study formulae to improve spreadsheet practices.
-		Therefore, we developed \toolnameend, a tool that analyzes spreadsheet corpora
-		to visualize patterns of function combination as an interactive tree, capable
-		of representing both the most common and most anomalous patterns of formula
-		construction and their contexts in actual workbooks. Using spreadsheets from
-		the Enron corpus, we conduct both a case study and a user study to explore
-		\toolnameposs various applications, particularly those in flexible smell
-		detection and spreadsheet education.
+		complex formulae. However, anticipating these combinations is difficult,
+		complicating matters for both researchers and practitioners who want to study
+		formulae to improve spreadsheet practices. Therefore, we developed
+		\toolnameend, a tool that analyzes spreadsheet corpora to visualize patterns of
+		function combination as an interactive tree, capable of representing both the
+		most common and most anomalous patterns of formula construction and their
+		contexts in actual workbooks. Using spreadsheets from the Enron corpus, we
+		conduct both a case study and a user study to explore \toolnameposs various
+		applications, particularly those in flexible smell detection and spreadsheet
+		education.
 
@@
 	already fueled productive research across the field, such as in the search for
-	code smells in spreadsheet environments~\cite{hermans2012detecting}~\cite{jansen2015code} or the creation of grammars to capture every possible
-	spreadsheet program in Excel~\cite{aivaloglou2015grammar}. Additionally, some
-	research has focused on comparing these collections, as Jansen did in 2015, to
-	discover variation in spreadsheet techniques over time and
-	location~\cite{jansen2015enron}.
+	code smells in spreadsheet
+	environments~\cite{hermans2012detecting}~\cite{jansen2015code} or the creation
+	of grammars to capture every possible spreadsheet program in
+	Excel~\cite{aivaloglou2015grammar}. Additionally, some research has focused on
+	comparing these collections, as Jansen did in 2015, to discover variation in
+	spreadsheet techniques over time and location~\cite{jansen2015enron}.
 
@@
 	are an important part of using spreadsheets efficiently, yet the number of
-	potential combinations between them quickly becomes massive when you consider that
-	there are hundreds of them. Tools, then, that empower people to explore
+	potential combinations between them quickly becomes massive when you consider
+	that there are hundreds of them. Tools, then, that empower people to explore
 	questions about which functions are used together in practice have the
@@
 	functions, like SUM and IF and hundreds more, which are the building blocks of
-	formulae that determine values across a spreadsheet. The tool
-	creates an interactive, exploratory visualization which captures how people
-	combine these functions in a selected collection of spreadsheets, quantifying
-	the broad patterns of function nesting while also being specific enough to find
-	anomalous formulae and link them back to the specific cell in spreadsheets
-	where they originate. \par
+	formulae that determine values across a spreadsheet. The tool creates an
+	interactive, exploratory visualization which captures how people combine these
+	functions in a selected collection of spreadsheets, quantifying the broad
+	patterns of function nesting while also being specific enough to find anomalous
+	formulae and link them back to the specific cell in spreadsheets where they
+	originate. \par
 
@@
 	studies to evaluate how much it could contribute to several different contexts,
-	most notably code smell detection and spreadsheet education. To better understand how people might use \toolnameend, we also conducted a
-	user study to judge how usable and intuitive the tool actually is. This grounds
-	the discussion of its potential uses while also underscoring some of its
-	inherent limitations and setting the way for future extensions and improvements
-	upon the concept.
+	most notably code smell detection and spreadsheet education. To better
+	understand how people might use \toolnameend, we also conducted a user study to
+	judge how usable and intuitive the tool actually is. This grounds the
+	discussion of its potential uses while also underscoring some of its inherent
+	limitations and setting the way for future extensions and improvements upon the
+	concept.
 
@@
 	spreadsheets instead of drawing connections inside the spreadsheet itself. In
-	contrast to the other visualization work, our work focuses on representing functions and how
-	they combine into complex formulae, rather than exploring the data structures of any
-	particular spreadsheet.  \par
+	contrast to the other visualization work, our work focuses on representing
+	functions and how they combine into complex formulae, rather than exploring the
+	data structures of any particular spreadsheet.  \par
 
@@
 
-		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool is meant
-		to foster understanding by linking pattern to example, it will not try to be
-		an explanatory tool that articulates what a complex formula accomplishes. Rather,
-		we will provide the structure and context, and the user	must infer this on their own.
+		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool is
+		meant to foster understanding by linking pattern to example, it will not try
+		to be an explanatory tool that articulates what a complex formula
+		accomplishes. Rather, we will provide the structure and context, and the user
+		must infer this on their own.
 
@@
 	observed, IF can have at most three arguments passed into it, which corresponds
-	with its specifications in the
-	API. \par
+	with its specifications in the API. \par
 
 	Knowing that it is the first argument which contains the conditionals, we click
-	on the square labeled ``1" to explore. To save space, when the tool finds more than 10 unique
-	arguments in a position, it displays only the first
-	ten, with an option to display the rest by clicking the arrow
+	on the square labeled ``1" to explore. To save space, when the tool finds more
+	than 10 unique arguments in a position, it displays only the first ten, with an
+	option to display the rest by clicking the arrow
 	\includegraphics{glossary-arrow}.
@@
 	can further explore the common options among these functions. Clicking on the
-	``=" node will yield two arguments and expanding each of them
-	will peer into the range of common values of equality comparison, which Figure
+	``=" node will yield two arguments and expanding each of them will peer into
+	the range of common values of equality comparison, which Figure
 	\ref{fig:fullpic} shows. \par
@@
 		\item  \vspace{.25cm} \includegraphics{glossary-solidline} - \textbf{Solid
-			lines} represent a function's list of parameters. As such, they
-		connect the function nodes to argument nodes.
+			lines} represent a function's list of parameters. As such, they connect the
+		function nodes to argument nodes.
 
@@
 		can take any number of arguments, up to 255. By default, the tree shows data
-		from AND functions with any number of arguments, but these trees, which have argument nodes of a lighter blue color, can show how AND was used when \textit{only} two arguments
-		were passed into it, or \textit{only} four, and so on. See
-		Figure~\ref{fig:optional} for how the data between tree types differs.
+		from AND functions with any number of arguments, but these trees, which have
+		argument nodes of a lighter blue color, can show how AND was used when
+		\textit{only} two arguments were passed into it, or \textit{only} four, and so
+		on. See Figure~\ref{fig:optional} for how the data between tree types differs.
 	\end{itemize}
@@
 	relationship of formulae as functions and their arguments, which could be yet
-	more functions. By adapting this structure for a broad range of
-	possibilities for nested functions, the branching factor depends alternatively
-	on the number of arguments in a function and the number of possible functions
-	observed as an argument in a function. \par
+	more functions. By adapting this structure for a broad range of possibilities
+	for nested functions, the branching factor depends alternatively on the number
+	of arguments in a function and the number of possible functions observed as an
+	argument in a function. \par
 
-	Another of our options was to represent the call trees as simple text hierarchies. 
-	Though this might work well for a single, uncomplicated call structure, we did not
-	do this because our tool combined many of these call trees into a more complicated 
-	structure. To capture the different relationships in the tree and to quantify the
-	frequency of arguments, we would need to be more verbose in our description. As such, we
-	decided that visualizing some dimensions was quicker than writing them out. 
-	\par
+	Another of our options was to represent the call trees as simple text
+	hierarchies. Though this might work well for a single, uncomplicated call
+	structure, we did not do this because our tool combined many of these call
+	trees into a more complicated structure. To capture the different relationships
+	in the tree and to quantify the frequency of arguments, we would need to be
+	more verbose in our description. As such, we decided that visualizing some
+	dimensions was quicker than writing them out. \par
 
 	Guided by the goals in Section \ref{goals}, we faced a number of decisions in
-	how to visualize the data. Below, we've outlined those that
-	had the largest impact in the values that appear in the tree. \begin{itemize}
+	how to visualize the data. Below, we've outlined those that had the largest
+	impact in the values that appear in the tree. \begin{itemize}
 
@@
 	What do the images tell us that the text could not? It is not enough to prove
-	that something can be visualized; we must also demonstrate what we can
-	gain from any particular visualization. As such, we raised a few tasks in the
+	that something can be visualized; we must also demonstrate what we can gain
+	from any particular visualization. As such, we raised a few tasks in the
 	introduction in which we thought the tool could help: detecting bad smells and
@@
 	emphasize as good or bad, the tool can be used to find strange or suboptimal
-	designs that exist outside these readily visible categories. Consider the second
-	argument of the ``='' operator, already shown expanded in
+	designs that exist outside these readily visible categories. Consider the
+	second argument of the ``='' operator, already shown expanded in
 	Figure~\ref{fig:fullpic}: among the top five argument types for the position in
@@
 	important elements of a good API was the use of code examples to demonstrate
-	function use~\cite{robillard2011field}. Examples in APIs, furthermore, come in a variety of forms: small
-	snippets or tutorials that show only the intended function, sample applications
-	that incorporate the function in a broader context, or even production code
-	that employs the function but was not initially intended to be an illustrative
-	example. Of these categories, \toolname aligns
-	entirely with the last; when a user chooses to explore a particular function
-	node, they will see examples of that formula as it was used in a working
-	environment, with the specifics depending on the dataset the tool is using.
-	\par
+	function use~\cite{robillard2011field}. Examples in APIs, furthermore, come in
+	a variety of forms: small snippets or tutorials that show only the intended
+	function, sample applications that incorporate the function in a broader
+	context, or even production code that employs the function but was not
+	initially intended to be an illustrative example. Of these categories,
+	\toolname aligns entirely with the last; when a user chooses to explore a
+	particular function node, they will see examples of that formula as it was used
+	in a working environment, with the specifics depending on the dataset the tool
+	is using. \par
 
 	Furthermore, Robillard and Deline's study makes the case for examples that show
-	``API usage patterns involving more than one method call"~\cite{robillard2011field}. Examples that show only a single function, they
-	find, are too simple, whereas those demonstrating the interaction of functions
-	will equip users for more complex tasks. \toolname is especially suited for
-	this focus on combination; consider again the question in the walkthrough
-	(Section \ref{sec:walkthrough}), asking which functions and operations are used
-	as conditions in IF. The design of this tool emphasizes the connection, then,
-	between what functions like ISNA and AND return and what IF accepts, and
-	specific examples for any of these combinations are only a click away.
+	``API usage patterns involving more than one method
+	call"~\cite{robillard2011field}. Examples that show only a single function,
+	they find, are too simple, whereas those demonstrating the interaction of
+	functions will equip users for more complex tasks. \toolname is especially
+	suited for this focus on combination; consider again the question in the
+	walkthrough (Section \ref{sec:walkthrough}), asking which functions and
+	operations are used as conditions in IF. The design of this tool emphasizes the
+	connection, then, between what functions like ISNA and AND return and what IF
+	accepts, and specific examples for any of these combinations are only a click
+	away.
 
@@
 	use, and, as such, they have warranted some extra attention with regards to
-	spreadsheet design. In short, these functions are for ``when you need to look in
-	a single row or column and find a value from the same position in a second row
-	or column"\footnote{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}.
-Examples of their use can be found in Figure \ref{fig:lookupexample}, and we will cover each type
-	in more depth to better understand the visualizations for these functions.
+	spreadsheet design. In short, these functions are for ``when you need to look
+	in a single row or column and find a value from the same position in a second
+	row or
+	column"\footnote{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}.
+Examples of their use can be found in Figure \ref{fig:lookupexample}, and we will cover each type in more depth to better understand the visualizations for these functions.
 
-	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookupexample}
-		\caption{Demonstrations of LOOKUP and VLOOKUP} \label{fig:lookupexample}
-	\end{figure}
+	\begin{figure}[h] \centering
+		\includegraphics[width=.5\textwidth]{lookupexample} \caption{Demonstrations of
+			LOOKUP and VLOOKUP} \label{fig:lookupexample} \end{figure}
 
@@
 	the value which you are trying to match in another column. If the formula is in
-	the vector form, that column is the second argument, so in Figure~\ref{fig:lookupexample}, 
-	the formula in cell D2 (\textit{=LOOKUP(3, A2:A6,
-		B2:B6)}) will search for the value of 3 between cells A2 and A6. The value the
-	formula returns then comes from the corresponding cell in the optional third
-	argument's column; since the lookup values matches the value in cell A4, it
-	returns the value from cell B4. The array form of the LOOKUP works the same
-	way, except that the second argument is a two-dimensional table where it
-	matches values in the table's first column and returns values from the last.
+	the vector form, that column is the second argument, so in
+	Figure~\ref{fig:lookupexample}, the formula in cell D2 (\textit{=LOOKUP(3,
+		A2:A6, B2:B6)}) will search for the value of 3 between cells A2 and A6. The
+	value the formula returns then comes from the corresponding cell in the
+	optional third argument's column; since the lookup values matches the value in
+	cell A4, it returns the value from cell B4. The array form of the LOOKUP works
+	the same way, except that the second argument is a two-dimensional table where
+	it matches values in the table's first column and returns values from the last.
 	Also, depending on the dimensions of the lookup table, the function may
@@
 	help. Because of its design, users can distinguish between forms of the same
-	function, as seen in Figure~\ref{fig:lookups} where one can explore both
-	the frequency with which the spreadsheet programmers used these different forms
-	-- three-argument vector form much more than the array form -- and then
-	retrieve examples of every configuration in the dataset. The same goes for the
-	V/HLOOKUP functions, as shown partially in Figure~\ref{fig:vhlookups}.
+	function, as seen in Figure~\ref{fig:lookups} where one can explore both the
+	frequency with which the spreadsheet programmers used these different forms --
+	three-argument vector form much more than the array form -- and then retrieve
+	examples of every configuration in the dataset. The same goes for the V/HLOOKUP
+	functions, as shown partially in Figure~\ref{fig:vhlookups}.
 
@@
 	allows them to answer the question of significance -- ``How often do
-	spreadsheet programmers use this function, with these particular
-	parameters?" Though \toolname does not discern whether neighboring columns are
-	sorted, it can nevertheless guide the educator to several examples in
-	production where this problem surfaces. \par
+	spreadsheet programmers use this function, with these particular parameters?"
+	Though \toolname does not discern whether neighboring columns are sorted, it
+	can nevertheless guide the educator to several examples in production where
+	this problem surfaces. \par
 
@@
 	\section{User Study} \label{sec:userstudy} During development, we conducted a
-	brief, four-participant user study to detect conflicts between our
-	design and the goals in Section \ref{goals}. We designed the study to be
-	exploratory; given trees based in the Enron dataset and at least twenty
-	minutes, we asked the participants to adopt the persona of a consultant
-	evaluating a company's spreadsheet practice, allowing for questions like which
-	functions on which the employees most depended or which sheets or employees
-	presented the most anomalous or dangerous designs. Though we instructed them on
-	how to use the tool and suggested that they visit one of the most populous
-	trees in the set, we put aside any specific tasks or questions and let them
-	choose their own paths. Though interpretation of the phrase ``spreadsheet
-	practice" can certainly vary from participant to participant, we readily
-	accepted this interpretive flexibility since we wanted a range of views and
-	backgrounds despite the persona. We clarified, furthermore, that their
-	observations could be directed either at the quality of the data conveyed by
-	the tool or at the tool's design itself. We present an overview of responses below, with the four participants
-	recorded simply as P1 through P4. \par
+	brief, four-participant user study to detect conflicts between our design and
+	the goals in Section \ref{goals}. We designed the study to be exploratory;
+	given trees based in the Enron dataset and at least twenty minutes, we asked
+	the participants to adopt the persona of a consultant evaluating a company's
+	spreadsheet practice, allowing for questions like which functions on which the
+	employees most depended or which sheets or employees presented the most
+	anomalous or dangerous designs. Though we instructed them on how to use the
+	tool and suggested that they visit one of the most populous trees in the set,
+	we put aside any specific tasks or questions and let them choose their own
+	paths. Though interpretation of the phrase ``spreadsheet practice" can
+	certainly vary from participant to participant, we readily accepted this
+	interpretive flexibility since we wanted a range of views and backgrounds
+	despite the persona. We clarified, furthermore, that their observations could
+	be directed either at the quality of the data conveyed by the tool or at the
+	tool's design itself. We present an overview of responses below, with the four
+	participants recorded simply as P1 through P4. \par
 
@@
 	diagnosed that either a spreadsheet author was ``totally incompetent, or [the
-	formula was] just something that's weird." Even though the visualization struggles
-	to scale well for this formula, it calls clearly to a problem in the underlying
-	spreadsheets -- awkward formulae make awkward trees. Other than these visual cues, value
-	errors, prefixed with \#s, also appear in the tree, which P4 said could be
-	useful for tracking these problems if marked well.
+	formula was] just something that's weird." Even though the visualization
+	struggles to scale well for this formula, it calls clearly to a problem in the
+	underlying spreadsheets -- awkward formulae make awkward trees. Other than
+	these visual cues, value errors, prefixed with \#s, also appear in the tree,
+	which P4 said could be useful for tracking these problems if marked well.
 
-	\begin{wrapfigure}{L}{.25\textwidth}
-		\centering \includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters in SUM, which was a commonly noted smell in the user study} \label{fig:sum} \end{wrapfigure}
+	\begin{wrapfigure}{L}{.25\textwidth} \centering
+		\includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters
+			in SUM, which was a commonly noted smell in the user study} \label{fig:sum}
+	\end{wrapfigure}
 
-	Additionally, because the Enron files had names with the author as a
-	prefix, P2 commented that companies could use the tool to
-	follow up with repeat offenders. For instance, they first encountered a
-	particular author's name when investigating an AVERAGE function with 18
-	distinct arguments for which our participant could not discern any logical
-	order even after opening the source spreadsheet; the same name popped up again
-	as P2 looked at a RATE function relying on several hard-coded values. P2 said
-	that, if they were a manager or project leader, this recurrence was a sign to
-	talk to the author personally and figure out why these problems were there, as
-	to prevent more in the future. They also added that these problems would grow
-	worse if this particular author left the company and no one remained who
-	understood these formulae, a concern that aligns with Hermans' transfer
-	scenarios \cite{hermans2011supporting}.
+	Additionally, because the Enron files had names with the author as a prefix, P2
+	commented that companies could use the tool to follow up with repeat offenders.
+	For instance, they first encountered a particular author's name when
+	investigating an AVERAGE function with 18 distinct arguments for which our
+	participant could not discern any logical order even after opening the source
+	spreadsheet; the same name popped up again as P2 looked at a RATE function
+	relying on several hard-coded values. P2 said that, if they were a manager or
+	project leader, this recurrence was a sign to talk to the author personally and
+	figure out why these problems were there, as to prevent more in the future.
+	They also added that these problems would grow worse if this particular author
+	left the company and no one remained who understood these formulae, a concern
+	that aligns with Hermans' transfer scenarios \cite{hermans2011supporting}.
 
@@
 	errors could work just as well for that purpose, and smell checkers can and
-	have been directly built into spreadsheets to point out bad design.
-	However, users also said that this visual interface is better when searching
-	for new smells. Because the exploratory design makes no qualitative judgment
-	and visualizes benign designs with the problematic, it allows for flexible
+	have been directly built into spreadsheets to point out bad design. However,
+	users also said that this visual interface is better when searching for new
+	smells. Because the exploratory design makes no qualitative judgment and
+	visualizes benign designs with the problematic, it allows for flexible
 	interpretation of what a smell is; that is, a user might not realize a certain
@@
 	be especially useful since none of the them considered themselves to be experts
-	of Excel, their self-reported proficiencies ranging from ``fairly familiar" (P2)
-	to ``not extremely familiar" (P4). For example, as P1 explored the VLOOKUP
+	of Excel, their self-reported proficiencies ranging from ``fairly familiar"
+	(P2) to ``not extremely familiar" (P4). For example, as P1 explored the VLOOKUP
 	function, they said they could use the tool to collect more examples than the
@@
 	Additionally, \toolname offers a simple way of finding examples where certain
-	functions were used together, demonstrated when P4 took special interest in how people
-	frequently used MATCH as the second argument of INDEX or how they used date functions
-	like DATE and MONTH as lookup values in VLOOKUP. Though a standard text-search tool might yield
-	the same results for a function alone, combinations can require more complex
-	text queries, whereas here, the information is already captured in nodes.  \par
+	functions were used together, demonstrated when P4 took special interest in how
+	people frequently used MATCH as the second argument of INDEX or how they used
+	date functions like DATE and MONTH as lookup values in VLOOKUP. Though a
+	standard text-search tool might yield the same results for a function alone,
+	combinations can require more complex text queries, whereas here, the
+	information is already captured in nodes.  \par
 
@@
 	orient their exploration around finance-related functions, potentially limiting
-	their findings or perceived users for the tool. However, one participant also said that,
-	without this essential context, they could not have intelligently explored a dataset
-	in the first place. Comments like these point out the trade-offs of unguided
-	exploration, too: though it might not restrict them to a single purpose, it
-	might, at the same time, not afford them any mindset at all with which to
-	interpret the data. \par
+	their findings or perceived users for the tool. However, one participant also
+	said that, without this essential context, they could not have intelligently
+	explored a dataset in the first place. Comments like these point out the
+	trade-offs of unguided exploration, too: though it might not restrict them to a
+	single purpose, it might, at the same time, not afford them any mindset at all
+	with which to interpret the data. \par
 
@@
 	had fully ensured that the tool could extract all of the useful data from the
-	spreadsheets, meaning some of the counts and patterns in the
-	trees were inaccurate. However, we decided that this was not a pressing
-	concern, being that we were primarily concerned with whether any interesting
-	reports could be made at all, not with whether these reports were 100\%
-	accurate assessments of reality. \par
+	spreadsheets, meaning some of the counts and patterns in the trees were
+	inaccurate. However, we decided that this was not a pressing concern, being
+	that we were primarily concerned with whether any interesting reports could be
+	made at all, not with whether these reports were 100\% accurate assessments of
+	reality. \par
 
@@
 
-	We realized early that some of the popular functions would have thousands of variations in large datasets, and showing all of
-	these variations at once would hopelessly overwhelm the user. We therefore made
-	a number of choices, such as the expansion arrows and the use of generic types
-	in place of specific primitive values, that would reduce the variation to
-	something more manageable.
+	We realized early that some of the popular functions would have thousands of
+	variations in large datasets, and showing all of these variations at once would
+	hopelessly overwhelm the user. We therefore made a number of choices, such as
+	the expansion arrows and the use of generic types in place of specific
+	primitive values, that would reduce the variation to something more manageable.
 
@@
 
-	\subsection{Informative Qualification} As we found in the case study, the tool
-	excels at making formula examples available throughout a tree. 	
-	However, the benefits described in the previous sections imply a hidden
-	complication: if the tool educates through example but does not explicitly
-	distinguish between good design and bad design, how can we be sure that people
-	will not inadvertently learn bad design from it? In the user study, we
-	discussed its use in education and smell detection by bringing up the issues
-	surrounding the LOOKUP functions; this discussion, though, presupposes a
-	distinguishing eye that knew which examples practiced good design and which
-	exhibited the common errors. A beginner might not know the difference.
-	Robillard and Deline, in their study, remarked that good API examples should
-	demonstrate best practices, but, right now, we have no way to assure this with
-	\toolnameend. As with the problems in achieving unbiased exploration, correcting
-	for this danger may entail a reevaluation of design goals.
+	\subsection{Informative Qualification}
 
-	\section{Future Work} For these user and case studies, we relied solely on
-	Enron's spreadsheets. However, Enron's focus on finances and energy represents
-	only one context in which people use spreadsheets. Other corpora, like EUSES
-	and Fuse, draw from other domains and industries, and, as Jansen found in his
-	comparison of spreadsheets Enron and EUSES \cite{jansen2015enron}, different
-	companies rely on different functions. Though the use of a single corpora
-	nevertheless suffices for evaluation, we may yet be able to find more
-	interesting applications and uses for the tool in other types of spreadsheet.
-	\par
+	As we found in the case study, the tool excels at making formula examples
+	available throughout a tree. However, the benefits described in the previous
+	sections imply a hidden complication: if the tool educates through example but
+	does not explicitly distinguish between good design and bad design, how can we
+	be sure that people will not inadvertently learn bad design from it? In the
+	user study, we discussed its use in education and smell detection by bringing
+	up the issues surrounding the LOOKUP functions; this discussion, though,
+	presupposes a distinguishing eye that knew which examples practiced good design
+	and which exhibited the common errors. A beginner might not know the
+	difference. Robillard and Deline, in their study, remarked that good API
+	examples should demonstrate best practices, but, right now, we have no way to
+	assure this with \toolnameend. As with the problems in achieving unbiased
+	exploration, correcting for this danger may entail a reevaluation of design
+	goals.
 
-	Additionally, Excel is only one of many different spreadsheet products
-	available, chosen for this project because of its prevalence. But other
-	spreadsheets, such as Gnumeric\footnote{http://www.gnumeric.org/} or Google
-	Sheets\footnote{https://www.google.com/sheets/about/} represent other
-	approaches to spreadsheet systems. Even within identical domains, there's no
-	guarantee that practices and functions will hold across these varied offerings.
-	This, then, warrants further analysis, in which good visualization might serve
+	\section{Future Work}
+
+	For these user and case studies, we relied solely on one type of spreadsheet (Excel)
+	from one source (Enron), but we have room to develop in either dimension. For sources, 
+	Enron's focus on finances and energy represents one context in
+	which people use spreadsheets, but other corpora, like EUSES and Fuse, draw from
+	other domains and industries. As Jansen found in his comparison of
+	spreadsheets Enron and EUSES \cite{jansen2015enron}, different companies rely
+	on different functions. For other types of spreadsheet, such as Gnumeric\footnote{http://www.gnumeric.org/} or Google
+	Sheets\footnote{https://www.google.com/sheets/about/}, we have no
+	guarantee that practices and functions will hold across these varied programs, even within
+	similar domains. This, then, warrants further analysis, in which good visualization might serve
 	well. \par
@@
 
-	%\begin{wrapfigure}{O}{.25\textwidth} \centering
-	%	\includegraphics[width=.25\textwidth]{longIF} \label{fig:longif} \caption{The
-	%		many possibilities of IF, argument 3, demonstrate the problem of having too
-	%		many options.} \end{wrapfigure}
+	\section{Conclusion}
 
-	\section{Conclusion} This paper presents a tool to support the exploration of
-	function combinations throughout a given spreadsheet dataset. By taking an
-	agnostic approach to design quality, it attempts to convey the dataset's
-	spreadsheet practices as is: the common along with the anomalous, and the
-	well-designed along with the odorous. As seen in the user and case studies,
-	this allows it to take on several potential roles at once, such as an
-	environment for investigating code smells as well as a repository for examples
-	for learning new techniques. \par
+	This paper presents a tool to support the exploration of function combinations
+	throughout a given spreadsheet dataset. By taking an agnostic approach to
+	design quality, it attempts to convey the dataset's spreadsheet practices as
+	is: the common along with the anomalous, and the well-designed along with the
+	odorous. As seen in the user and case studies, this allows it to take on
+	several potential roles at once, such as an environment for investigating code
+	smells as well as a repository for examples for learning new techniques. \par
 
@@
 	% use section* for acknowledgment
-	\section*{Acknowledgment} This material is based upon work supported in whole
-	or in part with funding from the Laboratory for Analytic Sciences (LAS). Any
-	opinions, findings, conclusions, or recommendations expressed in this material
-	are those of the author(s) and do not necessarily reflect the views of the LAS
-	and/or any agency or entity of the United States Government. I also thank the
-	anonymous reviewers who advised the direction of this paper.
+	\section*{Acknowledgment}
+
+	This material is based upon work supported in whole or in part with funding
+	from the Laboratory for Analytic Sciences (LAS). Any opinions, findings,
+	conclusions, or recommendations expressed in this material are those of the
+	author(s) and do not necessarily reflect the views of the LAS and/or any agency
+	or entity of the United States Government. I also thank the anonymous reviewers
+	who advised the direction of this paper.
 

### 2016-08-09 doc/paper.tex
Talk abou how index number breeds confusion. Closes #144.

@@
 
-	\subsection{Study Limitations} Though we did not start the study by telling
+	\subsection{Study Limitations} \label{subsec:studylimitations} Though we did not start the study by telling
 	that the data source came from Enron, two users studied the file names to
@@
 
-	We realized early that some of the popular functions would have thousands of
-	variations in large datasets, and showing all of these variations at once would
-	hopelessly overwhelm the user. We therefore made a number of choices, such as
-	the expansion arrows and the use of generic types in place of specific
-	primitive values, that would reduce the variation to something more manageable.
+	A threat to our goals arises from the problem of too much data,
+	particularly in the popular functions, like SUM and IF. We realized early that
+	these functions would overwhelm the user with options in large datasets, so we
+	included features, such as the expansion arrows and the use of generic types
+	instead of values, that would manage the variation. Nevertheless, P3 remarked
+	that they specifically avoided the most popular functions, anticipating a flood
+	of nodes from which they could salvage nothing interesting. P2 corroborated
+	this by explaining how they gravitated toward exploring specific examples in
+	particular value nodes over navigating the full, crowded tree, but they also
+	said that the tool at its best when it compares either every possibility of an
+	argument side-by-side or nothing on that branch at all. Despite our
+	precautions, balancing the desire to show a lot with the desire not to
+	overwhelm remains a challenge. \par
 
-	Nevertheless, during the user study, P3 remarked that they specifically avoided
-	the most popular functions, anticipating a flood of nodes from which they could
-	salvage nothing interesting. P2 corroborated this by explaining how they
-	gravitated toward exploring specific examples in particular value nodes over
-	navigating the full, crowded tree, but they complicate it further by also
-	saying that the tool at its best when it shows either every possibility of an
-	argument side-by-side (for comparison) or nothing on that branch at all, a
-	balance that is hard to strike with node-dense trees.
-
-	A threat to our goals, then, arises from the problem of too much data,
-	particularly in the popular functions, like SUM and IF. Despite our
-	precautions, balancing the desire to show every single possibility of design
-	with the desire not to overwhelm remains a challenge. \par
+	Some visual cues turned out to be more confusing than helpful, such as
+	the index number on each argument node. As discussed in Section~\ref{subsec:studylimitations},
+	users often mistook it for other features, like total number of arguments in the
+	function. Though we kept this feature present for all studies, future versions
+	of the tool would refine features like this to reduce confusion.
 

### 2016-08-09 src/scripts/SheetAnalysis.java
Commented out exception code.

@@ -67,7 +67,7 @@ public class SheetAnalysis {
     }
     
     Orchard trees = new Orchard();           
-    ExceptionCatcher catcher = new ExceptionCatcher();
+    //ExceptionCatcher catcher = new ExceptionCatcher();
     Queue<File> directoriesToAnalyze = new ArrayDeque<File>();  
     directoriesToAnalyze.add(sheetDirectory);                   
                                                                 
@@ -87,7 +87,7 @@ public class SheetAnalysis {
         try {
           workbook = new XSSFWorkbook(OPCPackage.open(file, PackageAccess.READ));
         } catch (IOException | InvalidFormatException ex) {
-          catcher.addFile(file.getName(), ex);
+          //catcher.addFile(file.getName(), ex);
           continue;
         }
         
@@ -119,8 +119,7 @@ public class SheetAnalysis {
                   r1c1 = formula.toR1C1String(cellRef);                  
                 } catch (Exception ex) {
                   System.err.println(formulaStr + " : " + ex.getMessage());
-                  //ex.printStackTrace();
-                  catcher.addFormula(formulaStr, ex);
+                  //catcher.addFormula(formulaStr, ex);
                   continue;
                 }
                 
@@ -138,21 +137,21 @@ public class SheetAnalysis {
           }
         }
         
-        if (catcher.countFiles() > 10) {
+        /*if (catcher.countFiles() > 10) {
           catcher.flushFiles();
         }
         
         if (catcher.countFormulae() > 1000) {
           catcher.flushFormulae();
-        }
+        }*/
         
         System.out.println();
       } //end for (File file : sheetDirectory.listFiles())
       
     } // end while (directoriesToAnalyze.isEmpty())
     
-    catcher.flushFiles();
-    catcher.flushFormulae();
+    //catcher.flushFiles();
+    //catcher.flushFormulae();
     trees.flush(OUTPUT_DIRECTORY);
   }
   

### 2016-08-09 doc/paper.tex
Participant info. Closes #155

@@
 
-	\section{User Study} \label{sec:userstudy} During development, we conducted a
-	brief, four-participant user study to detect conflicts between our design and
-	the goals in Section \ref{goals}. We designed the study to be exploratory;
-	given trees based in the Enron dataset and at least twenty minutes, we asked
-	the participants to adopt the persona of a consultant evaluating a company's
-	spreadsheet practice, allowing for questions like which functions on which the
-	employees most depended or which sheets or employees presented the most
-	anomalous or dangerous designs. Though we instructed them on how to use the
-	tool and suggested that they visit one of the most populous trees in the set,
-	we put aside any specific tasks or questions and let them choose their own
-	paths. Though interpretation of the phrase ``spreadsheet practice" can
-	certainly vary from participant to participant, we readily accepted this
-	interpretive flexibility since we wanted a range of views and backgrounds
-	despite the persona. We clarified, furthermore, that their observations could
-	be directed either at the quality of the data conveyed by the tool or at the
-	tool's design itself. We present an overview of responses below, with the four
-	participants recorded simply as P1 through P4. \par
+	\section{User Study} \label{sec:userstudy}
+
+	We conducted a brief, exploratory user study during development to detect
+	conflicts between our design and the goals in Section~\ref{goals}. In it, we
+	gave the participants a set of visualizations from the Enron dataset and at
+	least 20 minutes, and we asked them to adopt the persona of a consultant
+	evaluating a company's spreadsheet practice. Through this framing, we intended
+	to open the floor for questions like on which functions employees most depended
+	and which sheets contained the most dangerous formula practice. We clarified,
+	furthermore, that their observations could be directed either at the quality of
+	the data conveyed by the tool or at the tool's design itself. \par
+
+	We had four participants, labeled P1 through P4. Only P4 had no experience with
+	spreadsheets in a professional environment, having used spreadsheets
+	intermittently through university and hobbies. P1 through P3 all had varying
+	levels of experience with spreadsheets in a professional capacity: P1 for 1
+	year, P3 for 3, and P2 for 5. All participants were graduate students at the
+	time of study but with some prior experience in industry, and we presented each
+	with the same broad question about spreadsheet practice. Though interpretation
+	of the phrase ``spreadsheet practice" can certainly vary from participant to
+	participant, we readily accepted this interpretive flexibility since we wanted
+	a range of views and backgrounds despite the persona.
 

### 2016-08-09 doc/paper.tex
Clarify value of spreadsheet novices. Closes #157
Limitation refinement. Closes #158 and closes #148

@@
 	participant, we readily accepted this interpretive flexibility since we wanted
-	a range of views and backgrounds despite the persona.
+	a range of views and backgrounds despite the persona. Furthermore, their
+	differing levels of expertise let us judge the accessibility of the
+	visualization; even if a participant had no formal knowledge of code smells, we
+	found it valuable nevertheless if they could intuitively identify bad design.
 
@@
 
-	\subsection{Study Limitations} \label{subsec:studylimitations} Though we did not start the study by telling
-	that the data source came from Enron, two users studied the file names to
-	deduce its roots in finance, if not Enron itself. Because of these notorious
-	connotations, then, they might have been inclined from this information to
-	orient their exploration around finance-related functions, potentially limiting
-	their findings or perceived users for the tool. However, one participant also
-	said that, without this essential context, they could not have intelligently
-	explored a dataset in the first place. Comments like these point out the
+	\subsection{Study Limitations} \label{subsec:studylimitations}
+
+	In a few ways, these user studies might not fully assess \toolnameposs value.
+	For example, though we did not preface the study by revealing the source of the
+	files, two users studied the file names to deduce its roots in finance, if not
+	Enron itself. Because of these notorious connotations, then, they might have
+	been inclined to orient their exploration around financial functions,
+	potentially restricting their findings. However, one of these participants also
+	said that they could not have intelligently explored a dataset in the first
+	place without this essential context. Comments like these point out the
 	trade-offs of unguided exploration, too: though it might not restrict them to a
@@
 
-	Furthermore, the data which users explored was processed and created before we
-	had fully ensured that the tool could extract all of the useful data from the
-	spreadsheets, meaning some of the counts and patterns in the trees were
-	inaccurate. However, we decided that this was not a pressing concern, being
-	that we were primarily concerned with whether any interesting reports could be
-	made at all, not with whether these reports were 100\% accurate assessments of
-	reality. \par
+	Throughout the study, we noticed that users misunderstood the design
+	and, as such, their early discoveries were inaccurate. For example, P1
+	thought that the numbers on argument nodes as the number of arguments instead
+	of the index of that argument -- that is, clicking on the dark blue
+	``1" would return all the single-argument functions instead of the function's
+	first argument -- and P2 initially took the solid lines to mean
+	different paths in formula construction rather than different arguments of the
+	same function. Though these misunderstandings were useful in pinpointing weak
+	parts of the tool, their presence affected many of the participant's observations before we
+	could clarify, reducing the amount of useful information from these sessions.  \par
 
-	Throughout the study, we noticed that users misunderstood some of the icons
-	and, as such, their early discoveries were inaccurate. For example, P1
-	interpreted the numbers on the argument boxes to mean that all of the box's
-	children had exactly that many arguments -- that is, clicking on the dark blue
-	``1" would return all the single-argument functions instead of the first
-	argument of a function -- and P2 initially took the solid lines to mean
-	different paths in formula construction rather than different arguments of the
-	same function. Though the users naturally did not explicitly report
-	misinterpreting the icons, these misunderstandings became clear in their early
-	evaluations of the spreadsheet practice. Though we clarified the meanings when
-	these misunderstandings became apparent, these events point to a failure in the
-	tool to indicate every function clearly.   \par
+	\section{Tool Limitations}
 
-	\section{Limitations} We began these studies with the intention of evaluating
-	our progress towards the goals in Section \ref{goals}. Working from these
-	results, we noted many places where the tool aligned well or fell short.
+	We began these studies with the intention of evaluating
+	our progress towards the goals in Section~\ref{goals}. Working from these
+	results, we noted many places where \toolname itself aligned well or fell short.
 
-	\subsection{Unbiased Exploration} The first goal -- that of full exploration --
-	is threatened by the presence of certain formulae that the tool does not
-	display, such as those with nonstandard functions. Because the data collection
-	depends on POI's formula parser, it does not allow for any partial parsing of a
-	formula; it either processes a formula perfectly or throws it out. As such, the
-	visualization does not display anything with syntactical errors or third-party
-	functions that POI cannot parse. This poses larger problems, however, when POI
-	does not support the parsing of certain functions, such as EOMONTH, preventing
-	the healthy growth of those trees. \par
+	\subsection{Unbiased Exploration}
 
-	Other than that, we did avoid designing anything that intentionally evaluated
-	formula designs. Nevertheless, \toolname inadvertently emphasizes bad design of
-	certain types, such as all of those in Section~\ref{badsmells} marked by their
-	visual signatures. Even so, our participants found the discovery of bad smell
-	to be the most interesting aspect about it, to the point where they could
-	imagine business scenarios in which micromanagers use it to ensure precise
-	design parameters across a department's spreadsheets! To design in that
+	The goal of \toolname is exploration without bias, gap, or interruption, but 
+	this version does not solve everything. First, \toolname cannot reliably
+	salvage every formula. When a formula arises that the POI parser cannot handle,
+	whether because of typos or third-party functions, the entire formula is lost;
+	\toolname gets either the full formula or nothing at all. Second, while we 
+	hard-coded nothing that explicitly emphasizes bad design, the nature of the
+	visualization draws attention towards certain offenses, like those in
+	Section~\ref{badsmells}. While these may be fairly obvious, however, they 
+	may distract from subtler, more insidious patterns. \par
+
+	Despite this second point, our participants found the discovery of bad smell
+	to be the most interesting aspect about it. To design in that
 	direction, however, would mean a reevaluation of this design goal, since
@@
 
-	A threat to our goals arises from the problem of too much data,
-	particularly in the popular functions, like SUM and IF. We realized early that
-	these functions would overwhelm the user with options in large datasets, so we
-	included features, such as the expansion arrows and the use of generic types
-	instead of values, that would manage the variation. Nevertheless, P3 remarked
-	that they specifically avoided the most popular functions, anticipating a flood
+	We wanted to show everything, but everything overwhelms. We realized that danger
+	early on and included features, such as the expansion arrows and the use of generic types
+	instead of values, that would manage the variation. Nevertheless, P2 and P3 remarked
+	that they often avoided the most popular functions, anticipating a flood
 	of nodes from which they could salvage nothing interesting. P2 corroborated
-	this by explaining how they gravitated toward exploring specific examples in
-	particular value nodes over navigating the full, crowded tree, but they also
-	said that the tool at its best when it compares either every possibility of an
-	argument side-by-side or nothing on that branch at all. Despite our
+	this by explaining how they preferred to explore specific examples in
+	individuals nodes instead of navigating the full, crowded tree. Despite our
 	precautions, balancing the desire to show a lot with the desire not to
@@
 	function. Though we kept this feature present for all studies, future versions
-	of the tool would refine features like this to reduce confusion.
+	of \toolname would refine this design.
 
@@
 	be sure that people will not inadvertently learn bad design from it? In the
-	user study, we discussed its use in education and smell detection by bringing
-	up the issues surrounding the LOOKUP functions; this discussion, though,
-	presupposes a distinguishing eye that knew which examples practiced good design
+	user study, we discussed \toolnameposs use in education and smell detection by bringing
+	up the issues surrounding the LOOKUP functions. This discussion, though,
+	assumes a distinguishing eye that knew which examples practiced good design
 	and which exhibited the common errors. A beginner might not know the

### 2016-08-10 doc/paper.tex
Fixed author block and emails

--- 2016-08-09 doc/paper.tex
@@
 %% by Michael Shell
-%% See:
+%% See:f
 %% http://www.michaelshell.org/
@@
 % The documentation is contained in the cite.sty file itself.
+\usepackage{xspace}
 
@@
 
-\newcommand{\toolname}{Perquimans } \newcommand{\toolnameend}{Perquimans}
+\newcommand{\toolname}{Perquimans\xspace} \newcommand{\toolnameend}{Perquimans}
 \newcommand{\toolnameposs}{Perquimans' }
@@
 	% affiliations
-	\author{ \IEEEauthorblockN{Justin A. Middleton, Emerson Murphy-Hill}
-		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ \{jamiddl2,
-			ermurph3\}@ncsu.edu }}
+	\author{ \IEEEauthorblockN{Justin A. Middleton and Emerson Murphy-Hill}
+		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ jamiddl2@ncsu.edu, emerson@csc.ncsu.edu }}
 
@@
 		of functions and operations to manipulate data, which users can combine into
-		complex formulae. However, anticipating these combinations is difficult,
-		complicating matters for both researchers and practitioners who want to study
-		formulae to improve spreadsheet practices. Therefore, we developed
-		\toolnameend, a tool that analyzes spreadsheet corpora to visualize patterns of
-		function combination as an interactive tree, capable of representing both the
-		most common and most anomalous patterns of formula construction and their
-		contexts in actual workbooks. Using spreadsheets from the Enron corpus, we
-		conduct both a case study and a user study to explore \toolnameposs various
-		applications, particularly those in flexible smell detection and spreadsheet
-		education.
+		complex formulae. However, anticipating these
+		combinations is difficult, complicating matters for both researchers and
+		practitioners who want to study formulae to improve spreadsheet practices.
+		Therefore, we developed \toolnameend, a tool that analyzes spreadsheet corpora
+		to visualize patterns of function combination as an interactive tree, capable
+		of representing both the most common and most anomalous patterns of formula
+		construction and their contexts in actual workbooks. Using spreadsheets from
+		the Enron corpus, we conduct both a case study and a user study to explore
+		\toolnameposs various applications, particularly those in flexible smell
+		detection and spreadsheet education.
 
@@
 	Fuse~\cite{barik2015fuse}, and the Enron corpus~\cite{hermans2015enron} have
-	already fueled productive research across the field, such as in the search for
-	code smells in spreadsheet
-	environments~\cite{hermans2012detecting}~\cite{jansen2015code} or the creation
-	of grammars to capture every possible spreadsheet program in
+	already fueled productive research across the field, such as in
+	Hermans'~\cite{hermans2012detecting} and Jansen's~\cite{jansen2015code} search
+	for code smells in spreadsheet environments or Aivaloglou and colleague's work
+	on making a grammar to capture every possible spreadsheet program in
 	Excel~\cite{aivaloglou2015grammar}. Additionally, some research has focused on
@@
 	are an important part of using spreadsheets efficiently, yet the number of
-	potential combinations between them quickly becomes massive when you consider
-	that there are hundreds of them. Tools, then, that empower people to explore
+	potential combinations between them quickly becomes massive when you consider that
+	there are hundreds of them. Tools, then, that empower people to explore
 	questions about which functions are used together in practice have the
@@
 
-	This paper contributes such a tool, \toolnameend, that attempts to fulfill this
+	This paper contributes such a tool, \toolname, that attempts to fulfill this
 	need for better exploration by building on the aforementioned spreadsheet
@@
 	functions, like SUM and IF and hundreds more, which are the building blocks of
-	formulae that determine values across a spreadsheet. The tool creates an
-	interactive, exploratory visualization which captures how people combine these
-	functions in a selected collection of spreadsheets, quantifying the broad
-	patterns of function nesting while also being specific enough to find anomalous
-	formulae and link them back to the specific cell in spreadsheets where they
-	originate. \par
+	formula and programs that determine values across a spreadsheet. The tool
+	creates an interactive, exploratory visualization which captures how people
+	combine these functions in a selected collection of spreadsheets, quantifying
+	the broad patterns of function nesting while also being specific enough to find
+	anomalous formulae and link them back to the specific cell in spreadsheets
+	where they originate. \par
 
@@
 	studies to evaluate how much it could contribute to several different contexts,
-	most notably code smell detection and spreadsheet education. To better
-	understand how people might use \toolnameend, we also conducted a user study to
-	judge how usable and intuitive the tool actually is. This grounds the
-	discussion of its potential uses while also underscoring some of its inherent
-	limitations and setting the way for future extensions and improvements upon the
-	concept.
+	most notably code smell detection and spreadsheet education. To better understand how people might use \toolnameend, we also conducted a
+	user study to judge how usable and intuitive the tool actually is. This grounds
+	the discussion of its potential uses while also underscoring some of its
+	inherent limitations and setting the way for future extensions and improvements
+	upon the concept.
 
@@
 	spreadsheets instead of drawing connections inside the spreadsheet itself. In
-	contrast to the other visualization work, our work focuses on representing
-	functions and how they combine into complex formulae, rather than exploring the
-	data structures of any particular spreadsheet.  \par
+	contrast to Hermans' work, our work focuses on representing functions and how
+	they comprise complex formula, rather than exploring the data structures of any
+	particular spreadsheet.  \par
 
@@
 For example, Hermans, leveraging her work with the aforementioned dataflow diagrams, has worked with assessing common inter-worksheet smells, such as feature envy and inappropriate intimacy, wherein references between worksheets (rather than cells) in a file suggest a problem~\cite{hermans2012detectinginter}.
-Other tools, like Badame's Excel refactoring~\cite{badame2012refactoring}, are concerned more with understanding the formula in service of changing them.
+Other tools, like Badam's Excel refactoring~\cite{badame2012refactoring}, are concerned more with understanding the formula in service of changing them.
 However, these studies define standards of poor design and orient their searches around them.
@@
 	spreadsheets~\cite{hermans2015enron} or in its comparison with the EUSUS
-	corpus~\cite{jansen2015enron}, quantifies how often users employ certain
+	corpus~\cite{jansen2015enron}, quantify how ofter users employ certain
 	functions but not how they combine them. Researchers have applied such
@@
 	\subsection{Design Goals} \label{goals} In visualizing the spreadsheet data, we
-	set out a few core goals for what the tool should accomplish. Furthermore, with
+	follow a few core goals for what the tool should accomplish. Furthermore, with
 	these goals, we also considered the likely challenges of achieving those goals
@@
 		\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
-		especially, we anticipate that we'll have to show a lot of related data at
+		especially, we anticipated that we'd have to show a lot of related data at
 		once. Though everything should be accessible in accordance with Goal 1, we
@@
 
-		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool is
-		meant to foster understanding by linking pattern to example, it will not try
-		to be an explanatory tool that articulates what a complex formula
-		accomplishes. Rather, we will provide the structure and context, and the user
-		must infer this on their own.
+		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool will
+		to foster understanding by linking pattern to example, it will not try to be
+		an explanatory tool that articulates what a complex formula accomplishes. Rather,
+		we will provide the structure and context, and the user	must infer this on their own.
 
@@
 	true or false, it takes on the value of either the second or third argument,
-	respectively. Or, as the documentation writes out, ``IF(Something is True, then
+	respectively. Or, as the documentation writes out, "IF(Something is True, then
 	do something, otherwise do something
 	else)"\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}.
-Furthermore, the third argument is optional; if left out, the function will return a default ``FALSE" value if necessary.
+Furthermore, the third argument is optional; if left out, the function will return a default "FALSE" value if necessary.
 Examples of this function in practice can be seen in Figure~\ref{fig:ifexample}.
@@
 	the formula and is size according to its frequency relative to the number of
-	times the root function appeared; and the numbered squares
+	times to root function appeared; and the numbered squares
 	\includegraphics{glossary-blue}, which represent the positions of arguments
@@
 	observed, IF can have at most three arguments passed into it, which corresponds
-	with its specifications in the API. \par
+	with its specifications in the
+	API\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}. \par
 
 	Knowing that it is the first argument which contains the conditionals, we click
-	on the square labeled ``1" to explore. To save space, when the tool finds more
-	than 10 unique arguments in a position, it displays only the first ten, with an
-	option to display the rest by clicking the arrow
+	on the square labeled ``1" to explore. To save space, when more than 10 unique
+	arguments were found in a position, the tool displays only the first
+	ten, with an option to display the rest by clicking the arrow
 	\includegraphics{glossary-arrow}.
@@
 	such as = and $\le$, and boolean-returning functions, like ISNA and AND, with
-	simple equality being the most common and ABS being the least. From here, we
-	can further explore the common options among these functions. Clicking on the
-	``=" node will yield two arguments and expanding each of them will peer into
-	the range of common values of equality comparison, which Figure
+	simple equality being the most common and some use as ABS being the least seen
+	of everything actually used. From here, we can further explore the common options among these functions.
+	Clicking on the ``=" node will yield two arguments and expanding each of them
+	will peer into the range of common values of equality comparison, which Figure
 	\ref{fig:fullpic} shows. \par
@@
 		\item  \vspace{.25cm} \includegraphics{glossary-solidline} - \textbf{Solid
-			lines} represent a function's list of parameters. As such, they connect the
-		function nodes to argument nodes.
+			lines} represent a function's acceptance of its parameters. As such, they
+		connect the function nodes to argument nodes.
 
@@
 		can take any number of arguments, up to 255. By default, the tree shows data
-		from AND functions with any number of arguments, but these trees, which have
-		argument nodes of a lighter blue color, can show how AND was used when
-		\textit{only} two arguments were passed into it, or \textit{only} four, and so
-		on. See Figure~\ref{fig:optional} for how the data between tree types differs.
+		from AND functions with any number of argument, but these trees, marked with a
+		darker blue color, can show how AND was used when \textit{only} two arguments
+		were passed into it, or \textit{only} four, and so on. See
+		Figure~\ref{fig:optional} for how the data between tree types differs.
 	\end{itemize}
@@
 		for its accessibility: given the JSON, the visualization can be simply
-		embedded into a webpage accessible through a browser. \end{itemize} A
+		embedded into a webpage accessible through a browser. \end{itemize} The code and a
 	demonstration of \toolname can be found at
@@
 	relationship of formulae as functions and their arguments, which could be yet
-	more functions. By adapting this structure for a broad range of possibilities
-	for nested functions, the branching factor depends alternatively on the number
-	of arguments in a function and the number of possible functions observed as an
-	argument in a function. \par
-
-	Another of our options was to represent the call trees as simple text
-	hierarchies. Though this might work well for a single, uncomplicated call
-	structure, we did not do this because our tool combined many of these call
-	trees into a more complicated structure. To capture the different relationships
-	in the tree and to quantify the frequency of arguments, we would need to be
-	more verbose in our description. As such, we decided that visualizing some
-	dimensions was quicker than writing them out. \par
+	more functions. By adapting this structure to accommodate a broad range of
+	possibilities for nested functions, the branching factor depends alternatively
+	on the number of arguments in a function and the number of possible functions
+	observed as an argument in a function. \par
 
 	Guided by the goals in Section \ref{goals}, we faced a number of decisions in
-	how to visualize the data. Below, we've outlined those that had the largest
-	impact in the values that appear in the tree. \begin{itemize}
+	how to visualize the data. Below, we've outlined those that
+	had the largest impact in the values that appear in the tree. \begin{itemize}
 
@@
 	What do the images tell us that the text could not? It is not enough to prove
-	that something can be visualized; we must also demonstrate what we can gain
-	from any particular visualization. As such, we raised a few tasks in the
+	that something can be visualized; we must also demonstrate what we can be
+	gained from any particular visualization. As such, we raised a few tasks in the
 	introduction in which we thought the tool could help: detecting bad smells and
@@
 	emphasize as good or bad, the tool can be used to find strange or suboptimal
-	designs that exist outside these readily visible categories. Consider the
-	second argument of the ``='' operator, already shown expanded in
+	designs that exist outside these obvious categories. Consider the second
+	argument of the ``='' operator, already shown expanded in
 	Figure~\ref{fig:fullpic}: among the top five argument types for the position in
 	an IF function were boolean values. This corresponds to designs in which
-	conditions already in a boolean form were then checked against ``=TRUE" or
-	``=FALSE", such as in the formula \textit{IF(Formulas!C77=TRUE, ``Yes")}, which
+	conditions already in a boolean form were then checked against "=TRUE" or
+	"=FALSE", such as in the formula \textit{IF(Formulas!C77=TRUE, "Yes")}, which
 	appears in one of the sheets. Though this practice does not break anything in
@@
 	important elements of a good API was the use of code examples to demonstrate
-	function use~\cite{robillard2011field}. Examples in APIs, furthermore, come in
-	a variety of forms: small snippets or tutorials that show only the intended
-	function, sample applications that incorporate the function in a broader
-	context, or even production code that employs the function but was not
-	initially intended to be an illustrative example. Of these categories,
-	\toolname aligns entirely with the last; when a user chooses to explore a
-	particular function node, they will see examples of that formula as it was used
-	in a working environment, with the specifics depending on the dataset the tool
-	is using. \par
+	function use~\cite{robillard2011field}. Examples in APIs, furthermore, come in a variety of forms: small
+	snippets or tutorials that show only the intended function, sample applications
+	that incorporate the function in a broader context, or even production code
+	that employs the function but was not initially intended to be an illustrative
+	example. Of these categories, \toolname aligns
+	entirely with the last; when a user chooses to explore a particular function
+	node, they will see examples of that formula as it was used in a working
+	environment, with the specifics depending on the dataset the tool is using.
+	\par
 
 	Furthermore, Robillard and Deline's study makes the case for examples that show
-	``API usage patterns involving more than one method
-	call"~\cite{robillard2011field}. Examples that show only a single function,
-	they find, are too simple, whereas those demonstrating the interaction of
-	functions will equip users for more complex tasks. \toolname is especially
-	suited for this focus on combination; consider again the question in the
-	walkthrough (Section \ref{sec:walkthrough}), asking which functions and
-	operations are used as conditions in IF. The design of this tool emphasizes the
-	connection, then, between what functions like ISNA and AND return and what IF
-	accepts, and specific examples for any of these combinations are only a click
-	away.
+	``API usage patterns involving more than one method call"~\cite{robillard2011field}. Examples that show only a single function, they
+	find, are too simple, whereas those demonstrating the interaction of functions
+	will equip users for more complex tasks. \toolname is especially suited for
+	this focus on combination; consider again the question in the walkthrough
+	(Section \ref{sec:walkthrough}), asking which functions and operations are used
+	as conditions in IF. The design of this tool emphasizes the connection, then,
+	between what functions like ISNA and AND return and what IF accepts, and
+	specific examples for any of these combinations are only a click away.
 
@@
 	use, and, as such, they have warranted some extra attention with regards to
-	spreadsheet design. In short, these functions are for ``when you need to look
-	in a single row or column and find a value from the same position in a second
-	row or
-	column"\footnote{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}.
-Examples of their use can be found in Figure \ref{fig:lookupexample}, and we will cover each type in more depth to better understand the visualizations for these functions.
+	spreadsheet design. In short, these functions are for "when you need to look in
+	a single row or column and find a value from the same position in a second row
+	or column"\footnote{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}.
+Examples of their use can be found in Figure \ref{fig:lookupexample}, and we will cover each type
+	in more depth to better understand the visualizations for these functions.
 
-	\begin{figure}[h] \centering
-		\includegraphics[width=.5\textwidth]{lookupexample} \caption{Demonstrations of
-			LOOKUP and VLOOKUP} \label{fig:lookupexample} \end{figure}
+	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookupexample}
+		\caption{Demonstrations of LOOKUP and VLOOKUP} \label{fig:lookupexample}
+	\end{figure}
 
@@
 	the value which you are trying to match in another column. If the formula is in
-	the vector form, that column is the second argument, so in
-	Figure~\ref{fig:lookupexample}, the formula in cell D2 (\textit{=LOOKUP(3,
-		A2:A6, B2:B6)}) will search for the value of 3 between cells A2 and A6. The
-	value the formula returns then comes from the corresponding cell in the
-	optional third argument's column; since the lookup values matches the value in
-	cell A4, it returns the value from cell B4. The array form of the LOOKUP works
-	the same way, except that the second argument is a two-dimensional table where
-	it matches values in the table's first column and returns values from the last.
+	the vector form, that column is the second argument, so in Figure~\ref{fig:lookupexample}, 
+	the formula in cell D2 (\textit{=LOOKUP(3, A2:A6,
+		B2:B6)}) will search for the value of 3 between cells A2 and A6. The value the
+	formula returns then comes from the corresponding cell in the optional third
+	argument's column; since the lookup values matches the value in cell A4, it
+	returns the value from cell B4. The array form of the LOOKUP works the same
+	way, except that the second argument is a two-dimensional table where it
+	matches values in the table's first column and returns values from the last.
 	Also, depending on the dimensions of the lookup table, the function may
@@
 	help. Because of its design, users can distinguish between forms of the same
-	function, as seen in Figure~\ref{fig:lookups} where one can explore both the
-	frequency with which the spreadsheet programmers used these different forms --
-	three-argument vector form much more than the array form -- and then retrieve
-	examples of every configuration in the dataset. The same goes for the V/HLOOKUP
-	functions, as shown partially in Figure~\ref{fig:vhlookups}.
+	function, as seen in Figure~\ref{fig:lookups} where the one can explore both
+	the frequency with which the spreadsheet programmers used these different forms
+	-- three-argument vector form much more than the array form -- and then
+	retrieve examples of every configuration in the dataset. The same goes for the
+	V/HLOOKUP functions, as shown partially in Figure~\ref{fig:vhlookups}.
 
@@
 	Furthermore, these examples are good as well for exploring how it might bridge
-	issues of bad design with education. In a recent study, Hermans and colleagues
-	probed the Enron dataset for uses of VLOOKUP and HLOOKUP
-	specifically~\cite{hermans2015detecting}. The issue at hand was the optional
-	fourth argument, which requires that rows are sorted lest it return inaccurate
-	results. For someone seeking to increase awareness of this problem, it first
-	allows them to answer the question of significance -- ``How often do
-	spreadsheet programmers use this function, with these particular parameters?"
-	Though \toolname does not discern whether neighboring columns are sorted, it
-	can nevertheless guide the educator to several examples in production where
-	this problem surfaces. \par
+	issues of bad design with education. In a recent study, Hermans, Aivaloglou,
+	and Jansen probed the Enron dataset for uses of VLOOKUP and HLOOKUP
+	specifically. The issue at hand was the optional fourth argument, which
+	requires that rows are sorted lest it return inaccurate results
+	\cite{hermans2015detecting}. For someone seeking to increase awareness of this
+	problem, it first allows them to answer the question of significance -- "How
+	often do spreadsheet programmers use this function, with these particular
+	parameters?" Though \toolname does not discern whether neighboring columns are
+	sorted, it can nevertheless guide the educator to several examples in
+	production where this problem surfaces. \par
 
@@
 	\section{User Study} \label{sec:userstudy} During development, we conducted a
-	brief, four-participant user study to detect conflicts between our design and
-	the goals in Section \ref{goals}. We designed the study to be exploratory;
-	given trees based in the Enron dataset and at least twenty minutes, we asked
-	the participants to adopt the persona of a consultant evaluating a company's
-	spreadsheet practice, allowing for questions like which functions on which the
-	employees most depended or which sheets or employees presented the most
-	anomalous or dangerous designs. Though we instructed them on how to use the
-	tool and suggested that they visit one of the most populous trees in the set,
-	we put aside any specific tasks or questions and let them choose their own
-	paths. Though interpretation of the phrase ``spreadsheet practice" can
-	certainly vary from participant to participant, we readily accepted this
-	interpretive flexibility since we wanted a range of views and backgrounds
-	despite the persona. We clarified, furthermore, that their observations could
-	be directed either at the quality of the data conveyed by the tool or at the
-	tool's design itself. We present an overview of responses below, with the four
-	participants recorded simply as P1 through P4. \par
+	brief, four-participant user study to detect conflicts between our
+	design and the goals in Section \ref{goals}. We designed the study to be
+	exploratory; given trees based in the Enron dataset and at least twenty
+	minutes, we asked the participants to adopt the persona of a consultant
+	evaluating a company's spreadsheet practice, allowing for questions like which
+	functions on which the employees most depended or which sheets or employees
+	presented the most anomalous or dangerous designs. Though we instructed them on
+	how to use the tool and suggested that they visit one of the most populous
+	trees in the set, we put aside any specific tasks or questions and let them
+	choose their own paths. Though interpretation of the phrase ``spreadsheet
+	practice" can certainly vary from participant to participant, we readily
+	accepted this interpretive flexibility since we wanted a range of views and
+	backgrounds despite the persona. We clarified, furthermore, that their
+	observations could be directed either at the quality of the data conveyed by
+	the tool or at the tool's design itself. We present an overview of responses below, with the four participants
+	recorded simply as P1 through P4. \par
 
@@
 	initial design of the SUM tree, as seen in Figure \ref{fig:sum}, they readily
-	diagnosed that either a spreadsheet author was ``totally incompetent, or [the
-	formula was] just something that's weird." Even though the visualization
-	struggles to scale well for this formula, it calls clearly to a problem in the
-	underlying spreadsheets -- awkward formulae make awkward trees. Other than
-	these visual cues, value errors, prefixed with \#s, also appear in the tree,
-	which P4 said could be useful for tracking these problems if marked well.
+	diagnosed that either a spreadsheet author was "totally incompetent, or [the
+	formula was] just something that's weird." Other than these visual cues, value
+	errors, prefixed with \#s, also appear in the tree, which P4 said could be
+	useful for tracking these problems if marked well.
 
-	\begin{wrapfigure}{L}{.25\textwidth} \centering
-		\includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters
-			in SUM, which was a commonly noted smell in the user study} \label{fig:sum}
-	\end{wrapfigure}
+	\begin{wrapfigure}{O}{.25\textwidth}
+		\centering \includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters in SUM.
+			Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}
 
-	Additionally, because the Enron files had names with the author as a prefix, P2
-	commented that companies could use the tool to follow up with repeat offenders.
-	For instance, they first encountered a particular author's name when
-	investigating an AVERAGE function with 18 distinct arguments for which our
-	participant could not discern any logical order even after opening the source
-	spreadsheet; the same name popped up again as P2 looked at a RATE function
-	relying on several hard-coded values. P2 said that, if they were a manager or
-	project leader, this recurrence was a sign to talk to the author personally and
-	figure out why these problems were there, as to prevent more in the future.
-	They also added that these problems would grow worse if this particular author
-	left the company and no one remained who understood these formulae, a concern
-	that aligns with Hermans' transfer scenarios \cite{hermans2011supporting}.
+	Additionally, because the files in the Enron set had name with the author as a
+	prefix, P2 commented that they could use the tool in a company setting to
+	follow up with repeat offenders. For instance, they first encountered a
+	particular author's name when investigating an AVERAGE function with 18
+	distinct arguments for which our participant could not discern any logical
+	order, even after opening the source spreadsheet; the same name popped up again
+	as P2 looked at a RATE function relying on several hard-coded values. P2 said
+	that, if they were a manager or project leader, this recurrence was a sign to
+	talk to the author personally and figure out why these problems were there, as
+	to prevent more in the future. They also added that these problems would grow
+	worse if this particular author left the company and no one remained who
+	understood these formulae, a concern that aligns with Hermans' transfer
+	scenarios \cite{hermans2011supporting}.
 
 	The detection of bad design, however, is certainly not limited to a
-	visualization tool. Some users remarked that a tool which printed a list of
-	errors could work just as well for that purpose, and smell checkers can and
-	have been directly built into spreadsheets to point out bad design. However,
-	users also said that this visual interface is better when searching for new
-	smells. Because the exploratory design makes no qualitative judgment and
-	visualizes benign designs with the problematic, it allows for flexible
-	interpretation of what a smell is; that is, a user might not realize a certain
-	design is poor until they see it in the tree and, at the point, find specific
-	examples of where it occurs in the spreadsheets.
+	visualization tool, and some users remarked that a tool which printed a list of
+	errors could suffice just as well for that purpose. However, they also remarked
+	that this visual interface better supports the case when searching for new and
+	previously unknown smells. Because the exploratory design makes no
+	qualitative judgment and visualizes benign designs with the problematic, it
+	therefore allows for flexible interpretation of what is a smell; that is, a
+	user might not realize a certain design is suboptimal until they see it in the
+	tree and, at the point, find specific examples of where it occurs in the
+	spreadsheets.
 
@@
 	be especially useful since none of the them considered themselves to be experts
-	of Excel, their self-reported proficiencies ranging from ``fairly familiar"
-	(P2) to ``not extremely familiar" (P4). For example, as P1 explored the VLOOKUP
+	of Excel, their self-reported proficiencies ranging from "fairly familiar" (P2)
+	to "not extremely familiar" (P4). For example, as P1 explored the VLOOKUP
 	function, they said they could use the tool to collect more examples than the
@@
 	Additionally, \toolname offers a simple way of finding examples where certain
-	functions were used together, demonstrated when P4 took special interest in how
-	people frequently used MATCH as the second argument of INDEX or how they used
-	date functions like DATE and MONTH as lookup values in VLOOKUP. Though a
-	standard text-search tool might yield the same results for a function alone,
-	combinations can require more complex text queries, whereas here, the
-	information is already captured in nodes.  \par
+	functions were used together, demonstrated when P4 took special interest in how people
+	frequently used MATCH as the second argument of INDEX or how they used date functions
+	like DATE and MONTH as lookup values in VLOOKUP. Though a standard text-search tool might yield
+	the same results for a function alone, combinations can require more complex
+	text queries, whereas here, the information is already captured in nodes.  \par
 
@@
 
-	\subsection{Study Limitations} \label{subsec:studylimitations} Though we did not start the study by telling
+	\subsection{Study Limitations} Though we did not start the study by telling
 	that the data source came from Enron, two users studied the file names to
@@
 	orient their exploration around finance-related functions, potentially limiting
-	their findings or perceived users for the tool. However, one participant also
-	said that, without this essential context, they could not have intelligently
-	explored a dataset in the first place. Comments like these point out the
-	trade-offs of unguided exploration, too: though it might not restrict them to a
-	single purpose, it might, at the same time, not afford them any mindset at all
-	with which to interpret the data. \par
+	their findings or perceived users for the tool. However, one participant also said that,
+	without this essential context, they could not have intelligently explored a dataset
+	in the first place. Comments like these point out the trade-offs of unguided
+	exploration, too: though it might not restrict them to a single purpose, it
+	might, at the same time, not afford them any mindset at all with which to
+	interpret the data. \par
 
@@
 	had fully ensured that the tool could extract all of the useful data from the 
-	spreadsheets, meaning some of the counts and patterns in the trees were
-	inaccurate. However, we decided that this was not a pressing concern, being
-	that we were primarily concerned with whether any interesting reports could be
-	made at all, not with whether these reports were 100\% accurate assessments of
-	reality. \par
+	spreadsheets, meaning some of the counts and patterns in the
+	trees were inaccurate. However, we decided that this was not a pressing
+	concern, being that we were primarily concerned with whether any interesting
+	reports could be made at all, not with whether these reports were 100\%
+	accurate assessments of reality. \par
 
@@
 
-	A threat to our goals arises from the problem of too much data,
-	particularly in the popular functions, like SUM and IF. We realized early that
-	these functions would overwhelm the user with options in large datasets, so we
-	included features, such as the expansion arrows and the use of generic types
-	instead of values, that would manage the variation. Nevertheless, P3 remarked
-	that they specifically avoided the most popular functions, anticipating a flood
-	of nodes from which they could salvage nothing interesting. P2 corroborated
-	this by explaining how they gravitated toward exploring specific examples in
-	particular value nodes over navigating the full, crowded tree, but they also
-	said that the tool at its best when it compares either every possibility of an
-	argument side-by-side or nothing on that branch at all. Despite our
-	precautions, balancing the desire to show a lot with the desire not to
-	overwhelm remains a challenge. \par
+	We realized early that some of the popular functions would have thousands of variations in large datasets, and showing all of
+	these variations at once would hopelessly overwhelm the user. We therefore made
+	a number of choices, such as the expansion arrows and the use of generic types
+	in place of specific primitive values, that would reduce the variation to
+	something more manageable.
 
-	Some visual cues turned out to be more confusing than helpful, such as
-	the index number on each argument node. As discussed in Section~\ref{subsec:studylimitations},
-	users often mistook it for other features, like total number of arguments in the
-	function. Though we kept this feature present for all studies, future versions
-	of the tool would refine features like this to reduce confusion.
+	Nevertheless, during the user study, P3 remarked that they specifically avoided
+	the most popular functions, anticipating a flood of nodes from which they could
+	salvage nothing interesting. P2 corroborated this by explaining how they
+	gravitated toward exploring specific examples in particular value nodes over
+	navigating the full, crowded tree, but they complicate it further by also
+	saying that the tool at its best when it shows either every possibility of an
+	argument side-by-side (for comparison) or nothing on that branch at all, a
+	balance that is hard to strike with node-dense trees.
 
-	\subsection{Informative Qualification}
+	A threat to our goals, then, arises from the problem of too much data,
+	particularly in the popular functions, like SUM and IF. Despite our
+	precautions, balancing the desire to show every single possibility of design
+	with the desire not to overwhelm remains a challenge. \par
 
-	As we found in the case study, the tool excels at making formula examples
-	available throughout a tree. However, the benefits described in the previous
-	sections imply a hidden complication: if the tool educates through example but
-	does not explicitly distinguish between good design and bad design, how can we
-	be sure that people will not inadvertently learn bad design from it? In the
-	user study, we discussed its use in education and smell detection by bringing
-	up the issues surrounding the LOOKUP functions; this discussion, though,
-	presupposes a distinguishing eye that knew which examples practiced good design
-	and which exhibited the common errors. A beginner might not know the
-	difference. Robillard and Deline, in their study, remarked that good API
-	examples should demonstrate best practices, but, right now, we have no way to
-	assure this with \toolnameend. As with the problems in achieving unbiased
-	exploration, correcting for this danger may entail a reevaluation of design
-	goals.
+	\subsection{Informative Qualification} As we found in the case study, the tool
+	excels at making formula examples available throughout a tree. 	
+	However, the benefits described in the previous sections imply a hidden
+	complication: if the tool educates through example but does not explicitly
+	distinguish between good design and bad design, how can we be sure that people
+	will not inadvertently learn bad design from it? In the user study, we
+	discussed its use in education and smell detection by bringing up the issues
+	surrounding the LOOKUP functions; this discussion, though, presupposes a
+	distinguishing eye that knew which examples practiced good design and which
+	exhibited the common errors. A beginner might not know the difference.
+	Robillard and Deline, in their study, remarked that good API examples should
+	demonstrate best practices, but, right now, we have no way to assure this with
+	\toolname. As with the problems in achieving unbiased exploration, correcting
+	for this danger may entail a reevaluation of design goals.
 
-	\section{Future Work}
+	\section{Future Work} For these user and case studies, we relied solely on
+	Enron's spreadsheets. However, Enron's focus on finances and energy represents
+	only one context in which people use spreadsheets. Other corpora, like EUSES
+	and Fuse, draw from other domains and industries, and, as Jansen found in his
+	comparison of spreadsheets Enron and EUSES \cite{jansen2015enron}, different
+	companies rely on different functions. Though the use of a single corpora
+	nevertheless suffices for evaluation, we may yet be able to find more
+	interesting applications and uses for the tool in other types of spreadsheet.
+	\par
 
-	For these user and case studies, we relied solely on one type of spreadsheet (Excel)
-	from one source (Enron), but we have room to develop in either dimension. For sources, 
-	Enron's focus on finances and energy represents one context in
-	which people use spreadsheets, but other corpora, like EUSES and Fuse, draw from
-	other domains and industries. As Jansen found in his comparison of
-	spreadsheets Enron and EUSES \cite{jansen2015enron}, different companies rely
-	on different functions. For other types of spreadsheet, such as Gnumeric\footnote{http://www.gnumeric.org/} or Google
-	Sheets\footnote{https://www.google.com/sheets/about/}, we have no
-	guarantee that practices and functions will hold across these varied programs, even within
-	similar domains. This, then, warrants further analysis, in which good visualization might serve
+	Additionally, Excel is only one of many different spreadsheet products
+	available, chosen for this project because of its prevalence. But other
+	spreadsheets, such as Gnumeric\footnote{http://www.gnumeric.org/} or Google
+	Sheets\footnote{https://www.google.com/sheets/about/} represent other
+	approaches to spreadsheet systems. Even within identical domains, there's no
+	guarantee that practices and functions will hold across these varied offerings.
+	This, then, warrants further analysis, in which good visualization might serve
 	well. \par
@@
 
-	\section{Conclusion}
+	%\begin{wrapfigure}{O}{.25\textwidth} \centering
+	%	\includegraphics[width=.25\textwidth]{longIF} \label{fig:longif} \caption{The
+	%		many possibilities of IF, argument 3, demonstrate the problem of having too
+	%		many options.} \end{wrapfigure}
 
-	This paper presents a tool to support the exploration of function combinations
-	throughout a given spreadsheet dataset. By taking an agnostic approach to
-	design quality, it attempts to convey the dataset's spreadsheet practices as
-	is: the common along with the anomalous, and the well-designed along with the
-	odorous. As seen in the user and case studies, this allows it to take on
-	several potential roles at once, such as an environment for investigating code
-	smells as well as a repository for examples for learning new techniques. \par
+	\section{Conclusion} This paper presents a tool to support the exploration of
+	function combinations throughout a given spreadsheet dataset. By taking an
+	agnostic approach to design quality, it attempts to convey the dataset's
+	spreadsheet practices as is: the common along with the anomalous, and the
+	well-designed along with the odorous. As seen in the user and case studies,
+	this allows it to take on several potential roles at once, such as an
+	environment for search out bad code smells as well as a repository for examples
+	for learning new techniques. \par
 
@@
 	% use section* for acknowledgment
-	\section*{Acknowledgment}
-
-	This material is based upon work supported in whole or in part with funding
-	from the Laboratory for Analytic Sciences (LAS). Any opinions, findings,
-	conclusions, or recommendations expressed in this material are those of the
-	author(s) and do not necessarily reflect the views of the LAS and/or any agency
-	or entity of the United States Government. I also thank the anonymous reviewers
-	who advised the direction of this paper.
+	\section*{Acknowledgment} This material is based upon work supported in whole
+	or in part with funding from the Laboratory for Analytic Sciences (LAS). Any
+	opinions, findings, conclusions, or recommendations expressed in this material
+	are those of the author(s) and do not necessarily reflect the views of the LAS
+	and/or any agency or entity of the United States Government.
 

### 2016-08-11 doc/paper.tex
Abstract revisions

--- 2016-08-09 doc/paper.tex
@@
 	% in the abstract
-	\begin{abstract} Spreadsheet environments often come equipped with an abundance
-		of functions and operations to manipulate data, which users can combine into
-		complex formulae. However, anticipating these combinations is difficult,
-		complicating matters for both researchers and practitioners who want to study
-		formulae to improve spreadsheet practices. Therefore, we developed
-		\toolnameend, a tool that analyzes spreadsheet corpora to visualize patterns of
-		function combination as an interactive tree, capable of representing both the
-		most common and most anomalous patterns of formula construction and their
-		contexts in actual workbooks. Using spreadsheets from the Enron corpus, we
-		conduct both a case study and a user study to explore \toolnameposs various
-		applications, particularly those in flexible smell detection and spreadsheet
-		education.
+	\begin{abstract} Spreadsheet environments offer many
+		functions to manipulate data, which users can combine into
+		complex formulae. However, for both researchers and practitioners who want to
+		study formulae to improve spreadsheet practices, anticipating these
+		combinations is difficult. Therefore, we developed \toolnameend, a tool that
+		analyzes spreadsheet collections to visualize patterns of function combination
+		as an interactive tree, representing both the most common and most anomalous
+		patterns of formula construction and their contexts. Using spreadsheets from
+		the Enron corpus, we conduct a case study and a user study to explore
+		\toolnameposs various applications, such as those in flexible smell
+		detection and spreadsheet education.
 

### 2016-08-11 doc/paper.tex
Introduction revisions

@@
 
-	\section{Introduction} Spreadsheets surround us. They serve key roles in
-	industry, where as much as 95\% of U.S. financial firms use them
-	daily~\cite{panko2008sarbanes}, and academia, where teachers can use them to
-	track research and students' grades, not to mention many other
-	applications~\cite{ko2011state}. It's this flexibility that grants them their
-	allure: while a novice can still work without much experience, spreadsheets
-	offer hundreds of specialized functions to fulfill a wide range of advanced
+	\section{Introduction} Spreadsheets surround us. They are vital to
+	industry and academia alike, supporting as much as 95\% of U.S. financial firms use them
+	daily~\cite{panko2008sarbanes} and empowering teachers to
+	track research and students' grades~\cite{ko2011state}. This flexibility boosts their
+	allure: while a novice can work with basic offerings, advanced users can choose
+	among the hundreds of specialized functions to fulfill a wide range of
 	needs, from complex statistics to text
@@
 
-	However, this ubiquity is not without danger; as more people adopt these tools
-	and make larger and more complex sheets, the cost of failure grows too. To
-	illustrate this, the European Spreadsheet Risks Interest Group (EuSpRIG)
-	documents many horror stories of spreadsheets gone
-	wrong\footnote{http://www.eusprig.org/horror-stories.htm}. One story tells of a
-	2013 economics paper which drew connections between debt and national growth.
-	Its findings shaped many political initiatives throughout the United States and
-	Europe. However, other researchers soon discovered that a critical selection
-	error in the research spreadsheets hampered the results and that, by correcting
-	this error, the findings reversed completely! And this is only one of several
-	accounts; even if most spreadsheet errors are relatively benign, poor
-	spreadsheet practice can risk millions, if not billions, of
+	However, this ubiquity is not without danger; as more people make larger and
+	more complex spreadsheets, the cost of failure grows too. The European
+	Spreadsheet Risks Interest Group (EuSpRIG) documents many horror stories of
+	spreadsheets gone wrong\footnote{http://www.eusprig.org/horror-stories.htm},
+	where consequences range from the profuse loss of money to the inaccurate
+	outcomes of elections to the creation of extensive political initiatives based
+	on flawed economics. Even if most spreadsheet errors are relatively benign,
+	poor spreadsheet practice can risk millions, if not billions, of
 	dollars~\cite{powell2009impact}.
 
-	From these stories, we can see the dire importance of understanding how people
-	actually use spreadsheets. Fortunately, spreadsheet researchers have supported
-	this by amassing spreadsheet collections from diverse sources, industrial to
-	academic. Collections like EUSES~\cite{fisher2005euses},
-	Fuse~\cite{barik2015fuse}, and the Enron corpus~\cite{hermans2015enron} have
-	already fueled productive research across the field, such as in the search for
-	code smells in spreadsheet
+	Fortunately, spreadsheet researchers address these dangers by amassing
+	spreadsheet collections from diverse sources, industrial to academic, so
+	researchers can study how people use spreadsheets. Collections like
+	EUSES~\cite{fisher2005euses}, Fuse~\cite{barik2015fuse}, and the Enron
+	corpus~\cite{hermans2015enron} have already produced valueable research, such as the
+	documentation of code smells in spreadsheet
 	environments~\cite{hermans2012detecting}~\cite{jansen2015code} or the creation
-	of grammars to capture every possible spreadsheet program in
-	Excel~\cite{aivaloglou2015grammar}. Additionally, some research has focused on
-	comparing these collections, as Jansen did in 2015, to discover variation in
-	spreadsheet techniques over time and location~\cite{jansen2015enron}.
+	of grammars to describe every possible spreadsheet program in
+	Excel~\cite{aivaloglou2015grammar}. Additionally, some research compares these
+	collections to discover variation in spreadsheet techniques over time and
+	location~\cite{jansen2015enron}.
 
-	Considering the value of spreadsheets and all of these resources to describe
-	their use, it becomes necessary that we design tools to better enable the
-	exploration of these datasets and simplify the complex concepts that occur in
-	spreadsheet design. One such concept is that of formula construction; functions
-	are an important part of using spreadsheets efficiently, yet the number of
-	potential combinations between them quickly becomes massive when you consider
-	that there are hundreds of them. Tools, then, that empower people to explore
-	questions about which functions are used together in practice have the
-	potential to improve the current design of spreadsheets themselves and educate
-	new generations of spreadsheets users on how to work best.
+	The value of spreadsheets demands that we design tools to better understand
+	these datasets and simplify complexities we find in them. One such complexity
+	is formula construction; functions are an important part of using spreadsheets
+	efficiently, yet the number of potential combinations is massive considering
+	that Excel boasts over 400 functions. Tools that explore these combinations in
+	practice can aid researchers in understanding how people program and in
+	educating new generations of spreadsheets users on how to work best.
 
 	This paper contributes such a tool, \toolnameend, that attempts to fulfill this
-	need for better exploration by building on the aforementioned spreadsheet
+	need for better exploration of spreadsheet
 	corpora. Working with spreadsheets in Excel, \toolname focuses primarily on the
@@
 	formulae that determine values across a spreadsheet. The tool creates an
-	interactive, exploratory visualization which captures how people combine these
-	functions in a selected collection of spreadsheets, quantifying the broad
-	patterns of function nesting while also being specific enough to find anomalous
-	formulae and link them back to the specific cell in spreadsheets where they
-	originate. \par
+	interactive visualization which captures how people combine these
+	functions, quantifying the broad
+	patterns of function nesting while also capturing anomalous
+	formulae and their locations.
 
-	Alongside the tool, we discuss several of the key decisions we faced during
-	design, such as what to do with redundant formulae in a sheet or how to
+	We also discuss several of the key decisions we faced during
+	design, such as what to do with a sheet's redundant formulae or how to
 	represent optional arguments, and we describe how our overall design goals both

### 2016-08-11 doc/paper.tex
Related work

@@
 	\section{Introduction} Spreadsheets surround us. They are vital to
-	industry and academia alike, supporting as much as 95\% of U.S. financial firms use them
-	daily~\cite{panko2008sarbanes} and empowering teachers to
-	track research and students' grades~\cite{ko2011state}. This flexibility boosts their
+	industry and academia alike, supporting as much as 95\% of U.S. financial firms
+	use them daily~\cite{panko2008sarbanes} and empowering teachers to track
+	research and students' grades~\cite{ko2011state}. This flexibility boosts their
 	allure: while a novice can work with basic offerings, advanced users can choose
-	among the hundreds of specialized functions to fulfill a wide range of
-	needs, from complex statistics to text
-	manipulation~\cite{nardi1990spreadsheet}. As such, it should be no surprise
-	that tens of millions of workers rely on these programs
-	daily~\cite{scaffidi2005estimating}.
+	among the hundreds of specialized functions to fulfill a wide range of needs,
+	from complex statistics to text manipulation~\cite{nardi1990spreadsheet}. As
+	such, it should be no surprise that tens of millions of workers rely on these
+	programs daily~\cite{scaffidi2005estimating}.
 
@@
 	EUSES~\cite{fisher2005euses}, Fuse~\cite{barik2015fuse}, and the Enron
-	corpus~\cite{hermans2015enron} have already produced valueable research, such as the
-	documentation of code smells in spreadsheet
+	corpus~\cite{hermans2015enron} have already produced valueable research, such
+	as the documentation of code smells in spreadsheet
 	environments~\cite{hermans2012detecting}~\cite{jansen2015code} or the creation
@@
 	This paper contributes such a tool, \toolnameend, that attempts to fulfill this
-	need for better exploration of spreadsheet
-	corpora. Working with spreadsheets in Excel, \toolname focuses primarily on the
-	functions, like SUM and IF and hundreds more, which are the building blocks of
-	formulae that determine values across a spreadsheet. The tool creates an
-	interactive visualization which captures how people combine these
-	functions, quantifying the broad
-	patterns of function nesting while also capturing anomalous
-	formulae and their locations.
+	need for better exploration of spreadsheet corpora. Working with spreadsheets
+	in Excel, \toolname focuses primarily on the functions, like SUM and IF and
+	hundreds more, which are the building blocks of formulae that determine values
+	across a spreadsheet. The tool creates an interactive visualization which
+	captures how people combine these functions, quantifying the broad patterns of
+	function nesting while also capturing anomalous formulae and their locations.
 
-	We also discuss several of the key decisions we faced during
-	design, such as what to do with a sheet's redundant formulae or how to
-	represent optional arguments, and we describe how our overall design goals both
-	helped and hindered this process. We then apply the tool to a number of case
-	studies to evaluate how much it could contribute to several different contexts,
-	most notably code smell detection and spreadsheet education. To better
-	understand how people might use \toolnameend, we also conducted a user study to
-	judge how usable and intuitive the tool actually is. This grounds the
-	discussion of its potential uses while also underscoring some of its inherent
-	limitations and setting the way for future extensions and improvements upon the
-	concept.
+	We also discuss several of the key decisions we faced during design, such as
+	what to do with a sheet's redundant formulae or how to represent optional
+	arguments, and we describe how our overall design goals both helped and
+	hindered this process. We then apply the tool to a number of case studies to
+	evaluate how much it could contribute to several different contexts, most
+	notably code smell detection and spreadsheet education. To better understand
+	how people might use \toolnameend, we also conducted a user study to judge how
+	usable and intuitive the tool actually is. This grounds the discussion of its
+	potential uses while also underscoring some of its inherent limitations and
+	setting the way for future extensions and improvements upon the concept.
 
@@
 	efficiently~\cite{baeza1999modern}; the visualization of spreadsheets,
-	therefore, has offered much room for research. Several previous tools work
-	within a spreadsheet, seeking to clarify the connections between the visible
+	therefore, offers much room for research. Several previous tools work
+	within a spreadsheet, clarifying connections between the visible
 	values in cells, the formulae that produce them, and the dependencies between
@@
 	incorporating the layouts and labels of spreadsheets~\cite{hipfl2008using}.
+
 	Other tools focus on creating visualizations external to the sheets. Hermans
@@
 	GyroSAT~\cite{hermans2011supporting} and Breviz~\cite{hermans2011breviz}.
-	\toolname is among the latter class, creating standalone visualizations about
+	\toolname is among this type, creating standalone visualizations about
 	spreadsheets instead of drawing connections inside the spreadsheet itself. In
@@
 
-	Many other tools inspect the structure of formulae but often from the
+	Many other tools inspect the structure of formulae but from the
 	perspective of finding bad design.  Following Fowler's initial description of
@@
 Other tools, like Badame's Excel refactoring~\cite{badame2012refactoring}, are concerned more with understanding the formula in service of changing them.
-However, these studies define standards of poor design and orient their searches around them.
 Though \toolname supports the search for bad design, as we will see, the tool itself takes a much more agnostic approach in presentation, offering examples without regard for design quality.
@@
 	itself: Robillard and DeLine, for example conducted a series of surveys and
-	interviews to diagnose common problems with learning APIs, and they found that
-	code examples, one of the focuses of this tool, is one of the most important
+	interviews to diagnose common problems with learning APIs. They found that
+	code examples, which is one of the focuses of this tool, is one of the most important
 	aids to have in learning a new system~\cite{robillard2011field}. Though this

### 2016-08-12 doc/paper.tex
Fixes #152

--- 2016-08-11 doc/paper.tex
@@
 %% by Michael Shell
-%% See:f
+%% See:
 %% http://www.michaelshell.org/
@@
 % The documentation is contained in the cite.sty file itself.
-\usepackage{xspace}
+\usepackage{subfigure}
 
@@
 \graphicspath{{pic/}} % and their extensions so you won't have to specify these
-\DeclareGraphicsExtensions{.png} \else % or other class option (dvipsone,
+\DeclareGraphicsExtensions{.pdf,.png} \else % or other class option (dvipsone,
 % dvipdf, if not using dvips). graphicx
@@
 
-\newcommand{\toolname}{Perquimans\xspace} \newcommand{\toolnameend}{Perquimans}
+\newcommand{\toolname}{Perquimans } \newcommand{\toolnameend}{Perquimans}
 \newcommand{\toolnameposs}{Perquimans' }
@@
 	% affiliations
-	\author{ \IEEEauthorblockN{Justin A. Middleton and Emerson Murphy-Hill}
-		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ jamiddl2@ncsu.edu, emerson@csc.ncsu.edu }}
+	\author{ \IEEEauthorblockN{Justin A. Middleton, Emerson Murphy-Hill}
+		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ \{jamiddl2,
+			ermurph3\}@ncsu.edu }}
 
@@
 	% in the abstract
-	\begin{abstract} Spreadsheet environments offer many
-		functions to manipulate data, which users can combine into
-		complex formulae. However, for both researchers and practitioners who want to
-		study formulae to improve spreadsheet practices, anticipating these
-		combinations is difficult. Therefore, we developed \toolnameend, a tool that
-		analyzes spreadsheet collections to visualize patterns of function combination
-		as an interactive tree, representing both the most common and most anomalous
-		patterns of formula construction and their contexts. Using spreadsheets from
-		the Enron corpus, we conduct a case study and a user study to explore
-		\toolnameposs various applications, such as those in flexible smell
-		detection and spreadsheet education.
+	\begin{abstract} Spreadsheet environments often come equipped with an abundance
+		of functions and operations to manipulate data, which users can combine into
+		complex formulae. However, anticipating these combinations is difficult,
+		complicating matters for both researchers and practitioners who want to study
+		formulae to improve spreadsheet practices. Therefore, we developed
+		\toolnameend, a tool that analyzes spreadsheet corpora to visualize patterns of
+		function combination as an interactive tree, capable of representing both the
+		most common and most anomalous patterns of formula construction and their
+		contexts in actual workbooks. Using spreadsheets from the Enron corpus, we
+		conduct both a case study and a user study to explore \toolnameposs various
+		applications, particularly those in flexible smell detection and spreadsheet
+		education.
 
@@
 
-	\begin{figure}[h] \centering \includegraphics[scale=.4]{start} \caption{How the
+	\begin{figure}[h] \centering \includegraphics[width=.4\columnwidth]{start} \caption{How the
 			IF tree looks at the start} \label{fig:startpic} \end{figure}
@@
 
-	\begin{figure}[h] \centering \includegraphics[scale=.4]{IFexpand}
+	\begin{figure}[h] \centering \includegraphics[width=0.7\columnwidth]{IFexpand}
 		\caption{First argument of the IF tree} \label{fig:expandif} \end{figure}
@@
 
-	\begin{figure*}[t] \centering \includegraphics[scale=.5]{IFargslabel}
+	\begin{figure*}[t] \centering \includegraphics[width=0.8\textwidth]{IFargslabel}
 		\caption{A picture of \toolname displaying the common arguments to the IF
@@
 
-	\begin{figure}[h] \centering \includegraphics[width =
-		.46\textwidth]{comparison} \includegraphics[]{comparison-ss} \caption{The
+	\begin{figure}[h] 
+		\centering
+		\begin{subfigure}
+		  \centering
+		  \includegraphics[width=.4\linewidth]{comparison1}
+		\end{subfigure}%
+		\begin{subfigure}
+		  \centering
+		  \includegraphics[width=.4\linewidth]{comparison2}
+		\end{subfigure} 
+		\includegraphics[]{comparison-ss} \caption{The
 			contents of the default tree (left) and the optional argument trees (right)}

### 2016-08-12 doc/paper.tex
Walkthrough changes

--- 2016-08-11 doc/paper.tex
@@
 
-		\item [1] \textbf{Provide an interactive environment for free exploration.}
-		There are a lot of data in some of these spreadsheet corpora, and the user
-		should be able to pick for themselves which to explore while ignoring the
-		rest. Furthermore, this exploration should not be designed around answering
-		one specific question but rather helping to answer a variety of questions.
+		\item [1] \textbf{Unbiased Exploration} First, provide an interactive
+		environment for free exploration. There are a lot of data in some of these
+		spreadsheet corpora, and the user should be able to pick for themselves which
+		to explore while ignoring the rest. Second, avoid judgments about good and bad
+		design. Though users may certainly approach the tool with the intention of
+		exploring particular formulae, a formula visualization tool will not
+		prioritize any on metrics of good or bad practice.
 
-		\item [!1] \textbf{Do not make judgments about good and bad design.} Though
-		users may certainly approach the tool with the intention of exploring
-		particular formulae, a formula visualization tool will not prioritize any on
-		metrics of good or bad practice.
+		\item [2] \textbf{Uncluttered Quantification} \toolname should emphasize the
+		quantitative patterns in formula construction and address the questions of how
+		often the spreadsheet programmers used a certain function and where they used
+		it. To do this, it must show metrics, such as frequency of use and depth of
+		function nesting, but it must not overwhelm with numbers. Though everything
+		should be accessible in accordance with the first goal, we should reduce noise with our design.
 
-		\item [2] \textbf{Emphasize the quantitative patterns in formula
-			construction.} The tool should address the questions of how often the
-		spreadsheet programmers used a certain function and where they used it. To do
-		this, it must show metrics, such as frequency of use and depth of function
-		nesting, of the dataset it conveys.
-
-		\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
-		especially, we anticipate that we'll have to show a lot of related data at
-		once. Though everything should be accessible in accordance with Goal 1, we
-		should design in a way that reduces noise.
-
-		\item [3] \textbf{Promote a qualitative understanding of the patterns.} The
-		tool should supplement its observations with concrete instances of relevant
+		\item [3] \textbf{Informative Qualification} The tool should promote a qualitative understanding of the patterns by providing concrete instances of relevant
 		formulae from the corpus. Ideally, it should even direct users to the exact
@@
 
-		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool is
-		meant to foster understanding by linking pattern to example, it will not try
-		to be an explanatory tool that articulates what a complex formula
-		accomplishes. Rather, we will provide the structure and context, and the user
-		must infer this on their own.
-
 	\end{itemize}
 
-	Though we kept these guidelines in mind through the development of \toolname,
-	we nevertheless reached a number of points in which these principles
-	conflicted. For a discussion of these decisions, see Section
-	\ref{ssec:decisions}.
-
 	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing
-	the minutiae of tool's development, we will give a basic example of how to use
+	the tool's development, we will give a basic example of how to use
 	the tool. For this, we will work from the visualization built on the Enron
@@
 
-	First, a word on the IF function. In Excel, it serves as one of the logical
+	In Excel, the IF functions is one of the logical
 	functions: given a condition as the first argument that evaluates to either
@@
 	is, a function nested within none other -- only a few nodes are visible, as
-	shown in Figure \ref{fig:startpic}. \par
+	shown in Figure~\ref{fig:startpic}. \par
 
@@
 	\includegraphics{glossary-greenonly}, which represents a discrete function in
-	the formula and is size according to its frequency relative to the number of
+	the formula and is sized according to its frequency relative to the number of
 	times the root function appeared; and the numbered squares

### 2016-08-12 doc/paper.tex
Paper edits

@@
 % The documentation is contained in the cite.sty file itself.
+
 \usepackage{xspace}
+\usepackage{subfigure}
 
@@
 
-	\begin{figure}[h] \centering \includegraphics[scale=.9]{ifExample}
+	\begin{figure}[h] \centering \includegraphics[width=\columnwidth]{ifExample}
 		\caption{Configurations of the IF function} \label{fig:ifexample} \end{figure}

### 2016-08-13 doc/paper.tex
Walkthrough work

@@
 \usepackage{subfigure}
+\usepackage{url}
 
@@
 	functions and how they combine into complex formulae, rather than exploring the
-	data structures of any particular spreadsheet.  \par
+	data structures of any particular spreadsheet.
 
@@
 Though \toolname supports the search for bad design, as we will see, the tool itself takes a much more agnostic approach in presentation, offering examples without regard for design quality.
-\par
 
@@
 	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing
-	the tool's development, we will give a basic example of how to use
-	the tool. For this, we will work from the visualization built on the Enron
+	\toolnameposs development, we will give a basic example of how to use
+	it. We will work from the visualization built on the Enron
 	corpus to answer this question: \textit{ What kinds of functions do people use
-		to define the condition in an IF function?} \par
+		to define the condition in an IF function?}
 
-	In Excel, the IF functions is one of the logical
-	functions: given a condition as the first argument that evaluates to either
-	true or false, it takes on the value of either the second or third argument,
-	respectively. Or, as the documentation writes out, ``IF(Something is True, then
-	do something, otherwise do something
-	else)"\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}.
+	In Excel, the IF functions is one of the logical functions: given a condition
+	as the first argument that evaluates to either true or false, it takes on the
+	value of either the second or third argument respectively. Or, as the
+	documentation writes out, ``IF(Something is True, then do something, otherwise
+	do something
+	else)"\footnote{\url{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}}.
 Furthermore, the third argument is optional; if left out, the function will return a default ``FALSE" value if necessary.
@@
 	is, a function nested within none other -- only a few nodes are visible, as
-	shown in Figure~\ref{fig:startpic}. \par
+	shown in Figure~\ref{fig:startpic}.
 
@@
 
-	The visualization so far comprises two types of nodes: the circle
-	\includegraphics{glossary-greenonly}, which represents a discrete function in
-	the formula and is sized according to its frequency relative to the number of
-	times the root function appeared; and the numbered squares
-	\includegraphics{glossary-blue}, which represent the positions of arguments
-	within its parent function. From this, we can confirm that, of the times it was
-	observed, IF can have at most three arguments passed into it, which corresponds
-	with its specifications in the API. \par
+	The visualization so far comprises two types of nodes. The first are the
+	circles \includegraphics{glossary-greenonly}, which represens a discrete
+	function in the formula. These are sized according to their frequency relative
+	to the number of times the root function appeared. The second kind of node are
+	the numbered squares \includegraphics{glossary-blue}, which represent the
+	positions of arguments within its parent function. Looking back at the tree, we
+	can confirm that IF functions in this dataset had at most three arguments
+	passed into them, which corresponds with its specifications in the API.
 
-	Knowing that it is the first argument which contains the conditionals, we click
-	on the square labeled ``1" to explore. To save space, when the tool finds more
-	than 10 unique arguments in a position, it displays only the first ten, with an
-	option to display the rest by clicking the arrow
+	Knowing that the first argument of IF contains the conditionals, we click on
+	the square labeled ``1" to explore. When the tool finds more than 10 unique
+	arguments in a position, it saves space by displaying only the first ten and
+	includes an option to display the rest by clicking the arrow
 	\includegraphics{glossary-arrow}.
@@
 
-	We see that IF contains a number of comparison operators as its first argument,
-	such as = and $\le$, and boolean-returning functions, like ISNA and AND, with
-	simple equality being the most common and ABS being the least. From here, we
+	In Figure~\ref{fig:expandif}, we see that IF's first arguments are most often comparison operators,
+	such as = and $\le$, and boolean-returning functions, like ISNA and AND. Of these,
+	simple equality is the most common and ABS is the least. From here, we
 	can further explore the common options among these functions. Clicking on the
-	``=" node will yield two arguments and expanding each of them will peer into
-	the range of common values of equality comparison, which Figure
-	\ref{fig:fullpic} shows. \par
+	``=" node will yield two arguments and expanding each of them will show
+	the common values on either side of the equals sign, as in Figure~\ref{fig:fullpic}.
 
@@
 
-	For both sides of the equal sign, the operator has certain types of arguments
+	The equality operator has certain types of arguments
 	which predominate over the others: on the left side is most often a reference
-	to another cell; on the right, a string or number literal, which makes sense
+	to another cell; on the right is a string or number literal, which makes sense
 	for the case of confirming a value in another cell before assigning this one.
@@
 	concrete example of a function that uses this structure. If this single
-	instance is not enough, then the user also has the option to double-click the
-	individual function node, which will open up a new tab with a table of many
-	more examples from dataset.
+	instance is not enough, then the user also has the option to open up a new
+	window with a table of many more examples from dataset.
 

### 2016-08-13 doc/paper.tex
Got rid of redundant pars

@@
 	of arguments in a function and the number of possible functions observed as an
-	argument in a function. \par
+	argument in a function.
 
@@
 	more verbose in our description. As such, we decided that visualizing some
-	dimensions was quicker than writing them out. \par
+	dimensions was quicker than writing them out.
 
@@
 		should it be analyzed only as a nested function or would it also be valid to
-		analyze the nested function on its own? \par
+		analyze the nested function on its own?
 
@@
 	structures which create distinctive features within the tree, leading to easy
-	detection through our visualization: \par
+	detection through our visualization:
 
@@
 	operation -- ``SUM(C6+C7+C8+C9+C10+C11+C12+C13+...+C37)" -- representing a
-	technically valid but unusual and problematic design.\par
+	technically valid but unusual and problematic design.
 
@@
 	in a working environment, with the specifics depending on the dataset the tool
-	is using. \par
+	is using.
 
@@
 	can nevertheless guide the educator to several examples in production where
-	this problem surfaces. \par
+	this problem surfaces.
 
@@
 	furthermore, that their observations could be directed either at the quality of
-	the data conveyed by the tool or at the tool's design itself. \par
+	the data conveyed by the tool or at the tool's design itself.
 
@@
 	before, such as PV and IPMT, looking for new features in Excel to explore and
-	learn. \par
+	learn.
 
@@
 	combinations can require more complex text queries, whereas here, the
-	information is already captured in nodes.  \par
+	information is already captured in nodes.
 
@@
 	to such documentation from within the tool without violating any design
-	concerns in Section~\ref{goals}. \par
+	concerns in Section~\ref{goals}.
 
@@
 	single purpose, it might, at the same time, not afford them any mindset at all
-	with which to interpret the data. \par
+	with which to interpret the data.
 
@@
 	parts of the tool, their presence affected many of the participant's observations before we
-	could clarify, reducing the amount of useful information from these sessions.  \par
+	could clarify, reducing the amount of useful information from these sessions.
 
@@
 	Section~\ref{badsmells}. While these may be fairly obvious, however, they 
-	may distract from subtler, more insidious patterns. \par
+	may distract from subtler, more insidious patterns.
 
@@
 	precautions, balancing the desire to show a lot with the desire not to
-	overwhelm remains a challenge. \par
+	overwhelm remains a challenge.
 
@@
 	similar domains. This, then, warrants further analysis, in which good visualization might serve
-	well. \par
+	well.
 
@@
 	several potential roles at once, such as an environment for investigating code
-	smells as well as a repository for examples for learning new techniques. \par
+	smells as well as a repository for examples for learning new techniques.
 
@@
 	essential to this design conflict and will be overcome in future iterations of
-	design by refining icons and improving maneuverability. \par
+	design by refining icons and improving maneuverability.
 

### 2016-08-13 doc/paper.tex
Goodbye, middle initial.
Glyph work

@@
 	% affiliations
-	\author{ \IEEEauthorblockN{Justin A. Middleton and Emerson Murphy-Hill}
+	\author{ \IEEEauthorblockN{Justin Middleton and Emerson Murphy-Hill}
 		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ jamiddl2@ncsu.edu, emerson@csc.ncsu.edu }}
@@
 	spreadsheet collections from diverse sources, industrial to academic, so
-	researchers can study how people use spreadsheets. Collections like
+	they can study how people use spreadsheets. Collections like
 	EUSES~\cite{fisher2005euses}, Fuse~\cite{barik2015fuse}, and the Enron
@@
 	often~\cite{murphy2006java}. Others focus on the documentation of the API
-	itself: Robillard and DeLine, for example conducted a series of surveys and
+	itself: Robillard and DeLine, for example, conducted a series of surveys and
 	interviews to diagnose common problems with learning APIs. They found that
@@
 	corpus to answer this question: \textit{ What kinds of functions do people use
-		to define the condition in an IF function?}
+		to define the condition in an \texttt{IF} function?}
 
-	In Excel, the IF functions is one of the logical functions: given a condition
+	In Excel, the \texttt{IF} functions is one of the logical functions: given a condition
 	as the first argument that evaluates to either true or false, it takes on the
 	value of either the second or third argument respectively. Or, as the
-	documentation writes out, ``IF(Something is True, then do something, otherwise
+	documentation writes out, ``\texttt{IF(Something is True, then do something, otherwise
 	do something
-	else)"\footnote{\url{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}}.
+	else)}"\footnote{\url{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}}.
 Furthermore, the third argument is optional; if left out, the function will return a default ``FALSE" value if necessary.
@@
 	The visualization so far comprises two types of nodes. The first are the
-	circles \includegraphics{glossary-greenonly}, which represens a discrete
-	function in the formula. These are sized according to their frequency relative
+	circles \includegraphics{glossary-greenonly}, which represents a discrete
+	function in the formula. These nodes are sized according to their frequency relative
 	to the number of times the root function appeared. The second kind of node are
@@
 	positions of arguments within its parent function. Looking back at the tree, we
-	can confirm that IF functions in this dataset had at most three arguments
+	can confirm that \texttt{IF} functions in this dataset had at most three arguments
 	passed into them, which corresponds with its specifications in the API.
 
-	Knowing that the first argument of IF contains the conditionals, we click on
+	Knowing that the first argument of \texttt{IF} contains the conditionals, we click on
 	the square labeled ``1" to explore. When the tool finds more than 10 unique
@@
 	\begin{figure}[h] \centering \includegraphics[width=0.7\columnwidth]{IFexpand}
-		\caption{First argument of the IF tree} \label{fig:expandif} \end{figure}
+		\caption{First argument of the \texttt{IF} tree} \label{fig:expandif} \end{figure}
 
-	In Figure~\ref{fig:expandif}, we see that IF's first arguments are most often comparison operators,
-	such as = and $\le$, and boolean-returning functions, like ISNA and AND. Of these,
+	In Figure~\ref{fig:expandif}, we see that \texttt{IF}'s first arguments are most often comparison operators,
+	such as = and $\le$, and boolean-returning functions, like \texttt{ISNA} and \texttt{AND}. Of these,
 	simple equality is the most common and ABS is the least. From here, we
@@
 	\begin{figure*}[t] \centering \includegraphics[width=0.8\textwidth]{IFargslabel}
-		\caption{A picture of \toolname displaying the common arguments to the IF
+		\caption{A picture of \toolname displaying the common arguments to the \texttt{IF}
 			function's first parameter} \centering \label{fig:fullpic} \end{figure*}
@@
 
-	From these images, we can provide a quick glossary of glyphs within the
-	visualization to aid interpretation. \begin{itemize} \item
-		\includegraphics{glossary-green} - \textbf{Function nodes} are green circles
+	From these images, we provide glossary of glyphs to better interpret the visualizations. \begin{itemize} \item
+		\includegraphics{glossary-green} \textbf{Function nodes} are green circles
 		labeled with the function name. Their size is determined by their relative
@@
 
-		\item \vspace{.25cm}\includegraphics{glossary-leaf} - \textbf{Value nodes} are
-		white circles with a generic label. They represent elements of a formula which
+		\item \vspace{.25cm}\includegraphics{glossary-leaf} \textbf{Value nodes} are
+		white circles with a generic label. They represent elements of a formula that
 		accept no arguments, like references (A1), ranges (A1:A10), numbers, boolean
-		values, strings, and errors. However, \toolname treats still functions with
-		zero arguments, like NOW, as function nodes. Like function nodes, these also
-		contain examples.
+		values, strings, and errors. However, \toolname still treats functions with
+		zero arguments, like \texttt{NOW}, as function nodes. Like function nodes,
+		these also link to examples.
 
-		\item  \vspace{.25cm} \includegraphics{glossary-blue} - \textbf{Argument
-			nodes} are dark blue squares labeled with a number. The number is the position
-		of an argument within the function in the parent node. In Figure
-		\ref{fig:expandif} for example, argument node 1 shows every function or value
-		that was seen in the first argument.
+		\item  \vspace{.25cm} \includegraphics{glossary-blue} \textbf{Argument nodes}
+		are dark blue squares labeled with a number. The number is the position of an
+		argument within the function of the parent node. In Figure~\ref{fig:expandif}
+		for example, argument node 1 shows every function or value that was seen in
+		the first argument.
 
-		\item  \vspace{.25cm} \includegraphics{glossary-solidline} - \textbf{Solid
+		\item  \vspace{.25cm} \includegraphics{glossary-solidline} \textbf{Solid
 			lines} represent a function's list of parameters. As such, they connect the
@@
 
-		\item  \vspace{.25cm} \includegraphics{glossary-fadingline} - \textbf{Fading
-			lines} represents how a formula author can use several different possible
-		functions or values within a single argument position. As such, they connect
-		argument nodes to function or value nodes.
+		\item  \vspace{.25cm} \includegraphics{glossary-fadingline} \textbf{Fading
+			lines} represents how a formula author can choose from several possible
+		functions or values within a single argument position. As such, these lines
+		connect argument nodes to function or value nodes.
 
-		\item  \vspace{.25cm} \includegraphics{glossary-arrow} - \textbf{Expansion
+		\item  \vspace{.25cm} \includegraphics{glossary-arrow} \textbf{Expansion
 			arrows} appear within an argument node when there are over 10 possible
@@
 
-		\item  \vspace{.25cm} \includegraphics[scale=.75]{glossary-lightblue} -
+		\item  \vspace{.25cm}
+		$\vcenter{\hbox{\includegraphics[scale=.75]{glossary-lightblue}}}$
 		\textbf{Optional argument trees} are variations of trees that show only
-		formulae with a specific number of arguments. For example, the function AND
-		can take any number of arguments, up to 255. By default, the tree shows data
-		from AND functions with any number of arguments, but these trees, which have
-		argument nodes of a lighter blue color, can show how AND was used when
-		\textit{only} two arguments were passed into it, or \textit{only} four, and so
-		on. See Figure~\ref{fig:optional} for how the data between tree types differs.
+		formulae with a specific number of arguments. For example, the function
+		\texttt{AND} can take any number of arguments, up to 255. By default, the tree
+		shows data from \texttt{AND} functions with any number of arguments, but these
+		trees, which have argument nodes of a lighter blue color, can show how
+		\texttt{AND} was used when \textit{only} two arguments were passed into it, or
+		\textit{only} four, and so on. See Figure~\ref{fig:optional} for how the data
+		between tree types differs.
 	\end{itemize}
@@
 
-	\subsection{Implementation Details} The visualization is the product of two
-	discrete processes: \begin{itemize} \item \textit{Collection}: Given a set of
+	\subsection{Implementation Details} The visualization is the product of two processes: \begin{itemize} \item \textit{Collection}: Given a set of
 		Excel sheets, the tool, written in Java, uses Apache

### 2016-08-13 doc/paper.tex
Another glyph revision

@@
 		\texttt{AND} can take any number of arguments, up to 255. By default, the tree
-		shows data from \texttt{AND} functions with any number of arguments, but these
-		trees, which have argument nodes of a lighter blue color, can show how
-		\texttt{AND} was used when \textit{only} two arguments were passed into it, or
-		\textit{only} four, and so on. See Figure~\ref{fig:optional} for how the data
-		between tree types differs.
+		shows data from \texttt{AND} functions with any number of arguments, and an
+		example of the \texttt{AND} tree with sample contents is shown on the left of
+		Figure~\ref{fig:optional}. Optional argument trees, however, have argument
+		nodes of a lighter blue color and show how \texttt{AND} was used when
+		\textit{exactly} two arguments were passed into it, or \textit{exactly} four,
+		without including uses of this function with any other number of arguments.
 	\end{itemize}
@@
 		\includegraphics[]{comparison-ss} \caption{The
-			contents of the default tree (left) and the optional argument trees (right)}
+			contents of the default tree (left) and the optional argument tree with 4 arguments (right)}
 		\label{fig:optional} \end{figure}

### 2016-08-13 doc/paper.tex
misc revisions

@@
 		POI\footnote{https://poi.apache.org/} to identify and iterate over every cell
-		containing a valid formula. Afterward, it calls POI's formula parser to break
+		containing a valid formula. Afterward, it calls POI's formula parser to decompose
 		the formula text into an ordered set of individual tokens, which the tool then
@@
 	relationship of formulae as functions and their arguments, which could be yet
-	more functions. By adapting this structure for a broad range of possibilities
-	for nested functions, the branching factor depends alternatively on the number
-	of arguments in a function and the number of possible functions observed as an
-	argument in a function.
+	more functions. One option that we did not take was to represent the call trees
+	as simple text hierarchies. Though that might work well for a single,
+	uncomplicated call structure, we did not do this because our tool combined many
+	of these call trees into a more complicated structure. To capture the different
+	relationships in the tree and to quantify the frequency of arguments, we would
+	need to be more verbose in our description. As such, we decided that
+	visualizing some dimensions was quicker than writing them out.
 
-	Another of our options was to represent the call trees as simple text
-	hierarchies. Though this might work well for a single, uncomplicated call
-	structure, we did not do this because our tool combined many of these call
-	trees into a more complicated structure. To capture the different relationships
-	in the tree and to quantify the frequency of arguments, we would need to be
-	more verbose in our description. As such, we decided that visualizing some
-	dimensions was quicker than writing them out.
-
-	Guided by the goals in Section \ref{goals}, we faced a number of decisions in
-	how to visualize the data. Below, we've outlined those that had the largest
-	impact in the values that appear in the tree. \begin{itemize}
+	In balancing this chosen form with the goals in Section~\ref{goals}, we faced a
+	number of decisions in how to visualize the data. Below, we've outlined those
+	that had the largest impact in the values that appear in the tree.
+	\begin{itemize}
 
@@
 		\item \textit{Importance of depth}: When a function appears within another,
-		should it be analyzed only as a nested function or would it also be valid to
-		analyze the nested function on its own?
+		should it be analyzed only as a nested function or should \toolname
+		analyze the nested function as a top-level function as well?
 
-		\ \ For example, in the pictured IF function, we found that people often use
-		another IF statement as the second or third arguments of the top-level IF. If
+		\ \ For example, in the pictured \texttt{IF} function, we found that people often use
+		another IF statement as the second or third arguments of the top-level \texttt{IF}. If
 		we only consider functions exactly where they're found embedded in the
-		formula, then information about the same function -- IF, in this case -- will
+		formula, then information about the same function -- \texttt{IF}, in this case -- will
 		be scattered across different trees with no way to aggregate them. If we
 		record every instance of a function by ignoring their context -- that is,
-		including an IF embedded within a SUM function in the same node as the
-		top-level IF -- then the tool will represent some functions in multiple nodes
+		including an \texttt{IF} embedded within a \texttt{SUM} function in the same node as the
+		top-level \texttt{IF} -- then the tool will represent some functions in multiple nodes
 		to capture every possible level of nesting. For now, we only include the

### 2016-08-13 doc/paper.tex
more revisions

@@
 		\item \textit{Copied formulae}: Excel allows users to spread a formula over an
-		area, repeating the same task in each cell with minor adjustments. Without
+		area, repeating the same formula in each cell with minor adjustments. Without
 		checking for this, the analysis may not reveal the functions most commonly
@@
 
-	\section{Case Study} The obvious question to pose to any visualization is this:
+	\section{Case Study} The obvious question to pose any visualization is this:
 	What do the images tell us that the text could not? It is not enough to prove
 	that something can be visualized; we must also demonstrate what we can gain
-	from any particular visualization. As such, we raised a few tasks in the
-	introduction in which we thought the tool could help: detecting bad smells and
+	from any particular visualization. For this purpose, we outlined a few tasks in the
+	introduction in which we thought the tool could help, particularly detecting bad smells and
 	guiding spreadsheet education. To demonstrate the tool's applicability, we
@@
 	\subsection{Bad Smells} \label{badsmells} Fowler's description of code
-	smells~\cite{fowler2009refactoring} underscored an important point of code
+	smells~\cite{fowler2009refactoring} underscores an important point of code
 	quality: between elegant, efficient code and bug-crippled spaghetti, there is a
 	spectrum of code designs which, by themselves, are not faulty but nevertheless
-	suggest vulnerabilities in code design. Since then, researchers have applied
+	suggest problems in code design. Since then, researchers have applied
 	these concepts to spreadsheet programming, as discussed in
-	Section~\ref{related-work}. While some of the smells lie beyond the scope of
+	Section~\ref{related-work}. While some of the documented code smells lie beyond the scope of
 	the tool, such as those characterizing inter-worksheet connections, others have
@@
 		functions and operators~\cite{hermans2012detecting}. As a result, the formula
-		tends to be prohibitively complex. In the visualization, since each nested and
+		tends to be complex. In the visualization, since each nested and
 		combined function creates yet another level of depth within the tree, these
@@
 		for many functions which have a limited number of arguments that it accepts.
-		However, for functions that accept arguments indefinitely, such as SUM and
-		CONCATENATE, it creates tall towers of argument nodes from a single function
+		However, for functions that accept arguments indefinitely, such as \texttt{SUM} and
+		\texttt{CONCATENATE}, it creates tall towers of argument nodes from a single function
 		node.
 
-		\item \textit{Conditional Complexity}: A logical function, particularly IF,
+		\item \textit{Conditional Complexity}: A logical function, particularly \texttt{IF},
 		nests several other logical functions inside of it, reducing code
 		readability~\cite{hermans2012detecting}. These can be traced manually in the
-		trees for the logical functions. IF, for example, will have several more IF
+		trees for the logical functions. \texttt{IF}, for example, will have several more \texttt{IF}
 		function nodes within its second or third arguments, which in turn might have
@@
 
-	Some code issues are meaningful not for the space they occupy but for how they
-	clash with a function's expectations. For example, Excel offers a number of
-	functions that accept any number arguments given to them, up to a
-	resource-defined limit. SUM, for example, simply adds every argument given to
-	it. This also means that it can accept only one argument, and when the user
-	does so, they pass in a range of cells over 90\% of the time. However, using
-	the tool, we isolated an instance where the programmer used a single-argument
-	SUM where the argument was a series of 32 contiguous cells added with the +
-	operation -- ``SUM(C6+C7+C8+C9+C10+C11+C12+C13+...+C37)" -- representing a
-	technically valid but unusual and problematic design.
+	Aside from these three, some code issues are meaningful not for the space they
+	occupy but for how they clash with a function's expectations. For example,
+	Excel offers a number of functions that accept as many arguments given to
+	them, up to a resource-defined limit. \texttt{SUM}, for example, simply sums up every
+	argument given to it. This also means that it can accept only one argument, and
+	when the user does so, they pass in a range of cells over 90\% of the time.
+	However, using \toolname, we found an instance where the programmer used a
+	single-argument \texttt{SUM} where the argument was a series of 32 contiguous cells
+	added with the + operation -- ``\texttt{SUM(C6+C7+C8+C9+C10+C11+C12+C13+...+C37)}" --
+	representing a correct but redundant design.
 
@@
 	designs that exist outside these readily visible categories. Consider the
-	second argument of the ``='' operator, already shown expanded in
+	second argument of the \texttt{``=''} operator, already shown expanded in
 	Figure~\ref{fig:fullpic}: among the top five argument types for the position in
-	an IF function were boolean values. This corresponds to designs in which
-	conditions already in a boolean form were then checked against ``=TRUE" or
-	``=FALSE", such as in the formula \textit{IF(Formulas!C77=TRUE, ``Yes")}, which
+	an \texttt{IF} function were boolean values. This corresponds to designs in which
+	conditions already in a boolean form were then checked against \texttt{``=TRUE"} or
+	\texttt{``=FALSE"}, such as in the formula \texttt{IF(Formulas!C77=TRUE, ``Yes")}, which
 	appears in one of the sheets. Though this practice does not break anything in
 	itself, it nevertheless represents redundant operations in formula design and
-	indicates a possible misunderstanding of how the IF function works over the
-	hundreds of examples of this boolean comparison that our tool can return.
+	indicates a possible misunderstanding of how the IF function works.
 
@@
 	for programmers learning new APIs, they concluded that one of the most
-	important elements of a good API was the use of code examples to demonstrate
-	function use~\cite{robillard2011field}. Examples in APIs, furthermore, come in
+	important elements of a good API was the use of code examples~\cite{robillard2011field}. Examples in APIs, furthermore, come in
 	a variety of forms: small snippets or tutorials that show only the intended
@@
 	operations are used as conditions in IF. The design of this tool emphasizes the
-	connection, then, between what functions like ISNA and AND return and what IF
-	accepts, and specific examples for any of these combinations are only a click
-	away.
+	connection, then, between what functions like \texttt{ISNA} and \texttt{AND}
+	return and what \texttt{IF} accepts, and specific examples for any of these
+	combinations are only a click away.
 
@@
 	row or
-	column"\footnote{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}.
-Examples of their use can be found in Figure \ref{fig:lookupexample}, and we will cover each type in more depth to better understand the visualizations for these functions.
+	column"\footnote{\url{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}}.
+Examples of their use can be found in Figure~\ref{fig:lookupexample}, and we will cover each type in more depth to better understand the visualizations for these functions.
 
@@
 	the vector form, that column is the second argument, so in
-	Figure~\ref{fig:lookupexample}, the formula in cell D2 (\textit{=LOOKUP(3,
+	Figure~\ref{fig:lookupexample}, the formula in cell D2 (\texttt{=LOOKUP(3,
 		A2:A6, B2:B6)}) will search for the value of 3 between cells A2 and A6. The
-	value the formula returns then comes from the corresponding cell in the
+	value that the formula returns then comes from the corresponding cell in the
 	optional third argument's column; since the lookup values matches the value in
@@
 	VLOOKUP works closely with this array form, except the user defines in its
-	third argument which column from which to return values. In \textit{=VLOOKUP(3,
+	third argument which column from which to return values. In \texttt{=VLOOKUP(3,
 		A2:B6, 2)}, the argument ``2" tells to return the value from the second column,
@@
 	it. We demonstrate this in Figure~\ref{fig:lookupexample} in the bottom two
-	VLOOKUP functions, one returning ``Friday" and the other an error. HLOOKUP
+	\texttt{VLOOKUP} functions, one returning ``Friday" and the other an error. \texttt{HLOOKUP}
 	works identically but focuses on rows instead of columns.
@@
 	spreadsheets in a professional environment, having used spreadsheets
-	intermittently through university and hobbies. P1 through P3 all had varying
+	intermittently through education and hobbies. P1 through P3 all had varying
 	levels of experience with spreadsheets in a professional capacity: P1 for 1
@@
 
-	The participants were most vocal about their findings when they discovered, by
-	purpose or accident, instances of heinous design in the dataset. Many times,
-	they noted these examples shortly after opening a new tree, suggesting that the
-	distinctive visual signatures as discussed in Section \ref{badsmells} was a
-	salient force in their exploration. For example, when P3 encountered the
+		\begin{wrapfigure}{O}{.25\textwidth} \centering
+			\includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters
+				in SUM, which was a commonly noted smell in the user study} \label{fig:sum}
+		\end{wrapfigure}
+
+	The participants were most vocal about their findings when they discovered
+	instances of design they considered problematic. Many times, they noted these
+	examples shortly after opening a new tree, suggesting that the distinctive
+	visual signatures of code smells as discussed in Section~\ref{badsmells} were a salient force
+	in their exploration. For example, when P3 encountered the
 	initial design of the SUM tree, as seen in Figure \ref{fig:sum}, they readily
@@
 	these visual cues, value errors, prefixed with \#s, also appear in the tree,
-	which P4 said could be useful for tracking these problems if marked well.
-
-	\begin{wrapfigure}{L}{.25\textwidth} \centering
-		\includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters
-			in SUM, which was a commonly noted smell in the user study} \label{fig:sum}
-	\end{wrapfigure}
+	which P4 said could be useful for tracking these problems if they're easy to find.
 
@@
 	For instance, they first encountered a particular author's name when
-	investigating an AVERAGE function with 18 distinct arguments for which our
+	investigating an \texttt{AVERAGE} function with 18 distinct arguments for which our
 	participant could not discern any logical order even after opening the source
-	spreadsheet; the same name popped up again as P2 looked at a RATE function
+	spreadsheet; the same name popped up again as P2 looked at a \texttt{RATE} function
 	relying on several hard-coded values. P2 said that, if they were a manager or
@@
 	of Excel, their self-reported proficiencies ranging from ``fairly familiar"
-	(P2) to ``not extremely familiar" (P4). For example, as P1 explored the VLOOKUP
+	(P2) to ``not extremely familiar" (P4). For example, as P1 explored the \texttt{VLOOKUP}
 	function, they said they could use the tool to collect more examples than the
@@
 	trees, P1 and P3 also gravitated towards some functions they had not used
-	before, such as PV and IPMT, looking for new features in Excel to explore and
+	before, such as \texttt{PV} and \texttt{IPMT}, looking for new features in Excel to explore and
 	learn.
@@
 	functions were used together, demonstrated when P4 took special interest in how
-	people frequently used MATCH as the second argument of INDEX or how they used
-	date functions like DATE and MONTH as lookup values in VLOOKUP. Though a
+	people frequently used \texttt{MATCH} as the second argument of \texttt{INDEX} or how they used
+	date functions like \texttt{DATE} and \texttt{MONTH} as lookup values in \texttt{VLOOKUP}. Though a
 	standard text-search tool might yield the same results for a function alone,
@@
 	configurations, this does not mean that they will learn exactly what it does.
-	P1, examining unfamiliar functions like KURT and PV, could describe precisely
+	P1, examining unfamiliar functions like\texttt{KURT} and \texttt{PV}, could describe precisely
 	what types of arguments it accepted and how many. But even after exploring the
@@
 	Though our focus was specifically on function combination, there are several
-	other elements of a formula's context that we do no currently consider. For
+	other elements of a formula's context that we do not currently consider. For
 	example, \toolname does not current capture argument combination; in Figure

### 2016-08-13 doc/paper.tex
hrefs

@@
 \usepackage{url}
+\usepackage{hyperref}
 
@@
 	do something
-	else)}"\footnote{\url{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}}.
+	else)}"\footnote{\href{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}}.
 Furthermore, the third argument is optional; if left out, the function will return a default ``FALSE" value if necessary.
@@
 		Excel sheets, the tool, written in Java, uses Apache
-		POI\footnote{https://poi.apache.org/} to identify and iterate over every cell
+		POI\footnote{\href{https://poi.apache.org/}{https://poi.apache.org/}} to identify and iterate over every cell
 		containing a valid formula. Afterward, it calls POI's formula parser to decompose
@@
 		presentation code, implemented in Javascript with much help from the
-		visualization library D3\footnote{https://d3js.org/}. We chose D3 primarily
+		visualization library D3\footnote{\href{https://d3js.org/}{https://d3js.org/}}. We chose D3 primarily
 		for its accessibility: given the JSON, the visualization can be simply
@@
 	demonstration of \toolname can be found at
-	https://github.com/DeveloperLiberationFront/Excel-Function-Visualizer.
+	\href{https://github.com/DeveloperLiberationFront/Excel-Function-Visualizer}{https://github.com/DeveloperLiberationFront/Excel-Function-Visualizer}.
 
@@
 	row or
-	column"\footnote{\url{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}}.
+	column"\footnote{\href{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}}.
 Examples of their use can be found in Figure~\ref{fig:lookupexample}, and we will cover each type in more depth to better understand the visualizations for these functions.
@@
 
-	LOOKUP has two forms: vector and array. In either case, the first argument is
+	\texttt{LOOKUP} has two forms: vector and array. In either case, the first argument is
 	the value which you are trying to match in another column. If the formula is in
@@
 
-	VLOOKUP works closely with this array form, except the user defines in its
+	\texttt{VLOOKUP} works closely with this array form, except the user defines in its
 	third argument which column from which to return values. In \texttt{=VLOOKUP(3,
@@
 	three-argument vector form much more than the array form -- and then retrieve
-	examples of every configuration in the dataset. The same goes for the V/HLOOKUP
+	examples of every configuration in the dataset. The same goes for the \texttt{V/HLOOKUP}
 	functions, as shown partially in Figure~\ref{fig:vhlookups}.
@@
 	spreadsheets Enron and EUSES \cite{jansen2015enron}, different companies rely
-	on different functions. For other types of spreadsheet, such as Gnumeric\footnote{http://www.gnumeric.org/} or Google
-	Sheets\footnote{https://www.google.com/sheets/about/}, we have no
+	on different functions. For other types of spreadsheet, such as Gnumeric\footnote{\href{http://www.gnumeric.org/}{http://www.gnumeric.org/}} or Google
+	Sheets\footnote{\href{https://www.google.com/sheets/about/}{https://www.google.com/sheets/about/}}, we have no
 	guarantee that practices and functions will hold across these varied programs, even within
@@
 	author(s) and do not necessarily reflect the views of the LAS and/or any agency
-	or entity of the United States Government. I also thank the anonymous reviewers
-	who advised the direction of this paper.
+	or entity of the United States Government. We also thank the anonymous reviewers
+	who advised the direction of this paper, the study participants for their comments,
+	and Shivom Gargava for his help.
 

### 2016-08-13 doc/paper.tex
misc last minute updates

@@
 	industry and academia alike, supporting as much as 95\% of U.S. financial firms
-	use them daily~\cite{panko2008sarbanes} and empowering teachers to track
-	research and students' grades~\cite{ko2011state}. This flexibility boosts their
-	allure: while a novice can work with basic offerings, advanced users can choose
-	among the hundreds of specialized functions to fulfill a wide range of needs,
-	from complex statistics to text manipulation~\cite{nardi1990spreadsheet}. As
-	such, it should be no surprise that tens of millions of workers rely on these
+	daily~\cite{panko2008sarbanes} and empowering teachers to track research and
+	students' grades~\cite{ko2011state}, among many other tasks. This flexibility
+	grants them their allure: while a novice can work with basic offerings, advanced
+	users can choose among the hundreds of specialized functions to fulfill a wide
+	range of needs, from complex statistics to text
+	manipulation~\cite{nardi1990spreadsheet}. As such, it should be no surprise
+	that tens of millions of workers rely on these
 	programs daily~\cite{scaffidi2005estimating}.
 
-	However, this ubiquity is not without danger; as more people make larger and
+	However, this ubiquity is not without danger. As more people make larger and
 	more complex spreadsheets, the cost of failure grows too. The European
 	Spreadsheet Risks Interest Group (EuSpRIG) documents many horror stories of
-	spreadsheets gone wrong\footnote{http://www.eusprig.org/horror-stories.htm},
-	where consequences range from the profuse loss of money to the inaccurate
-	outcomes of elections to the creation of extensive political initiatives based
-	on flawed economics. Even if most spreadsheet errors are relatively benign,
-	poor spreadsheet practice can risk millions, if not billions, of
-	dollars~\cite{powell2009impact}.
+	spreadsheets gone
+	wrong\footnote{\href{http://www.eusprig.org/horror-stories.htm}{http://www.eusprig.org/horror-stories.htm}}, where consequences range from the profuse loss of money to the inaccurate outcomes of elections to the creation of extensive political initiatives based on flawed economics.
+Even if most spreadsheet errors are relatively benign, poor spreadsheet practice can risk millions, if not billions, of dollars~\cite{powell2009impact}.
 
@@
 	EUSES~\cite{fisher2005euses}, Fuse~\cite{barik2015fuse}, and the Enron
-	corpus~\cite{hermans2015enron} have already produced valueable research, such
+	corpus~\cite{hermans2015enron} have already produced valuable research, such
 	as the documentation of code smells in spreadsheet
-	environments~\cite{hermans2012detecting}~\cite{jansen2015code} or the creation
+	environments~\cite{hermans2012detecting}~\cite{jansen2015code} and the creation
 	of grammars to describe every possible spreadsheet program in
@@
 
-	The value of spreadsheets demands that we design tools to better understand
-	these datasets and simplify complexities we find in them. One such complexity
+	From this wealth of research and data, we must design tools to better understand
+	the datasets and simplify complexities we find in them. One such complexity
 	is formula construction; functions are an important part of using spreadsheets
@@
 	need for better exploration of spreadsheet corpora. Working with spreadsheets
-	in Excel, \toolname focuses primarily on the functions, like SUM and IF and
+	in Excel, \toolname focuses primarily on the functions, like \texttt{SUM} and \texttt{IF} and
 	hundreds more, which are the building blocks of formulae that determine values
@@
 	GyroSAT~\cite{hermans2011supporting} and Breviz~\cite{hermans2011breviz}.
-	\toolname is among this type, creating standalone visualizations about
+	\toolname is among this type of tool, creating standalone visualizations about
 	spreadsheets instead of drawing connections inside the spreadsheet itself. In
@@
 	\subsection{Design Goals} \label{goals} In visualizing the spreadsheet data, we
-	set out a few core goals for what the tool should accomplish. Furthermore, with
-	these goals, we also considered the likely challenges of achieving those goals
+	set out a few core goals for what the tool should accomplish. With
+	these goals, we also considered the likely challenges of achieving them
 	and particular outcomes which we considered beyond the scope of the research.
-	We present both sides of these goals below:
+	We present these goals below:
 

### 2016-08-13 doc/paper.tex
paper done?

@@
 		function nesting, but it must not overwhelm with numbers. Though everything
-		should be accessible in accordance with the first goal, we should reduce noise with our design.
+		should be accessible in accordance with the first goal, we should reduce noise
+		with our design.
 
@@
 	else)}"\footnote{\href{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}}.
-Furthermore, the third argument is optional; if left out, the function will return a default ``FALSE" value if necessary.
+Furthermore, the third argument is optional; if left out, the function will return a default \texttt{FALSE} value if necessary.
 Examples of this function in practice can be seen in Figure~\ref{fig:ifexample}.
@@
 	\begin{figure}[h] \centering \includegraphics[width=\columnwidth]{ifExample}
-		\caption{Configurations of the IF function} \label{fig:ifexample} \end{figure}
+		\caption{Configurations of the \texttt{IF} function} \label{fig:ifexample} \end{figure}
 
@@
 	\begin{figure}[h] \centering \includegraphics[width=.4\columnwidth]{start} \caption{How the
-			IF tree looks at the start} \label{fig:startpic} \end{figure}
+			\texttt{IF} tree looks at the start} \label{fig:startpic} \end{figure}
 
@@
 	Knowing that the first argument of \texttt{IF} contains the conditionals, we click on
-	the square labeled ``1" to explore. When the tool finds more than 10 unique
+	the square labeled \texttt{1} to explore. When the tool finds more than 10 unique
 	arguments in a position, it saves space by displaying only the first ten and
@@
 	such as = and $\le$, and boolean-returning functions, like \texttt{ISNA} and \texttt{AND}. Of these,
-	simple equality is the most common and ABS is the least. From here, we
+	simple equality is the most common and \texttt{ABS} is the least. From here, we
 	can further explore the common options among these functions. Clicking on the
-	``=" node will yield two arguments and expanding each of them will show
+	\texttt{=} node will yield two arguments and expanding each of them will show
 	the common values on either side of the equals sign, as in Figure~\ref{fig:fullpic}.
@@
 
-		\item \vspace{.25cm}\includegraphics{glossary-leaf} \textbf{Value nodes} are
+		\item \vspace{.15cm}\includegraphics{glossary-leaf} \textbf{Value nodes} are
 		white circles with a generic label. They represent elements of a formula that
-		accept no arguments, like references (A1), ranges (A1:A10), numbers, boolean
+		accept no arguments, like references (\texttt{A1}), ranges (\texttt{A1:A10}), numbers, boolean
 		values, strings, and errors. However, \toolname still treats functions with
@@
 
-		\item  \vspace{.25cm} \includegraphics{glossary-blue} \textbf{Argument nodes}
+		\item  \vspace{.15cm} \includegraphics{glossary-blue} \textbf{Argument nodes}
 		are dark blue squares labeled with a number. The number is the position of an
@@
 
-		\item  \vspace{.25cm} \includegraphics{glossary-solidline} \textbf{Solid
+		\item  \vspace{.15cm} \includegraphics{glossary-solidline} \textbf{Solid
 			lines} represent a function's list of parameters. As such, they connect the
@@
 
-		\item  \vspace{.25cm} \includegraphics{glossary-fadingline} \textbf{Fading
+		\item  \vspace{.15cm} \includegraphics{glossary-fadingline} \textbf{Fading
 			lines} represents how a formula author can choose from several possible
@@
 
-		\item  \vspace{.25cm} \includegraphics{glossary-arrow} \textbf{Expansion
-			arrows} appear within an argument node when there are over 10 possible
+		\item  \vspace{.15cm} \includegraphics{glossary-arrow} \textbf{Expansion
+			arrows} appear within an argument node when there are over 10 possibilities for
 		functions or values in an argument position. By default, only the first 10
@@
 
-		\item  \vspace{.25cm}
+		\item  \vspace{.15cm}
 		$\vcenter{\hbox{\includegraphics[scale=.75]{glossary-lightblue}}}$
@@
 		\end{subfigure} 
-		\includegraphics[]{comparison-ss} \caption{The
+		\includegraphics[]{comparison-ss} \caption{Sample
 			contents of the default tree (left) and the optional argument tree with 4 arguments (right)}
@@
 		the formula text into an ordered set of individual tokens, which the tool then
-		parses into the tree-like form. When all formulae have been analyzed like this,
+		parses into the hierarchical form. When all formulae have been analyzed like this,
 		it produces JSON files for each top-level function in the set.
@@
 	chose the tree form for its inherent ability to represent the parent-children
-	relationship of formulae as functions and their arguments, which could be yet
-	more functions. One option that we did not take was to represent the call trees
+	relationship of formulae as functions and their arguments. One option that we did not take was to represent the call trees
 	as simple text hierarchies. Though that might work well for a single,
@@
 		combat this, we converted formulae from their native A1 format to the relative
-		R1C1, in which copied formulae should be identical, and considered only each
+		R1C1\footnote{\href{https://support.office.com/en-us/article/Overview-of-formulas-7abfda78-eff3-4cc6-b4a7-6350d512d2dc}{https://support.office.com/en-us/article/Overview-of-formulas-7abfda78-eff3-4cc6-b4a7-6350d512d2dc}}, in which copied formulae should be identical, and considered only each
 		R1C1 formulae once per worksheet.
@@
 
-		\ \ For example, in the pictured \texttt{IF} function, we found that people often use
-		another IF statement as the second or third arguments of the top-level \texttt{IF}. If
-		we only consider functions exactly where they're found embedded in the
-		formula, then information about the same function -- \texttt{IF}, in this case -- will
-		be scattered across different trees with no way to aggregate them. If we
-		record every instance of a function by ignoring their context -- that is,
-		including an \texttt{IF} embedded within a \texttt{SUM} function in the same node as the
-		top-level \texttt{IF} -- then the tool will represent some functions in multiple nodes
-		to capture every possible level of nesting. For now, we only include the
-		first, with the latter to be added as an option in the future.
+		\ \ For example, in the pictured \texttt{IF} function, we found that people
+		often use another \texttt{IF} statement as the second or third arguments of
+		the top-level \texttt{IF}. If we only consider functions exactly where they're
+		found embedded in the formula, then information about the same function --
+		\texttt{IF}, in this case -- will be scattered across different trees with no
+		way to aggregate them and see, for example, how many times \texttt{IF} was
+		used overall. If we record every instance of a function by ignoring their
+		context -- that is, including an \texttt{IF} embedded within a \texttt{SUM}
+		function in the same node as the top-level \texttt{IF} -- then the tool will
+		represent some functions in multiple redundant nodes to capture every possible
+		level of nesting. For now, we only include the first, with the latter to be
+		added as an option in the future.
 
@@
 	What do the images tell us that the text could not? It is not enough to prove
-	that something can be visualized; we must also demonstrate what we can gain
+	that something can be visualized, but we must also demonstrate what we can gain
 	from any particular visualization. For this purpose, we outlined a few tasks in the
@@
 	designs that exist outside these readily visible categories. Consider the
-	second argument of the \texttt{``=''} operator, already shown expanded in
+	second argument of the \texttt{=} operator, already shown expanded in
 	Figure~\ref{fig:fullpic}: among the top five argument types for the position in
 	an \texttt{IF} function were boolean values. This corresponds to designs in which
-	conditions already in a boolean form were then checked against \texttt{``=TRUE"} or
-	\texttt{``=FALSE"}, such as in the formula \texttt{IF(Formulas!C77=TRUE, ``Yes")}, which
+	conditions already in a boolean form were then checked against \texttt{=TRUE} or
+	\texttt{=FALSE}, such as in the formula \texttt{IF(Formulas!C77=TRUE, ``Yes")}, which
 	appears in one of the sheets. Though this practice does not break anything in
 	itself, it nevertheless represents redundant operations in formula design and
-	indicates a possible misunderstanding of how the IF function works.
+	indicates a possible misunderstanding of how the \texttt{IF} function works.
 
@@
 	optional third argument's column; since the lookup values matches the value in
-	cell A4, it returns the value from cell B4. The array form of the LOOKUP works
+	cell A4, it returns the value from cell B4. The array form of the \texttt{LOOKUP} works
 	the same way, except that the second argument is a two-dimensional table where
@@
 	which is \textit{B2:B6} here. Furthermore, it also accepts a boolean value for
-	an optional argument: when set to FALSE, it returns only exact matches, and
-	when TRUE or left out, it approximates the match to the closest value beneath
+	an optional argument: when set to \texttt{FALSE}, it returns only exact matches, and
+	when \texttt{TRUE} or left out, it approximates the match to the closest value beneath
 	it. We demonstrate this in Figure~\ref{fig:lookupexample} in the bottom two
@@
 
-	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
-		\includegraphics[width=.5\textwidth]{lookup-3} \caption{LOOKUP with two and
-			three arguments}  \label{fig:lookups} \end{figure}
-
-	Furthermore, these examples are good as well for exploring how it might bridge
+	Furthermore, these examples are good for exploring how it might bridge
 	issues of bad design with education. In a recent study, Hermans and colleagues
-	probed the Enron dataset for uses of VLOOKUP and HLOOKUP
+	probed the Enron dataset for uses of \texttt{VLOOKUP} and \texttt{HLOOKUP}
 	specifically~\cite{hermans2015detecting}. The issue at hand was the optional
@@
 	this problem surfaces.
+
+	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
+		\includegraphics[width=.5\textwidth]{lookup-3} \caption{LOOKUP with two and
+			three arguments}  \label{fig:lookups} \end{figure}
 
@@
 	evaluating a company's spreadsheet practice. Through this framing, we intended
-	to open the floor for questions like on which functions employees most depended
+	to encourage questions like on which functions employees most depended
 	and which sheets contained the most dangerous formula practice. We clarified,
@@
 	underlying spreadsheets -- awkward formulae make awkward trees. Other than
-	these visual cues, value errors, prefixed with \#s, also appear in the tree,
-	which P4 said could be useful for tracking these problems if they're easy to find.
+	these visual cues, value errors, which were prefixed with \#s, also appear in the tree,
+	and P4 said these could be useful for tracking these problems if such error nodes are easy to find.
 
@@
 	configurations, this does not mean that they will learn exactly what it does.
-	P1, examining unfamiliar functions like\texttt{KURT} and \texttt{PV}, could describe precisely
+	P1, examining unfamiliar functions like \texttt{KURT} and \texttt{PV}, could describe precisely
 	what types of arguments it accepted and how many. But even after exploring the
@@
 
-	Throughout the study, we noticed that users misunderstood the design
+	Throughout the study, we noticed that some users misunderstood some design feature
 	and, as such, their early discoveries were inaccurate. For example, P1
-	thought that the numbers on argument nodes as the number of arguments instead
+	thought that the numbers on argument nodes were the number of arguments instead
 	of the index of that argument -- that is, clicking on the dark blue
@@
 	user study, we discussed \toolnameposs use in education and smell detection by bringing
-	up the issues surrounding the LOOKUP functions. This discussion, though,
+	up the issues surrounding the \texttt{LOOKUP} functions. This discussion, though,
 	assumes a distinguishing eye that knew which examples practiced good design
@@
 	example, \toolname does not current capture argument combination; in Figure
-	\ref{fig:index}, it is impossible to state how often the function MATCH
+	\ref{fig:index}, it is impossible to state how often the function \texttt{MATCH}
 	occurred in both the second and third arguments or whether they were more often
@@
 	is used inside of takes considerably more work -- we see again in Figure
-	\ref{fig:index} that MATCH is used inside INDEX, but we cannot know which
-	functions have INDEX inside them without searching every other tree. More
+	\ref{fig:index} that \texttt{MATCH} is used inside \texttt{INDEX}, but we cannot know which
+	functions have \texttt{INDEX} inside them without searching every other tree. More
 	distant concerns might be exploring which functions often occur in adjacent
-	cells in the sheet -- whenever INDEX occurs, which functions are seen most
+	cells in the sheet -- whenever \texttt{INDEX} occurs, which functions are seen most
 	often in the cells around it?

### 2016-08-13 doc/paper.tex
final, please be no typos please be no typos

@@
 \usepackage{url}
-\usepackage{hyperref}
+\usepackage[bookmarks=false]{hyperref}
 
@@
 	\author{ \IEEEauthorblockN{Justin Middleton and Emerson Murphy-Hill}
-		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ jamiddl2@ncsu.edu, emerson@csc.ncsu.edu }}
+		\IEEEauthorblockA{North Carolina State University\\Raleigh, North Carolina, USA\\ jamiddl2@ncsu.edu, emerson@csc.ncsu.edu }}
 
@@
 		design. Though users may certainly approach the tool with the intention of
-		exploring particular formulae, a formula visualization tool will not
+		exploring particular formulae, our formula visualization tool will not
 		prioritize any on metrics of good or bad practice.
@@
 	\begin{figure*}[t] \centering \includegraphics[width=0.8\textwidth]{IFargslabel}
-		\caption{A picture of \toolname displaying the common arguments to the \texttt{IF}
+		\caption{\toolname displaying the common arguments to the \texttt{IF}
 			function's first parameter} \centering \label{fig:fullpic} \end{figure*}
@@
 	In balancing this chosen form with the goals in Section~\ref{goals}, we faced a
-	number of decisions in how to visualize the data. Below, we've outlined those
+	number of decisions in how to visualize the data. Below, we have outlined those
 	that had the largest impact in the values that appear in the tree.
@@
 		often use another \texttt{IF} statement as the second or third arguments of
-		the top-level \texttt{IF}. If we only consider functions exactly where they're
+		the top-level \texttt{IF}. If we only consider functions exactly where they are
 		found embedded in the formula, then information about the same function --
@@
 	%Lookup example
-	For a deeper example, the LOOKUP functions are some of the most popular in
+	For a deeper example, the \texttt{LOOKUP} functions are some of the most popular in
 	Excel yet come with a number of important but silent requirements for proper
@@
 		\includegraphics[width=.5\textwidth]{lookupexample} \caption{Demonstrations of
-			LOOKUP and VLOOKUP} \label{fig:lookupexample} \end{figure}
+			\texttt{LOOKUP} and \texttt{VLOOKUP}} \label{fig:lookupexample} \end{figure}
 
@@
 	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
-		\includegraphics[width=.5\textwidth]{lookup-3} \caption{LOOKUP with two and
+		\includegraphics[width=.5\textwidth]{lookup-3} \caption{\texttt{LOOKUP} with two and
 			three arguments}  \label{fig:lookups} \end{figure}
@@
 	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
-		\includegraphics[width=.5\textwidth]{hlookup} \caption{VLOOKUP and HLOOKUP with
+		\includegraphics[width=.5\textwidth]{hlookup} \caption{\texttt{VLOOKUP} and \texttt{HLOOKUP} with
 			four arguments} \label{fig:vhlookups}\end{figure}
@@
 			\includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters
-				in SUM, which was a commonly noted smell in the user study} \label{fig:sum}
+				in \texttt{SUM}, which was a commonly noted smell in the user study} \label{fig:sum}
 		\end{wrapfigure}
@@
 
-	\subsection{Use in Education} Users found \toolname's inclusion of examples to
+	\subsection{Use in Education} Users found \toolname' inclusion of examples to
 	be especially useful since none of the them considered themselves to be experts
@@
 	\begin{figure} \centering \includegraphics[width=.4\textwidth]{index}
-		\caption{A difficult question: how often is MATCH used in both the second and
+		\caption{A difficult question: how often is \texttt{MATCH} used in both the second and
 			third arguments?} \label{fig:index} \end{figure}
